### 2022-11-10 R/model_fcs_target_markdown.Rmd
Update FCS model 2

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preparation

#### Packages

```{r message = FALSE, tidy = TRUE}
library(here)
library(tidyverse)
library(ggbeeswarm)
library(patchwork)
library(brms)
library(DHARMa)
library(bayesplot)
library(loo)
library(tidybayes)
library(emmeans)

```

```{r echo = FALSE}
rm(list = ls())
rm(list = setdiff(ls(), c(
  "m_simple", "m_full", "m1", "m3", "m3_flat", "m_simple_flat", "m3_iter"
  )))
```

#### Load data

```{r}
sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
                  col_names = TRUE, na = c("na", "NA", ""), col_types =
                    cols(
                      .default = "?",
                      plot = "f",
                      site = "f",
                      sand_ratio = "f",
                      substrate_depth = "f",
                      target_type = col_factor(levels = c(
                        "dry_grassland", "hay_meadow"
                        )),
                      seed_density = "f",
                      exposition = col_factor(levels = c(
                        "north", "south"
                      )),
                      survey_year = "d"
                    )) %>%
  ### Exclude data of seed mixtures
  filter(survey_year != "seeded") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    botanist_year = str_c(survey_year, botanist, sep = " "),
    botanist_year = factor(botanist_year),
    n = fcs_target,
    id = factor(id)
    ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, botanist_year, n
    )
```

# Statistics

## Data exploration

### Graphs of raw data

```{r echo = FALSE}
plot1 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = sand_ratio)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Sand ratio [vol%] (Data of 2021)")
plot2 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = substrate_depth)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Substrate depth [cm] (Data of 2021)")
plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = target_type)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Target type (Data of 2021)")
plot4 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = seed_density)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Seed density [g/m²] (Data of 2021)")
(plot1 + plot2) / (plot3 + plot4)
plot1 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = exposition)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Exposition (Data of 2021)")
plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Survey year")
plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = site)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Blocks (Data of 2021)")
plot4 <- ggplot(sites, aes(y = n, x = botanist_year)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Botanists and survey year") +
  theme(axis.text.x = element_text(angle = 90))
(plot1 + plot2) / (plot3 + plot4)
ggplot(data = sites,
       aes(x = sand_ratio, y = n, color = target_type)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Target type vs. sand ratio [vol%]")
ggplot(data = sites,
       aes(x = sand_ratio, y = n, color = substrate_depth)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Substrate depth [cm] vs. sand ratio [vol%]")
ggplot(data = sites,
       aes(x = seed_density, y = n, color = target_type)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Target type vs. Seed density [g/m²]")
```

### Outliers, zero-inflation, transformations?

```{r}
dotchart((sites$n), groups = factor(sites$exposition),
         main = "Cleveland dotplot")
sites %>% group_by(exposition) %>% count(site)
boxplot(sites$n)
plot(table((sites$n)), type = "h",
     xlab = "Observed values", ylab = "Frequency")
ggplot(sites, aes(x = n)) + geom_density()
ggplot(sites, aes(sqrt(n))) + geom_density()
```

### 2022-11-10 R/model__fcs_target.R

@@ -15,6 +15,7 @@
 library(here)
 library(tidyverse)
 library(ggbeeswarm)
+library(patchwork)
 library(brms)
 library(DHARMa)
 library(bayesplot)
@@ -30,25 +31,30 @@ rm(list = setdiff(ls(), c(
   )))
 
 ### Load data ###
-sites <- read_csv("data_processed_sites.csv",
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
                   col_names = TRUE, na = c("na", "NA", ""), col_types =
                     cols(
                       .default = "?",
                       plot = "f",
                       site = "f",
-                      survey_year = "d",
-                      exposition = "f",
                       sand_ratio = "f",
                       substrate_depth = "f",
+                      target_type = col_factor(levels = c(
+                        "dry_grassland", "hay_meadow"
+                      )),
                       seed_density = "f",
-                      target_type = "f"
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "d"
                     )) %>%
+  ### Exclude data of seed mixtures
   filter(survey_year != "seeded") %>%
   mutate(
-    n = fcs_target,
     survey_year_fct = factor(survey_year),
-    botanist_year = str_c(botanist, survey_year, sep = " "),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
     botanist_year = factor(botanist_year),
+    n = fcs_target,
     id = factor(id)
   ) %>%
   select(
@@ -58,92 +64,67 @@ sites <- read_csv("data_processed_sites.csv",
 
 
 
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# B Statistics ################################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# B Statistics #################################################################
[…]

### 2022-11-10 R/model_fcs_target_markdown.Rmd
Separate model building and model check of FCS

@@
 ```
+
+## Model building
+
+### Models
+
+#### Preparation
+
+```{r}
+### Posssible priors ###
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot) + (1 | botanist_year),
+          data = sites)
+### Example of normal distribution
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1))
+### Example of cauchy distribution
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1))
+### Example of a student t distribution
+ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5))
+```
+
+#### Calculation
+
+Specifications for the models
+
+```{r}
+iter = 10000
+chains = 4
+thin = 2
+priors <- c(
+  set_prior("normal(0, 1)", class = "b"),
+  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
+  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
+  set_prior("normal(0.1, 1)", class = "b", coef = "expositionsouth"),
+  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
+  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
+  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
+  set_prior("cauchy(0, 1)", class = "sigma")
+)
+```
+
+Model caluclations
+
+```{r}
+m1 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
+             substrate_depth + seed_density +
+             (1 | site/plot) + (1 | botanist_year),
+           data = sites, 
+           family = gaussian("identity"),
+           prior = priors,
+           chains = chains,
+           iter = iter,
+           thin = thin,
+           warmup = floor(iter / 2),
+           save_pars = save_pars(all = TRUE),
+           cores = parallel::detectCores(),
+           seed = 123)
+
+m2 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
+            substrate_depth + seed_density +
+            sand_ratio:substrate_depth +
+            (1 | site/plot) + (1 | botanist_year),
+          data = sites, 
+          family = gaussian("identity"),
+          prior = priors,
+          chains = chains,
+          iter = iter,
+          thin = thin,
+          warmup = floor(iter / 2),
+          save_pars = save_pars(all = TRUE),
+          cores = parallel::detectCores(),
+          seed = 123)
+
+m3 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^2 +
+                 substrate_depth + seed_density +
+                 substrate_depth:sand_ratio +
+                 seed_density:exposition +
+                 target_type:exposition:survey_year_fct +
+                 sand_ratio:exposition:survey_year_fct +
+                 seed_density:exposition:survey_year_fct +
+                 (1 | site/plot) + (1 | botanist_year),
+               data = sites, 
+               family = gaussian("identity"),
+               prior = priors,
+               chains = chains,
+               iter = iter,
+               thin = thin,
+               warmup = floor(iter / 2),
+               save_pars = save_pars(all = TRUE),
+               cores = parallel::detectCores(),
+               seed = 123)
+```
+
+### Model comparison
+
+```{r}
+m_1 <- m1
+m_2 <- m3
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+```
+
+### Model check
+
+#### DHARMa
+
+```{r}
+createDHARMa(
+  simulatedResponse = t(posterior_predict(m_1)),
+  observedResponse = sites$n,
+  fittedPredictedResponse = apply(t(posterior_epred(m_1)), 1, mean),
+  integerResponse = TRUE
+  ) %>%
+  plot()
+createDHARMa(
+  simulatedResponse = t(posterior_predict(m_2)),
+  observedResponse = sites$n,
+  fittedPredictedResponse = apply(t(posterior_epred(m_2)), 1, mean),
+  integerResponse = TRUE
+  ) %>%
+  plot()
+```
+
+#### Preparation
+
+```{r}
+posterior1 <- m_1 %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(
+    variable = c(
+      "b_sand_ratio25",
+      "b_sand_ratio50",
+      "b_substrate_depth30",
+      "b_target_typehay_meadow",
+      "b_seed_density8",
+      "b_expositionsouth",
+      "b_survey_year_fct2019",
+      "b_survey_year_fct2020",
+      "b_survey_year_fct2021",
+      "sd_site__Intercept",
+      "sd_site:plot__Intercept",
+      "sd_botanist_year__Intercept",
+      "sigma"
+    )
+  )
+posterior2 <- m_2 %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(
+    variable = c(
+      "b_sand_ratio25",
+      "b_sand_ratio50",
+      "b_substrate_depth30",
+      "b_target_typehay_meadow",
+      "b_seed_density8",
+      "b_expositionsouth",
+      "b_survey_year_fct2019",
+      "b_survey_year_fct2020",
+      "b_survey_year_fct2021",
+      "sd_site__Intercept",
+      "sd_site:plot__Intercept",
+      "sd_botanist_year__Intercept",
+      "sigma"
+    )
+  )
+hmc_diagnostics1 <- nuts_params(m_1)
+hmc_diagnostics2 <- nuts_params(m_2)
+y <- sites$n
+yrep1 <- posterior_predict(m_1, draws = 500)
+yrep2 <- posterior_predict(m_2, draws = 500)
+loo1 <- loo(m_1, save_psis = TRUE, moment_match = FALSE)
+loo2 <- loo(m_2, save_psis = TRUE, moment_match = FALSE)
+draws1 <- m_1 %>%
+  posterior::as_draws() %>%
+  posterior::summarize_draws() %>%
+  filter(str_starts(variable, "b_"))
+draws2 <- m_2 %>%
+  posterior::as_draws() %>%
+  posterior::summarize_draws() %>%
+  filter(str_starts(variable, "b_"))
+```
+
+#### Samling efficency/effectiveness (Rhat and EFF)
+
+```{r}
+range(draws1$rhat)
+range(draws2$rhat)
+range(draws1$ess_bulk)
+range(draws2$ess_bulk)
+range(draws1$ess_tail)
+range(draws2$ess_tail)
+```
+
+#### MCMC diagnostics
+
+```{r}
+mcmc_trace(posterior1, np = hmc_diagnostics1)
+mcmc_trace(posterior2, np = hmc_diagnostics2)
+```
+
+#### Posterior predictive check
+
+##### Kernel density
+
+```{r}
+ppc_dens_overlay(y, yrep1[1:50, ])
+ppc_dens_overlay(y, yrep2[1:50, ])
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
+ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
+ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
+```
+
+##### Histograms of statistics skew
+
+```{r}
+ppc_stat(y, yrep1, binwidth = 0.001)
+ppc_stat(y, yrep2, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+```
+
+##### LOO-PIT plots
+
+```{r}
+ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+plot(loo1)
+plot(loo2)
+```
+
+#### Autocorrelation check
+
+```{r}
+mcmc_acf(posterior1, lags = 10)
+mcmc_acf(posterior2, lags = 10)
+```
+
+## Output of choosen model
+
+### Model output
+
+```{r}
+prior_summary(m_1)
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+draws1
+mcmc_intervals(
+  posterior1,
+  prob = 0.5,
+  prob_outer = 0.95,
+  point_est = "mean"
+)
+sjPlot::plot_model(m_1, m_2, type = "est")
+sjPlot::plot_model(m_2, type = "est")
+sjPlot::plot_model(
+  m_1, m_2, type = "est", ppd = TRUE,
+  terms = c(
+    "sand_ratio", "substrate_depth", "target_type",
+    "seed_density",  "exposition", "survey_year_fct"
+    )
+  )
+```
+
+### Effect sizes
+
+```{r}
+(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
+                  exposition | survey_year_fct, type = "response"))
+(emm <- emmeans(m_1, revpairwise ~ substrate_depth + sand_ratio |
+                  exposition | survey_year_fct, type = "response"))
+(emm <- emmeans(m_1, revpairwise ~ seed_density |
+                  exposition | survey_year_fct, type = "response"))
+```

### 2022-11-10 R/model__fcs_target.R

@@ -1,7 +1,9 @@
 # Dike grassland field experiment
 # Favourable conservation status ####
+# Model building
+
 # Markus Bauer
-# 2022-10-18
+# 2022-11-10
 
 
 
@@ -17,18 +19,9 @@ library(tidyverse)
 library(ggbeeswarm)
 library(patchwork)
 library(brms)
-library(DHARMa)
-library(bayesplot)
-library(loo)
-library(tidybayes)
-library(emmeans)
 
 ### Start ###
 rm(list = ls())
-setwd(here("data", "processed"))
-rm(list = setdiff(ls(), c(
-  "m_simple", "m_full", "m3", "m3_flat", "m_simple_flat", "m3_iter"
-  )))
 
 ### Load data ###
 sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
@@ -127,7 +120,7 @@ ggplot(data = sites,
   labs(title = "Target type vs. Seed density [g/m²]")
 
 
-#### b Outliers, zero-inflation, transformations? ----------------------------
+### b Outliers, zero-inflation, transformations? ----------------------------
 
 dotchart((sites$n), groups = factor(sites$exposition),
          main = "Cleveland dotplot")
@@ -143,9 +136,7 @@ ggplot(sites, aes(sqrt(n))) + geom_density()
 ## 2 Model building ###########################################################
 
 
-### a Models -----------------------------------------------------------------
-
-### * Preparation ####
+### a Preparation -------------------------------------------------------------
 
 ### Posssible priors ###
 get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
@@ -162,7 +153,7 @@ ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
 ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5))
 
-### * Calculation ####
+### a Models ------------------------------------------------------------------
 
 ### Specifications ###
 iter = 10000
@@ -226,6 +217,8 @@ m1 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
 m2 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
[…]

### 2022-11-10 R/model_fcs_target_check.R

@@ -1,0 +1,242 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Model check
+
+# Markus Bauer
+# 2022-11-10
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(brms)
+library(DHARMa)
+library(bayesplot)
+library(loo)
+library(tidybayes)
+library(emmeans)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+load(file = here("data", "processed", "model_fcs_1.Rdata"))
+load(file = here("data", "processed", "model_fcs_2.Rdata"))
+load(file = here("data", "processed", "model_fcs_3.Rdata"))
+load(file = here("data", "processed", "model_fcs_1_flat.Rdata"))
+
+
+
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# B Statistics #################################################################
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+## 1 Model check ###############################################################
+
+### a Model comparison ---------------------------------------------------------
+
+m_1 <- m1
+m_2 <- m3
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+
+
+### b Model check -----------------------------------------------------------
+
+#### * DHARMa ####
+createDHARMa(
+  simulatedResponse = t(posterior_predict(m_1)),
[…]

### 2022-11-10 R/show_figure_2_fcs_target.R

@@ -21,26 +21,6 @@ rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
 setwd(here("data", "processed"))
 
 ### Load data ###
-France <- read_csv("red_knot.csv")
-france3_mbrms <- brms::brm(pop ~ I(year - 1976) + Location.of.population,
-                           data = France, family = poisson(), chains = 3,
-                           iter = 3000, warmup = 1000)
-France_plot <- France %>%
-  add_predicted_draws(france3_mbrms)
-library(tidybayes)
-
-(model_fit <- France %>%
-    add_predicted_draws(france3_mbrms) %>%  # adding the posterior distribution
-    ggplot(aes(x = year, y = pop)) +  
-    stat_lineribbon(aes(y = .prediction), .width = c(.95, .80, .50),  # regression line and CI
-                    alpha = 0.5, colour = "black") +
-    geom_point(data = France, colour = "darkseagreen4", size = 3) +   # raw data
-    scale_fill_brewer(palette = "Greys") +
-    ylab("Calidris canutus abundance\n") +  # latin name for red knot
-    xlab("\nYear") +
-    theme_bw() +
-    theme(legend.title = element_blank(),
-          legend.position = c(0.15, 0.85)))
 sites <- read_csv("data_processed_sites.csv",
                   col_names = TRUE,
                   na = c("na", "NA", ""), col_types =

### 2022-11-10 R/model_fcs_target_markdown.Rmd
Update

@@
 ```{r}
-m1 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
-             substrate_depth + seed_density +
-             (1 | site/plot) + (1 | botanist_year),
-           data = sites, 
-           family = gaussian("identity"),
-           prior = priors,
-           chains = chains,
-           iter = iter,
-           thin = thin,
-           warmup = floor(iter / 2),
-           save_pars = save_pars(all = TRUE),
-           cores = parallel::detectCores(),
-           seed = 123)
-
-m2 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
-            substrate_depth + seed_density +
-            sand_ratio:substrate_depth +
-            (1 | site/plot) + (1 | botanist_year),
-          data = sites, 
-          family = gaussian("identity"),
-          prior = priors,
-          chains = chains,
-          iter = iter,
-          thin = thin,
-          warmup = floor(iter / 2),
-          save_pars = save_pars(all = TRUE),
-          cores = parallel::detectCores(),
-          seed = 123)
-
-m3 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^2 +
-                 substrate_depth + seed_density +
-                 substrate_depth:sand_ratio +
-                 seed_density:exposition +
-                 target_type:exposition:survey_year_fct +
-                 sand_ratio:exposition:survey_year_fct +
-                 seed_density:exposition:survey_year_fct +
-                 (1 | site/plot) + (1 | botanist_year),
-               data = sites, 
-               family = gaussian("identity"),
-               prior = priors,
-               chains = chains,
-               iter = iter,
-               thin = thin,
-               warmup = floor(iter / 2),
-               save_pars = save_pars(all = TRUE),
-               cores = parallel::detectCores(),
-               seed = 123)
+load(file = here("data", "processed", "model_fcs_1.Rdata"))
+m1
+load(file = here("data", "processed", "model_fcs_2.Rdata"))
+m2
 ```

### 2022-11-10 R/model_fcs_target.R

@@ -1,0 +1,276 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Model building
+
+# Markus Bauer
+# 2022-11-10
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(ggbeeswarm)
+library(patchwork)
+library(brms)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+                  col_names = TRUE, na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      plot = "f",
+                      site = "f",
+                      sand_ratio = "f",
+                      substrate_depth = "f",
+                      target_type = col_factor(levels = c(
+                        "dry_grassland", "hay_meadow"
+                      )),
+                      seed_density = "f",
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "d"
+                    )) %>%
+  ### Exclude data of seed mixtures
+  filter(survey_year != "seeded") %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = factor(botanist_year),
+    n = fcs_target,
+    id = factor(id)
+  ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, survey_year, botanist_year, n
+  )
+
+
+
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# B Statistics #################################################################
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+## 1 Data exploration ##########################################################
+
+
+### a Graphs of raw data -------------------------------------------------------
+
+plot1 <- ggplot(sites %>% filter(survey_year == 2021),
[…]

### 2022-11-11 R/model_fcs_calculation.R
Revert "Figure FCS coef ready for m3"
This reverts commit dc36b39e51e7e5d73bf00a737d8574022277f857.

@@ -1,0 +1,274 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Model building
+
+# Markus Bauer
+# 2022-11-10
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(ggbeeswarm)
+library(patchwork)
+library(brms)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+                  col_names = TRUE, na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      plot = "f",
+                      site = "f",
+                      sand_ratio = "f",
+                      substrate_depth = "f",
+                      target_type = col_factor(levels = c(
+                        "dry_grassland", "hay_meadow"
+                      )),
+                      seed_density = "f",
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "d"
+                    )) %>%
+  ### Exclude data of seed mixtures
+  filter(survey_year != "seeded") %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = factor(botanist_year),
+    n = fcs_target,
+    id = factor(id)
+  ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, survey_year, botanist_year, n
+  )
+
+
+
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# B Statistics #################################################################
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+## 1 Data exploration ##########################################################
+
+
+### a Graphs of raw data -------------------------------------------------------
+
+plot1 <- ggplot(sites %>% filter(survey_year == 2021),
[…]

### 2022-11-11 R/model_fcs_check.R

@@ -1,0 +1,334 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Model check
+
+# Markus Bauer
+# 2022-11-10
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(brms)
+library(DHARMa)
+library(bayesplot)
+library(loo)
+library(tidybayes)
+library(emmeans)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+                  col_names = TRUE, na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      plot = "f",
+                      site = "f",
+                      sand_ratio = "f",
+                      substrate_depth = "f",
+                      target_type = col_factor(levels = c(
+                        "dry_grassland", "hay_meadow"
+                      )),
+                      seed_density = "f",
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "d"
+                    )) %>%
+  ### Exclude data of seed mixtures
+  filter(survey_year != "seeded") %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = factor(botanist_year),
+    n = fcs_target,
+    id = factor(id)
+    ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, survey_year, botanist_year, n
+    )
[…]

### 2022-11-11 R/model_fcs_target.R

@@ -268,8 +268,8 @@ m1_flat <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
                seed = 123)
 
 ### Save ###
-save(m_simple, file = here("data", "processed", "model_fcs_simmple.Rdata"))
-save(m_full, file = here("data", "processed", "model_fcs_full_.Rdata"))
+save(m_simple, file = here("data", "processed", "model_fcs_simple.Rdata"))
+save(m_full, file = here("data", "processed", "model_fcs_full.Rdata"))
 save(m1, file = here("data", "processed", "model_fcs_1.Rdata"))
 save(m2, file = here("data", "processed", "model_fcs_2.Rdata"))
 save(m3, file = here("data", "processed", "model_fcs_3.Rdata"))

### 2022-11-11 R/model_fcs_target_check.R

@@ -1,242 +1,0 @@
-# Dike grassland field experiment
-# Favourable conservation status ####
-# Model check
-
-# Markus Bauer
-# 2022-11-10
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(brms)
-library(DHARMa)
-library(bayesplot)
-library(loo)
-library(tidybayes)
-library(emmeans)
-
-### Start ###
-rm(list = ls())
-
-### Load data ###
-load(file = here("data", "processed", "model_fcs_1.Rdata"))
-load(file = here("data", "processed", "model_fcs_2.Rdata"))
-load(file = here("data", "processed", "model_fcs_3.Rdata"))
-load(file = here("data", "processed", "model_fcs_1_flat.Rdata"))
-
-
-
-#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# B Statistics #################################################################
-#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-## 1 Model check ###############################################################
-
-### a Model comparison ---------------------------------------------------------
-
-m_1 <- m1
-m_2 <- m3
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-
-
-### b Model check -----------------------------------------------------------
-
-#### * DHARMa ####
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_1)),
[…]

### 2022-11-11 R/show_figure_2_fcs.R

@@ -1,0 +1,199 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Show figure 2
+
+# Markus Bauer
+# 2022-11-10
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+suppressPackageStartupMessages(library(brms))
+suppressPackageStartupMessages(library(tidybayes))
+library(ggbeeswarm)
+
+### Start ###
+rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
+setwd(here("data", "processed"))
+
+### Load data ###
+sites <- read_csv("data_processed_sites.csv",
+                  col_names = TRUE,
+                  na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      id = "f",
+                      plot = "f",
+                      site = "f",
+                      exposition = col_factor(levels = c("north", "south")),
+                      sand_ratio = "f",
+                      substrate_depth = col_factor(levels = c("30", "15")),
+                      target_type = "f",
+                      seed_density = "f"
+                    )) %>%
+  filter(survey_year != "seeded") %>%
+  mutate(
+    n = fcs_target,
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year_fct, botanist, sep = "_"),
+    botanist_year = str_replace_all(botanist_year, " ", "_")
+  ) %>%
+  select(
+    id, plot, site, botanist_year, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, n
+  )
+
+### * Model ####
+load(file = "model_fcs_3.Rdata")
+
+model <- sites %>%
+  add_predicted_draws(m3, allow_new_levels = TRUE)
+
+### * Functions ####
+theme_mb <- function() {
+  theme(
+    panel.background = element_rect(fill = "white"),
+    text = element_text(size = 9, color = "black"),
+    strip.text = element_text(size = 10),
[…]

### 2022-11-11 R/show_figure_2_fcs_target.R

@@ -1,239 +1,0 @@
-# Dike grassland experiment
-# Show_figure species composition ####
-# Markus Bauer
-# 2022-11-09
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-suppressPackageStartupMessages(library(brms))
-suppressPackageStartupMessages(library(tidybayes))
-library(ggbeeswarm)
-
-### Start ###
-rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
-setwd(here("data", "processed"))
-
-### Load data ###
-sites <- read_csv("data_processed_sites.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      id = "f",
-                      plot = "f",
-                      site = "f",
-                      exposition = col_factor(levels = c("north", "south")),
-                      sand_ratio = "f",
-                      substrate_depth = col_factor(levels = c("30", "15")),
-                      target_type = "f",
-                      seed_density = "f"
-                    )) %>%
-  filter(survey_year != "seeded") %>%
-  mutate(
-    n = fcs_target,
-    survey_year_fct = factor(survey_year),
-    botanist_year = str_c(botanist, survey_year_fct, sep = "_"),
-    botanist_year = str_replace_all(botanist_year, " ", "_")
-  ) %>%
-  select(
-    id, plot, site, botanist_year, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, n
-  )
-
-### * Model ####
-load(file = "model_fcs_3.Rdata")
-
-### * Functions ####
-theme_mb <- function() {
-  theme(
-    panel.background = element_rect(fill = "white"),
-    text = element_text(size = 9, color = "black"),
-    strip.text = element_text(size = 10),
-    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
[…]

### 2022-11-11 R/model_fcs_markdown.Rmd
Update model_fcs_markdown.Rmd

--- 2022-11-10 R/model_fcs_target_markdown.Rmd
@@
 ```{r}
-dotchart((sites$n), groups = factor(sites$exposition),
-         main = "Cleveland dotplot")
 sites %>% group_by(exposition) %>% count(site)
 boxplot(sites$n)
-plot(table((sites$n)), type = "h",
-     xlab = "Observed values", ylab = "Frequency")
+ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
+ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
 ggplot(sites, aes(x = n)) + geom_density()
-ggplot(sites, aes(sqrt(n))) + geom_density()
 ```
@@
 ### Models
-
-#### Preparation
-
-```{r}
-### Posssible priors ###
-get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site/plot) + (1 | botanist_year),
-          data = sites)
-### Example of normal distribution
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1))
-### Example of cauchy distribution
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1))
-### Example of a student t distribution
-ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5))
-```
-
-#### Calculation
 
@@
 load(file = here("data", "processed", "model_fcs_1.Rdata"))
-m1
 load(file = here("data", "processed", "model_fcs_2.Rdata"))
-m2
+load(file = here("data", "processed", "model_fcs_3.Rdata"))
 ```
@@
 m_2 <- m3
+m_1$formula
+m_2$formula
+```
+
+Conditional and marginal R² values
+
+```{r}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 ```{r}
-ppc_dens_overlay(y, yrep1[1:50, ])
-ppc_dens_overlay(y, yrep2[1:50, ])
+p1 <- ppc_dens_overlay(y, yrep1[1:50, ])
+p2 <- ppc_dens_overlay(y, yrep2[1:50, ])
+p1 / p2
 ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
 ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
+p1 / p2
 ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
 ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
+p1 / p2
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
+p1 / p2
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
+p1 / p2
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
+p1 / p2
 ```
@@
 ```{r}
-ppc_stat(y, yrep1, binwidth = 0.001)
-ppc_stat(y, yrep2, binwidth = 0.001)
+p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
+p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+p1 / p2
 ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
 ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
-ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+p1 / p2
 ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
 ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
-ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
-ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
-ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
-ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 / p2
 ```
@@
 ```{r}
-ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 / p2
 plot(loo1)

### 2022-11-11 R/model_fcs_markdown.Rmd
Update Markdown

@@
 rm(list = ls())
-rm(list = setdiff(ls(), c(
-  "m_simple", "m_full", "m1", "m3", "m3_flat", "m_simple_flat", "m3_iter"
-  )))
 ```
@@
 ```{r}
-prior_summary(m_1)
+prior_summary(m_2, all = FALSE)
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
          re_formula = 1 ~ 1)
-draws1
+draws2
 mcmc_intervals(
   posterior1,
+  prob = 0.66,
+  prob_outer = 0.95,
+  point_est = "mean"
+)
+mcmc_intervals(
+  posterior2,
   prob = 0.5,
@@
   point_est = "mean"
-)
-sjPlot::plot_model(m_1, m_2, type = "est")
-sjPlot::plot_model(m_2, type = "est")
-sjPlot::plot_model(
-  m_1, m_2, type = "est", ppd = TRUE,
-  terms = c(
-    "sand_ratio", "substrate_depth", "target_type",
-    "seed_density",  "exposition", "survey_year_fct"
-    )
 )
@@
                   exposition | survey_year_fct, type = "response"))
-(emm <- emmeans(m_1, revpairwise ~ substrate_depth + sand_ratio |
-                  exposition | survey_year_fct, type = "response"))
-(emm <- emmeans(m_1, revpairwise ~ seed_density |
-                  exposition | survey_year_fct, type = "response"))
 ```

### 2022-11-11 R/model_fcs_markdown.Rmd
Update model_fcs_markdown.Rmd

@@
 
-Conditional and marginal R² values
+Conditional R² values
 
@@
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
+```
+
+Marginal R² values
+
+```{r}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),

### 2022-11-11 R/model_fcs_markdown.Rmd
Update

@@
 
+Priors and conditional and marignal R²
+
 ```{r}
 prior_summary(m_2, all = FALSE)
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
+```
+
+Posteriors
+
+```{r}
 draws2
@@
   posterior2,
-  prob = 0.5,
+  prob = 0.66,
   prob_outer = 0.95,

### 2022-11-11 R/model__persistence.R

@@ -1,445 +1,0 @@
-# Dike grassland field experiment
-# Persistence (Presence-absence data) ####
-# Markus Bauer
-# 2022-10-18
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tibble)
-library(tidyr)
-library(dplyr)
-library(readr)
-library(stringr)
-library(ggbeeswarm)
-library(brms)
-library(DHARMa)
-library(bayesplot)
-library(tidybayes)
-library(emmeans)
-
-### Start ###
-#rm(list = ls())
-setwd(here("data", "processed"))
-
-### Load data ###
-sites <- read_csv("data_processed_sites.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      id = "f",
-                      plot = "f",
-                      block = "f",
-                      exposition = col_factor(levels = c("north", "south")),
-                      sandRatio = "f",
-                      substrateDepth = "f",
-                      targetType = "f",
-                      seedDensity = "f"
-                    )) %>%
-  filter(
-    !str_detect(id, "C") &
-      presabu == "presence" &
-      surveyYear != "seeded"
-  ) %>%
-  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
-               names_transform = as.factor) %>%
-  mutate(
-    index = fct_rev(index),
-    botanist_year = str_c(botanist, surveyYear),
-    surveyYear = as.double(surveyYear),
-    surveyYear_fac = as.factor(surveyYear)
-  ) %>%
-  select(
-    id, plot, site, block, exposition,
-    sandRatio, substrateDepth, targetType, seedDensity,
-    surveyYear, age, botanist_year, surveyYear_fac,
-    index, n
-  )
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# B Statistics ################################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
[…]

### 2022-11-11 R/model_persistence.R

@@ -1,0 +1,276 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Model building
+
+# Markus Bauer
+# 2022-11-10
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(ggbeeswarm)
+library(patchwork)
+library(brms)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+                  col_names = TRUE, na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      plot = "f",
+                      site = "f",
+                      sand_ratio = "f",
+                      substrate_depth = "f",
+                      target_type = col_factor(levels = c(
+                        "dry_grassland", "hay_meadow"
+                      )),
+                      seed_density = "f",
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "d"
+                    )) %>%
+  ### Exclude data of seed mixtures
+  filter(survey_year != "seeded") %>%
+  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
+               names_transform = as.factor) %>%
+  filter(index = C) %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = factor(botanist_year),
+    id = factor(id)
+  ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, survey_year, botanist_year, n
+  )
+
+
+
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# B Statistics #################################################################
+#+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+## 1 Data exploration ##########################################################
+
+
[…]

### 2022-11-11 R/model_persistence_markdown.Rmd
Update persistence

--- 2022-11-11 R/model_fcs_markdown.Rmd
@@
 ---
-title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
+title: "Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment"
 author: "Markus Bauer <br>"
@@
   filter(survey_year != "seeded") %>%
+  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
+               names_transform = as.factor) %>%
+  filter(index = C) %>%
   mutate(
@@
     botanist_year = factor(botanist_year),
-    n = fcs_target,
     id = factor(id)

### 2022-11-11 R/model_persistence_check.R

@@ -1,0 +1,278 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Model check
+
+# Markus Bauer
+# 2022-11-11
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(brms)
+library(DHARMa)
+library(bayesplot)
+library(loo)
+library(tidybayes)
+library(emmeans)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+                  col_names = TRUE, na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      plot = "f",
+                      site = "f",
+                      sand_ratio = "f",
+                      substrate_depth = "f",
+                      target_type = col_factor(levels = c(
+                        "dry_grassland", "hay_meadow"
+                      )),
+                      seed_density = "f",
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "d"
+                    )) %>%
+  ### Exclude data of seed mixtures
+  filter(survey_year != "seeded") %>%
+  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
+               names_transform = as.factor) %>%
+  filter(index = C) %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = factor(botanist_year),
+    id = factor(id)
+  ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
[…]

### 2022-11-14 R/model_persistence_markdown.Rmd
Update model_persistence_markdown.Rmd

@@
 ```{r}
-sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites_temporal.csv"),
   col_names = TRUE, na = c("na", "NA", ""), col_types =
@@
       )),
-                      survey_year = "d"
-                    )) %>%
+      survey_year = "c"
+    )
+  ) %>%
   ### Exclude data of seed mixtures
@@
                names_transform = as.factor) %>%
-  filter(index = C) %>%
+  filter(index == "B" & presabu == "presence") %>%
   mutate(
     survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
-    botanist_year = factor(botanist_year),
     id = factor(id)
@@
     id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, survey_year, botanist_year, n
+    seed_density, survey_year_fct, survey_year, n
   )
@@
 ```{r echo = FALSE}
-plot1 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = sand_ratio)) +
+plot1 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = sand_ratio)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
   labs(title = "Sand ratio [vol%] (Data of 2021)")
-plot2 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = substrate_depth)) +
+plot2 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = substrate_depth)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
   labs(title = "Substrate depth [cm] (Data of 2021)")
-plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = target_type)) +
+plot3 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = target_type)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
   labs(title = "Target type (Data of 2021)")
-plot4 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = seed_density)) +
+plot4 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = seed_density)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
@@
 (plot1 + plot2) / (plot3 + plot4)
-plot1 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = exposition)) +
+plot1 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = exposition)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
@@
   labs(title = "Blocks (Data of 2021)")
-plot4 <- ggplot(sites, aes(y = n, x = botanist_year)) +
-  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Botanists and survey year") +
-  theme(axis.text.x = element_text(angle = 90))
-(plot1 + plot2) / (plot3 + plot4)
+(plot1 + plot2) / (plot3)
 ggplot(data = sites,
@@
   set_prior("normal(0, 1)", class = "b"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "expositionsouth"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
-  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
-  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
+  set_prior("normal(-0.025, 1)", class = "b", coef = "sand_ratio25"),
+  set_prior("normal(-0.050, 1)", class = "b", coef = "sand_ratio50"),
+  set_prior("normal(0.050, 1)", class = "b", coef = "expositionsouth"),
+  set_prior("normal(-0.025, 1)", class = "b", coef = "survey_year_fct2019"),
+  set_prior("normal(-0.050, 1)", class = "b", coef = "survey_year_fct2020"),
+  set_prior("normal(-0.075, 1)", class = "b", coef = "survey_year_fct2021"),
   set_prior("cauchy(0, 1)", class = "sigma")
@@
       "sd_site:plot__Intercept",
-      "sd_botanist_year__Intercept",
       "sigma"
@@
 ```{r}
-prior_summary(m_2, all = FALSE)
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+prior_summary(m_1, all = FALSE)
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
@@
 ```{r}
-draws2
+draws1
 mcmc_intervals(

### 2022-11-14 R/model_persistence_markdown.Rmd
Update persistence

@@
 ```{r}
-load(file = here("data", "processed", "model_fcs_1.Rdata"))
-load(file = here("data", "processed", "model_fcs_2.Rdata"))
-load(file = here("data", "processed", "model_fcs_3.Rdata"))
+load(file = here("data", "processed", "model_persistence_1.Rdata"))
+load(file = here("data", "processed", "model_persistence_2.Rdata"))
+load(file = here("data", "processed", "model_persistence_3.Rdata"))
 ```

### 2022-11-14 R/show_figure_2_fcs.R

@@ -1,199 +1,0 @@
-# Dike grassland field experiment
-# Favourable conservation status ####
-# Show figure 2
-
-# Markus Bauer
-# 2022-11-10
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-suppressPackageStartupMessages(library(brms))
-suppressPackageStartupMessages(library(tidybayes))
-library(ggbeeswarm)
-
-### Start ###
-rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
-setwd(here("data", "processed"))
-
-### Load data ###
-sites <- read_csv("data_processed_sites.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      id = "f",
-                      plot = "f",
-                      site = "f",
-                      exposition = col_factor(levels = c("north", "south")),
-                      sand_ratio = "f",
-                      substrate_depth = col_factor(levels = c("30", "15")),
-                      target_type = "f",
-                      seed_density = "f"
-                    )) %>%
-  filter(survey_year != "seeded") %>%
-  mutate(
-    n = fcs_target,
-    survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year_fct, botanist, sep = "_"),
-    botanist_year = str_replace_all(botanist_year, " ", "_")
-  ) %>%
-  select(
-    id, plot, site, botanist_year, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, n
-  )
-
-### * Model ####
-load(file = "model_fcs_3.Rdata")
-
-model <- sites %>%
-  add_predicted_draws(m3, allow_new_levels = TRUE)
-
-### * Functions ####
-theme_mb <- function() {
-  theme(
-    panel.background = element_rect(fill = "white"),
-    text = element_text(size = 9, color = "black"),
-    strip.text = element_text(size = 10),
[…]

### 2022-11-14 R/show_figure_2_nmds.R

@@ -1,0 +1,285 @@
+# Dike grassland experiment
+# Show_figure species composition ####
+# Markus Bauer
+# 2022-10-28
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(vegan)
+
+### Start ###
+rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d", "ordi")))
+setwd(here("data", "processed"))
+
+### Functions ###
+theme_mb <- function() {
+  theme(
+    panel.background = element_rect(fill = "white"),
+    text = element_text(size = 9, color = "black"),
+    strip.text = element_text(size = 10),
+    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
+                             color = "black"),
+    axis.title = element_text(angle = 0, hjust = 0.5, size = 9,
+                              color = "black"),
+    axis.line = element_line(),
+    legend.key = element_rect(fill = "white"),
+    legend.position = "right",
+    legend.margin = margin(0, 0, 0, 0, "cm"),
+    plot.margin = margin(0, 0, 0, 0, "cm")
+  )
+}
+
+vegan_cov_ellipse <- function(cov, center = c(0, 0), scale = 1, npoints = 100) {
+  theta <- (0:npoints) * 2 * pi / npoints
+  Circle <- cbind(cos(theta), sin(theta))
+  t(center + scale * t(Circle %*% chol(cov)))
+}
+
+#### * Load sites data ####
+
+sites_experiment <- read_csv("data_processed_sites.csv",
+                             col_names = TRUE, na = c("na", "NA", ""),
+                             col_types = cols(.default = "?")) %>%
+  mutate(reference = survey_year)
+sites_splot <- read_csv("data_processed_sites_splot.csv",
+                             col_names = TRUE, na = c("na", "NA", ""),
+                             col_types = cols(
+                               .default = "?",
+                               survey_year = "c"
+                               )) %>%
+  mutate(
+    reference = if_else(
+      esy == "E12a", "+Reference", if_else(
[…]

### 2022-11-14 R/show_figure_3_fcs.R

@@ -1,0 +1,182 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Show figure 2
+
+# Markus Bauer
+# 2022-11-10
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+suppressPackageStartupMessages(library(brms))
+suppressPackageStartupMessages(library(tidybayes))
+library(ggbeeswarm)
+
+### Start ###
+rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
+setwd(here("data", "processed"))
+
+### Load data ###
+sites <- read_csv("data_processed_sites.csv",
+                  col_names = TRUE,
+                  na = c("na", "NA", ""), col_types =
+                    cols(
+                      .default = "?",
+                      id = "f",
+                      plot = "f",
+                      site = "f",
+                      exposition = col_factor(levels = c("north", "south")),
+                      sand_ratio = "f",
+                      substrate_depth = col_factor(levels = c("30", "15")),
+                      target_type = "f",
+                      seed_density = "f"
+                    )) %>%
+  filter(survey_year != "seeded") %>%
+  mutate(
+    n = fcs_target,
+    survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year_fct, botanist, sep = "_"),
+    botanist_year = str_replace_all(botanist_year, " ", "_")
+  ) %>%
+  select(
+    id, plot, site, botanist_year, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, n
+  )
+
+### * Model ####
+load(file = "model_fcs_3.Rdata")
+
+model <- sites %>%
+  add_predicted_draws(m3, allow_new_levels = TRUE)
+
+### * Functions ####
+theme_mb <- function() {
+  theme(
+    panel.background = element_rect(fill = "white"),
+    text = element_text(size = 9, color = "black"),
[…]

### 2022-11-14 R/show_figure_4_persistence.R

@@ -1,0 +1,185 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Show figure
+
+# Markus Bauer
+# 2022-11-14
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(ggbeeswarm)
+
+### Start ###
+rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
+
+### Load data ###
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites_temporal.csv"),
+  col_names = TRUE, na = c("na", "NA", ""), col_types =
+    cols(
+      .default = "?",
+      plot = "f",
+      site = "f",
+      sand_ratio = "f",
+      substrate_depth = "f",
+      target_type = col_factor(levels = c(
+        "dry_grassland", "hay_meadow"
+      )),
+      seed_density = "f",
+      exposition = col_factor(levels = c(
+        "north", "south"
+      )),
+      survey_year = "c"
+    )
+) %>%
+  ### Exclude data of seed mixtures
+  filter(survey_year != "seeded") %>%
+  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
+               names_transform = as.factor) %>%
+  filter(index == "B" & presabu == "presence") %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    id = factor(id)
+  ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, survey_year, n
+  )
+
+### * Model ####
+load(file = "model_persistence_1.Rdata")
+
+model <- sites %>%
+  add_predicted_draws(m1, allow_new_levels = TRUE)
+
+### * Functions ####
+theme_mb <- function() {
+  theme(
+    panel.background = element_rect(fill = "white"),
+    text = element_text(size = 9, color = "black"),
+    strip.text = element_text(size = 10),
+    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
+                             color = "black"),
[…]

### 2022-11-14 R/show_figure_nmds.R

@@ -1,285 +1,0 @@
-# Dike grassland experiment
-# Show_figure species composition ####
-# Markus Bauer
-# 2022-10-28
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(vegan)
-
-### Start ###
-rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d", "ordi")))
-setwd(here("data", "processed"))
-
-### Functions ###
-theme_mb <- function() {
-  theme(
-    panel.background = element_rect(fill = "white"),
-    text = element_text(size = 9, color = "black"),
-    strip.text = element_text(size = 10),
-    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
-                             color = "black"),
-    axis.title = element_text(angle = 0, hjust = 0.5, size = 9,
-                              color = "black"),
-    axis.line = element_line(),
-    legend.key = element_rect(fill = "white"),
-    legend.position = "right",
-    legend.margin = margin(0, 0, 0, 0, "cm"),
-    plot.margin = margin(0, 0, 0, 0, "cm")
-  )
-}
-
-vegan_cov_ellipse <- function(cov, center = c(0, 0), scale = 1, npoints = 100) {
-  theta <- (0:npoints) * 2 * pi / npoints
-  Circle <- cbind(cos(theta), sin(theta))
-  t(center + scale * t(Circle %*% chol(cov)))
-}
-
-#### * Load sites data ####
-
-sites_experiment <- read_csv("data_processed_sites.csv",
-                             col_names = TRUE, na = c("na", "NA", ""),
-                             col_types = cols(.default = "?")) %>%
-  mutate(reference = survey_year)
-sites_splot <- read_csv("data_processed_sites_splot.csv",
-                             col_names = TRUE, na = c("na", "NA", ""),
-                             col_types = cols(
-                               .default = "?",
-                               survey_year = "c"
-                               )) %>%
-  mutate(
-    reference = if_else(
-      esy == "E12a", "+Reference", if_else(
[…]

### 2022-11-14 R/show_figure_persistence.R

@@ -1,186 +1,0 @@
-# Dike grassland experiment
-# Show_figure species composition ####
-# Markus Bauer
-# 2022-05-17
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(ggbeeswarm)
-
-### Start ###
-#rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
-setwd(here("data", "processed"))
-
-### Load data ###
-sites <- read_csv("data_processed_sites.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      id = "f",
-                      plot = "f",
-                      block = "f",
-                      exposition = col_factor(levels = c("north", "south")),
-                      sandRatio = "f",
-                      substrateDepth = "f",
-                      targetType = "f",
-                      seedDensity = "f"
-                    )) %>%
-  filter(
-    !str_detect(id, "C") & presabu == "presence" & surveyYear != "seeded"
-    ) %>%
-  select(
-    id, plot, block, exposition, sandRatio, substrateDepth, targetType,
-    seedDensity, surveyYear, B, C, D
-  ) %>%
-  pivot_longer(cols = c(B, C, D), names_to = "index", values_to = "n",
-               names_transform = as.factor) %>%
-  mutate(
-    index = fct_rev(index),
-    surveyYear = as.double(surveyYear),
-    surveyYear_fac = as.factor(surveyYear)
-  )
-
-### * Model ####
-m <- m31
-
-### * Functions ####
-theme_mb <- function() {
-  theme(
-    panel.background = element_rect(fill = "white"),
-    text = element_text(size = 9, color = "black"),
-    strip.text = element_text(size = 10),
-    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
-                             color = "black"),
-    axis.title = element_text(angle = 0, hjust = 0.5, size = 9,
-                              color = "black"),
[…]

### 2022-11-15 R/model_fcs_markdown.Rmd
Update

@@
 ```{r}
-load(file = here("data", "processed", "model_fcs_1.Rdata"))
-load(file = here("data", "processed", "model_fcs_2.Rdata"))
-load(file = here("data", "processed", "model_fcs_3.Rdata"))
+load(file = here("outputs", "models", "model_fcs_1.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2.Rdata"))
+load(file = here("outputs", "models", "model_fcs_3.Rdata"))
 ```
@@
 mcmc_trace(posterior2, np = hmc_diagnostics2)
+mcmc_parcoord(posterior1, np = hmc_diagnostics1)
+mcmc_parcoord(posterior2, np = hmc_diagnostics2)
 ```
@@
 ```{r}
-(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
+(emm <- emmeans(m_3, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))

### 2022-11-15 R/_prepare_data_vegetation.R

@@ -25,10 +25,24 @@
 
 #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
+remove.packages("rlang")
+remove.packages("tidyselect")
+remove.packages("tidyverse")
+remove.packages("Brobdingnag")
+remove.packages("dbplyr")
+remove.packages("Matrix")
 
+#devtools::install_github("RobinHankin/Brobdingnag") 
+install.packages("Matrix", dependencies = TRUE)
+install.packages("rlang", dependencies = TRUE)
+install.packages("Brobdingnag", dependencies = TRUE)
+install.packages("tidyselect", dependencies = TRUE)
+install.packages("dbplyr", dependencies = TRUE)
+install.packages("tidyverse", dependencies = TRUE)
+library(tidyverse)
 
 ### Packages ###
-library(renv)
+suppressPackageStartupMessages(library(renv))
 library(here)
 library(tidyverse)
 suppressPackageStartupMessages(library(lubridate))

### 2022-11-15 R/model_fcs_check.R

@@ -3,7 +3,7 @@
 # Model check
 
 # Markus Bauer
-# 2022-11-11
+# 2022-11-15
 
 
 
@@ -57,12 +57,12 @@ sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
     id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
     seed_density, survey_year_fct, survey_year, botanist_year, n
     )
-load(file = here("data", "processed", "model_fcs_simple.Rdata"))
-load(file = here("data", "processed", "model_fcs_full.Rdata"))
-load(file = here("data", "processed", "model_fcs_1.Rdata"))
-load(file = here("data", "processed", "model_fcs_2.Rdata"))
-load(file = here("data", "processed", "model_fcs_3.Rdata"))
-load(file = here("data", "processed", "model_fcs_3_flat.Rdata"))
+load(file = here("outputs", "models", "model_fcs_simple.Rdata"))
+load(file = here("outputs", "models", "model_fcs_full.Rdata"))
+load(file = here("outputs", "models", "model_fcs_1.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2.Rdata"))
+load(file = here("outputs", "models", "model_fcs_3.Rdata"))
+load(file = here("outputs", "models", "model_fcs_3_flat.Rdata"))
 
 
 
@@ -75,8 +75,8 @@ load(file = here("data", "processed", "model_fcs_3_flat.Rdata"))
 
 ### a Model comparison ---------------------------------------------------------
 
-m_1 <- m_simple
-m_2 <- m_full
+m_1 <- m_1
+m_2 <- m_3
 m_1$formula
 m_2$formula
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@ -277,9 +277,4 @@ mcmc_intervals(
 (emm <- emmeans(m_2, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))
 
-(draws <- m %>%
-    posterior::as_draws() %>%
-    posterior::summarize_draws() %>%
-    filter(str_starts(variable, "b_")))
-
-write.csv(draws, here("outputs", "statistics", "table_cwm_abu_sla.csv"))
+write.csv(draws2, here("outputs", "statistics", "table_fcs.csv"))

### 2022-11-15 R/model_persistence_check.R

@@ -246,7 +246,7 @@ mcmc_acf(posterior2, lags = 10)
 
 ### a Model output ------------------------------------------------------------
 
-prior_summary(m_2, all = FALSE)
+prior_summary(m_1, all = FALSE)
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
@@ -255,7 +255,7 @@ bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
-draws2
+draws1
 mcmc_intervals(
   posterior1,
   prob = 0.66,
@@ -272,5 +272,7 @@ mcmc_intervals(
 
 ### b Effect sizes ------------------------------------------------------------
 
-(emm <- emmeans(m_2, revpairwise ~ target_type + sand_ratio |
+(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))
+
+write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))

### 2022-11-15 R/model_persistence_markdown.Rmd
Update

@@
   ### Exclude data of seed mixtures
-  filter(survey_year != "seeded") %>%
-  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
-               names_transform = as.factor) %>%
-  filter(index == "B" & presabu == "presence") %>%
+  filter(presabu == "presence") %>%
   mutate(
     survey_year_fct = factor(survey_year),
-    id = factor(id)
+    id = factor(id),
+    n = persistence
   ) %>%
@@
 ```{r}
-load(file = here("data", "processed", "model_persistence_1.Rdata"))
-load(file = here("data", "processed", "model_persistence_2.Rdata"))
-load(file = here("data", "processed", "model_persistence_3.Rdata"))
+load(file = here("outputs", "models", "model_persistence_1.Rdata"))
+load(file = here("outputs", "models", "model_persistence_3.Rdata"))
 ```
@@
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+         re_formula =  ~ (1 | site/plot)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
+         re_formula =  ~ (1 | site/plot))
 ```
@@
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+         re_formula =  ~ (1 | site/plot)) 
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),

### 2022-11-15 R/model_fcs_check.R

@@ -266,7 +266,7 @@ mcmc_intervals(
 )
 mcmc_intervals(
   posterior2,
-  prob = 0.5,
+  prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
 )

### 2022-11-15 R/model_persistence_calculation.R

@@ -48,7 +48,7 @@ sites <- read_csv(
   mutate(
     survey_year_fct = factor(survey_year),
     id = factor(id),
-    n = persistence
+    n = scale(persistence)
   ) %>%
   select(
     id, plot, site, exposition, sand_ratio, substrate_depth, target_type,

### 2022-11-15 R/model_persistence_check.R

@@ -51,18 +51,18 @@ sites <- read_csv(
   mutate(
     survey_year_fct = factor(survey_year),
     id = factor(id),
-    n = persistence
+    n = scale(persistence)
   ) %>%
   select(
     id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
     seed_density, survey_year_fct, survey_year, n
   )
-load(file = here("data", "processed", "model_persistence_1.Rdata"))
-load(file = here("data", "processed", "model_persistence_2.Rdata"))
-load(file = here("data", "processed", "model_persistence_3.Rdata"))
-load(file = here("data", "processed", "model_persistence_simple.Rdata"))
-load(file = here("data", "processed", "model_persistence_full.Rdata"))
-load(file = here("data", "processed", "model_persistence_1_flat.Rdata"))
+load(file = here("outputs", "models", "model_persistence_1.Rdata"))
+load(file = here("outputs", "models", "model_persistence_2.Rdata"))
+load(file = here("outputs", "models", "model_persistence_3.Rdata"))
+load(file = here("outputs", "models", "model_persistence_simple.Rdata"))
+load(file = here("outputs", "models", "model_persistence_full.Rdata"))
+load(file = here("outputs", "models", "model_persistence_1_flat.Rdata"))
 
 
 
@@ -80,9 +80,9 @@ m_2 <- m3
 m_1$formula
 m_2$formula
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+         re_formula =  ~ (1 | site/plot)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+         re_formula =  ~ (1 | site/plot)) 
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
@@ -248,12 +248,8 @@ mcmc_acf(posterior2, lags = 10)
 
 prior_summary(m_1, all = FALSE)
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
[…]

### 2022-11-15 R/show_figure_3_fcs.R

@@ -167,8 +167,8 @@ m3 %>%
       )
   ) %>%
   ggplot(aes(x = .value, y = .variable)) +
-  stat_halfeye() +
   geom_vline(xintercept = 0, linetype = "dashed") +
+  stat_halfeye() +
   labs(x = expression(Delta ~ Favourabale ~ Conservation ~ Status ~ "(FCS)"), y = "") +
   theme_mb()
 

### 2022-11-15 R/show_figure_4_persistence.R

@@ -176,8 +176,8 @@ m1 %>%
   ) %>%
   mutate(.value = ((1 - .value) * 100) - 100) %>%
   ggplot(aes(x = .value, y = .variable)) +
-  stat_halfeye() +
   geom_vline(xintercept = 0, linetype = "dashed") +
+  stat_halfeye() +
   scale_x_continuous(breaks = seq(-100, 400, 10)) +
   labs(x = expression(Delta ~ Persistence ~ "[%]"), y = "") +
   theme_mb()

### 2022-11-15 R/model_fcs_markdown.Rmd
Update

@@
 library(DHARMa)
+library(DHARMa.helpers)
 library(bayesplot)
@@
 ```{r}
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_1)),
-  observedResponse = sites$n,
-  fittedPredictedResponse = apply(t(posterior_epred(m_1)), 1, mean),
-  integerResponse = TRUE
-  ) %>%
-  plot()
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_2)),
-  observedResponse = sites$n,
-  fittedPredictedResponse = apply(t(posterior_epred(m_2)), 1, mean),
-  integerResponse = TRUE
-  ) %>%
-  plot()
+DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
+DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
 ```
@@
 ```{r}
-(emm <- emmeans(m_3, revpairwise ~ target_type + sand_ratio |
+(emm <- emmeans(m_2, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))

### 2022-11-15 R/model_fcs_check.R

@@ -18,6 +18,8 @@ library(here)
 library(tidyverse)
 library(brms)
 library(DHARMa)
+#remotes::install_github("Pakillo/DHARMa.helpers")
+library(DHARMa.helpers)
 library(bayesplot)
 library(loo)
 library(tidybayes)
@@ -75,8 +77,8 @@ load(file = here("outputs", "models", "model_fcs_3_flat.Rdata"))
 
 ### a Model comparison ---------------------------------------------------------
 
-m_1 <- m_1
-m_2 <- m_3
+m_1 <- m1
+m_2 <- m3
 m_1$formula
 m_2$formula
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@ -92,20 +94,8 @@ bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
 ### b Model check -----------------------------------------------------------
 
 #### * DHARMa ####
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_1)),
-  observedResponse = sites$n,
-  fittedPredictedResponse = apply(t(posterior_epred(m_1)), 1, mean),
-  integerResponse = TRUE
-  ) %>%
-  plot()
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_2)),
-  observedResponse = sites$n,
-  fittedPredictedResponse = apply(t(posterior_epred(m_2)), 1, mean),
-  integerResponse = TRUE
-  ) %>%
-  plot()
+DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
+DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
 
 #### * Preparation ####
 posterior1 <- m_1 %>%
@@ -249,12 +239,8 @@ mcmc_acf(posterior2, lags = 10)
 ### a Model output ------------------------------------------------------------
 
 prior_summary(m_2, all = FALSE)
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
 draws2

### 2022-11-15 R/model_persistence_check.R

@@ -18,6 +18,8 @@ library(here)
 library(tidyverse)
 library(brms)
 library(DHARMa)
+#remotes::install_github("Pakillo/DHARMa.helpers")
+library(DHARMa.helpers)
 library(bayesplot)
 library(loo)
 library(tidybayes)
@@ -92,20 +94,8 @@ bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
 ### b Model check -----------------------------------------------------------
 
 #### * DHARMa ####
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_1)),
-  observedResponse = sites$n,
-  fittedPredictedResponse = apply(t(posterior_epred(m_1)), 1, mean),
-  integerResponse = TRUE
-  ) %>%
-  plot()
-createDHARMa(
-  simulatedResponse = t(posterior_predict(m_2)),
-  observedResponse = sites$n,
-  fittedPredictedResponse = apply(t(posterior_epred(m_2)), 1, mean),
-  integerResponse = TRUE
-  ) %>%
-  plot()
+DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
+DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
 
 #### * Preparation ####
 posterior1 <- m_1 %>%

### 2022-11-15 R/show_figure_3_fcs.R

@@ -169,6 +169,7 @@ m3 %>%
   ggplot(aes(x = .value, y = .variable)) +
   geom_vline(xintercept = 0, linetype = "dashed") +
   stat_halfeye() +
+  scale_x_continuous(breaks = seq(-100, 400, .5)) +
   labs(x = expression(Delta ~ Favourabale ~ Conservation ~ Status ~ "(FCS)"), y = "") +
   theme_mb()
 

### 2022-11-15 R/model_persistence_markdown.Rmd
Update

@@
 date: "`r format(Sys.time(), '%Y-%m-%d')`"
-output: github_document
+#output: github_document
+knit: (function(inputFile, encoding) {
+  rmarkdown::render(inputFile, encoding = encoding, output_dir = "pdf") })
 ---

### 2022-11-15 R/model_nmds.R

@@ -83,6 +83,7 @@ sites <- sites_experiment %>%
     exposition, sand_ratio, substrate_depth, target_type, seed_density,
     survey_year, longitude, latitude, elevation, plot_size
   ) %>%
+  mutate(survey_year_fct = factor(survey_year)) %>%
   arrange(id)
 
 
@@ -128,59 +129,6 @@ rm(list = setdiff(ls(), c(
   "sites", "species", "theme_mb", "vegan_cov_ellipse", "ordi"
 )))
 
-#### * Model ####
-
-set.seed(12)
-(ordi <- metaMDS(species, binary = TRUE,
-                 try = 50, previous.best = TRUE, na.rm = TRUE))
-#Wisonsin sqrt transformation, stress type 1
-stressplot(ordi) # stress: 0.205; Non-metric fit R² =.958
-
-
-
-library(tidyverse)
-library(vegan)
-
-### Start ###
-rm(list = ls())
-setwd(here("data", "processed"))
-
-### Load data ###
-sites <- read_csv("data_processed_sites.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""),
-                  col_types =
-                    cols(
-                      .default = "?",
-                      id = "f",
-                      plot = "f",
-                      site = "f",
-                      exposition = col_factor(levels = c("north", "south")),
-                      sand_ratio = "f",
-                      substrate_depth = "f",
-                      target_type = "c",
-                      seed_density = "f"
-                    )) %>%
-  select(
-    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year
-  ) %>%
-  mutate(survey_year_fct = factor(survey_year))
-
-species <- read_csv("data_processed_species.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""),
-                  col_types = cols(
-                    .default = "d",
-                    name = "f",
-                  )) %>%
-  pivot_longer(-name, names_to = "id", values_to = "value") %>%
-  pivot_wider(names_from = "name", values_from = "value") %>%
-  arrange(id) %>%
-  semi_join(sites, by = "id") %>%
-  column_to_rownames("id") %>%
-  mutate(across(where(is.numeric), ~replace(., 0, NA)))
-
 
 
 #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
[…]

### 2022-11-15 R/model_persistence_calculation.R

@@ -261,10 +261,14 @@ m1_flat <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
                cores = parallel::detectCores(),
                seed = 123)
 
-### Save ###
-save(m_simple, file = here("outputs", "models", "model_persistence_simple.Rdata"))
-save(m_full, file = here("outputs", "models", "model_persistence_full.Rdata"))
+### c Save ---------------------------------------------------------------------
+save(m_simple, file = here(
+  "outputs", "models", "model_persistence_simple.Rdata"))
+save(m_full, file = here("outputs", "models", "model_persistence_full.Rdata"
+                         ))
 save(m1, file = here("outputs", "models", "model_persistence_1.Rdata"))
 save(m2, file = here("outputs", "models", "model_persistence_2.Rdata"))
 save(m3, file = here("outputs", "models", "model_persistence_3.Rdata"))
-save(m1_flat, file = here("outputs", "models", "model_persistence_1_flat.Rdata"))
+save(m1_flat, file = here(
+  "outputs", "models", "model_persistence_1_flat.Rdata"
+  ))

### 2022-11-15 R/show_figure_2_nmds.R

@@ -157,6 +157,8 @@ rm(list = setdiff(ls(), c(
 set.seed(12)
 (ordi <- metaMDS(species, binary = TRUE,
                  try = 50, previous.best = TRUE, na.rm = TRUE))
+save(ordi, file = here(
+  "outputs", "models", "model_nmds.Rdata"))
 #Wisonsin sqrt transformation, stress type 1
 stressplot(ordi) # stress: 0.205; Non-metric fit R² =.958
 

### 2022-11-15 R/show_figure_3_fcs.R

@@ -50,7 +50,7 @@ sites <- read_csv("data_processed_sites.csv",
   )
 
 ### * Model ####
-load(file = "model_fcs_3.Rdata")
+load(file = here("outputs", "models", "model_fcs_3.Rdata"))
 
 model <- sites %>%
   add_epred_draws(m3, allow_new_levels = TRUE)

### 2022-11-15 R/model_persistence_markdown.Rmd
Update

@@
 priors <- c(
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("normal(-0.025, 1)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(-0.050, 1)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(0.050, 1)", class = "b", coef = "expositionsouth"),
-  set_prior("normal(-0.025, 1)", class = "b", coef = "survey_year_fct2019"),
-  set_prior("normal(-0.050, 1)", class = "b", coef = "survey_year_fct2020"),
-  set_prior("normal(-0.075, 1)", class = "b", coef = "survey_year_fct2021"),
-  set_prior("cauchy(0, 1)", class = "sigma")
+  set_prior("normal(0, 20)", class = "b"),
+  set_prior("normal(-2.5, 20)", class = "b", coef = "sand_ratio25"),
+  set_prior("normal(-5, 20)", class = "b", coef = "sand_ratio50"),
+  set_prior("normal(5, 20)", class = "b", coef = "expositionsouth"),
+  set_prior("normal(-2.5, 20)", class = "b", coef = "survey_year_fct2019"),
+  set_prior("normal(-5, 20)", class = "b", coef = "survey_year_fct2020"),
+  set_prior("normal(-7.5, 20)", class = "b", coef = "survey_year_fct2021"),
+  set_prior("cauchy(0, 10)", class = "sigma")
 )

### 2022-11-15 R/model_persistence_calculation.R

@@ -1,9 +1,9 @@
 # Dike grassland field experiment
-# Favourable conservation status ####
+# Persistence ####
 # Model building
 
 # Markus Bauer
-# 2022-11-10
+# 2022-11-15
 
 
 
@@ -130,7 +130,9 @@ ggplot(sites, aes(sqrt(n))) + geom_density()
 ## 2 Model building ###########################################################
 
 
+
 ### a Preparation -------------------------------------------------------------
+
 
 ### Posssible priors ###
 get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
@@ -150,7 +152,8 @@ ggplot(data.frame(x = c(-30, 30)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
   expand_limits(y = 0)
 
-### a Models ------------------------------------------------------------------
+
+### b Models ------------------------------------------------------------------
 
 ### Specifications ###
 iter = 10000
@@ -264,7 +267,9 @@ m1_flat <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
                cores = parallel::detectCores(),
                seed = 123)
 
+
 ### c Save ---------------------------------------------------------------------
+
 save(m_simple, file = here(
   "outputs", "models", "model_persistence_simple.Rdata"
   ))

### 2022-11-15 R/model_persistence_check.R

@@ -1,9 +1,9 @@
 # Dike grassland field experiment
-# Favourable conservation status ####
+# Persistence ####
 # Model check
 
 # Markus Bauer
-# 2022-11-11
+# 2022-11-15
 
 
 
@@ -73,7 +73,9 @@ load(file = here("outputs", "models", "model_persistence_1_flat.Rdata"))
 #+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
 
+
 ## 1 Model check ###############################################################
+
 
 ### a Model comparison ---------------------------------------------------------
 

### 2022-11-15 R/model_recover_time_calculation.R

@@ -1,7 +1,10 @@
 # Dike grassland field experiment
-# Recover time (presence-absence data) ####
+# Dike grassland field experiment
+# Recover time ####
+# Model building
+
 # Markus Bauer
-# 2022-05-24
+# 2022-11-15
 
 
 

### 2022-11-15 R/model_recover_time_check.R

@@ -1,0 +1,337 @@
+# Dike grassland field experiment
+# Recover time ####
+# Model check
+
+# Markus Bauer
+# 2022-11-15
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(ggbeeswarm)
+library(brms)
+library(DHARMa)
+library(bayesplot)
+library(loo)
+library(tidybayes)
+library(emmeans)
+
+### Start ###
+rm(list = ls())
+
+### Load data ###
+sites_experiment <- read_csv("data_processed_sites.csv",
+                             col_names = TRUE, na = c("na", "NA", ""),
+                             col_types = cols(.default = "?")) %>%
+  mutate(reference = survey_year)
+sites_splot <- read_csv("data_processed_sites_splot.csv",
+                        col_names = TRUE, na = c("na", "NA", ""),
+                        col_types = cols(
+                          .default = "?",
+                          survey_year = "c"
+                        )) %>%
+  mutate(
+    reference = if_else(
+      esy == "E12a", "+Reference", if_else(
+        esy == "E22", "+Reference", "other"
+      )
+    ),
+    target_type = if_else(
+      esy == "E12a", "dry_grassland", if_else(
+        esy == "E22", "hay_meadow", "other"
+      )
+    ),
+    exposition = "other"
+  )
+sites_bauer <- read_csv("data_processed_sites_bauer.csv",
+                        col_names = TRUE, na = c("na", "NA", ""),
+                        col_types = cols(
+                          .default = "?",
+                          survey_year = "c"
+                        )) %>%
+  filter(exposition == "south" | exposition == "north") %>%
+  mutate(
+    reference = if_else(
+      esy == "R1A", "+Reference", if_else(
+        esy == "R22", "+Reference", if_else(
[…]

### 2022-11-15 R/show_figure_4_persistence.R

@@ -57,12 +57,7 @@ sites <- read_csv(
 load(file = here("outputs", "models", "model_persistence_1.Rdata"))
 
 model <- sites %>%
-  add_epred_draws(m1, allow_new_levels = TRUE) %>%
-  mutate(
-    mean = mean(n),
-    sd = sd(n),
-    .epred = .epred * sd + mean
-  )
+  add_epred_draws(m1, allow_new_levels = TRUE)
 
 ### * Functions ####
 theme_mb <- function() {
@@ -180,7 +175,6 @@ m1 %>%
       "2018 vs. 2021" = "b_survey_year_fct2021"
     )
   ) %>%
-  mutate(.value = ((1 - .value) * 100) - 100) %>%
   ggplot(aes(x = .value, y = .variable)) +
   geom_vline(xintercept = 0, linetype = "dashed") +
   stat_halfeye() +

### 2022-11-15 R/show_figure_5_recover_time.R

@@ -1,0 +1,198 @@
+# Dike grassland field experiment
+# Favourable conservation status ####
+# Show figure
+
+# Markus Bauer
+# 2022-11-15
+
+
+
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+# A Preparation ###############################################################
+#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+
+### Packages ###
+library(here)
+library(tidyverse)
+library(ggbeeswarm)
+library(ggrepel)
+
+### Start ###
+rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
+
+### Load data ###
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites_temporal.csv"),
+  col_names = TRUE, na = c("na", "NA", ""), col_types =
+    cols(
+      .default = "?",
+      plot = "f",
+      site = "f",
+      sand_ratio = "f",
+      substrate_depth = "f",
+      target_type = col_factor(levels = c(
+        "dry_grassland", "hay_meadow"
+      )),
+      seed_density = "f",
+      exposition = col_factor(levels = c(
+        "north", "south"
+      )),
+      survey_year = "c"
+    )
+) %>%
+  ### Exclude data of seed mixtures
+  filter(presabu == "presence") %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    id = factor(id),
+    n = persistence
+  ) %>%
+  select(
+    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
+    seed_density, survey_year_fct, survey_year, n
+  )
+
+### * Model ####
+load(file = here("outputs", "models", "model_persistence_1.Rdata"))
+
+model <- sites %>%
+  add_epred_draws(m1, allow_new_levels = TRUE) %>%
+  mutate(
+    mean = mean(n),
+    sd = sd(n),
+    .epred = .epred * sd + mean
+  )
+
+### * Functions ####
+theme_mb <- function() {
+  theme(
+    panel.background = element_rect(fill = "white"),
+    text = element_text(size = 9, color = "black"),
+    strip.text = element_text(size = 10),
+    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
+                             color = "black"),
[…]

### 2022-11-15 R/model_recovery_time_markdown.Rmd
Update

--- 2022-11-15 R/model_fcs_markdown.Rmd
@@
 ---
-title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
+title: "Recover time to reference state: <br> Analysis of Bauer et al. (unpublished) Field experiment"
 author: "Markus Bauer <br>"
@@
 ```{r}
-sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
-                  col_names = TRUE, na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      plot = "f",
-                      site = "f",
-                      sand_ratio = "f",
-                      substrate_depth = "f",
-                      target_type = col_factor(levels = c(
-                        "dry_grassland", "hay_meadow"
-                        )),
-                      seed_density = "f",
-                      exposition = col_factor(levels = c(
-                        "north", "south"
-                      )),
-                      survey_year = "d"
-                    )) %>%
-  ### Exclude data of seed mixtures
-  filter(survey_year != "seeded") %>%
-  mutate(
-    survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
-    botanist_year = factor(botanist_year),
-    n = fcs_target,
-    id = factor(id)
-    ) %>%
-  select(
-    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, survey_year, botanist_year, n
-    )
+
 ```

### 2022-11-15 R/model_recovery_time_calculation.R

@@ -31,8 +31,19 @@ rm(list = ls())
 ### Load data ###
 sites_experiment <- read_csv("data_processed_sites.csv",
                              col_names = TRUE, na = c("na", "NA", ""),
-                             col_types = cols(.default = "?")) %>%
-  mutate(reference = survey_year)
+                             col_types = cols(
+                               .default = "?",
+                               sand_ratio = "f",
+                               substrate_depth = "f",
+                               target_type = "f",
+                               seed_density = "f",
+                               exposition = "f",
+                               site = "f"
+                               )) %>%
+  mutate(
+    reference = survey_year,
+    survey_year_fct = factor(survey_year)
+    )
 sites_splot <- read_csv("data_processed_sites_splot.csv",
                         col_names = TRUE, na = c("na", "NA", ""),
                         col_types = cols(
@@ -128,15 +139,30 @@ sites <- sites %>%
 
 load(file = here("outputs", "models", "model_nmds.Rdata"))
 
-sites2 <- sites %>%
+sites %>%
   mutate(nmds1 = ordi$points[, 1], nmds2 = ordi$points[, 2]) %>%
-  group_by(exposition, target_type)
-  mutate(data = sites %>% filter(reference == "+Reference"), mean = mean(nmds1))
-  
-rm(list = setdiff(ls(), c(
-  "sites", "theme_mb", "vegan_cov_ellipse", "ordi"
-)))
+  filter(reference == "+Reference") %>%
+  group_by(exposition, target_type) %>%
+  summarise(mean_reference = mean(nmds1))
 
+sites <- sites %>%
+  mutate(
+    nmds1 = ordi$points[, 1], nmds2 = ordi$points[, 2],
+    mean_reference = if_else(
+      exposition == "north" & target_type == "dry_grassland", 0.644, if_else(
+        exposition == "north" & target_type == "hay_meadow", 0.485, if_else(
+          exposition == "south" & target_type == "dry_grassland", 0.542, if_else(
+            exposition == "south" & target_type == "hay_meadow", 0.469, NA_real_
+          )
+        )
+      )
+    ),
+    n = mean_reference - nmds1
+    ) %>%
+  filter(reference == "2018" | reference == "2019" | reference == "2020" |
+           reference == "2021")
+
+rm(list = setdiff(ls(), c("sites")))
 
 
 

### 2022-11-15 R/model_recovery_time_check.R

@@ -334,4 +334,4 @@ mcmc_intervals(
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))
 
-write.csv(draws1, here("outputs", "statistics", "table_recover_time.csv"))
+write.csv(draws1, here("outputs", "statistics", "table_recovery_time.csv"))

### 2022-11-15 R/show_figure_5_recovery_time.R

@@ -22,39 +22,116 @@ library(ggrepel)
 rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
 
 ### Load data ###
-sites <- read_csv(
-  here("data", "processed", "data_processed_sites_temporal.csv"),
-  col_names = TRUE, na = c("na", "NA", ""), col_types =
-    cols(
-      .default = "?",
-      plot = "f",
-      site = "f",
-      sand_ratio = "f",
-      substrate_depth = "f",
-      target_type = col_factor(levels = c(
-        "dry_grassland", "hay_meadow"
-      )),
-      seed_density = "f",
-      exposition = col_factor(levels = c(
-        "north", "south"
-      )),
-      survey_year = "c"
-    )
-) %>%
-  ### Exclude data of seed mixtures
-  filter(presabu == "presence") %>%
+sites_experiment <- read_csv("data_processed_sites.csv",
+                             col_names = TRUE, na = c("na", "NA", ""),
+                             col_types = cols(.default = "?")) %>%
+  mutate(reference = survey_year)
+sites_splot <- read_csv("data_processed_sites_splot.csv",
+                        col_names = TRUE, na = c("na", "NA", ""),
+                        col_types = cols(
+                          .default = "?",
+                          survey_year = "c"
+                        )) %>%
   mutate(
-    survey_year_fct = factor(survey_year),
-    id = factor(id),
-    n = persistence
-  ) %>%
-  select(
-    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, survey_year, n
+    reference = if_else(
+      esy == "E12a", "+Reference", if_else(
+        esy == "E22", "+Reference", "other"
+      )
+    ),
+    target_type = if_else(
+      esy == "E12a", "dry_grassland", if_else(
+        esy == "E22", "hay_meadow", "other"
+      )
+    ),
+    exposition = "other"
   )
+sites_bauer <- read_csv("data_processed_sites_bauer.csv",
+                        col_names = TRUE, na = c("na", "NA", ""),
+                        col_types = cols(
+                          .default = "?",
+                          survey_year = "c"
+                        )) %>%
+  filter(exposition == "south" | exposition == "north") %>%
+  mutate(
[…]

### 2022-11-17 R/model_fcs_markdown.Rmd
Update FCS

@@
                       sand_ratio = "f",
-                      substrate_depth = "f",
+                      substrate_depth = col_factor(levels = c("30", "15")),
                       target_type = col_factor(levels = c(
-                        "dry_grassland", "hay_meadow"
+                        "hay_meadow", "dry_grassland"
                       )),
@@
                       )),
-                      survey_year = "d"
+                      survey_year = "c"
                     )) %>%
@@
 ```{r echo = FALSE}
-plot1 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = sand_ratio)) +
+plot1 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = sand_ratio)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Sand ratio [vol%] (Data of 2021)")
-plot2 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = substrate_depth)) +
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Sand ratio [vol%]")
+plot2 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = substrate_depth)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Substrate depth [cm] (Data of 2021)")
-plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = target_type)) +
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Substrate depth [cm]")
+plot3 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = target_type)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Target type (Data of 2021)")
-plot4 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = seed_density)) +
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Target type")
+plot4 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = seed_density)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Seed density [g/m²] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Seed density [g/m²]")
 (plot1 + plot2) / (plot3 + plot4)
-plot1 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = exposition)) +
+plot1 <- ggplot(sites %>% filter(survey_year == 2021),
+                aes(y = n, x = exposition)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Exposition (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Exposition")
 plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Blocks (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Blocks")
 plot4 <- ggplot(sites, aes(y = n, x = botanist_year)) +
@@
 
-Conditional R² values
+Conditional italic(R)² values
 
@@
 
-Marginal R² values
+Marginal italic(R)² values
 
@@
       "b_sand_ratio50",
-      "b_substrate_depth30",
-      "b_target_typehay_meadow",
+      "b_substrate_depth15",
+      "b_target_typedry_grassland",
       "b_seed_density8",
@@
 
-Priors and conditional and marignal R²
+Prior summary
 
@@
 prior_summary(m_2, all = FALSE)
+```
+
+Conditional and marignal italic(R)²
+
+```{r}
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),

### 2022-11-17 R/model_fcs_calculation.R

@@ -31,15 +31,15 @@ sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
                       plot = "f",
                       site = "f",
                       sand_ratio = "f",
-                      substrate_depth = "f",
+                      substrate_depth = col_factor(levels = c("30", "15")),
                       target_type = col_factor(levels = c(
-                        "dry_grassland", "hay_meadow"
+                        "hay_meadow", "dry_grassland"
                       )),
                       seed_density = "f",
                       exposition = col_factor(levels = c(
                         "north", "south"
                       )),
-                      survey_year = "d"
+                      survey_year = "c"
                     )) %>%
   ### Exclude data of seed mixtures
   filter(survey_year != "seeded") %>%
@@ -71,30 +71,36 @@ sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = sand_ratio)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Sand ratio [vol%] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Sand ratio [vol%]")
 plot2 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = substrate_depth)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Substrate depth [cm] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Substrate depth [cm]")
 plot3 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = target_type)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Target type (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Target type")
 plot4 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = seed_density)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Seed density [g/m²] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Seed density [g/m²]")
 (plot1 + plot2) / (plot3 + plot4)
[…]

### 2022-11-17 R/model_fcs_check.R

@@ -36,15 +36,15 @@ sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
                       plot = "f",
                       site = "f",
                       sand_ratio = "f",
-                      substrate_depth = "f",
+                      substrate_depth = col_factor(levels = c("30", "15")),
                       target_type = col_factor(levels = c(
-                        "dry_grassland", "hay_meadow"
+                        "hay_meadow", "dry_grassland"
                       )),
                       seed_density = "f",
                       exposition = col_factor(levels = c(
                         "north", "south"
                       )),
-                      survey_year = "c",
+                      survey_year = "c"
                     )) %>%
   ### Exclude data of seed mixtures
   filter(survey_year != "seeded") %>%

### 2022-11-17 R/show_figure_3_fcs.R

@@ -23,19 +23,22 @@ rm(list = setdiff(ls(), c("graph_a", "graph_b", "graph_c", "graph_d")))
 setwd(here("data", "processed"))
 
 ### Load data ###
-sites <- read_csv("data_processed_sites.csv",
-                  col_names = TRUE,
-                  na = c("na", "NA", ""), col_types =
+sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+                  col_names = TRUE, na = c("na", "NA", ""), col_types =
                     cols(
                       .default = "?",
-                      id = "f",
                       plot = "f",
                       site = "f",
-                      exposition = col_factor(levels = c("north", "south")),
                       sand_ratio = "f",
                       substrate_depth = col_factor(levels = c("30", "15")),
-                      target_type = "f",
-                      seed_density = "f"
+                      target_type = col_factor(levels = c(
+                        "hay_meadow", "dry_grassland"
+                      )),
+                      seed_density = "f",
+                      exposition = col_factor(levels = c(
+                        "north", "south"
+                      )),
+                      survey_year = "c"
                     )) %>%
   filter(survey_year != "seeded") %>%
   mutate(
@@ -85,44 +88,42 @@ theme_mb <- function() {
 ## 1 Marginal effects #########################################################
 
 (p1 <- ggplot(data = sites) +
-  geom_quasirandom(
-    aes(y = n, x = sand_ratio, color = target_type),
-    alpha = 0.2,
-    dodge.width = 0.9,
-    cex = .5
-    ) +
-  geom_hline(
-    yintercept = 0,
-    linetype = "dashed",
-    linewidth = .3,
-    color = "black"
-  ) +
-  stat_pointinterval(
-    aes(y = .epred, x = sand_ratio, color = target_type),
-    data = model,
-    .width = c(0.66, 0.95),
-    point_size = 2,
-    position = "dodge"
-  ) +
-  facet_grid(
-    exposition ~ survey_year_fct,
-    labeller = as_labeller(
-      c(south = "South", north = "North",
-        "2018" = "2018", "2019" = "2019", "2020" = "2020", "2021" = "2021")
-    )
-  ) +
[…]

### 2022-11-17 R/model_fcs_markdown.Rmd
Update model_fcs_markdown.Rmd

@@
 mcmc_trace(posterior2, np = hmc_diagnostics2)
+mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
+           pars = c(
+             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
+             "b_target_typedry_grassland", "b_seed_density8",
+             "b_expositionsouth", "sigma"
+           ))
+mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
+           pars = c(
+             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
+             "b_target_typedry_grassland", "b_seed_density8",
+             "b_expositionsouth", "sigma"
+           ))
 mcmc_parcoord(posterior1, np = hmc_diagnostics1)

### 2022-11-17 R/model_fcs_markdown.Rmd
Update

@@
 thin = 2
+seed = 123
 priors <- c(
@@
 ```{r}
-load(file = here("outputs", "models", "model_fcs_1.Rdata"))
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
-load(file = here("outputs", "models", "model_fcs_3.Rdata"))
+load(file = here("outputs", "models", "model_fcs_full.Rdata"))
 ```
@@
 ```{r}
-m_1 <- m1
-m_2 <- m3
+m_1 <- m2
+m_2 <- m_full
 m_1$formula
@@
 
-##### LOO-PIT plots
+##### LOO Leave one out
+
+```{r}
+loo1
+loo2
+plot(loo1)
+plot(loo2)
+```
+
+Leave one out probability integral transform
 
@@
 p1 / p2
-plot(loo1)
-plot(loo2)
+
 ```
@@
 ```{r}
-prior_summary(m_2, all = FALSE)
+prior_summary(m_1, all = FALSE)
 ```
@@
 ```{r}
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
@@
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 mcmc_intervals(
@@
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 ```
@@
 ```{r}
-(emm <- emmeans(m_2, revpairwise ~ target_type + sand_ratio |
+(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))

### 2022-11-17 R/model_persistence_markdown.Rmd
Update

@@
 date: "`r format(Sys.time(), '%Y-%m-%d')`"
-#output: github_document
-knit: (function(inputFile, encoding) {
-  rmarkdown::render(inputFile, encoding = encoding, output_dir = "pdf") })
+output: github_document
 ---
@@
       sand_ratio = "f",
-      substrate_depth = "f",
+      substrate_depth = col_factor(levels = c("30", "15")),
       target_type = col_factor(levels = c(
-        "dry_grassland", "hay_meadow"
+        "hay_meadow", "dry_grassland"
       )),
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Sand ratio [vol%] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Sand ratio [vol%]")
 plot2 <- ggplot(sites %>% filter(survey_year == 2021),
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Substrate depth [cm] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Substrate depth [cm]")
 plot3 <- ggplot(sites %>% filter(survey_year == 2021),
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Target type (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Target type")
 plot4 <- ggplot(sites %>% filter(survey_year == 2021),
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Seed density [g/m²] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Seed density [g/m²]")
 (plot1 + plot2) / (plot3 + plot4)
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Exposition (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Exposition")
 plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
@@
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Blocks (Data of 2021)")
-(plot1 + plot2) / (plot3)
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Blocks")
+plot4 <- ggplot(sites, aes(y = n, x = botanist_year)) +
+  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
+  labs(title = "Botanists and survey year") +
+  theme(axis.text.x = element_text(angle = 90))
+(plot1 + plot2) / (plot3 + plot4)
 ggplot(data = sites,
@@
 
-##### LOO-PIT plots
+##### LOO-PIT: Leave one out probability integral transform checks
 

### 2022-11-17 R/model_recovery_time_markdown.Rmd
Update

@@
 ```{r}
-
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites_nmds.csv"),
+  col_names = TRUE, na = c("na", "NA", ""),
+  col_types = cols(
+    .default = "?",
+    id = "f",
+    plot = "f",
+    site = "f",
+    exposition = col_factor(levels = c("north", "south",
+                                       "other")),
+    sand_ratio = "f",
+    substrate_depth = col_factor(levels = c("30", "15")),
+    target_type = col_factor(
+      levels = c("hay_meadow", "dry_grassland", "other")
+      ),
+    seed_density = "f"
+    )
+  ) %>%
+  filter(reference == "2018" | reference == "2019" | reference == "2020" |
+           reference == "2021") %>%
+  mutate(
+    survey_year_fct = factor(survey_year),
+    survey_year = as.numeric(survey_year),
+    botanist_year = str_c(survey_year, botanist, sep = " "),
+    n = recovery_time
+    )
 ```

### 2022-11-17 R/model_fcs_calculation.R

@@ -24,23 +24,25 @@ library(brms)
 rm(list = ls())
 
 ### Load data ###
-sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
-                  col_names = TRUE, na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      plot = "f",
-                      site = "f",
-                      sand_ratio = "f",
-                      substrate_depth = col_factor(levels = c("30", "15")),
-                      target_type = col_factor(levels = c(
-                        "hay_meadow", "dry_grassland"
-                      )),
-                      seed_density = "f",
-                      exposition = col_factor(levels = c(
-                        "north", "south"
-                      )),
-                      survey_year = "c"
-                    )) %>%
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites.csv"),
+  col_names = TRUE, na = c("na", "NA", ""), col_types =
+    cols(
+      .default = "?",
+      plot = "f",
+      site = "f",
+      sand_ratio = "f",
+      substrate_depth = col_factor(levels = c("30", "15")),
+      target_type = col_factor(levels = c(
+        "hay_meadow", "dry_grassland"
+      )),
+      seed_density = "f",
+      exposition = col_factor(levels = c(
+        "north", "south"
+      )),
+      survey_year = "c"
+    )
+  ) %>%
   ### Exclude data of seed mixtures
   filter(survey_year != "seeded") %>%
   mutate(
@@ -147,15 +149,15 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             (1 | site/plot) + (1 | botanist_year),
           data = sites)
 ### Example of normal distribution
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)) +
   expand_limits(y = 0)
 ### Example of cauchy distribution
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0)
 ### Example of a student t distribution
-ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
[…]

### 2022-11-17 R/model_fcs_check.R

@@ -23,6 +23,7 @@ library(DHARMa.helpers)
 library(bayesplot)
 library(loo)
 library(tidybayes)
+library(patchwork)
 library(emmeans)
 
 ### Start ###
@@ -64,7 +65,7 @@ load(file = here("outputs", "models", "model_fcs_full.Rdata"))
 load(file = here("outputs", "models", "model_fcs_1.Rdata"))
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
 load(file = here("outputs", "models", "model_fcs_3.Rdata"))
-load(file = here("outputs", "models", "model_fcs_3_flat.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
 
 
 
@@ -77,7 +78,7 @@ load(file = here("outputs", "models", "model_fcs_3_flat.Rdata"))
 
 ### a Model comparison ---------------------------------------------------------
 
-m_1 <- m_simple
+m_1 <- m2
 m_2 <- m_full
 m_1$formula
 m_2$formula
@@ -257,13 +258,15 @@ mcmc_intervals(
   prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 mcmc_intervals(
   posterior2,
   prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 
 
 ### b Effect sizes ------------------------------------------------------------

### 2022-11-17 R/model_persistence_calculation.R

@@ -32,9 +32,9 @@ sites <- read_csv(
       plot = "f",
       site = "f",
       sand_ratio = "f",
-      substrate_depth = "f",
+      substrate_depth = col_factor(levels = c("30", "15")),
       target_type = col_factor(levels = c(
-        "dry_grassland", "hay_meadow"
+        "hay_meadow", "dry_grassland"
       )),
       seed_density = "f",
       exposition = col_factor(levels = c(
@@ -71,31 +71,41 @@ sites <- read_csv(
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = sand_ratio)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Sand ratio [vol%] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Sand ratio [vol%]")
 plot2 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = substrate_depth)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Substrate depth [cm] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Substrate depth [cm]")
 plot3 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = target_type)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Target type (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Target type")
 plot4 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = seed_density)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Seed density [g/m²] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Seed density [g/m²]")
 (plot1 + plot2) / (plot3 + plot4)
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = exposition)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Exposition (Data of 2021)")
[…]

### 2022-11-17 R/model_persistence_check.R

@@ -249,13 +249,15 @@ mcmc_intervals(
   prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 mcmc_intervals(
   posterior2,
   prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 
 
 ### b Effect sizes ------------------------------------------------------------

### 2022-11-17 R/model_recovery_time_calculation.R

@@ -24,21 +24,24 @@ library(brms)
 rm(list = ls())
 
 ### Load data ###
-sites <- read_csv(here("data", "processed", "data_processed_sites_nmds.csv"),
-                  col_names = TRUE, na = c("na", "NA", ""),
-                  col_types = cols(
-                    .default = "?",
-                    id = "f",
-                    plot = "f",
-                    site = "f",
-                    exposition = col_factor(levels = c("north", "south",
-                                                       "other")),
-                    sand_ratio = "f",
-                    substrate_depth = col_factor(levels = c("30", "15")),
-                    target_type = col_factor(levels = c("dry_grassland",
-                                                        "hay_meadow", "other")),
-                    seed_density = "f"
-                    )) %>%
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites_nmds.csv"),
+  col_names = TRUE, na = c("na", "NA", ""),
+  col_types = cols(
+    .default = "?",
+    id = "f",
+    plot = "f",
+    site = "f",
+    exposition = col_factor(levels = c("north", "south",
+                                       "other")),
+    sand_ratio = "f",
+    substrate_depth = col_factor(levels = c("30", "15")),
+    target_type = col_factor(
+      levels = c("hay_meadow", "dry_grassland", "other")
+      ),
+    seed_density = "f"
+    )
+  ) %>%
   filter(reference == "2018" | reference == "2019" | reference == "2020" |
            reference == "2021") %>%
   mutate(
@@ -66,30 +69,36 @@ rm(list = setdiff(ls(), c("sites")))
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = sand_ratio)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Sand ratio [vol%] (Data of 2021)")
+  facet_grid(~ survey_year_fct) +
+  labs(title = "Sand ratio [vol%]")
 plot2 <- ggplot(sites %>% filter(survey_year == 2021),
                 aes(y = n, x = substrate_depth)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Substrate depth [cm] (Data of 2021)")
[…]

### 2022-11-17 R/model_recovery_time_check.R

@@ -245,13 +245,15 @@ mcmc_intervals(
   prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 mcmc_intervals(
   posterior2,
   prob = 0.66,
   prob_outer = 0.95,
   point_est = "mean"
-)
+  ) +
+  theme_classic()
 
 
 ### b Effect sizes ------------------------------------------------------------

### 2022-11-17 R/show_figure_3_fcs.R

@@ -44,8 +44,7 @@ sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
   mutate(
     n = fcs_target,
     survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year_fct, botanist, sep = "_"),
-    botanist_year = str_replace_all(botanist_year, " ", "_")
+    botanist_year = str_c(survey_year_fct, botanist, sep = " "),
   ) %>%
   select(
     id, plot, site, botanist_year, exposition, sand_ratio, substrate_depth,
@@ -53,10 +52,10 @@ sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
   )
 
 ### * Model ####
-load(file = here("outputs", "models", "model_fcs_3.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2.Rdata"))
 
 model <- sites %>%
-  add_epred_draws(m3, allow_new_levels = TRUE)
+  add_epred_draws(m2, allow_new_levels = TRUE)
 
 ### * Functions ####
 theme_mb <- function() {
@@ -114,7 +113,7 @@ theme_mb <- function() {
          "2018" = "2018", "2019" = "2019", "2020" = "2020", "2021" = "2021")
      )
    ) +
-   scale_y_continuous(limits = c(-2.8, 1.9), breaks = seq(-100, 400, 1)) +
+   scale_y_continuous(limits = c(-2.8, 2.0), breaks = seq(-100, 400, 1)) +
    scale_color_manual(breaks = c("hay_meadow", "dry_grassland"),
                       labels = c("Hay meadow", "Dry grassland"),
                       values = c("#00BFC4", "#F8766D")) +
@@ -139,28 +138,27 @@ ggsave(here("outputs", "figures",
 
 ## 2 Coefficients #############################################################
 
-m3 %>%
+m2 %>%
   gather_draws(
-    b_sand_ratio25, b_sand_ratio50, b_substrate_depth30,
-    b_target_typehay_meadow, b_seed_density8,
-    b_expositionsouth, b_survey_year_fct2019,
-    b_survey_year_fct2020, b_survey_year_fct2021
+    b_sand_ratio25, b_sand_ratio50, b_substrate_depth15,
+    b_target_typedry_grassland, b_seed_density8,
+    b_expositionsouth,
   ) %>%
   mutate(
     .variable = as.factor(.variable),
[…]

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@
 
-```{r}
+```{r echo = FALSE}
 sites %>% group_by(exposition) %>% count(site)
@@
 
-##### LOO Leave one out
+##### LOO (Leave one out)
 

### 2022-11-18 R/model_persistence_markdown.Rmd
Update

@@
 
-##### LOO-PIT: Leave one out probability integral transform checks
+##### LOO (Leave one out)
+
+```{r}
+loo1
+loo2
+plot(loo1)
+plot(loo2)
+```
+
+Leave one out probability integral transform
 

### 2022-11-18 R/model_fcs_calculation.R

@@ -298,4 +298,4 @@ save(m_full, file = here("outputs", "models", "model_fcs_full.Rdata"))
 save(m1, file = here("outputs", "models", "model_fcs_1.Rdata"))
 save(m2, file = here("outputs", "models", "model_fcs_2.Rdata"))
 save(m3, file = here("outputs", "models", "model_fcs_3.Rdata"))
-save(m3_flat, file = here("outputs", "models", "model_fcs_3_flat.Rdata"))
+save(m2_flat, file = here("outputs", "models", "model_fcs_2_flat.Rdata"))

### 2022-11-18 R/model_recovery_time_calculation.R

@@ -273,11 +273,12 @@ m1_flat <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
                cores = parallel::detectCores(),
                seed = seed)
 
-### * Save ####
+
+### c Save ---------------------------------------------------------------------
 
 save(m_simple, file = here("outputs", "models", "model_recovery_simple.Rdata"))
 save(m_full, file = here("outputs", "models", "model_recovery_full.Rdata"))
 save(m1, file = here("outputs", "models", "model_recovery_1.Rdata"))
 save(m2, file = here("outputs", "models", "model_recovery_2.Rdata"))
 save(m3, file = here("outputs", "models", "model_recovery_3.Rdata"))
-save(m3_flat, file = here("outputs", "models", "model_recovery_3_flat.Rdata"))
+save(m1_flat, file = here("outputs", "models", "model_recovery_1_flat.Rdata"))

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@
 ```{r}
-sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
+sites <- read_csv(
+  here("data", "processed", "data_processed_sites.csv"),
   col_names = TRUE, na = c("na", "NA", ""), col_types =
@@
       seed_density = "f",
-                      exposition = col_factor(levels = c(
-                        "north", "south"
-                      )),
+      exposition = col_factor(levels = c("north", "south")),
       survey_year = "c"
-                    )) %>%
+      )
+  ) %>%
   ### Exclude data of seed mixtures

### 2022-11-18 R/model_fcs_calculation.R

@@ -33,13 +33,9 @@ sites <- read_csv(
       site = "f",
       sand_ratio = "f",
       substrate_depth = col_factor(levels = c("30", "15")),
-      target_type = col_factor(levels = c(
-        "hay_meadow", "dry_grassland"
-      )),
+      target_type = col_factor(levels = c("hay_meadow", "dry_grassland")),
       seed_density = "f",
-      exposition = col_factor(levels = c(
-        "north", "south"
-      )),
+      exposition = col_factor(levels = c("north", "south")),
       survey_year = "c"
     )
   ) %>%
@@ -179,116 +175,123 @@ priors <- c(
   set_prior("cauchy(0, 1)", class = "sigma")
 )
 ### Models ###
-m_simple <- brm(n ~ sand_ratio + target_type + exposition + survey_year_fct +
-                  substrate_depth + seed_density +
-                  botanist_year +
-                  (1 | site/plot),
-                data = sites, 
-                family = gaussian("identity"),
-                prior = priors,
-                chains = chains,
-                iter = iter,
-                thin = thin,
-                control = list(max_treedepth = 13),
-                warmup = warmup,
-                save_pars = save_pars(all = TRUE),
-                cores = parallel::detectCores(),
-                seed = seed)
+m_simple <- brm(
+  n ~ sand_ratio + target_type + exposition + survey_year_fct +
+    substrate_depth + seed_density +
+    botanist_year + (1 | site/plot),
+  data = sites, 
+  family = gaussian("identity"),
+  prior = priors,
+  chains = chains,
+  iter = iter,
+  thin = thin,
+  control = list(max_treedepth = 13),
+  warmup = warmup,
+  save_pars = save_pars(all = TRUE),
+  cores = parallel::detectCores(),
+  seed = seed
+)
 
-m_full <- brm(n ~ sand_ratio * target_type * exposition * survey_year_fct +
-                substrate_depth * seed_density +
-                substrate_depth:exposition +
-                seed_density:exposition +
-                substrate_depth:survey_year_fct +
-                seed_density:survey_year_fct +
-                substrate_depth:exposition:survey_year_fct +
-                seed_density:exposition:survey_year_fct +
-                botanist_year +
-                (1 | site/plot),
-              data = sites, 
-              family = gaussian("identity"),
-              prior = priors,
-              chains = chains,
[…]

### 2022-11-18 R/model_fcs_check.R

@@ -225,8 +225,10 @@ p1 / p2
 p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
 p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth,
+                       binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth,
+                       binwidth = 0.001)
 p1 / p2
 #### LOO-PIT plots
 p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))

### 2022-11-18 R/model_persistence_calculation.R

@@ -26,23 +26,19 @@ rm(list = ls())
 ### Load data ###
 sites <- read_csv(
   here("data", "processed", "data_processed_sites_temporal.csv"),
-  col_names = TRUE, na = c("na", "NA", ""), col_types =
-    cols(
-      .default = "?",
-      plot = "f",
-      site = "f",
-      sand_ratio = "f",
-      substrate_depth = col_factor(levels = c("30", "15")),
-      target_type = col_factor(levels = c(
-        "hay_meadow", "dry_grassland"
-      )),
-      seed_density = "f",
-      exposition = col_factor(levels = c(
-        "north", "south"
-      )),
-      survey_year = "c"
-    )
-  ) %>%
+  col_names = TRUE, na = c("na", "NA", ""),
+  col_types = cols(
+    .default = "?",
+    plot = "f",
+    site = "f",
+    sand_ratio = "f",
+    substrate_depth = col_factor(levels = c("30", "15")),
+    target_type = col_factor(levels = c("hay_meadow", "dry_grassland")),
+    seed_density = "f",
+    exposition = col_factor(levels = c("north", "south")),
+    survey_year = "c"
+  )
+) %>%
   ### Exclude data of seed mixtures
   filter(presabu == "presence") %>%
   mutate(
@@ -180,19 +176,21 @@ priors <- c(
   set_prior("cauchy(0, 10)", class = "sigma")
 )
 ### Models ###
-m_simple <- brm(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-                  seed_density + substrate_depth +
-                  (1 | site/plot),
-                data = sites, 
-                family = gaussian("identity"),
-                prior = priors,
-                chains = chains,
-                iter = iter,
-                thin = thin,
-                warmup = floor(iter / 2),
-                save_pars = save_pars(all = TRUE),
-                cores = parallel::detectCores(),
-                seed = 121)
+m_simple <- brm(
+  n ~ target_type + exposition + sand_ratio + survey_year_fct +
+    seed_density + substrate_depth +
+    (1 | site/plot),
+  data = sites, 
+  family = gaussian("identity"),
+  prior = priors,
+  chains = chains,
+  iter = iter,
+  thin = thin,
+  warmup = floor(iter / 2),
+  save_pars = save_pars(all = TRUE),
+  cores = parallel::detectCores(),
+  seed = seed
+)
 
 m_full <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct +
                      seed_density + substrate_depth)^3 +

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@
 
+Possible prior distributions
+
+```{r}
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)) +
+  expand_limits(y = 0) + ggtitle("Normal distribution")
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
+ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  expand_limits(y = 0) + ggtitle(expression(Student ~ italic(t)"-distribution"))
+```
+
 Specifications for the models
@@
 seed = 123
+warmup = floor(iter / 2)
 priors <- c(
@@
   set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "expositionsouth"),
   set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),

### 2022-11-18 R/model_fcs_calculation.R

@@ -144,16 +144,15 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
             (1 | site/plot) + (1 | botanist_year),
           data = sites)
-### Examples of normal, cauchy and student t distributions
 ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle("Normal distribution")
 ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
 ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle(expression(Student ~ italic(t)"-distribution"))
 
 ### Model specifications ###
 iter = 10000

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0) + ggtitle(expression(Student ~ italic(t)"-distribution"))
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
 ```

### 2022-11-18 R/model_persistence_markdown.Rmd
Update

@@
 ### Models
+
+Possible prior distributions
+
+```{r}
+ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
+  expand_limits(y = 0) + ggtitle("Normal distribution")
+ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
+ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
+```
 

### 2022-11-18 R/model_recovery_time_markdown.Rmd
Update

@@
 ### Models
+
+Possible prior distributions
+
+```{r}
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
+  expand_limits(y = 0) + ggtitle("Normal distribution")
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
+ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
+```
 

### 2022-11-18 R/model_fcs_calculation.R

@@ -152,7 +152,7 @@ ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
   expand_limits(y = 0) + ggtitle("Cauchy distribution")
 ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0) + ggtitle(expression(Student ~ italic(t)"-distribution"))
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
 
 ### Model specifications ###
 iter = 10000

### 2022-11-18 R/model_persistence_calculation.R

@@ -143,16 +143,15 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
             (1 | site/plot),
           data = sites)
-### Examples of normal, cauchy and student t distributions
 ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle("Normal distribution")
 ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
 ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
 
 ### Model specifications ###
 iter = 10000

### 2022-11-18 R/model_recovery_time_calculation.R

@@ -145,16 +145,15 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
             (1 | site/plot) + (1 | botanist_year),
           data = sites)
-### Examples of normal, cauchy and student t distributions
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle("Normal distribution")
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
 ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0)
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
 
 ### Model specifications ###
 iter = 10000

### 2022-11-18 R/model_fcs_calculation.R
Update

@@ -3,7 +3,7 @@
 # Model building
 
 # Markus Bauer
-# 2022-11-10
+# 2022-11-18
 
 
 

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@
 ```
+
+FCS sensu Helm et al. (2015) https://doi.org/10.1111/ddi.12285
 

### 2022-11-18 R/model_fcs_check.R

@@ -254,7 +254,7 @@ bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
-draws2
+draws1
 mcmc_intervals(
   posterior1,
   prob = 0.66,

### 2022-11-21 R/model_fcs_calculation.R
Update

@@ -282,7 +282,7 @@ m2_flat <- brm(
     set_prior("cauchy(0, 1)", class = "sigma")
   ),
   chains = chains,
-  iter = iter,
+  iter = 1000,
   thin = thin,
   control = list(max_treedepth = 13),
   warmup = warmup,

### 2022-11-21 R/model_fcs_check.R

@@ -178,8 +178,10 @@ mcmc_scatter(m_1, np = hmc_diagnostics1, size = 1,
              pars = c("b_survey_year_fct2020", "b_survey_year_fct2019"))
 mcmc_scatter(m_2, np = hmc_diagnostics2, size = 1,
              pars = c("b_survey_year_fct2020", "b_survey_year_fct2019"))
-mcmc_parcoord(posterior1, np = hmc_diagnostics1)
-mcmc_parcoord(posterior2, np = hmc_diagnostics2)
+mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
+  theme(axis.text.x = element_text(angle = 90))
+mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
+  theme(axis.text.x = element_text(angle = 90))
 
 #### * Posterior predictive check ####
 #### Kernel density

### 2022-11-21 R/model_recovery_markdown.Rmd
Update

--- 2022-11-18 R/model_recovery_time_markdown.Rmd
@@
 ---
-title: "Recover time to reference state: <br> Analysis of Bauer et al. (unpublished) Field experiment"
+title: "Recovery completeness: <br> Analysis of Bauer et al. (unpublished) Field experiment"
 author: "Markus Bauer <br>"
@@
 ```
+
+Recovery completeness sensu Rydgren et al. (2018) https://doi.org/10.1111/1365-2664.13526
 
@@
     botanist_year = str_c(survey_year, botanist, sep = " "),
-    n = recovery_time
+    n = recovery_completeness
     )
@@
 m_2 <- m3
+```
+
+```{r echo = FALSE}
 m_1$formula
@@
 
-Conditional R² values
+Conditional _R_² values
 
@@
 
-Marginal R² values
+Marginal _R_² values
 
@@
 
-Priors and conditional and marignal R²
+Priors and conditional and marignal _R_²
 

### 2022-11-21 R/_prepare_data_vegetation.R

@@ -952,7 +952,7 @@ sites_nmds <- sites_nmds %>%
         )
       )
     ),
-    recovery_time = NMDS1 - mean_reference
+    recovery_completeness = NMDS1 - mean_reference
   )
 
 rm(list = setdiff(ls(), c(

### 2022-11-21 R/model_recovery_calculation.R

@@ -1,5 +1,5 @@
 # Dike grassland field experiment
-# Recovery time ####
+# Recovery completeness ####
 # Model building
 
 # Markus Bauer
@@ -47,7 +47,7 @@ sites <- read_csv(
     survey_year_fct = factor(survey_year),
     survey_year = as.numeric(survey_year),
     botanist_year = str_c(survey_year, botanist, sep = " "),
-    n = recovery_time
+    n = recovery_completeness
     )
 
 rm(list = setdiff(ls(), c("sites")))

### 2022-11-21 R/model_recovery_check.R

@@ -1,5 +1,5 @@
 # Dike grassland field experiment
-# Recover time ####
+# Recover completeness ####
 # Model check
 
 # Markus Bauer
@@ -51,7 +51,7 @@ sites <- read_csv(
     survey_year_fct = factor(survey_year),
     survey_year = as.numeric(survey_year),
     botanist_year = str_c(survey_year, botanist, sep = " "),
-    n = recovery_time
+    n = recovery_completeness
   )
 
 ### Load models ###
@@ -273,4 +273,4 @@ mcmc_intervals(
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                   exposition | survey_year_fct, type = "response"))
 
-write.csv(draws1, here("outputs", "statistics", "table_recovery_time.csv"))
+write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))

### 2022-12-01 R/model_fcs_check.Rmd
Update

--- 2022-11-18 R/model_fcs_markdown.Rmd
@@
 library(emmeans)
-
 ```
@@
 
+Model caluclations
+
+```{r}
+load(file = here("outputs", "models", "model_fcs_2.Rdata"))
+load(file = here("outputs", "models", "model_fcs_full.Rdata"))
+```
+
+### Model comparison
+
+```{r}
+m_1 <- m2
+m_2 <- m_full
+```
+
+Model forumlas for m_1 and m_2
+
+```{r tidy = FALSE}
+m_1$formula
+m_2$formula
+```
+
 Possible prior distributions
@@
 
-Specifications for the models
+Prior summary
 
 ```{r}
-iter = 10000
-chains = 4
-thin = 2
-seed = 123
-warmup = floor(iter / 2)
-priors <- c(
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
-  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
-  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
-  set_prior("cauchy(0, 1)", class = "sigma")
-)
+prior_summary(m_1, all = FALSE)
 ```
 
-Model caluclations
-
-```{r}
-load(file = here("outputs", "models", "model_fcs_2.Rdata"))
-load(file = here("outputs", "models", "model_fcs_full.Rdata"))
-```
-
-### Model comparison
-
-```{r}
-m_1 <- m2
-m_2 <- m_full
-m_1$formula
-m_2$formula
-```
-
-Conditional italic(R)² values
+Conditional <i>R</i>² values
 
@@
 
-Marginal italic(R)² values
+Marginal <i>R</i>² values
 
@@
 
-#### Samling efficency/effectiveness (Rhat and EFF)
+#### Sampling efficency/effectiveness (Rhat and EFF)
 
@@
 
-Prior summary
-
-```{r}
-prior_summary(m_1, all = FALSE)
-```
-
-Conditional and marignal italic(R)²
+Conditional and marignal <i>R</i>²
 
@@
 
-Posteriors
+Posteriors of chosen model
 
@@
   theme_classic()
+```
+
+Posteriors of second model:
+
+```{r}
 mcmc_intervals(
@@
 
+Just, to get exact values if necessary, which is not possible from the figure
+
 ```{r}
@@
 ```
+
+The system for these calculations
+
+```{r}
+sessionInfo()
+```
+
+```{r echo = FALSE}
+write.csv(draws1, here("outputs", "statistics", "table_fcs_test.csv"))
+```

### 2022-12-01 R/model_fcs_check.R

@@ -1,281 +1,0 @@
-# Dike grassland field experiment
-# Favourable conservation status ####
-# Model check
-
-# Markus Bauer
-# 2022-11-15
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(brms)
-library(DHARMa)
-#remotes::install_github("Pakillo/DHARMa.helpers")
-library(DHARMa.helpers)
-library(bayesplot)
-library(loo)
-library(tidybayes)
-library(patchwork)
-library(emmeans)
-
-### Start ###
-rm(list = ls())
-
-### Load data ###
-sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
-                  col_names = TRUE, na = c("na", "NA", ""), col_types =
-                    cols(
-                      .default = "?",
-                      plot = "f",
-                      site = "f",
-                      sand_ratio = "f",
-                      substrate_depth = col_factor(levels = c("30", "15")),
-                      target_type = col_factor(levels = c(
-                        "hay_meadow", "dry_grassland"
-                      )),
-                      seed_density = "f",
-                      exposition = col_factor(levels = c(
-                        "north", "south"
-                      )),
-                      survey_year = "c"
-                    )) %>%
-  ### Exclude data of seed mixtures
-  filter(survey_year != "seeded") %>%
-  mutate(
-    survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
-    botanist_year = factor(botanist_year),
-    n = fcs_target,
-    id = factor(id)
-    ) %>%
-  select(
-    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
[…]

### 2022-12-01 R/model_persistence_check.R

@@ -1,274 +1,0 @@
-# Dike grassland field experiment
-# Persistence ####
-# Model check
-
-# Markus Bauer
-# 2022-11-15
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(brms)
-library(DHARMa)
-#remotes::install_github("Pakillo/DHARMa.helpers")
-library(DHARMa.helpers)
-library(bayesplot)
-library(loo)
-library(tidybayes)
-library(emmeans)
-
-### Start ###
-rm(list = ls())
-
-### Load data ###
-sites <- read_csv(
-  here("data", "processed", "data_processed_sites_temporal.csv"),
-  col_names = TRUE, na = c("na", "NA", ""),
-  col_types = cols(
-      .default = "?",
-      plot = "f",
-      site = "f",
-      sand_ratio = "f",
-      substrate_depth = "f",
-      target_type = col_factor(levels = c("dry_grassland", "hay_meadow")),
-      seed_density = "f",
-      exposition = col_factor(levels = c("north", "south")),
-      survey_year = "c"
-    )
-) %>%
-  ### Exclude data of seed mixtures and scale
-  filter(presabu == "presence") %>%
-  mutate(
-    survey_year_fct = factor(survey_year),
-    id = factor(id),
-    n = persistence
-  ) %>%
-  select(
-    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, survey_year, n
-  )
-load(file = here("outputs", "models", "model_persistence_1.Rdata"))
-load(file = here("outputs", "models", "model_persistence_2.Rdata"))
-load(file = here("outputs", "models", "model_persistence_3.Rdata"))
-load(file = here("outputs", "models", "model_persistence_simple.Rdata"))
-load(file = here("outputs", "models", "model_persistence_full.Rdata"))
[…]

### 2022-12-01 R/model_recovery_check.R

@@ -1,276 +1,0 @@
-# Dike grassland field experiment
-# Recover completeness ####
-# Model check
-
-# Markus Bauer
-# 2022-11-15
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(ggbeeswarm)
-library(brms)
-library(DHARMa)
-library(bayesplot)
-library(loo)
-library(tidybayes)
-library(emmeans)
-
-### Start ###
-rm(list = ls())
-
-### Load data ###
-sites <- read_csv(
-  here("data", "processed", "data_processed_sites_nmds.csv"),
-  col_names = TRUE, na = c("na", "NA", ""),
-  col_types = cols(
-    .default = "?",
-    id = "f",
-    plot = "f",
-    site = "f",
-    exposition = col_factor(levels = c("north", "south", "other")),
-    sand_ratio = "f",
-    substrate_depth = col_factor(levels = c("30", "15")),
-    target_type = col_factor(levels = c(
-      "dry_grassland", "hay_meadow", "other"
-      )),
-    seed_density = "f"
-  )
-) %>%
-  filter(reference == "2018" | reference == "2019" | reference == "2020" |
-           reference == "2021") %>%
-  mutate(
-    survey_year_fct = factor(survey_year),
-    survey_year = as.numeric(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
-    n = recovery_completeness
-  )
-
-### Load models ###
-base::load(file = here("outputs", "models", "model_recovery_simple.Rdata"))
-base::load(file = here("outputs", "models", "model_recovery_full.Rdata"))
-base::load(file = here("outputs", "models", "model_recovery_1.Rdata"))
-base::load(file = here("outputs", "models", "model_recovery_2.Rdata"))
-base::load(file = here("outputs", "models", "model_recovery_3.Rdata"))
[…]

### 2022-12-02 R/model_fcs_check.Rmd
Update

@@
 title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
-author: "Markus Bauer <br>"
+author: "Markus Bauer^* <br>"
 date: "`r format(Sys.time(), '%Y-%m-%d')`"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(
+  echo = TRUE,
+  fig.width = 12,
+  fig.height = 12,
+  dpi = 600
+  )
 ```
 
-FCS sensu Helm et al. (2015) https://doi.org/10.1111/ddi.12285
+Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
+
+* Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
+<br>
+[ORCiD ID: 0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
+<br>
+[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
+<br>
+[GitHub: markus1bauer](https://github.com/markus1bauer)
+
+Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
 
@@
 
-```{r message = FALSE, tidy = TRUE}
+```{r message = FALSE}
 library(here)
@@
 
-```{r}
+```{r collapse = TRUE}
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
 load(file = here("outputs", "models", "model_fcs_full.Rdata"))
-```
-
-### Model comparison
-
-```{r}
 m_1 <- m2
 m_2 <- m_full
-```
-
-Model forumlas for m_1 and m_2
-
-```{r tidy = FALSE}
 m_1$formula
@@
 
-Possible prior distributions
+### Priors
+
+#### Possible prior distributions
 
@@
 ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)) +
+  stat_function(
+    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)
+    ) +
   expand_limits(y = 0) + ggtitle("Normal distribution")
 ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  stat_function(
+    fun = dcauchy, n = 101, args = list(location = 0, scale = 1)
+    ) +
   expand_limits(y = 0) + ggtitle("Cauchy distribution")
 ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  stat_function(
+    fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)
+    ) +
   expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
@@
 
-Prior summary
+#### Prior summary
 
@@
 
-```{r}
+```{r collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
-```{r}
+```{r collapse = TRUE}
 DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
@@
 
-#### Sampling efficency/effectiveness (Rhat and EFF)
+#### Sampling efficency and effectiveness
 
-```{r}
+Rhat
+
+```{r collapse = TRUE}
 range(draws1$rhat)
 range(draws2$rhat)
+```
+
+Effective sampling size (ESS)
+
+```{r collapse = TRUE}
 range(draws1$ess_bulk)
@@
 
-The system for these calculations
+```{r echo = FALSE}
+write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
+```
 
-```{r}
+## Session info
+
+```{r echo = FALSE}
 sessionInfo()
 ```
-
-```{r echo = FALSE}
-write.csv(draws1, here("outputs", "statistics", "table_fcs_test.csv"))
-```

### 2022-12-02 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 date: "`r format(Sys.time(), '%Y-%m-%d')`"
-output: github_document
+output:
+  github_document:
+    toc: true
+    toc_depth: 2
+    dev: jpeg
+    fig_width: 12
+    fig_height: 12
 ---
@@
 knitr::opts_chunk$set(
-  echo = TRUE,
-  fig.width = 12,
-  fig.height = 12,
-  dpi = 600
+  echo = TRUE
   )

### 2022-12-02 R/model_fcs_check.Rmd
Update

@@
 title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
-author: "Markus Bauer^* <br>"
-date: "`r format(Sys.time(), '%Y-%m-%d')`"
+author: "<b>Markus Bauer*</b> <br>"
+date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
 output:
@@
     toc: true
-    toc_depth: 2
+    toc_depth: 3
     dev: jpeg
     fig_width: 12
-    fig_height: 12
+    fig_height: 7
 ---
@@
 
+```{r, include=FALSE}
+knitr::knit_hooks$set(output = function(x, options){
+  if(!is.null(options$max_height)){
+    paste('<pre style = "max-height:', options$max_height, '; float: left; width: 910px; overflow-y: auto;">', x, "</pre>", sep = "")
+  }else{
+    x
+  }
+
+})
+```
+
 Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
 
-* Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
+<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
 <br>
-[ORCiD ID: 0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
+ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
 <br>
@@
 <br>
-[GitHub: markus1bauer](https://github.com/markus1bauer)
+GitHub: [markus1bauer](https://github.com/markus1bauer)
 
@@
 m_2$formula
+m_1$family
+m_2$family
 ```
@@
 ```{r collapse = TRUE}
-range(draws1$rhat)
-range(draws2$rhat)
+mcmc_rhat(draws1$rhat)
+mcmc_rhat(draws2$rhat)
 ```
@@
 ```{r collapse = TRUE}
-range(draws1$ess_bulk)
-range(draws2$ess_bulk)
-range(draws1$ess_tail)
-range(draws2$ess_tail)
+mcmc_neff(neff_ratio(m_1))
+mcmc_neff(neff_ratio(m_2))
 ```
@@
 
-```{r}
+```{r max_height = '100px'}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 
-## Session info
+# Session info
 
-```{r echo = FALSE}
+```{r echo = FALSE, max_height = "100px"}
 sessionInfo()

### 2022-12-02 R/model_fcs_check.Rmd
Update FCS max.height mess up

@@
     fig_width: 12
-    fig_height: 7
+    fig_height: 6
 ---
@@
   )
-```
-
-```{r, include=FALSE}
-knitr::knit_hooks$set(output = function(x, options){
-  if(!is.null(options$max_height)){
-    paste('<pre style = "max-height:', options$max_height, '; float: left; width: 910px; overflow-y: auto;">', x, "</pre>", sep = "")
-  }else{
-    x
-  }
-
-})
 ```
@@
 
-```{r max_height = '100px'}
+```{r max_height = "1000px"}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 
-```{r echo = FALSE, max_height = "100px"}
+```{r echo = FALSE, max_height = "500px"}
 sessionInfo()

### 2022-12-02 R/model_fcs_check.Rmd
Update FCS (image size)

@@
 ---
-title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
+title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
 author: "<b>Markus Bauer*</b> <br>"
@@
     dev: jpeg
-    fig_width: 12
-    fig_height: 6
+    fig_width: 7
+    fig_height: 5
 ---
@@
 m_2 <- m_full
+```
+
+```{r collapse = TRUE}
 m_1$formula
 m_2$formula
+```
+
+```{r collapse = TRUE}
 m_1$family

### 2022-12-02 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
     toc_depth: 3
-    dev: jpeg
+    dev: png
     fig_width: 7
     fig_height: 5
+    df_print: tibble
 ---
@@
 
-## Model building
-
-### Models
-
-Model caluclations
+## Models
 
@@
 
-### Model check
+## Model check
 
-#### DHARMa
+### DHARMa
 
@@
 
-#### Preparation
+### Preparation
 
@@
 
-#### Sampling efficency and effectiveness
+### Sampling efficency and effectiveness
 
-Rhat
+#### Rhat
 
@@
 
-Effective sampling size (ESS)
+#### Effective sampling size (ESS)
 
@@
 
-#### MCMC diagnostics
+### MCMC diagnostics
 
@@
 
-#### Posterior predictive check
+### Posterior predictive check
 
-##### Kernel density
+#### Kernel density
 
@@
 
-##### Histograms of statistics skew
+#### Histograms of statistics skew
 
@@
 
-##### LOO (Leave one out)
+#### LOO (Leave one out)
 
@@
 
-#### Autocorrelation check
+### Autocorrelation check
 

### 2022-12-05 R/model_persistence_check.Rmd
Update
Create model_persistence_check.Rmd

--- 2022-11-18 R/model_persistence_markdown.Rmd
@@
 ---
-title: "Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment"
-author: "Markus Bauer <br>"
-date: "`r format(Sys.time(), '%Y-%m-%d')`"
-output: github_document
+title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence"
+author: "<b>Markus Bauer*</b> <br>"
+date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
+output:
+  github_document:
+    toc: true
+    toc_depth: 3
+    dev: png
+    fig_width: 7
+    fig_height: 5
+    df_print: tibble
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(
+  echo = TRUE
+  )
 ```
+
+Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
+
+<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
+<br>
+ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
+<br>
+[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
+<br>
+GitHub: [markus1bauer](https://github.com/markus1bauer)
+
+Persistence sensu Wilsey (2021) Restor Ecol [DOI: 10.1111/rec.13132](https://doi.org/10.1111/rec.13132)
 
@@
   here("data", "processed", "data_processed_sites_temporal.csv"),
-  col_names = TRUE, na = c("na", "NA", ""), col_types =
-    cols(
+  col_names = TRUE, na = c("na", "NA", ""),
+  col_types = cols(
     .default = "?",
@@
     substrate_depth = col_factor(levels = c("30", "15")),
-      target_type = col_factor(levels = c(
-        "hay_meadow", "dry_grassland"
-      )),
+    target_type = col_factor(levels = c("hay_meadow", "dry_grassland")),
     seed_density = "f",
-      exposition = col_factor(levels = c(
-        "north", "south"
-      )),
+    exposition = col_factor(levels = c("north", "south")),
     survey_year = "c"
@@
     survey_year_fct = factor(survey_year),
+    botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
+    botanist_year = factor(botanist_year),
     id = factor(id),
@@
     id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, survey_year, n
+    seed_density, survey_year_fct, survey_year, botanist_year, n
   )
@@
 
-## Model building
+## Models
 
-### Models
-
-Specifications for the models
-
-```{r}
-iter = 10000
-chains = 4
-thin = 2
-priors <- c(
-  set_prior("normal(0, 20)", class = "b"),
-  set_prior("normal(-2.5, 20)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(-5, 20)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(5, 20)", class = "b", coef = "expositionsouth"),
-  set_prior("normal(-2.5, 20)", class = "b", coef = "survey_year_fct2019"),
-  set_prior("normal(-5, 20)", class = "b", coef = "survey_year_fct2020"),
-  set_prior("normal(-7.5, 20)", class = "b", coef = "survey_year_fct2021"),
-  set_prior("cauchy(0, 10)", class = "sigma")
-)
+```{r collapse = TRUE}
+load(file = here("outputs", "models", "model_persistence_1.Rdata"))
+load(file = here("outputs", "models", "model_persistence_full.Rdata"))
+m_1 <- m1
+m_2 <- m_full
 ```
 
-Model caluclations
-
-```{r}
-load(file = here("outputs", "models", "model_persistence_1.Rdata"))
-load(file = here("outputs", "models", "model_persistence_3.Rdata"))
-```
-
-### Model comparison
-
-```{r}
-m_1 <- m1
-m_2 <- m3
+```{r collapse = TRUE}
 m_1$formula
@@
 
-Conditional R² values
+```{r collapse = TRUE}
+m_1$family
+m_2$family
+```
+
+### Priors
+
+#### Possible prior distributions
 
 ```{r}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot))
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot),
+          data = sites)
+ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
+  expand_limits(y = 0) + ggtitle("Normal distribution")
+ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")
+ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
+  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
 ```
 
-Marginal R² values
+#### Prior summary
 
 ```{r}
+prior_summary(m_1, all = FALSE)
+```
+
+Conditional <i>R</i>² values
+
+```{r collapse = TRUE}
+bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
+```
+
+Marginal <i>R</i>² values
+
+```{r collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
-### Model check
+## Model check
 
-#### DHARMa
+### DHARMa
 
-```{r}
+```{r collapse = TRUE}
 DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
@@
 
-#### Samling efficency/effectiveness (Rhat and EFF)
+### Sampling efficency and effectiveness
 
-```{r}
-range(draws1$rhat)
-range(draws2$rhat)
-range(draws1$ess_bulk)
-range(draws2$ess_bulk)
-range(draws1$ess_tail)
-range(draws2$ess_tail)
+#### Rhat
+
+```{r collapse = TRUE}
+mcmc_rhat(draws1$rhat)
+mcmc_rhat(draws2$rhat)
 ```
 
-#### MCMC diagnostics
+#### Effective sampling size (ESS)
+
+```{r collapse = TRUE}
+mcmc_neff(neff_ratio(m_1))
+mcmc_neff(neff_ratio(m_2))
+```
+
+### MCMC diagnostics
 
@@
 
-Priors and conditional and marignal R²
+Conditional and marignal <i>R</i>²
 
-```{r}
-prior_summary(m_1, all = FALSE)
+```{r collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
   point_est = "mean"
-)
+  ) +
+  theme_classic()
+```
+
+Posteriors of second model:
+
+```{r}
 mcmc_intervals(
@@
 
-```{r}
+Just, to get exact values if necessary, which is not possible from the figure
+
+```{r max_height = "1000px"}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 ```
+
+```{r echo = FALSE}
+write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
+```
+
+# Session info
+
+```{r echo = FALSE, max_height = "500px"}
+sessionInfo()
+```

### 2022-12-05 R/model_persistence_check.Rmd
Update all persistence models

@@
     fig_height: 5
-    df_print: tibble
 ---
@@
 
-```{r collapse = TRUE}
-load(file = here("outputs", "models", "model_persistence_1.Rdata"))
+```{r collapse = TRUE, message = FALSE}
+load(file = here("outputs", "models", "model_persistence_2.Rdata"))
 load(file = here("outputs", "models", "model_persistence_full.Rdata"))
-m_1 <- m1
+m_1 <- m2
 m_2 <- m_full

### 2022-12-05 R/model_persistence_calculation.R

@@ -162,12 +162,12 @@ warmup = floor(iter / 2)
 priors <- c(
   set_prior("normal(0, 20)", class = "Intercept"),
   set_prior("normal(0, 20)", class = "b"),
-  set_prior("normal(-2.5, 20)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(-5, 20)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(5, 20)", class = "b", coef = "expositionsouth"),
-  set_prior("normal(-2.5, 20)", class = "b", coef = "survey_year_fct2019"),
-  set_prior("normal(-5, 20)", class = "b", coef = "survey_year_fct2020"),
-  set_prior("normal(-7.5, 20)", class = "b", coef = "survey_year_fct2021"),
+  set_prior("normal(2.5, 20)", class = "b", coef = "sand_ratio25"),
+  set_prior("normal(5, 20)", class = "b", coef = "sand_ratio50"),
+  set_prior("normal(-5, 20)", class = "b", coef = "expositionsouth"),
+  set_prior("normal(2.5, 20)", class = "b", coef = "survey_year_fct2019"),
+  set_prior("normal(5, 20)", class = "b", coef = "survey_year_fct2020"),
+  set_prior("normal(7.5, 20)", class = "b", coef = "survey_year_fct2021"),
   set_prior("cauchy(0, 10)", class = "sigma")
 )
 
@@ -310,5 +310,5 @@ save(m1, file = here("outputs", "models", "model_persistence_1.Rdata"))
 save(m2, file = here("outputs", "models", "model_persistence_2.Rdata"))
 save(m3, file = here("outputs", "models", "model_persistence_3.Rdata"))
 save(m2_flat, file = here(
-  "outputs", "models", "model_persistence_1_flat.Rdata"
+  "outputs", "models", "model_persistence_2_flat.Rdata"
   ))

### 2022-12-05 R/model_fcs_calculation.R
fcs comparison botanist_year vs botanist_year_exposition

@@ -43,7 +43,7 @@ sites <- read_csv(
   filter(survey_year != "seeded") %>%
   mutate(
     survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
     botanist_year = factor(botanist_year),
     n = fcs_target,
     id = factor(id)
@@ -231,7 +231,7 @@ m1 <- brm(
   seed = seed
 )
 
-m2 <- brm(
+m2_new <- brm(
   n ~ sand_ratio * target_type * exposition * survey_year_fct +
     substrate_depth + seed_density +
     substrate_depth:exposition +

### 2022-12-06 R/model_fcs_check.Rmd
Compare wider prior with narrwoer prior

@@
     survey_year_fct = factor(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
+    botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
     botanist_year = factor(botanist_year),
@@
 
-```{r collapse = TRUE}
+```{r collapse = TRUE, message = FALSE}
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
-load(file = here("outputs", "models", "model_fcs_full.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2_test.Rdata"))
+#load(file = here("outputs", "models", "model_fcs_full.Rdata"))
 m_1 <- m2
-m_2 <- m_full
+m_2 <- m2_test
+#m_2 <- m_full
 ```
@@
 ```{r}
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data = data.frame(x = c(-3, 3)), aes(x = x)) +
   stat_function(
-    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)
+    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 2)
     ) +
   expand_limits(y = 0) + ggtitle("Normal distribution")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data = data.frame(x = c(-3, 3)), aes(x = x)) +
   stat_function(
@@
   expand_limits(y = 0) + ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data.frame(x = c(-3, 3)), aes(x = x)) +
   stat_function(

### 2022-12-06 R/model_fcs_check.Rmd

@@
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
-load(file = here("outputs", "models", "model_fcs_2_test.Rdata"))
-#load(file = here("outputs", "models", "model_fcs_full.Rdata"))
+load(file = here("outputs", "models", "model_fcs_full.Rdata"))
 m_1 <- m2
-m_2 <- m2_test
-#m_2 <- m_full
+m_2 <- m_full
 ```
@@
 
-Just, to get exact values if necessary, which is not possible from the figure
+Effect sizes are presented just to get exact values of the means if necessary.
 
-```{r max_height = "1000px"}
+```{r}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 
-```{r echo = FALSE, max_height = "500px"}
+```{r echo = FALSE}
 sessionInfo()

### 2022-12-06 R/model_fcs_check.Rmd
Update markdowns

--- 2022-12-05 R/model_fcs_check.Rmd
@@
     fig_height: 5
+    df_print: tibble
 ---
@@
 
+Only here you have to modify the script to compare other models
+
 ```{r collapse = TRUE}
@@
 
-Conditional <i>R</i>² values
+### Coefficient of determination (<i>R</i>²)
+
+#### Conditional <i>R</i>² values
 
@@
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+         re_formula =  ~ (1 | site/plot)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
+         re_formula =  ~ (1 | site/plot))
 ```
 
-Marginal <i>R</i>² values
+#### Marginal <i>R</i>² values
 
@@
 ```{r}
-mcmc_trace(posterior1, np = hmc_diagnostics1)
-mcmc_trace(posterior2, np = hmc_diagnostics2)
+mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
+mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
            ))
-mcmc_parcoord(posterior1, np = hmc_diagnostics1)
-mcmc_parcoord(posterior2, np = hmc_diagnostics2)
+mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
+  theme(axis.text.x = element_text(angle = 90))
+mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
+  theme(axis.text.x = element_text(angle = 90))
 ```

### 2022-12-06 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd
Update markdowns

@@
 
+Only here you have to modify the script to compare other models
+
 ```{r collapse = TRUE, message = FALSE}
@@
 ```{r echo = FALSE}
-write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
+write.csv(draws1, here("outputs", "statistics", "table_persistence.csv"))
 ```

### 2022-12-06 R/model_recovery_check.Rmd
Update markdowns

--- 2022-12-06 R/model_persistence_check.Rmd
@@
 sites <- read_csv(
-  here("data", "processed", "data_processed_sites_temporal.csv"),
+  here("data", "processed", "data_processed_sites_nmds.csv"),
   col_names = TRUE, na = c("na", "NA", ""),
@@
     .default = "?",
+    id = "f",
     plot = "f",
     site = "f",
+    exposition = col_factor(levels = c("north", "south", "other")),
     sand_ratio = "f",
     substrate_depth = col_factor(levels = c("30", "15")),
-    target_type = col_factor(levels = c("hay_meadow", "dry_grassland")),
-    seed_density = "f",
-    exposition = col_factor(levels = c("north", "south")),
-    survey_year = "c"
+    target_type = col_factor(levels = c(
+      "hay_meadow", "dry_grassland", "other"
+      )),
+    seed_density = "f"
     )
   ) %>%
-  ### Exclude data of seed mixtures
-  filter(presabu == "presence") %>%
+  filter(reference == "2018" | reference == "2019" | reference == "2020" |
+           reference == "2021") %>%
   mutate(
     survey_year_fct = factor(survey_year),
+    survey_year = as.numeric(survey_year),
     botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
     botanist_year = factor(botanist_year),
-    id = factor(id),
-    n = persistence
-  ) %>%
-  select(
-    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
-    seed_density, survey_year_fct, survey_year, botanist_year, n
+    n = recovery_time
     )
@@
 ```{r collapse = TRUE, message = FALSE}
-load(file = here("outputs", "models", "model_persistence_2.Rdata"))
-load(file = here("outputs", "models", "model_persistence_full.Rdata"))
-m_1 <- m2
-m_2 <- m_full
+load(file = here("outputs", "models", "model_recovery_full.Rdata"))
+load(file = here("outputs", "models", "model_recovery_full_flat.Rdata"))
+m_1 <- m_full
+m_2 <- mfull_flat
 ```
@@
           data = sites)
-ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) +
   expand_limits(y = 0) + ggtitle("Normal distribution")
-ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) + ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
+ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
@@
 
-### Coefficient of determination (<i>R</i>²)
+### Coefficient of determination (<i>R</i>^2)
 
-#### Conditional <i>R</i>² values
+#### Conditional <i>R</i>^2 values
 
@@
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
 bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot))
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
 ```
 
-#### Marginal <i>R</i>² values
+#### Marginal <i>R</i>^2 values
 
@@
 
-Just, to get exact values if necessary, which is not possible from the figure
+Effect sizes just to get exact values of means etc. if necessary.
 
-```{r max_height = "1000px"}
+```{r}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 ```{r echo = FALSE}
-write.csv(draws1, here("outputs", "statistics", "table_persistence.csv"))
+write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))
 ```

### 2022-12-06 R/model_persistence_calculation.R

@@ -46,7 +46,7 @@ sites <- read_csv(
     botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
     botanist_year = factor(botanist_year),
     id = factor(id),
-    n = persistence
+    n = persistence / 100
   ) %>%
   select(
     id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
@@ -143,14 +143,17 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
             (1 | site/plot),
           data = sites)
-ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
-  expand_limits(y = 0) + ggtitle("Normal distribution")
-ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
+ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
+  stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
+  expand_limits(y = 0) + ggtitle("Beta distribution for Intercept")
+ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .2)) +
+  expand_limits(y = 0) + ggtitle("Normal distribution for treatments")
+ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) + ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
+ggplot(data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
 
 ### Model specifications ###
@@ -160,7 +163,7 @@ thin = 2
 seed = 123
 warmup = floor(iter / 2)
[…]

### 2022-12-06 R/model_recovery_calculation.R

@@ -3,7 +3,7 @@
 # Model building
 
 # Markus Bauer
-# 2022-12-02
+# 2022-12-06
 
 
 
@@ -46,8 +46,9 @@ sites <- read_csv(
   mutate(
     survey_year_fct = factor(survey_year),
     survey_year = as.numeric(survey_year),
-    botanist_year = str_c(survey_year, botanist, sep = " "),
-    n = recovery_completeness
+    botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
+    botanist_year = factor(botanist_year),
+    n = recovery_time
     )
 
 rm(list = setdiff(ls(), c("sites")))
@@ -130,7 +131,6 @@ boxplot(sites$n)
 ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
 ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
 ggplot(sites, aes(x = n)) + geom_density()
-ggplot(sites, aes(sqrt(n))) + geom_density()
 
 
 
@@ -142,10 +142,10 @@ ggplot(sites, aes(sqrt(n))) + geom_density()
 ### Posssible priors ###
 get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
-            (1 | site/plot) + (1 | botanist_year),
+            (1 | site/plot),
           data = sites)
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) +
   expand_limits(y = 0) + ggtitle("Normal distribution")
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
@@ -159,24 +159,34 @@ iter = 10000
 chains = 4
 thin = 2
 seed = 123
+warmup = floor(iter / 2)
 priors <- c(
-  set_prior("normal(0, 2)", class = "b"),
-  set_prior("normal(0.1, 2)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(0.2, 2)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(-0.1, 2)", class = "b", coef = "expositionsouth"),
[…]

### 2022-12-07 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
+<br/>
+<br/>
+<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
 
-<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
-<br>
 ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
@@
 
+Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+
+Analysis guided by
+<br>
+Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<br>
+Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
+<br>
+Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
+<br>
+Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
+
 # Preparation
@@
 
-```{r message = FALSE}
+```{r libraries message = FALSE}
 library(here)
@@
 
-```{r}
+```{r load-data}
 sites <- read_csv(
@@
 
-```{r echo = FALSE}
+```{r data-exploration echo = FALSE}
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
@@
 
-```{r echo = FALSE}
+```{r outliers echo = FALSE}
 sites %>% group_by(exposition) %>% count(site)
@@
 
+### Load models
+
 Only here you have to modify the script to compare other models
 
-```{r collapse = TRUE}
+```{r load-models collapse = TRUE}
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
@@
 
-```{r collapse = TRUE}
+```{r formulas collapse = TRUE}
 m_1$formula
@@
 
-```{r collapse = TRUE}
+```{r families collapse = TRUE}
 m_1$family
 m_2$family
-```
-
-### Priors
-
-#### Possible prior distributions
-
-```{r}
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)
-    ) +
-  expand_limits(y = 0) + ggtitle("Normal distribution")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dcauchy, n = 101, args = list(location = 0, scale = 1)
-    ) +
-  expand_limits(y = 0) + ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)
-    ) +
-  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
-```
-
-#### Prior summary
-
-```{r}
-prior_summary(m_1, all = FALSE)
 ```
@@
 
-```{r collapse = TRUE}
+```{r conditional-r2 collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
-```{r collapse = TRUE}
+```{r marginal-r2 collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
+### Priors
+
+#### Possible prior distributions
+
+```{r possible-priors}
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot) + (1 | botanist_year),
+          data = sites)
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(
+    fun = dnorm, n = 101, args = list(mean = 0, sd = 1)
+    ) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for Intercept")
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(
+    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)
+    ) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for treatments")
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(
+    fun = dcauchy, n = 101, args = list(location = 0, scale = 1)
+    ) +
+  expand_limits(y = 0) +
+  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
+ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(
+    fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)
+    ) +
+  expand_limits(y = 0) +
+  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+```
+
+#### Prior summary
+
+```{r prior-summary}
+prior_summary(m_1, all = FALSE)
+```
+
 ## Model check
@@
 
-```{r collapse = TRUE}
+```{r dharma collapse = TRUE}
 DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
@@
 
-```{r}
+```{r analysis-preparation}
 posterior1 <- m_1 %>%
@@
 
-```{r collapse = TRUE}
+```{r rhat collapse = TRUE}
 mcmc_rhat(draws1$rhat)
@@
 
-```{r collapse = TRUE}
+```{r ess collapse = TRUE}
 mcmc_neff(neff_ratio(m_1))
@@
 
-```{r}
+```{r mcmc}
 mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
@@
 mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
-  theme(axis.text.x = element_text(angle = 90))
+  theme(axis.text.x = element_text(angle = 45))
 mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
-  theme(axis.text.x = element_text(angle = 90))
+  theme(axis.text.x = element_text(angle = 45))
 ```
@@
 
-```{r}
+```{r kernel-density}
 p1 <- ppc_dens_overlay(y, yrep1[1:50, ])
@@
 
-```{r}
+```{r histogram}
 p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
@@
 
-```{r}
+```{r loo}
 loo1
@@
 
-```{r}
+```{r loo-pit}
 p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
@@
 
-```{r}
+```{r autocorrelation}
 mcmc_acf(posterior1, lags = 10)
@@
 
-```{r collapse = TRUE}
+```{r conditional-marginal-r2 collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
-```{r}
+```{r posterior-chosen-model}
 draws1
@@
 
-```{r}
+```{r posterior-second-model}
 mcmc_intervals(
@@
 
-```{r max_height = "1000px"}
+```{r effect-sizes}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 
-```{r echo = FALSE}
+```{r write-csv echo = FALSE}
 write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
@@
 
-```{r echo = FALSE, max_height = "500px"}
+```{r session-info echo = FALSE}
 sessionInfo()

### 2022-12-07 R/model_persistence_check.Rmd
Update

@@
 
-Persistence sensu Wilsey (2021) Restor Ecol [DOI: 10.1111/rec.13132](https://doi.org/10.1111/rec.13132)
+Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
+
+Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+
+Analysis guided by
+<br>
+Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<br>
+Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
+<br>
+Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
+<br>
+Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
 
@@
 
+### Load models
+
 Only here you have to modify the script to compare other models
@@
 m_2$family
-```
-
-### Priors
-
-#### Possible prior distributions
-
-```{r}
-get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site/plot),
-          data = sites)
-ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
-  expand_limits(y = 0) + ggtitle("Normal distribution")
-ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
-  expand_limits(y = 0) + ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
-  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
-```
-
-#### Prior summary
-
-```{r}
-prior_summary(m_1, all = FALSE)
 ```
@@
          re_formula = 1 ~ 1)
+```
+
+### Priors
+
+#### Possible prior distributions
+
+```{r}
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot) + (1 | botanist_year),
+          data = sites)
+ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
+  stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
+  expand_limits(y = 0) +
+  ggtitle("Beta distribution for Intercept")
+ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .2)) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for treatments")
+ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
+ggplot(data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  expand_limits(y = 0) +
+  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+```
+
+#### Prior summary
+
+```{r}
+prior_summary(m_1, all = FALSE)
 ```

### 2022-12-07 R/model_fcs_check.Rmd

@@
   stat_function(
-    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)
+    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 2)
     ) +
@@
 
-Just, to get exact values if necessary, which is not possible from the figure
+Effect sizes are presented just to get exact values of the means if necessary.
 

### 2022-12-07 R/model_recovery_check.Rmd

@@
 
-Persistence sensu Wilsey (2021) Restor Ecol [DOI: 10.1111/rec.13132](https://doi.org/10.1111/rec.13132)
+Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
+
+Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+
+Analysis guided by
+<br>
+Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<br>
+Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
+<br>
+Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
+<br>
+Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
+
+To compare different models, you only have to change the models in section 'Load models'
 
@@
 
+### Load models
+
 Only here you have to modify the script to compare other models
 
-```{r collapse = TRUE, message = FALSE}
+```{r load-models collapse = TRUE, message = FALSE}
 load(file = here("outputs", "models", "model_recovery_full.Rdata"))
-load(file = here("outputs", "models", "model_recovery_full_flat.Rdata"))
+load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
 m_1 <- m_full
-m_2 <- mfull_flat
+m_2 <- mfull_prior
 ```
 
-```{r collapse = TRUE}
+```{r formulas collapse = TRUE}
 m_1$formula
@@
 
-```{r collapse = TRUE}
+```{r families collapse = TRUE}
 m_1$family
 m_2$family
-```
-
-### Priors
-
-#### Possible prior distributions
-
-```{r}
-get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site/plot),
-          data = sites)
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) +
-  expand_limits(y = 0) + ggtitle("Normal distribution")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0) + ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
-```
-
-#### Prior summary
-
-```{r}
-prior_summary(m_1, all = FALSE)
 ```
@@
 
-```{r collapse = TRUE}
+```{r conditonal-r2 collapse = TRUE}
 bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
+### Priors
+
+#### Possible prior distributions
+
+```{r possible priors}
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot) + (1|botanist_year),
+          data = sites)
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for Intecepts")
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for treatments")
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
+ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  expand_limits(y = 0) +
+  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+```
+
+#### Prior summary
+
+```{r prior-summary}
+prior_summary(m_1, all = FALSE)
+```
+
 ## Model check
@@
 
-```{r}
-mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
-mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
+```{r mcmc}
+mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
+mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
 
-```{r}
+```{r histograms}
 p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
@@
 
-```{r}
+```{r loo}
 loo1
-loo2
+#loo2
 plot(loo1)
-plot(loo2)
+#plot(loo2)
 ```
@@
 
-```{r}
+```{r loo-pit}
 p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
-p1 / p2
+#p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+#p1 / p2
 
@@
 
-```{r}
-mcmc_acf(posterior1, lags = 10)
-mcmc_acf(posterior2, lags = 10)
+```{r autocorrelation}
+mcmc_acf(posterior1, lags = 10, facet_args = list(ncol = 4))
+#mcmc_acf(posterior2, lags = 10, facet_args = list(ncol = 4))
 ```
@@
 
-```{r}
+```{r posteriors-chosen-model}
 draws1
@@
 
-```{r}
+```{r posterors-2nd-model}
 mcmc_intervals(
@@
 
-```{r}
+```{r effect-sizes}
 (emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
@@
 
-```{r echo = FALSE}
+```{r write-csv echo = FALSE}
 write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))
@@
 
-```{r echo = FALSE}
+```{r session-info echo = FALSE}
 sessionInfo()

### 2022-12-07 R/model_fcs_check.Rmd
mark library of functions

--- 2022-12-07 R/model_fcs_check.Rmd
@@
 ```{r conditional-r2 collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot))
@@
 ```{r marginal-r2 collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
@@
 ```{r prior-summary}
-prior_summary(m_1, all = FALSE)
+brms::prior_summary(m_1, all = FALSE)
 ```
@@
   )
-hmc_diagnostics1 <- nuts_params(m_1)
-hmc_diagnostics2 <- nuts_params(m_2)
+hmc_diagnostics1 <- bayesplot::nuts_params(m_1)
+hmc_diagnostics2 <- bayesplot::nuts_params(m_2)
 y <- sites$n
-yrep1 <- posterior_predict(m_1, draws = 500)
-yrep2 <- posterior_predict(m_2, draws = 500)
-loo1 <- loo(m_1, save_psis = TRUE, moment_match = FALSE)
-loo2 <- loo(m_2, save_psis = TRUE, moment_match = FALSE)
+yrep1 <- brms::posterior_predict(m_1, draws = 500)
+yrep2 <- brms::posterior_predict(m_2, draws = 500)
+loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
+loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
 draws1 <- m_1 %>%
@@
 ### Sampling efficency and effectiveness
+
+All 'mcmc_' functions are from library 'bayesplot'
 
@@
 ```{r mcmc}
-mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
-mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
+mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
+mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
 ```{r conditional-marginal-r2 collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)

### 2022-12-07 R/model_persistence_check.Rmd
mark library of functions

@@
 ```{r collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot))
@@
 ```{r collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
@@
 ```{r}
-prior_summary(m_1, all = FALSE)
+brms::prior_summary(m_1, all = FALSE)
 ```
@@
 ```{r}
-mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
-mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
+mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
+mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
 ```{r collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)

### 2022-12-07 R/model_recovery_check.Rmd
mark library of functions

@@
 ```{r conditonal-r2 collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot) + (1 | botanist_year))

### 2022-12-07 R/model_fcs_check.Rmd
Refer to BARG framework

@@
 <br>
-Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+Bayesian analysis reporting guidelines (BARG): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
 <br>
@@
 
-#### Packages
+#### Packages (BARG 2.A)
 
@@
 
-### Load models
+### Load models (BARG 1.D/6.G)
 
@@
 load(file = here("outputs", "models", "model_fcs_full.Rdata"))
+# BARG 5
+load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
+# BARG 1.E
+load(file = here("outputs", "models", "model_fcs_2_prior.Rdata"))
 m_1 <- m2
@@
 ```
+
+### Model comparison
 
@@
 ```
-
-### Coefficient of determination (<i>R</i>²)
 
@@
          re_formula = 1 ~ 1)
+```
+
+#### Bayes factor (BARG 3.C)
+
+```{r}
+brms::bayes_factor(m_1, m_2)
 ```
@@
 
-#### Prior summary
+#### Prior summary (BARG 1.D)
 
@@
 
-#### Rhat
+#### Rhat (BARG 2.B)
 
@@
 
-#### Effective sampling size (ESS)
+#### Effective sampling size (ESS) (BARG 2.C)
 
@@
 
-### Posterior predictive check
+### Posterior predictive check (BARG 3.A)
 
@@
 
-## Output of choosen model
+## Posterior distributions (BARG 3.B)
 
-### Model output
+### Forest plot
 
-Conditional and marignal <i>R</i>²
+Chosen model:
 
-```{r conditional-marginal-r2 collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-```
-
-Posteriors of chosen model
-
-```{r posterior-chosen-model}
-draws1
+```{r posteriors-chosen-model}
 mcmc_intervals(
@@
 
-Posteriors of second model:
+Second model:
 
-```{r posterior-second-model}
+```{r posteriors-2nd-model}
 mcmc_intervals(
@@
 
-Just, to get exact values if necessary, which is not possible from the figure
+Effect sizes of chosen model just to get exact values of means etc. if necessary.
 
@@
 
-# Session info
+# Session info (BARG 2.A/6.A/6.B)
 

### 2022-12-07 R/model_persistence_check.Rmd
Refer to BARG framework

@@
 load(file = here("outputs", "models", "model_persistence_full.Rdata"))
+# BARG 5
+load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
+# BARG 1.E
+load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
 m_1 <- m2
@@
 
-## Output of choosen model
+## Posterior distributions (BARG 3.B)
 
-### Model output
+### Forest plot
 
-Conditional and marignal <i>R</i>²
+Chosen model:
 
-```{r collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-```
-
-Posteriors of chosen model
-
-```{r}
-draws1
+```{r posteriors-chosen-model}
 mcmc_intervals(
@@
 
-Posteriors of second model:
+Second model:
 
-```{r}
+```{r posteriors-2nd-model}
 mcmc_intervals(

### 2022-12-07 R/model_recovery_check.Rmd

@@
 load(file = here("outputs", "models", "model_recovery_full.Rdata"))
+# BARG 5
+load(file = here("outputs", "models", "model_recovery_full_flat.Rdata"))
+# BARG 1.E
 load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
@@
 m_2$family
-```
-
-### Coefficient of determination (<i>R</i>^2)
-
-#### Conditional <i>R</i>^2 values
-
-```{r conditonal-r2 collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
-brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
-```
-
-#### Marginal <i>R</i>^2 values
-
-```{r marginal-r2 collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
 ```
@@
 
-## Output of choosen model
+## Model comparison
 
-### Model output
+### Conditional <i>R</i>^2 values
 
-Conditional and marignal <i>R</i>²
+```{r conditonal-r2 collapse = TRUE}
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
+```
 
-```{r conditional-marginal-r2 collapse = TRUE}
+### Marginal <i>R</i>^2 values
+
+```{r marginal-r2 collapse = TRUE}
 brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
@@
 
-Posteriors of chosen model
+### Bayes factor (BARG 3.C)
+
+```{r}
+brms::bayes_factor(m_1, m_2)
+```
+
+## Posterior distributions (BARG 3.B)
+
+### Forest plot
+
+Chosen model:
 
 ```{r posteriors-chosen-model}
-draws1
 mcmc_intervals(
@@
 
-Posteriors of second model:
+Second model:
 
-```{r posterors-2nd-model}
+```{r posteriors-2nd-model}
 mcmc_intervals(
@@
 
-Effect sizes just to get exact values of means etc. if necessary.
+Effect sizes of chosen model just to get exact values of means etc. if necessary.
 

### 2022-12-07 R/model_fcs_check.Rmd
Update Markdown format

@@
 <br>
-Bayesian analysis reporting guidelines (BARG): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
 <br>
@@
 library(brms)
-library(DHARMa)
 library(DHARMa.helpers)
@@
 
-### Load models (BARG 1.D/6.G)
+### Load models (6.G)
 
@@
 load(file = here("outputs", "models", "model_fcs_full.Rdata"))
-# BARG 5
-load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
 # BARG 1.E
-load(file = here("outputs", "models", "model_fcs_2_prior.Rdata"))
+#load(file = here("outputs", "models", "model_fcs_2_prior.Rdata"))
+# BARG 5.A/B/C
+#load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
 m_1 <- m2
@@
 
-### Model comparison
+### Model specifications (BARG 1.D)
 
@@
 
-#### Conditional <i>R</i>² values
-
-```{r conditional-r2 collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
-brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot))
+```{r model-specification-chains collapse = TRUE}
+m_1$fit@sim$chains
+m_2$fit@sim$chains
 ```
 
-#### Marginal <i>R</i>² values
-
-```{r marginal-r2 collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
+```{r model-specification-iterations collapse = TRUE}
+m_1$fit@sim$iter
+m_2$fit@sim$iter
 ```
 
-#### Bayes factor (BARG 3.C)
+```{r model-specification-warmup collapse = TRUE}
+m_1$fit@sim$warmup
+m_2$fit@sim$warmup
+```
 
-```{r}
-brms::bayes_factor(m_1, m_2)
+```{r model-specification-thinning collapse = TRUE}
+m_1$fit@sim$thin
+m_2$fit@sim$thin
 ```
@@
   )
-hmc_diagnostics1 <- bayesplot::nuts_params(m_1)
-hmc_diagnostics2 <- bayesplot::nuts_params(m_2)
+hmc_diagnostics1 <- brms::nuts_params(m_1)
+hmc_diagnostics2 <- brms::nuts_params(m_2)
 y <- sites$n
@@
 ### Sampling efficency and effectiveness
-
-All 'mcmc_' functions are from library 'bayesplot'
 
@@
 ```{r mcmc}
-mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
-mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
+mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
 
-### Posterior predictive check (BARG 3.A)
+### Posterior predictive check
 
@@
 ```{r loo-pit}
-p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 <- loo::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+p2 <- loo::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
 p1 / p2
@@
 mcmc_acf(posterior2, lags = 10)
+```
+
+## Model comparison
+
+### Conditional <i>R</i>² values
+
+```{r collapse = TRUE}
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot)) 
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot))
+```
+
+### Marginal <i>R</i>² values
+
+```{r collapse = TRUE}
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+```
+
+### Bayes factor (BARG 3.C)
+
+```{r}
+brms::bayes_factor(m_1, m_2)
 ```
@@
 
-```{r posteriors-2nd-model}
+```{r posterors-2nd-model}
 mcmc_intervals(

### 2022-12-07 R/model_persistence_check.Rmd
Update Markdown format

--- 2022-12-07 R/model_persistence_check.Rmd
@@
 
-### Load models
+### Load models (BARG 6.G)
 
@@
 load(file = here("outputs", "models", "model_persistence_full.Rdata"))
+# BARG 1.E
+#load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
+# BARG 5.A/B/C
+#load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
 m_1 <- m2
@@
 
-```{r collapse = TRUE}
+### Model specifications (BARG 1.D)
+
+```{r formulas collapse = TRUE}
 m_1$formula
@@
 
-```{r collapse = TRUE}
+```{r families collapse = TRUE}
 m_1$family
@@
 
-### Coefficient of determination (<i>R</i>²)
-
-#### Conditional <i>R</i>² values
-
-```{r collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot))
+```{r model-specification-chains collapse = TRUE}
+m_1$fit@sim$chains
+m_2$fit@sim$chains
 ```
 
-#### Marginal <i>R</i>² values
+```{r model-specification-iterations collapse = TRUE}
+m_1$fit@sim$iter
+m_2$fit@sim$iter
+```
 
-```{r collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
+```{r model-specification-warmup collapse = TRUE}
+m_1$fit@sim$warmup
+m_2$fit@sim$warmup
+```
+
+```{r model-specification-thinning collapse = TRUE}
+m_1$fit@sim$thin
+m_2$fit@sim$thin
 ```
@@
 
-#### Prior summary
+#### Prior summary (BARG 1.D)
 
 ```{r}
-prior_summary(m_1, all = FALSE)
+brms::prior_summary(m_1, all = FALSE)
 ```
@@
   )
-hmc_diagnostics1 <- nuts_params(m_1)
-hmc_diagnostics2 <- nuts_params(m_2)
+hmc_diagnostics1 <- brms::nuts_params(m_1)
+hmc_diagnostics2 <- brms::nuts_params(m_2)
 y <- sites$n
-yrep1 <- posterior_predict(m_1, draws = 500)
-yrep2 <- posterior_predict(m_2, draws = 500)
-loo1 <- loo(m_1, save_psis = TRUE, moment_match = FALSE)
-loo2 <- loo(m_2, save_psis = TRUE, moment_match = FALSE)
+yrep1 <- brms::posterior_predict(m_1, draws = 500)
+yrep2 <- brms::posterior_predict(m_2, draws = 500)
+loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
+loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
 draws1 <- m_1 %>%
@@
 ```{r}
-p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 <- loo::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+p2 <- loo::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
 p1 / p2
@@
 
-## Output of choosen model
+## Model comparison
 
-### Model output
-
-Conditional and marignal <i>R</i>²
+### Conditional <i>R</i>² values
 
 ```{r collapse = TRUE}
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
          re_formula =  ~ (1 | site/plot)) 
-bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
+         re_formula =  ~ (1 | site/plot))
+```
+
+### Marginal <i>R</i>² values
+
+```{r collapse = TRUE}
+brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
+         re_formula = 1 ~ 1)
+brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
          re_formula = 1 ~ 1)
@@
 
-Posteriors of chosen model
+### Bayes factor (BARG 3.C)
 
 ```{r}
-draws1
+brms::bayes_factor(m_1, m_2)
+```
+
+## Posterior distributions (BARG 3.B)
+
+### Forest plot
+
+Chosen model:
+
+```{r posteriors-chosen-model}
 mcmc_intervals(
@@
 
-Posteriors of second model:
+Second model:
 
-```{r}
+```{r posterors-2nd-model}
 mcmc_intervals(

### 2022-12-07 R/model_recovery_check.Rmd
Update Markdown format

@@
 
-#### Packages (BARG 2.A)
+#### Packages
 
@@
 load(file = here("outputs", "models", "model_recovery_full.Rdata"))
-# BARG 5
-load(file = here("outputs", "models", "model_recovery_full_flat.Rdata"))
+load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
 # BARG 1.E
-load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
+#load(file = here("outputs", "models", "model_recovery_2_prior.Rdata"))
+# BARG 5.A/B/C
+#load(file = here("outputs", "models", "model_recovery_2_flat.Rdata"))
 m_1 <- m_full
@@
 ```
+
+### Model specifications (BARG 1.D)
 
@@
 m_2$family
+```
+
+```{r model-specification-chains collapse = TRUE}
+m_1$fit@sim$chains
+m_2$fit@sim$chains
+```
+
+```{r model-specification-iterations collapse = TRUE}
+m_1$fit@sim$iter
+m_2$fit@sim$iter
+```
+
+```{r model-specification-warmup collapse = TRUE}
+m_1$fit@sim$warmup
+m_2$fit@sim$warmup
+```
+
+```{r model-specification-thinning collapse = TRUE}
+m_1$fit@sim$thin
+m_2$fit@sim$thin
 ```
@@
 ```{r loo-pit}
-p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-#p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 <- loo::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+#p2 <- loo::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
 #p1 / p2
@@
 
-### Conditional <i>R</i>^2 values
+### Conditional <i>R</i>² values
 
-```{r conditonal-r2 collapse = TRUE}
+```{r collapse = TRUE}
 brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
+         re_formula =  ~ (1 | site/plot)) 
 brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
+         re_formula =  ~ (1 | site/plot))
 ```
 
-### Marginal <i>R</i>^2 values
+### Marginal <i>R</i>² values
 
-```{r marginal-r2 collapse = TRUE}
+```{r collapse = TRUE}
 brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),

### 2022-12-07 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 
-```{r libraries message = FALSE}
+```{r libraries, message = FALSE}
 library(here)
@@
 
-```{r data-exploration echo = FALSE}
+```{r data-exploration, echo = FALSE}
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
@@
 
-```{r outliers echo = FALSE}
+```{r outliers, echo = FALSE}
 sites %>% group_by(exposition) %>% count(site)
@@
 
-```{r load-models collapse = TRUE}
+```{r load-models, collapse = TRUE}
 load(file = here("outputs", "models", "model_fcs_2.Rdata"))
@@
 
-```{r formulas collapse = TRUE}
+```{r formulas, collapse = TRUE}
 m_1$formula
@@
 
-```{r families collapse = TRUE}
+```{r families, collapse = TRUE}
 m_1$family
@@
 
-```{r model-specification-chains collapse = TRUE}
+```{r model-specification-chains, collapse = TRUE}
 m_1$fit@sim$chains
@@
 
-```{r model-specification-iterations collapse = TRUE}
+```{r model-specification-iterations, collapse = TRUE}
 m_1$fit@sim$iter
@@
 
-```{r model-specification-warmup collapse = TRUE}
+```{r model-specification-warmup, collapse = TRUE}
 m_1$fit@sim$warmup
@@
 
-```{r model-specification-thinning collapse = TRUE}
+```{r model-specification-thinning, collapse = TRUE}
 m_1$fit@sim$thin
@@
 
-```{r dharma collapse = TRUE}
+```{r dharma, collapse = TRUE}
 DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
@@
 
-```{r rhat collapse = TRUE}
+```{r rhat, collapse = TRUE}
 mcmc_rhat(draws1$rhat)
@@
 
-```{r ess collapse = TRUE}
+```{r ess, collapse = TRUE}
 mcmc_neff(neff_ratio(m_1))
@@
 
-```{r collapse = TRUE}
+```{r conditional-r2, collapse = TRUE}
 brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
-```{r collapse = TRUE}
+```{r marginal-r2, collapse = TRUE}
 brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
@@
 
-```{r}
+```{r bayes-factor}
 brms::bayes_factor(m_1, m_2)
@@
 
-```{r write-csv echo = FALSE}
+```{r write-csv, echo = FALSE}
 write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
@@
 
-```{r session-info echo = FALSE}
+```{r session-info, echo = FALSE}
 sessionInfo()

### 2022-12-07 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd

@@
 
-```{r echo = FALSE}
+```{r data-exploration, echo = FALSE}
 plot1 <- ggplot(sites %>% filter(survey_year == 2021),
@@
 
-```{r echo = FALSE}
+```{r outliers, echo = FALSE}
 sites %>% group_by(exposition) %>% count(site)
@@
 
-```{r collapse = TRUE, message = FALSE}
+```{r load-models, collapse = TRUE, message = FALSE}
 load(file = here("outputs", "models", "model_persistence_2.Rdata"))
@@
 
-```{r}
+```{r possible-priors}
 get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
@@
 
-```{r}
+```{r prior-summary}
 brms::prior_summary(m_1, all = FALSE)
@@
 
-```{r collapse = TRUE}
+```{r dharma, collapse = TRUE}
 DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
@@
 
-```{r collapse = TRUE}
+```{r rhat, collapse = TRUE}
 mcmc_rhat(draws1$rhat)
@@
 
-```{r collapse = TRUE}
+```{r ess, collapse = TRUE}
 mcmc_neff(neff_ratio(m_1))
@@
 
-```{r}
+```{r loo-pit}
 p1 <- loo::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
@@
 
-```{r echo = FALSE}
+```{r write-csv, echo = FALSE}
 write.csv(draws1, here("outputs", "statistics", "table_persistence.csv"))
@@
 
-```{r echo = FALSE, max_height = "500px"}
+```{r session-info, echo = FALSE}
 sessionInfo()

### 2022-12-07 R/model_recovery_check.Rmd
Update model_recovery_check.Rmd

@@
 
-```{r load-models collapse = TRUE, message = FALSE}
+```{r load-models, collapse = TRUE, message = FALSE}
 load(file = here("outputs", "models", "model_recovery_full.Rdata"))
@@
 
-```{r write-csv echo = FALSE}
+```{r write-csv, echo = FALSE}
 write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))

### 2022-12-07 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
-author: "<b>Markus Bauer*</b> <br>"
+author: "<b>Markus Bauer</b> <br>"
 date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
@@
 
+<b>Markus Bauer</b>
+
 Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
-<br/>
-<br/>
-<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
+
+[markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
 
@@
 
+To compare different models, you only have to change the models in section 'Load models'
+
+# Preparation
+
 Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
@@
 <br>
-Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<b>BARG</b> (Bayesian Analysis Reporting Guidelines): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
 <br>
@@
 Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
-
-# Preparation
 
@@
 
-```{r mcmc}
+#### Trace plots
+
+```{r mcmc-trace, fig.height = 14}
 mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
 mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+```
+
+#### Pairs plot
+
+```{r mcmc-pairs, collapse = TRUE, fig.height = 7}
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
            ))
+```
+
+#### Parallel coordinate plot
+
+```{r mcmc-parcoord, collapse = TRUE}
 mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
@@
 loo2
-plot(loo1)
-plot(loo2)
+#plot(loo1)
+#plot(loo2)
 ```
@@
 ```{r loo-pit}
-p1 <- loo::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-p2 <- loo::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
-p1 / p2
+#p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+#p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+#p1 / p2
 
@@
 
-```{r autocorrelation}
+```{r autocorrelation, fig.height = 7}
 mcmc_acf(posterior1, lags = 10)

### 2022-12-07 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd

@@
 title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence"
-author: "<b>Markus Bauer*</b> <br>"
+author: "<b>Markus Bauer</b> <br>"
 date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
@@
 
-# Preparation
-
-#### Packages
+#### Packages (BARG 2.A)
 
@@
     id = factor(id),
-    n = persistence
+    n = persistence / 100
   ) %>%
@@
 ```{r histograms}
-p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
-p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
-p1 / p2
-ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
-p1 / p2
-ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
-p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
-p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
-p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
-p1 / p2
+#p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
+#p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+#p1 / p2
+#ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
+#ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+#p1 / p2
+#ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
+#ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+#p1 / p2
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+#p1 / p2
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+#p1 / p2
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+#p1 / p2
 ```

### 2022-12-07 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 
+Amount of chains for MCMC
+
 ```{r model-specification-chains, collapse = TRUE}
@@
 ```
+
+Total amount of iterations for MCMC
 
@@
 
+Amount of iterations before burn-in
+
 ```{r model-specification-warmup, collapse = TRUE}
@@
 ```
+
+Thinning rate
 
@@
 
-### Priors
+### Priors (BARG 1.D)
 
@@
 
-```{r mcmc-pairs, collapse = TRUE, fig.height = 7}
+```{r mcmc-pairs, collapse = TRUE, fig.height = 6.5}
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
 ```{r histogram}
-p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
-p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
-p1 / p2
-ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
-p1 / p2
-ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
-p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
-p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
-p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
-p1 / p2
+#p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
+#p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+#p1 / p2
+#ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
+#ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+#p1 / p2
+#ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
+#ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+#p1 / p2
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+#p1 / p2
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+#p1 / p2
+#p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
+#p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+#p1 / p2
 ```

### 2022-12-07 R/model_recovery_check.Rmd
Update recovery

@@
 GitHub: [markus1bauer](https://github.com/markus1bauer)
-
+<br/>
+<br/>
 Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
@@
 
-### Sampling efficency and effectiveness
+### Sampling efficency and effectiveness (BARG 2.B/C)
 
@@
 
-```{r mcmc}
+#### Trace plots
+
+```{r mcmc-trace, fig.height = 14}
 mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
 mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+```
+
+#### Pairs plot
+
+```{r mcmc-pairs, collapse = TRUE, fig.height = 6.5}
 mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
@@
 #loo2
-plot(loo1)
+#plot(loo1)
 #plot(loo2)
@@
 ```{r loo-pit}
-p1 <- loo::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-#p2 <- loo::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+#p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+#p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
 #p1 / p2
@@
 
-```{r autocorrelation}
+```{r autocorrelation, fig.height = 7}
 mcmc_acf(posterior1, lags = 10, facet_args = list(ncol = 4))
@@
 
-### Conditional <i>R</i>² values
+### Conditional <i>R</i>^2 values
 
@@
 
-### Marginal <i>R</i>² values
+### Marginal <i>R</i>^2 values
 

### 2022-12-07 R/model_recovery_calculation.R

@@ -162,7 +162,7 @@ ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
   ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
 
 ### Model specifications ###
-iter = 10000
+iter = 20000
 chains = 4
 thin = 2
 seed = 123

### 2022-12-07 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd

@@
 load(file = here("outputs", "models", "model_persistence_2.Rdata"))
-load(file = here("outputs", "models", "model_persistence_full.Rdata"))
+#load(file = here("outputs", "models", "model_persistence_full.Rdata"))
 # BARG 1.E
-#load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
+load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
 # BARG 5.A/B/C
@@
 m_1 <- m2
-m_2 <- m_full
+#m_2 <- m_full
+m_2 <- m2_prior
 ```

### 2022-12-07 R/model_fcs_check.Rmd
Update emmeans
Update model scripts

@@
 load(file = here("outputs", "models", "model_fcs_full.Rdata"))
-# BARG 1.E
-#load(file = here("outputs", "models", "model_fcs_2_prior.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2_prior.Rdata"))
 # BARG 5.A/B/C
@@
 m_2 <- m_full
+m_prior <- m2_prior
 ```
@@
 
-### Priors (BARG 1.D)
+### Preparation for analysis
+
+```{r analysis-preparation}
+posterior1 <- m_1 %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(
+    variable = c(
+      "b_sand_ratio25",
+      "b_sand_ratio50",
+      "b_substrate_depth15",
+      "b_target_typedry_grassland",
+      "b_seed_density8",
+      "b_expositionsouth",
+      "b_survey_year_fct2019",
+      "b_survey_year_fct2020",
+      "b_survey_year_fct2021",
+      "sd_site__Intercept",
+      "sd_site:plot__Intercept",
+      "sigma"
+    )
+  )
+posterior2 <- m_2 %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(
+    variable = c(
+      "b_sand_ratio25",
+      "b_sand_ratio50",
+      "b_substrate_depth15",
+      "b_target_typedry_grassland",
+      "b_seed_density8",
+      "b_expositionsouth",
+      "b_survey_year_fct2019",
+      "b_survey_year_fct2020",
+      "b_survey_year_fct2021",
+      "sd_site__Intercept",
+      "sd_site:plot__Intercept",
+      "sigma"
+    )
+  )
+posterior_prior <- m_prior %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(
+    variable = c(
+      "b_sand_ratio25",
+      "b_sand_ratio50",
+      "b_substrate_depth15",
+      "b_target_typedry_grassland",
+      "b_seed_density8",
+      "b_expositionsouth",
+      "b_survey_year_fct2019",
+      "b_survey_year_fct2020",
+      "b_survey_year_fct2021"
+    )
+  )
+hmc_diagnostics1 <- brms::nuts_params(m_1)
+hmc_diagnostics2 <- brms::nuts_params(m_2)
+y <- sites$n
+yrep1 <- brms::posterior_predict(m_1, draws = 500)
+yrep2 <- brms::posterior_predict(m_2, draws = 500)
+loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
+loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
+draws1 <- m_1 %>%
+  posterior::as_draws() %>%
+  posterior::summarize_draws() %>%
+  filter(str_starts(variable, "b_"))
+draws2 <- m_2 %>%
+  posterior::as_draws() %>%
+  posterior::summarize_draws() %>%
+  filter(str_starts(variable, "b_"))
+```
+
+### Priors (BARG 1.D/E)
 
@@
 
+#### Prior predictive check (BARG 1.E)
+
+```{r prior-predictive-check}
+bayesplot::mcmc_intervals(
+  posterior_prior,
+  prob = 0.66,
+  prob_outer = 0.95,
+  point_est = "mean"
+  ) +
+  theme_classic()
+```
+
 ## Model check
@@
 
-### Preparation
-
-```{r analysis-preparation}
-posterior1 <- m_1 %>%
-  posterior::as_draws() %>%
-  posterior::subset_draws(
-    variable = c(
-      "b_sand_ratio25",
-      "b_sand_ratio50",
-      "b_substrate_depth15",
-      "b_target_typedry_grassland",
-      "b_seed_density8",
-      "b_expositionsouth",
-      "b_survey_year_fct2019",
-      "b_survey_year_fct2020",
-      "b_survey_year_fct2021",
-      "sd_site__Intercept",
-      "sd_site:plot__Intercept",
-      "sigma"
-    )
-  )
-posterior2 <- m_2 %>%
-  posterior::as_draws() %>%
-  posterior::subset_draws(
-    variable = c(
-      "b_sand_ratio25",
-      "b_sand_ratio50",
-      "b_substrate_depth15",
-      "b_target_typedry_grassland",
-      "b_seed_density8",
-      "b_expositionsouth",
-      "b_survey_year_fct2019",
-      "b_survey_year_fct2020",
-      "b_survey_year_fct2021",
-      "sd_site__Intercept",
-      "sd_site:plot__Intercept",
-      "sigma"
-    )
-  )
-hmc_diagnostics1 <- brms::nuts_params(m_1)
-hmc_diagnostics2 <- brms::nuts_params(m_2)
-y <- sites$n
-yrep1 <- brms::posterior_predict(m_1, draws = 500)
-yrep2 <- brms::posterior_predict(m_2, draws = 500)
-loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
-loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
-draws1 <- m_1 %>%
-  posterior::as_draws() %>%
-  posterior::summarize_draws() %>%
-  filter(str_starts(variable, "b_"))
-draws2 <- m_2 %>%
-  posterior::as_draws() %>%
-  posterior::summarize_draws() %>%
-  filter(str_starts(variable, "b_"))
-```
-
-### Sampling efficency and effectiveness
+### Sampling efficency and effectiveness (BARG 2.B/C)
 
@@
 ```{r effect-sizes}
-(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
-                  exposition | survey_year_fct, type = "response"))
+#emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
+#survey_year_fct, type = "response"))
 ```

### 2022-12-07 R/model_persistence_check.Rmd
Update emmeans
Update model scripts

@@
 load(file = here("outputs", "models", "model_persistence_2.Rdata"))
-#load(file = here("outputs", "models", "model_persistence_full.Rdata"))
-# BARG 1.E
+load(file = here("outputs", "models", "model_persistence_full.Rdata"))
 load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
@@
 m_1 <- m2
-#m_2 <- m_full
-m_2 <- m2_prior
+m_2 <- m_full
+m_prior <- m2_prior
 ```
@@
 
-### Priors (BARG 1.D)
-
-#### Possible prior distributions
-
-```{r possible-priors}
-get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site/plot) + (1 | botanist_year),
-          data = sites)
-ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
-  stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
-  expand_limits(y = 0) +
-  ggtitle("Beta distribution for Intercept")
-ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .2)) +
-  expand_limits(y = 0) +
-  ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0) +
-  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-.4, .4)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0) +
-  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
-```
-
-#### Prior summary (BARG 1.D)
-
-```{r prior-summary}
-brms::prior_summary(m_1, all = FALSE)
-```
-
-## Model check
-
-### DHARMa
-
-```{r dharma, collapse = TRUE}
-DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
-DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
-```
-
-### Preparation
+### Preparation for analysis
 
@@
   )
+posterior_prior <- m_prior %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(
+    variable = c(
+      "b_sand_ratio25",
+      "b_sand_ratio50",
+      "b_substrate_depth15",
+      "b_target_typedry_grassland",
+      "b_seed_density8",
+      "b_expositionsouth",
+      "b_survey_year_fct2019",
+      "b_survey_year_fct2020",
+      "b_survey_year_fct2021"
+    )
+  )
 hmc_diagnostics1 <- brms::nuts_params(m_1)
@@
 
-### Sampling efficency and effectiveness
+### Priors (BARG 1.D/E)
+
+#### Possible prior distributions
+
+```{r possible-priors}
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot) + (1 | botanist_year),
+          data = sites)
+ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
+  stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
+  expand_limits(y = 0) +
+  ggtitle("Beta distribution for Intercept")
+ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .2)) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for treatments")
+ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
+ggplot(data.frame(x = c(-.4, .4)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  expand_limits(y = 0) +
+  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+```
+
+#### Prior summary (BARG 1.D)
+
+```{r prior-summary}
+brms::prior_summary(m_1, all = FALSE)
+```
+
+#### Prior predictive check (BARG 1.E)
+
+```{r prior-predictive-check}
+bayesplot::mcmc_intervals(
+  posterior_prior,
+  prob = 0.66,
+  prob_outer = 0.95,
+  point_est = "mean"
+  ) +
+  theme_classic()
+```
+
+## Model check
+
+### DHARMa
+
+```{r dharma, collapse = TRUE}
+DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
+DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
+```
+
+### Sampling efficency and effectiveness (BARG 2.B/C)
 
@@
 ```{r posterors-2nd-model}
-mcmc_intervals(
+bayesplot::mcmc_intervals(
   posterior2,

### 2022-12-07 R/model_recovery_check.Rmd
Update emmeans
Update model scripts

@@
 load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
-# BARG 1.E
-#load(file = here("outputs", "models", "model_recovery_2_prior.Rdata"))
+load(file = here("outputs", "models", "model_recovery_2_prior.Rdata"))
 # BARG 5.A/B/C
@@
 m_2 <- mfull_prior
+m_prior <- m2_prior
 ```
@@
 
-### Priors (BARG 1.D)
-
-#### Possible prior distributions
-
-```{r possible priors}
-get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site/plot) + (1|botanist_year),
-          data = sites)
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
-  expand_limits(y = 0) +
-  ggtitle("Normal distribution for Intecepts")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) +
-  expand_limits(y = 0) +
-  ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0) +
-  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
-  expand_limits(y = 0) +
-  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
-```
-
-#### Prior summary (BARG 1.D)
-
-```{r prior-summary}
-brms::prior_summary(m_1, all = FALSE)
-```
-
-## Model check
-
-### DHARMa
-
-```{r dharma, collapse = TRUE}
-DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
-DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
-```
-
-### Preparation
+### Preparation for analysis
 
@@
   filter(str_starts(variable, "b_"))
+```
+
+### Priors (BARG 1.D/E)
+
+#### Possible prior distributions
+
+```{r possible priors}
+get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+            seed_density + substrate_depth +
+            (1 | site/plot) + (1|botanist_year),
+          data = sites)
+ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for Intecepts")
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .8)) +
+  expand_limits(y = 0) +
+  ggtitle("Normal distribution for treatments")
+ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
+  expand_limits(y = 0) +
+  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
+ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
+  expand_limits(y = 0) +
+  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+```
+
+#### Prior summary (BARG 1.D)
+
+```{r prior-summary}
+brms::prior_summary(m_1, all = FALSE)
+```
+
+#### Prior predictive check (BARG 1.E)
+
+```{r prior-predictive-check}
+bayesplot::mcmc_intervals(
+  posterior_prior,
+  prob = 0.66,
+  prob_outer = 0.95,
+  point_est = "mean"
+  ) +
+  theme_classic()
+```
+
+## Model check
+
+### DHARMa
+
+```{r dharma, collapse = TRUE}
+DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
+DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
 ```

### 2022-12-07 R/model_persistence_calculation.R

@@ -141,7 +141,7 @@ ggplot(sites, aes(x = n)) + geom_density()
 ### Posssible priors ###
 get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
-            (1 | site/plot),
+            (1 | site/plot) + (1|botanist_year),
           data = sites)
 ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
   stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +

### 2022-12-07 R/model_recovery_calculation.R

@@ -144,12 +144,12 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
             (1 | site/plot) + (1|botanist_year),
           data = sites)
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for Intecepts")
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .8)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for treatments")
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
@@ -169,23 +169,15 @@ seed = 123
 warmup = floor(iter / 2)
 priors <- c(
   set_prior("normal(-1, 1)", class = "Intercept"),
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
-  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
-  set_prior("normal(-0.1, 1)", class = "b", coef = "expositionsouth"),
-  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
-  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
-  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
+  set_prior("normal(0, .8)", class = "b"),
+  set_prior("normal(0.1, .8)", class = "b", coef = "sand_ratio25"),
+  set_prior("normal(0.2, .8)", class = "b", coef = "sand_ratio50"),
+  set_prior("normal(-0.1, .8)", class = "b", coef = "expositionsouth"),
+  set_prior("normal(0.1, .8)", class = "b", coef = "survey_year_fct2019"),
+  set_prior("normal(0.2, .8)", class = "b", coef = "survey_year_fct2020"),
[…]

### 2022-12-08 R/model_recovery_check.Rmd
Update recovery

@@
 ```
-
+<br/>
+<br/>
 <b>Markus Bauer</b>
@@
 
-### Load models (6.G)
+### Load models (BARG 5.B/6.G)
 
@@
 ```{r load-models, collapse = TRUE, message = FALSE}
+load(file = here("outputs", "models", "model_recovery_2.Rdata"))
 load(file = here("outputs", "models", "model_recovery_full.Rdata"))
-load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
 load(file = here("outputs", "models", "model_recovery_2_prior.Rdata"))
 # BARG 5.A/B/C
-#load(file = here("outputs", "models", "model_recovery_2_flat.Rdata"))
-m_1 <- m_full
-m_2 <- mfull_prior
+load(file = here("outputs", "models", "model_recovery_2_flat.Rdata"))
+m_1 <- m2
+m_2 <- m2_flat
+#m_2 <- m_full
 m_prior <- m2_prior
@@
 ```
+
+NUTS sampler is used.
 
@@
     variable = c(
+      "Intercept",
       "b_sand_ratio25",
@@
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for Intecepts")
+  ggtitle("Normal distribution for Intecept")
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
@@
 loo1
-#loo2
+loo2
 #plot(loo1)
@@
 
-```{r autocorrelation, fig.height = 7}
-mcmc_acf(posterior1, lags = 10, facet_args = list(ncol = 4))
-#mcmc_acf(posterior2, lags = 10, facet_args = list(ncol = 4))
+```{r autocorrelation}
+mcmc_acf(posterior1, lags = 10)
+mcmc_acf(posterior2, lags = 10)
 ```
@@
 
-### Conditional <i>R</i>^2 values
+### Conditional <i>R</i><sup>2</sup> values
 
@@
 
-### Marginal <i>R</i>^2 values
+### Marginal <i>R</i><sup>2</sup> values
 
@@
 
-```{r posteriors-chosen-model}
-mcmc_intervals(
-  posterior1,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
+```{r posteriors}
+combined <- rbind(
+  mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95),
+  mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95)
+  )
+combined$model <- rep(
+  c("Model 1", "Model 2"),
+  each = ncol(posterior1)
+  )
+pos <- position_nudge(y = ifelse(combined$model == "Model 2", 0, 0.1))
+ggplot(data = combined, aes(x = m, y = parameter, color = model)) + 
+  geom_linerange(aes(xmin = l, xmax = h), position = pos, size = 2) +
+  geom_linerange(aes(xmin = ll, xmax = hh), position = pos) +
+  geom_point(position = pos, color = "black")
 ```

### 2022-12-08 R/model_recovery_calculation.R

@@ -146,7 +146,7 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
 ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for Intecepts")
+  ggtitle("Normal distribution for Intecept")
 ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .8)) +
   expand_limits(y = 0) +
@@ -163,6 +163,7 @@ ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
 
 ### b Model specifications -----------------------------------------------------
 
+# NUTS sampler used
 iter = 20000
 chains = 4
 thin = 2

### 2022-12-08 R/model_fcs_check.Rmd
Update persistence and fcs

@@
 
-```{r autocorrelation, fig.height = 7}
+```{r autocorrelation}
 mcmc_acf(posterior1, lags = 10)
@@
 
-### Conditional <i>R</i>² values
+### Conditional <i>R</i><sup>2</sup> values
 
@@
 
-### Marginal <i>R</i>² values
+### Marginal <i>R</i><sup>2</sup> values
 

### 2022-12-08 R/model_persistence_check.Rmd
Update persistence and fcs

@@
 
-### Load models (BARG 6.G)
+### Load models (BARG 5.B/6.G)
 

### 2022-12-08 R/model_fcs_calculation.R

@@ -164,6 +164,7 @@ ggplot(data.frame(x = c(-5, 5)), aes(x = x)) +
 
 ### b Model specifications -----------------------------------------------------
 
+# NUTS sampler used
 iter = 10000
 chains = 4
 thin = 2

### 2022-12-08 R/model_persistence_calculation.R

@@ -161,6 +161,7 @@ ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
 
 ### b Model specifications -----------------------------------------------------
 
+# NUTS sampler used
 iter = 10000
 chains = 4
 thin = 2

### 2022-12-08 R/model_fcs_check.Rmd
Update markdown

@@
     fig_height: 5
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 ```
-<br/>
-<br/>
-<b>Markus Bauer</b>
 
-Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
+<br/> <br/> <b>Markus Bauer</b>
 
-[markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
+Technichal University of Munich, TUM School of Life Sciences, Chair of
+Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
+
+[markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de)
 
 ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
-<br>
-[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
-<br>
-GitHub: [markus1bauer](https://github.com/markus1bauer)
+<br> [Google
+Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
+<br> GitHub: [markus1bauer](https://github.com/markus1bauer)
 
-To compare different models, you only have to change the models in section 'Load models'
+To compare different models, you only have to change the models in
+section 'Load models'
 
@@
 
-Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
+Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers
+Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
 
-Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI:
+10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
 
-Analysis guided by
-<br>
-<b>BARG</b> (Bayesian Analysis Reporting Guidelines): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
-<br>
-Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
-<br>
-Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
-<br>
-Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
+Analysis guided by <br> <b>BARG</b> (Bayesian Analysis Reporting
+Guidelines): Kruschke (2021) Nat Hum Behav [DOI:
+10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<br> Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI:
+10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378) <br> Priors:
+Lemoine (2019) Oikos [DOI:
+10.1111/oik.05985](https://doi.org/10.1111/oik.05985) <br> Model check:
+Deapoli & Schoot (2017) Psychol Methods [DOI:
+10.1037/met0000065](https://doi.org/10.1037/met0000065)
 
@@
 # BARG 5.A/B/C
-#load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
+load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
 m_1 <- m2
@@
 m_prior <- m2_prior
+m_flat <- m2_flat
 ```
@@
 ```{r analysis-preparation}
-posterior1 <- m_1 %>%
-  posterior::as_draws() %>%
-  posterior::subset_draws(
-    variable = c(
+# Chose variables
+variables <- c(
+      "Intercept",
       "b_sand_ratio25",
@@
     )
-  )
+# Subset draws
+posterior1 <- m_1 %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(variable = variables)
 posterior2 <- m_2 %>%
   posterior::as_draws() %>%
-  posterior::subset_draws(
-    variable = c(
-      "b_sand_ratio25",
-      "b_sand_ratio50",
-      "b_substrate_depth15",
-      "b_target_typedry_grassland",
-      "b_seed_density8",
-      "b_expositionsouth",
-      "b_survey_year_fct2019",
-      "b_survey_year_fct2020",
-      "b_survey_year_fct2021",
-      "sd_site__Intercept",
-      "sd_site:plot__Intercept",
-      "sigma"
-    )
-  )
+  posterior::subset_draws(variable = variables)
 posterior_prior <- m_prior %>%
   posterior::as_draws() %>%
-  posterior::subset_draws(
-    variable = c(
-      "Intercept",
-      "b_sand_ratio25",
-      "b_sand_ratio50",
-      "b_substrate_depth15",
-      "b_target_typedry_grassland",
-      "b_seed_density8",
-      "b_expositionsouth",
-      "b_survey_year_fct2019",
-      "b_survey_year_fct2020",
-      "b_survey_year_fct2021"
-    )
-  )
+  posterior::subset_draws(variable = variables)
+posterior_flat <- m_flat %>%
+  posterior::as_draws() %>%
+  posterior::subset_draws(variable = variables)
+# R hat
+rhat1 <- rhat(m_1)
+rhat2 <- rhat(m_2)
+# NEFF ratio
+neff1 <- neff_ratio(m_1)
+neff2 <- neff_ratio(m_2)
+# Long format of draws
 hmc_diagnostics1 <- brms::nuts_params(m_1)
@@
 y <- sites$n
+# Posterior predictive distribution
 yrep1 <- brms::posterior_predict(m_1, draws = 500)
 yrep2 <- brms::posterior_predict(m_2, draws = 500)
+# Leave-one-out cross validation based on posterior likelihood
 loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
 loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
+# Summary statistics
 draws1 <- m_1 %>%
@@
 
-#### Prior predictive check (BARG 1.E)
-
-```{r prior-predictive-check}
-bayesplot::mcmc_intervals(
-  posterior_prior,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
-```
-
 ## Model check
@@
 ```{r rhat, collapse = TRUE}
-mcmc_rhat(draws1$rhat)
-mcmc_rhat(draws2$rhat)
+mcmc_rhat(rhat1)
+mcmc_rhat(rhat2)
 ```
@@
 ```{r ess, collapse = TRUE}
-mcmc_neff(neff_ratio(m_1))
-mcmc_neff(neff_ratio(m_2))
+mcmc_neff(neff1)
+mcmc_neff(neff2)
 ```
@@
 
-Chosen model:
-
-```{r posteriors-chosen-model}
-mcmc_intervals(
-  posterior1,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
-```
-
-Second model:
-
-```{r posterors-2nd-model}
-mcmc_intervals(
-  posterior2,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
+```{r posteriors, fig.height = 7}
+combined <- rbind(
+  bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95)
+  )
+combined$model <- rep(
+  c("m_1", "m_2", "m_flat", "m_prior"),
+  each = posterior1$"1" %>% as_tibble() %>% ncol()
+  )
+pos <- position_nudge(
+  y = if_else(
+    combined$model == "m_2", -.2, if_else(
+      combined$model == "m_prior", -.4, if_else(
+        combined$model == "m_flat", -.6, 0
+        )
+      )
+    )
+  )
+ggplot(data = combined, aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)) + 
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_linerange(aes(xmin = l, xmax = h), position = pos, linewidth = 2) +
+  geom_linerange(aes(xmin = ll, xmax = hh), position = pos) +
+  geom_point(position = pos, color = "black") +
+  coord_cartesian(xlim = c(-1, .6)) +
+  bayesplot::theme_default() +
+  ggtitle("Posterior distbributions (mean, CI66, CI95)")
 ```
@@
 
-Effect sizes of chosen model just to get exact values of means etc. if necessary.
+Effect sizes of chosen model just to get exact values of means etc. if
+necessary.
 

### 2022-12-08 R/model_persistence_check.Rmd
Update markdown

@@
 # BARG 5.A/B/C
-#load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
+load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
 m_1 <- m2
@@
 ```{r rhat, collapse = TRUE}
-mcmc_rhat(draws1$rhat)
-mcmc_rhat(draws2$rhat)
+mcmc_rhat(rhat1)
+mcmc_rhat(rhat1)
 ```
@@
 
-Chosen model:
-
-```{r posteriors-chosen-model}
-mcmc_intervals(
-  posterior1,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
-```
-
-Second model:
-
-```{r posterors-2nd-model}
-bayesplot::mcmc_intervals(
-  posterior2,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
+```{r posteriors, fig.height = 7}
+combined <- rbind(
+  bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95)
+  )
+combined$model <- rep(
+  c("m_1", "m_2", "m_flat", "m_prior"),
+  each = posterior1$"1" %>% as_tibble() %>% ncol()
+  )
+pos <- position_nudge(
+  y = if_else(
+    combined$model == "m_2", -.2, if_else(
+      combined$model == "m_prior", -.4, if_else(
+        combined$model == "m_flat", -.6, 0
+        )
+      )
+    )
+  )
+ggplot(data = combined, aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)) + 
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_linerange(aes(xmin = l, xmax = h), position = pos, linewidth = 2) +
+  geom_linerange(aes(xmin = ll, xmax = hh), position = pos) +
+  geom_point(position = pos, color = "black") +
+  coord_cartesian(xlim = c(-1, 1)) +
+  bayesplot::theme_default() +
+  ggtitle("Posterior distbributions (mean, CI66, CI95)")
 ```

### 2022-12-08 R/model_recovery_check.Rmd
Update markdown

@@
 m_1 <- m2
-m_2 <- m2_flat
-#m_2 <- m_full
+m_2 <- m_full
 m_prior <- m2_prior
+m_flat <- m2_flat
 ```
@@
 ```{r histograms}
-#p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
-#p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
-#p1 / p2
-#ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-#ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
-#p1 / p2
-#ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-#ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
-#p1 / p2
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
-#p1 / p2
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
-#p1 / p2
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
-#p1 / p2
+p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
+p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+p1 / p2
+ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+p1 / p2
+ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 / p2
 ```
@@
 loo2
-#plot(loo1)
-#plot(loo2)
+plot(loo1)
+plot(loo2)
 ```
@@
 ```{r loo-pit}
-#p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-#p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
-#p1 / p2
+p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
+p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 / p2
 
@@
 
-Chosen model:
-
-```{r posteriors}
+```{r posteriors, fig.height = 7}
 combined <- rbind(
-  mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95),
-  mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95)
+  bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95)
   )
 combined$model <- rep(
-  c("Model 1", "Model 2"),
-  each = ncol(posterior1)
+  c("m_1", "m_2", "m_flat", "m_prior"),
+  each = posterior1$"1" %>% as_tibble() %>% ncol()
   )
-pos <- position_nudge(y = ifelse(combined$model == "Model 2", 0, 0.1))
-ggplot(data = combined, aes(x = m, y = parameter, color = model)) + 
-  geom_linerange(aes(xmin = l, xmax = h), position = pos, size = 2) +
+pos <- position_nudge(
+  y = if_else(
+    combined$model == "m_2", -.2, if_else(
+      combined$model == "m_prior", -.4, if_else(
+        combined$model == "m_flat", -.6, 0
+        )
+      )
+    )
+  )
+ggplot(data = combined, aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)) + 
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_linerange(aes(xmin = l, xmax = h), position = pos, linewidth = 2) +
   geom_linerange(aes(xmin = ll, xmax = hh), position = pos) +
-  geom_point(position = pos, color = "black")
-```
-
-Second model:
-
-```{r posterors-2nd-model}
-mcmc_intervals(
-  posterior2,
-  prob = 0.66,
-  prob_outer = 0.95,
-  point_est = "mean"
-  ) +
-  theme_classic()
+  geom_point(position = pos, color = "black") +
+  coord_cartesian(xlim = c(-1, .6)) +
+  bayesplot::theme_default() +
+  ggtitle("Posterior distbributions (mean, CI66, CI95)")
 ```
@@
 ```{r effect-sizes}
-#emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
-#survey_year_fct, type = "response"))
+emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
+          survey_year_fct, type = "response")
 ```

### 2022-12-08 R/model_fcs_check.Rmd
Update markdowns

@@
     combined$model == "m_2", -.2, if_else(
-      combined$model == "m_prior", -.4, if_else(
-        combined$model == "m_flat", -.6, 0
+      combined$model == "m_flat", -.4, if_else(
+        combined$model == "m_prior", -.6, 0
         )

### 2022-12-09 R/model_fcs_check.Rmd
Update markdown

@@
 
-<br/> <br/> <b>Markus Bauer</b>
+<br/>
+<br/>
+<b>Markus Bauer</b>
 
@@
 ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
-<br> [Google
-Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
-<br> GitHub: [markus1bauer](https://github.com/markus1bauer)
+<br>
+[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
+<br>
+GitHub: [markus1bauer](https://github.com/markus1bauer)
 
@@
 
-Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI:
-10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
 
-Analysis guided by <br> <b>BARG</b> (Bayesian Analysis Reporting
-Guidelines): Kruschke (2021) Nat Hum Behav [DOI:
-10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
-<br> Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI:
-10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378) <br> Priors:
-Lemoine (2019) Oikos [DOI:
-10.1111/oik.05985](https://doi.org/10.1111/oik.05985) <br> Model check:
-Deapoli & Schoot (2017) Psychol Methods [DOI:
-10.1037/met0000065](https://doi.org/10.1037/met0000065)
+Analysis guided by
+<br>
+<b>BARG</b> (Bayesian Analysis Reporting
+Guidelines): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<br>
+Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
+<br>
+Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
+<br>
+Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
 
@@
 
-### Load models (BARG 5.B/6.G)
+### Load models (BARG 6.G)
 
@@
 yrep2 <- brms::posterior_predict(m_2, draws = 500)
+yrep_prior <- brms::posterior_predict(m_prior, draws = 500)
 # Leave-one-out cross validation based on posterior likelihood
@@
           data = sites)
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dnorm, n = 101, args = list(mean = 0, sd = 1)
-    ) +
+
+ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for Intercept")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 2)
-    ) +
+ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0.3, sd = 2)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dcauchy, n = 101, args = list(location = 0, scale = 1)
-    ) +
+ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) +
-  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
-  stat_function(
-    fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)
-    ) +
+  ggtitle("Cauchy distribution")
+ggplot(data.frame(x = c(-5, 5)), aes(x = x)) +
+  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) +
-  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+  ggtitle(expression(Student~italic(t)*"-distribution"))
 ```
@@
 brms::prior_summary(m_1, all = FALSE)
+```
+
+#### Prior predictive check (BARG 1.E)
+
+```{r prior-predictive-check}
+ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
+                 binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
+                 binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
+                 binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
+                 binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
+                 binwidth = 0.1) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
+                 binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
+ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
+                 binwidth = 0.2) +
+  coord_cartesian(xlim = c(-2, 2))
 ```
@@
 ```{r histogram}
-#p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
-#p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
-#p1 / p2
-#ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-#ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
-#p1 / p2
-#ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-#ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
-#p1 / p2
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
-#p1 / p2
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
-#p1 / p2
-#p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-#p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
-#p1 / p2
+p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
+p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+p1 / p2
+ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+p1 / p2
+ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
+ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+p1 / p2
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 / p2
 ```
@@
 
-### Forest plot
+### Forest plot(BARG 3.B/5.B)
 
@@
   bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95),
-  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95),
-  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95)
+  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95),
+  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95)
   )
@@
 ```{r effect-sizes}
-#emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
-#survey_year_fct, type = "response"))
+emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
+          survey_year_fct, type = "response"))
 ```

### 2022-12-09 R/model_persistence_check.Rmd
Update markdown

@@
 
-Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
+Persistence sensu Wilsey (2021) Restor Ecol [DOI: 10.1111/rec.13132](https://doi.org/10.1111/rec.13132)
 
@@
             seed_density + substrate_depth +
-            (1 | site/plot) + (1 | botanist_year),
+            (1 | site/plot) + (1|botanist_year),
           data = sites)
@@
   ggtitle("Beta distribution for Intercept")
-ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
-  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .2)) +
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .35)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
+ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0) +
-  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-.4, .4)), aes(x = x)) +
+  expand_limits(y = 0) + ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
+ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
@@
 
-### Forest plot
+### Forest plot (BARG 2.B/5.B)
 

### 2022-12-09 R/model_recovery_check.Rmd
Update markdown

@@
 GitHub: [markus1bauer](https://github.com/markus1bauer)
-<br/>
-<br/>
-Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
+
+To compare different models, you only have to change the models in section 'Load models'
+
+# Preparation
+
+Recovery sensu Rydgren et al. (2019)  [DOI: 10.1111/1365-2664.13254](https://doi.org/10.1111/1365-2664.13254)
 
@@
 Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
-
-To compare different models, you only have to change the models in section 'Load models'
-
-# Preparation
 
@@
 
-```{r possible priors}
+```{r possible-priors}
 get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
@@
 
-### Forest plot
+### Forest plot (BARG 3.B/5.B)
 

### 2022-12-09 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
   geom_point(position = pos, color = "black") +
-  coord_cartesian(xlim = c(-1, .6)) +
+  coord_cartesian(xlim = c(-1, 1)) +
   bayesplot::theme_default() +
@@
 emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
-          survey_year_fct, type = "response"))
+          survey_year_fct, type = "response")
 ```

### 2022-12-09 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 ```{r posteriors, fig.height = 7}
-combined <- rbind(
-  bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95),
-  bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95),
-  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95),
-  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95)
+combined <- bind_rows(
+  bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95) %>%
+    mutate(model = "m_1"),
+  bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95) %>%
+    mutate(model = "m_2"),
+  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95) %>%
+    mutate(model = "m_flat"),
+  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95) %>%
+    mutate(model = "m_prior")
   )
-combined$model <- rep(
-  c("m_1", "m_2", "m_flat", "m_prior"),
-  each = posterior1$"1" %>% as_tibble() %>% ncol()
-  )
+
 pos <- position_nudge(
@@
   )
+
 ggplot(data = combined, aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)) + 

### 2022-12-09 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

@@
 
-Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+Bayesian analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
 
@@
 
-```{r bayes-factor}
-brms::bayes_factor(m_1, m_2)
+```{r bayes-factor-1, results = FALSE}
+bayes_factor <- brms::bayes_factor(m_1, m_2)
+```
+
+```{r bayes-factor-2}
+bayes_factor
 ```
@@
 ```{r effect-sizes}
+draws1
 emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |

### 2022-12-09 R/model_persistence_check.Rmd
Update markdown

@@
 ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
                  binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
                  binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
                  binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
                  binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
                  binwidth = 0.1) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
                  binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
                  binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+  coord_cartesian(xlim = c(-1, 1))
 ```
@@
   geom_point(position = pos, color = "black") +
-  coord_cartesian(xlim = c(-1, 1)) +
+  coord_cartesian(xlim = c(-.25, .65)) +
   bayesplot::theme_default() +
@@
 ```{r effect-sizes}
+draws1
 emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
-          survey_year_fct, type = "response"))
+          survey_year_fct, type = "response")
 ```

### 2022-12-09 R/model_recovery_check.Rmd
Update markdown

@@
 ---
-title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence"
+title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Recovery completeness"
 author: "<b>Markus Bauer</b> <br>"
@@
 
-```{r setup, include=FALSE}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(
@@
 
-Recovery sensu Rydgren et al. (2019)  [DOI: 10.1111/1365-2664.13254](https://doi.org/10.1111/1365-2664.13254)
+Recovery completeness sensu Rydgren et al. (2019) J Appl Ecol [DOI: 10.1111/1365-2664.13254](https://doi.org/10.1111/1365-2664.13254)
 
-Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+Bayesian analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
 

### 2022-12-09 R/model_fcs_check.Rmd
Update

@@
           data = sites)
-
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+data <- data.frame(x = c(-5, 5))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
+  stat_function(fun = dnorm, xlim = c(min(data$x), q025), geom = "area") +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for Intercept")
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0.3, sd = 2)) +
@@
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
@@
   ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +

### 2022-12-09 R/model_persistence_check.Rmd
Update

@@
   ggtitle("Beta distribution for Intercept")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+data <- data.frame(x = c(-1, 1))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .35)) +
@@
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) + ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +

### 2022-12-09 R/model_recovery_check.Rmd
Update

@@
   ggtitle("Normal distribution for Intecept")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+data <- data.frame(x = c(-2, 2))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .8)) +
@@
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
@@
   ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +

### 2022-12-09 R/model_fcs_calculation.R

@@ -143,20 +143,21 @@ get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
             (1 | site/plot) + (1 | botanist_year),
           data = sites)
-
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+data <- data.frame(x = c(-5, 5))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
+  stat_function(fun = dnorm, xlim = c(min(data$x), q025), geom = "area") +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for Intercept")
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0.3, sd = 2)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) +
   ggtitle("Cauchy distribution")
-ggplot(data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) +
   ggtitle(expression(Student~italic(t)*"-distribution"))

### 2022-12-09 R/model_persistence_calculation.R

@@ -146,14 +146,15 @@ ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
   stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
   expand_limits(y = 0) +
   ggtitle("Beta distribution for Intercept")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+data <- data.frame(x = c(-1, 1))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .35)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) + ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) +
   ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard

### 2022-12-09 R/model_recovery_calculation.R

@@ -147,15 +147,16 @@ ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for Intecept")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+data <- data.frame(x = c(-2, 2))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .8)) +
   expand_limits(y = 0) +
   ggtitle("Normal distribution for treatments")
-ggplot(data = data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) +
   ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data.frame(x = c(-2, 2)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) +
   ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard

### 2022-12-14 manuscript.Rmd
Create manuscript.Rmd

---
title: "Dike experiment"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  bookdown::word_document2:
    reference_docx: 2111_Wissenschaftliche_Arbeit.docx # template containing the formatting you want to have in your knitted word document
    # number_sections: false # only works for html or pdf...
    # using bookdown cross-referencing of sections possible, for flextable with pictures: officedown::rdocx_document
fontfamily: Arial
fontsize: 11pt
geometry: margin = 1in
csl: journal-of-vegetation-science.csl
---

Chair of Restoration Ecology, TUM School of Life Sciences, Technichal University of Munich, Germany

\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de){.email}

Open Research: Data and code are permanently available on Zenodo under: <https://doi.org/10.XXXX>.

\clearpage

\newpage

```{r set.up, include = F}
# Create objects for easy access to the folders related to the project
figures_dir <- file.path("outputs", "figures")

# plot figures high resolution
knitr::opts_chunk$set(dpi = 600)

library(knitr) # importing figures

# read analysis
#rmarkdown::render(here::here("results", "scripts", "Models.Rmd"), quiet = TRUE) # quiet to not get text from rendering
```

# Abstract {.unnumbered}

We looked at blablabla

**keywords:** keyword1, keyword2, keyword3, keyword4, keyword5

# Introduction {.unnumbered}

Climate change is globally one of the main drivers restructuring species communities [@halsch2021; @parmesan2006; @hill2021]. [...] to answer the following questions:

-   Question 1?
-   Question 2?

# Material & Methods {.unnumbered}

## Study area {.unnumbered}

Text

## Data Collection {.unnumbered}

Text

## Statistical analyses {.unnumbered}

Text

# Results {.unnumbered}

# Discussion {.unnumbered}

Text

# Conclusions

Text

# Acknowledgements {.unnumbered}

# References {.unnumbered}

::: {#refs}
:::

\clearpage

\newpage

# Figure legends {.unnumbered}

**Figure 1:**

Description Figure 1.

**Figure 2:** Description Figure 2.

**Figure 3:** Description Figure 3.

\clearpage

\newpage

**Figure 1:**

```{r chunk-figure1, fig.cap = "", echo=FALSE}
include_graphics(here::here(figures_dir, "figure_1_map_tmap_300dpi_8x11cm.tiff"))
```

\clearpage

\newpage

**Figure 2:**

```{r chunk-figure2, fig.cap = "", echo = FALSE}
include_graphics(here::here(figures_dir, "figure_2_800dpi_16.5x5cm.tiff"))
```

\clearpage

\newpage

# Supplementary Material {.unnumbered}

**Figure S1:**

```{r chunk-supp-1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Legend Figure S1", dpi=600}
#include_graphics(here::here("text", "supplementary", "figureS1.png"))
```

\clearpage

\newpage

**Figure S2:**

```{r chunk-supp-2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Legend Figure S2", dpi=600}
#include_graphics(here::here("text", "supplementary", "figureS2.png"))
```

\clearpage

\newpage

## Session Info

*R version, the OS and attached or loaded packages:*

```{r sessioninfo}
sessionInfo()
```

### 2022-12-14 manuscript.Rmd
Start manuscript

@@
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
-output:
-  bookdown::word_document2:
-    reference_docx: 2111_Wissenschaftliche_Arbeit.docx # template containing the formatting you want to have in your knitted word document
-    # number_sections: false # only works for html or pdf...
-    # using bookdown cross-referencing of sections possible, for flextable with pictures: officedown::rdocx_document
-fontfamily: Arial
+output: bookdown::html_document2
+fontfamily: Times New Roman
 fontsize: 11pt
 geometry: margin = 1in
-csl: journal-of-vegetation-science.csl
+csl: template-journal-of-vegetation-science.csl
+bibliography: bibliography.bib
+github-repo: markus1bauer/2023_danube_dike_experiment
 ---
 
-Chair of Restoration Ecology, TUM School of Life Sciences, Technichal University of Munich, Germany
+Chair of Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
 
-\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de){.email}
+\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de)
 
 Open Research: Data and code are permanently available on Zenodo under: <https://doi.org/10.XXXX>.
+
+**Max 8000 words**
 
@@
 
-```{r set.up, include = F}
-# Create objects for easy access to the folders related to the project
-figures_dir <- file.path("outputs", "figures")
-
-# plot figures high resolution
-knitr::opts_chunk$set(dpi = 600)
-
-library(knitr) # importing figures
+```{r set-up, include = F}
+library(knitr)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  dpi = 100
+  )
 
@@
 
-# Abstract {.unnumbered}
+# Abstract (max 300 words) {.unnumbered}
 
@@
 
-**keywords:** keyword1, keyword2, keyword3, keyword4, keyword5
+# Keywords {.unnumbered}
 
-# Introduction {.unnumbered}
+dike grassland
 
-Climate change is globally one of the main drivers restructuring species communities [@halsch2021; @parmesan2006; @hill2021]. [...] to answer the following questions:
+embankment
 
--   Question 1?
--   Question 2?
+species composition
 
-# Material & Methods {.unnumbered}
+environmental filter
 
-## Study area {.unnumbered}
+\clearpage
+
+\newpage
+
+# Introduction
+
+"Ecological theory can point restoration toward important processes that need manipulation [...].
+However, for this information to be relevant, restoration ecology needs to employ evidence-based assessments [...]" (Suding 2011) --\> No evidence for theory with our project
+
+-   Endangered grasslands
+
+-   Predictability of restorations --\> experiments, evidence-based restoration (cooke 2018)
+
+-   Brudvig 2017 among restoration outcomes and in comparison to reference
+
+-   Substrate modification to influence habitat filtering
+
+-   Sowing a typical approach + priority effects + species pool
+
+-   Introduce FCS, Recovery time, Persistence
+
+-   Dike grasslands as case study
+
+-   The aim of the study is
+
+We asked following question to evaluate the restoration success after four years:
+
+1.  How close is the vegetation to the reference state?
+
+2.  How strong differs the Favourable Conservation Status (FCS) among the seed mixture-substrate combinations?
+
+3.  How strong differs the persistence of the sown species among the seed mixture-substrate combinations?
+
+\clearpage
+
+\newpage
+
+# Material & Methods
+
+## Experimental design {.unnumbered}
+
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
+The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm (**Deutscher Wetterdienst [DWD], 2021**).
+During the study, three exceptionally dry years (2018--2020) occurred **(Climate Data Center of the German Meteorological Service [CDC], 2022a, 2022b**), and three minor floods which did not reach the plots (**Bayerisches Landesamt für Umwelt [LfU], 2021a, 2021b)** (Table \@ref(tab:table-s1)).
+Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <mark>Is that right?</mark> and a with an excavator the substrates were mixed <mark>Is that right?</mark> and the plots prepared.
+The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, **Mucina et al., 2016**).
+The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <mark>check numbers</mark>, respectively.
+The seeds were received from a commercial producer of autochtonous seeds.
+From the species pools, 20 species were randomly selected for each plot.
+The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:table-2))<mark>check</mark>.
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:table-3)) <mark>more details and check</mark>.
+The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
+In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.
+
+We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates).
+The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-1)).
+The split plot was cuased by testing all 24 treatments on both sides of the dike.
+We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs.
+30 cm).
+Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:table-1)).
+The two seed mixture types were tested with two seeding densities (4 vs.
+8 g m-2).
+The vegetation was surveyed in June or July 2018--2021 (**Braun-Blanquet, 1928/1964**).
+Establishment rates of species
+
+## Statistical analyses {.unnumbered}
+
+We performed all analyses in R (Version 4.2.2; @base), with the functions 'blme' (based on 'lme4') for BLMM [@lme4] **(Bates, Mächler, Bolker, & Walker, 2015; Chung, Rabe-Hesketh, Dorie, Gelman, & Liu, 2013)**; and 'DHARMa' for model evaluation [@DHARMa].
+
+<mark>We calculated Bayesian linear mixed-effects models (BLMM) with the random effect 'plot' and used the restricted maximum-likelihood estimation (REML), the optimiser Nelder-Mead and, for the random effect, the Wishart prior.
+To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model (Appendix A4).
+Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95% confidence intervals of the response variables.</mark>
+
+\clearpage
+
+\newpage
+
+# Results
+
+Figure @ref(fig:figure-1)
+
+@teixeira2022
+
+\clearpage
+
+\newpage
+
+# Discussion
 
@@
 
-## Data Collection {.unnumbered}
+\clearpage
 
-Text
-
-## Statistical analyses {.unnumbered}
-
-Text
-
-# Results {.unnumbered}
-
-# Discussion {.unnumbered}
-
-Text
+\newpage
 
@@
 
+\clearpage
+
+\newpage
+
 # Acknowledgements {.unnumbered}
+
+We would like to thank our project partners Dr.
+Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) for numerous discussions on restoration and management of dike grasslands.
+Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
+<mark>Mention Naturschutzbehörde and funding from WIGES.</mark> We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H.
+Teixeira, and Linda Weggler for assisting with the field surveys or soil analyses in 2018--2020.
+The German Federal Environmental Foundation (DBU) supported MB with a doctoral scholarship.
+
+# Author contribution {.unnumbered}
+
+JH and JK designed the experiment. JH did the surveys in the years 2018--2020 and MB in 2019 and 2021. MB did the analyses and wrote the manuscript. JK and JH critically revised the manuscript.
+
+# Open research {.unnumbered}
+
+Data and code is available on Zenodo: <mark><https://doi.org/10.XXXX></mark>
+
+Model evaluation is stored on GitHub: [github.com/markus1bauer/2023_danube_dike_experiment](https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown)
+
+# Funding {.unnumbered}
+
+MB is funded by a doctoral scholarship of the German Federal Environmental Foundation (DBU) (No.
+20021/698).
+The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020.
 
@@
 
-# Figure legends {.unnumbered}
+# Tables {.unnumbered}
 
-**Figure 1:**
+## Table 1 {.unnumbered}
 
-Description Figure 1.
-
-**Figure 2:** Description Figure 2.
-
-**Figure 3:** Description Figure 3.
-
-\clearpage
-
-\newpage
-
-**Figure 1:**
-
-```{r chunk-figure1, fig.cap = "", echo=FALSE}
-include_graphics(here::here(figures_dir, "figure_1_map_tmap_300dpi_8x11cm.tiff"))
+```{r table-1, fig.cap = ""}
+#include_graphics(here::here("outputs", "tables", "figureS1.png"))
 ```
@@
 
-**Figure 2:**
+## Table 2 {.unnumbered}
 
-```{r chunk-figure2, fig.cap = "", echo = FALSE}
-include_graphics(here::here(figures_dir, "figure_2_800dpi_16.5x5cm.tiff"))
+```{r table-2, fig.cap = ""}
+#include_graphics(here::here("outputs", "tables", "figureS1.png"))
 ```
+
+\clearpage
+
+\newpage
+
+# Figure legends {.unnumbered}
+
+## Figure 1 {.unnumbered}
+
+```{r figure-1, fig.cap = "figure-1"}
+knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
+```
+
+\clearpage
+
+\newpage
+
+## Figure 2 {.unnumbered}
+
+```{r figure-2, fig.cap = ""}
+knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
+```
+
+\clearpage
+
+\newpage
+
+## Figure 3 {.unnumbered}
+
+```{r figure-3, fig.cap = ""}
+knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
+```
+
+\clearpage
+
+\newpage
+
+## Figure 4 {.unnumbered}
+
+```{r figure-4, fig.cap = ""}
+knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
+```
+
+\clearpage
+
+\newpage
+
+## Figure 5 {.unnumbered}
+
+```{r figure-5, fig.cap = ""}
+knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
+```
+
+Fig. 5:
+
+\clearpage
+
+\newpage
+
+## Figure 6 {.unnumbered}
+
+```{r figure-6, fig.cap = ""}
+knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
+```
+
+Fig. 6:
 
@@
 
-**Figure S1:**
+## Table S1 {.unnumbered}
 
-```{r chunk-supp-1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Legend Figure S1", dpi=600}
-#include_graphics(here::here("text", "supplementary", "figureS1.png"))
+Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten (mean, 1981--2010; ID, 3271; WGS84 (lat/lon), 48.85476 and 12.918911; CDC, 2022a, 2022b) and stream gauge Pfelling (ID, 10078000; WGS84 (lat/lon), 48.87975 and 12.74716; LfU, 2021a).
+HQ2 = Highest discharge with a probability of occurrence every second year.
+HSW = Highest water level for shipping.
+
+```{r table-s1}
+#knitr::include_graphics(here::here("outputs", "tables", "figureS1.png"))
 ```
@@
 
-**Figure S2:**
+## Table S2 {.unnumbered}
 
-```{r chunk-supp-2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Legend Figure S2", dpi=600}
-#include_graphics(here::here("text", "supplementary", "figureS2.png"))
+```{r table-s2}
+#knitr::include_graphics(here::here("outputs", "tables", "figureS2.png"))
 ```
@@
 
-## Session Info
+## Table S3 {.unnumbered}
 
-*R version, the OS and attached or loaded packages:*
+```{r table-s3}
+#knitr::include_graphics(here::here("outputs", "tables", "table_a3_seedmixes.csv"))
+```
+
+\clearpage
+
+\newpage
+
+## Session Info {.unnumbered}
 

### 2022-12-14 R/model_fcs_check.Rmd
Update FCS markdown

--- 2022-12-09 R/model_fcs_check.Rmd
@@
     )
+sites
 ```
@@
           data = sites)
-
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+data <- data.frame(x = c(-5, 5))
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
@@
   ggtitle("Normal distribution for Intercept")
-ggplot(data = data.frame(x = c(-5, 5)), aes(x = x)) +
+ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0.3, sd = 2)) +
@@
 ```{r effect-sizes}
-draws1
+draws1 %>%
+  gt::gt()
 emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |

### 2022-12-14 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd

@@
   )
+sites
 ```

### 2022-12-14 manuscript.Rmd
Update manuscript

@@
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
-output: bookdown::html_document2
-fontfamily: Times New Roman
-fontsize: 11pt
+output:
+  bookdown::word_document2:
+  reference_docx: StylesTemplate.docx
+fontfamily: Arial
+fontsize: 10pt
 geometry: margin = 1in
@@
 
-```{r set-up, include = F}
+```{r set-up, include = FALSE}
 library(knitr)
@@
   echo = FALSE,
-  dpi = 100
+  dpi = 50
   )
@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm (**Deutscher Wetterdienst [DWD], 2021**).
-During the study, three exceptionally dry years (2018--2020) occurred **(Climate Data Center of the German Meteorological Service [CDC], 2022a, 2022b**), and three minor floods which did not reach the plots (**Bayerisches Landesamt für Umwelt [LfU], 2021a, 2021b)** (Table \@ref(tab:table-s1)).
+During the study, three exceptionally dry years (2018--2020) occurred **(Climate Data Center of the German Meteorological Service [CDC], 2022a, 2022b**), and three minor floods which did not reach the plots (**Bayerisches Landesamt für Umwelt [LfU], 2021a, 2021b)** (Table \@ref(table-s1)).
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <mark>Is that right?</mark> and a with an excavator the substrates were mixed <mark>Is that right?</mark> and the plots prepared.
@@
 From the species pools, 20 species were randomly selected for each plot.
-The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:table-2))<mark>check</mark>.
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:table-3)) <mark>more details and check</mark>.
+The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(table-2))<mark>check</mark>.
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(table-3)) <mark>more details and check</mark>.
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
@@
 We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates).
-The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-1)).
+The experiment used a split plot design combined with randomized complete block design (Figure \@ref(figure-1)).
 The split plot was cuased by testing all 24 treatments on both sides of the dike.
@@
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:table-1)).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(table-1)).
 The two seed mixture types were tested with two seeding densities (4 vs.
-8 g m-2).
+8 g m^-2 ).
 The vegetation was surveyed in June or July 2018--2021 (**Braun-Blanquet, 1928/1964**).
@@
 
-We performed all analyses in R (Version 4.2.2; @base), with the functions 'blme' (based on 'lme4') for BLMM [@lme4] **(Bates, Mächler, Bolker, & Walker, 2015; Chung, Rabe-Hesketh, Dorie, Gelman, & Liu, 2013)**; and 'DHARMa' for model evaluation [@DHARMa].
+We performed all analyses in R (Version 4.2.2; @base), with the functions 'blme' (based on 'lme4') for BLMM [@lme4] **Chung, Rabe-Hesketh, Dorie, Gelman, & Liu, 2013)**; and 'DHARMa' for model evaluation [@DHARMa].
 
@@
 
-Figure @ref(fig:figure-1)
-
-@teixeira2022
+Figure \@ref(figure-1)
 
@@
 The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020.
+<mark>funding number WIGES</mark>
 
@@
 
-```{r table-1, fig.cap = ""}
+```{r table-1, fig.cap = "table-1"}
 #include_graphics(here::here("outputs", "tables", "figureS1.png"))
@@
 
-# Figure legends {.unnumbered}
+# Figures {.unnumbered}
 
@@
 
-```{r figure-1, fig.cap = "figure-1"}
+```{r figure-1, fig.cap = ""}
 knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
@@
 ```{r figure-2, fig.cap = ""}
-knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
+#knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
 ```
@@
 ```{r figure-3, fig.cap = ""}
-knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
+#knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
 ```
@@
 ```{r figure-4, fig.cap = ""}
-knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
+#knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
 ```
@@
 ```{r figure-5, fig.cap = ""}
-knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
+#knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
 ```
@@
 ```{r figure-6, fig.cap = ""}
-knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
+#knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
 ```

### 2022-12-15 manuscript.Rmd
Update manuscript

@@
   bookdown::word_document2:
-  reference_docx: StylesTemplate.docx
-fontfamily: Arial
-fontsize: 10pt
-geometry: margin = 1in
+    reference_docx: template_word.docx
+    global_numbering: TRUE
 csl: template-journal-of-vegetation-science.csl
 bibliography: bibliography.bib
-github-repo: markus1bauer/2023_danube_dike_experiment
 ---
 
-Chair of Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
+Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
 
@@
 
+See Figure \@ref(fig:figure-map)
+
 \clearpage
@@
 ```{r set-up, include = FALSE}
+library(bookdown)
 library(knitr)
@@
 # Abstract (max 300 words) {.unnumbered}
-
-We looked at blablabla
 
@@
 The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
-The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm (**Deutscher Wetterdienst [DWD], 2021**).
-During the study, three exceptionally dry years (2018--2020) occurred **(Climate Data Center of the German Meteorological Service [CDC], 2022a, 2022b**), and three minor floods which did not reach the plots (**Bayerisches Landesamt für Umwelt [LfU], 2021a, 2021b)** (Table \@ref(table-s1)).
+The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021].
+During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(table-s1)).
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <mark>Is that right?</mark> and a with an excavator the substrates were mixed <mark>Is that right?</mark> and the plots prepared.
-The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, **Mucina et al., 2016**).
+The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016 ).
 The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <mark>check numbers</mark>, respectively.
@@
 The two seed mixture types were tested with two seeding densities (4 vs.
-8 g m^-2 ).
+8 g m\^-2 ).
 The vegetation was surveyed in June or July 2018--2021 (**Braun-Blanquet, 1928/1964**).
@@
 # Results
-
-Figure \@ref(figure-1)
 
@@
 
-```{r figure-1, fig.cap = ""}
+```{r figure-1, fig.cap = "\\label{fig:figure-1}This is a caption"}
 knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))

### 2022-12-15 manuscript.tex
Update manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Dike experiment},
  pdfauthor={Markus Bauer*, Jakob Huber, Johannes Kollmann},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Dike experiment}
\author{Markus Bauer*, Jakob Huber, Johannes Kollmann}
\date{}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany

* Corresponding author: \href{mailto:markus1.bauer@tum.de}{\nolinkurl{markus1.bauer@tum.de}}

Open Research: Data and code are permanently available on Zenodo under: \url{https://doi.org/10.XXXX}.

\textbf{Max 8000 words}

\clearpage

\newpage

\hypertarget{abstract-max-300-words}{%
\section*{Abstract (max 300 words)}\label{abstract-max-300-words}}
\addcontentsline{toc}{section}{Abstract (max 300 words)}

\ref{fig:figure-1}

\hypertarget{keywords}{%
\section*{Keywords}\label{keywords}}
\addcontentsline{toc}{section}{Keywords}

dike grassland

embankment

species composition

environmental filter

\clearpage

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

``Ecological theory can point restoration toward important processes that need manipulation {[}\ldots{]}. However, for this information to be relevant, restoration ecology needs to employ evidence-based assessments {[}\ldots{]}'' (Suding 2011) --\textgreater{} No evidence for theory with our project

\begin{itemize}
\item
  Endangered grasslands
\item
  Predictability of restorations --\textgreater{} experiments, evidence-based restoration (cooke 2018)
\item
  Brudvig 2017 among restoration outcomes and in comparison to reference
\item
  Substrate modification to influence habitat filtering
\item
  Sowing a typical approach + priority effects + species pool
\item
  Introduce FCS, Recovery time, Persistence
\item
  Dike grasslands as case study
\item
  The aim of the study is
\end{itemize}

We asked following question to evaluate the restoration success after four years:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  How close is the vegetation to the reference state?
\item
  How strong differs the Favourable Conservation Status (FCS) among the seed mixture-substrate combinations?
\item
  How strong differs the persistence of the sown species among the seed mixture-substrate combinations?
\end{enumerate}

\clearpage

\newpage

\hypertarget{material-methods}{%
\section{Material \& Methods}\label{material-methods}}

\hypertarget{experimental-design}{%
\subsection*{Experimental design}\label{experimental-design}}
\addcontentsline{toc}{subsection}{Experimental design}

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \ref{figure-1}), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm (Deutscher Wetterdienst 2021). During the study, three exceptionally dry years (2018--2020) occurred (Climate Data Center of the German Meteorological Service 2022a; Climate Data Center of the German Meteorological Service 2022b), and three minor floods which did not reach the plots (\textbf{Bayerisches Landesamt für Umwelt {[}LfU{]}, 2021a, 2021b)} (Table \ref{table-s1}). Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike Is that right? and a with an excavator the substrates were mixed Is that right? and the plots prepared. The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, Mucina et al. (2016) ). The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species check numbers, respectively. The seeds were received from a commercial producer of autochtonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt\% of total seed mixture), three legumes (5\%) and ten herbs (35\%) (Table \ref{table-2})check. The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \ref{table-3}) more details and check. The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by `normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.

We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates). The experiment used a split plot design combined with randomized complete block design (Figure \ref{figure-1}). The split plot was cuased by testing all 24 treatments on both sides of the dike. We tested three substrates with 0\%, 25\% and 50\% sand admixture and two soil depths (15 vs.~30 cm). Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed. The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \ref{table-1}). The two seed mixture types were tested with two seeding densities (4 vs.~8 g m\^{}-2 ). The vegetation was surveyed in June or July 2018--2021 (\textbf{Braun-Blanquet, 1928/1964}). Establishment rates of species

\hypertarget{statistical-analyses}{%
\subsection*{Statistical analyses}\label{statistical-analyses}}
\addcontentsline{toc}{subsection}{Statistical analyses}

We performed all analyses in R (Version 4.2.2; R Core Team (2022)), with the functions `blme' (based on `lme4') for BLMM (Bates et al. 2015) \textbf{Chung, Rabe-Hesketh, Dorie, Gelman, \& Liu, 2013)}; and `DHARMa' for model evaluation (Hartig 2022).

We calculated Bayesian linear mixed-effects models (BLMM) with the random effect `plot' and used the restricted maximum-likelihood estimation (REML), the optimiser Nelder-Mead and, for the random effect, the Wishart prior. To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model (Appendix A4). Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95\% confidence intervals of the response variables.

\clearpage

\newpage

\hypertarget{results}{%
\section{Results}\label{results}}

\clearpage

\newpage

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Text

\clearpage

\newpage

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

Text

\clearpage

\newpage

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

We would like to thank our project partners Dr.~Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) for numerous discussions on restoration and management of dike grasslands. Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf). Mention Naturschutzbehörde and funding from WIGES. We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H. Teixeira, and Linda Weggler for assisting with the field surveys or soil analyses in 2018--2020. The German Federal Environmental Foundation (DBU) supported MB with a doctoral scholarship.

\hypertarget{author-contribution}{%
\section*{Author contribution}\label{author-contribution}}
\addcontentsline{toc}{section}{Author contribution}

JH and JK designed the experiment. JH did the surveys in the years 2018--2020 and MB in 2019 and 2021. MB did the analyses and wrote the manuscript. JK and JH critically revised the manuscript.

\hypertarget{open-research}{%
\section*{Open research}\label{open-research}}
\addcontentsline{toc}{section}{Open research}

Data and code is available on Zenodo: \url{https://doi.org/10.XXXX}

Model evaluation is stored on GitHub: \href{https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown}{github.com/markus1bauer/2023\_danube\_dike\_experiment}

\hypertarget{funding}{%
\section*{Funding}\label{funding}}
\addcontentsline{toc}{section}{Funding}

MB is funded by a doctoral scholarship of the German Federal Environmental Foundation (DBU) (No.~20021/698). The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020. funding number WIGES

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-lme4}{}}%
Bates, D., Machler, M., Bolker, B., \& Walker, S. 2015. \href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear mixed-effects models using {\textbraceleft}lme4{\textbraceright}}. 67:

\leavevmode\vadjust pre{\hypertarget{ref-cdc2022temp}{}}%
Climate Data Center of the German Meteorological Service. 2022a. \href{https://cdc.dwd.de/portal/}{Annual station observations of air temperature at 2 m above ground in °c for germany. Version v21.3: Station metten}.

\leavevmode\vadjust pre{\hypertarget{ref-cdc2022prec}{}}%
Climate Data Center of the German Meteorological Service. 2022b. \href{https://cdc.dwd.de/portal/}{Annual station observations of precipitation in mm for germany. Version v21.3: Station metten}.

\leavevmode\vadjust pre{\hypertarget{ref-dwd2021}{}}%
Deutscher Wetterdienst. 2021. \href{https://www.dwd.de}{Langjähriges mittel der wetterstation metten 1981-2010}.

\leavevmode\vadjust pre{\hypertarget{ref-DHARMa}{}}%
Hartig, F. 2022. \href{https://CRAN.R-project.org/package=DHARMa}{DHARMa: Residual diagnostics for hierarchical (multi-level / mixed) regression models}.

\leavevmode\vadjust pre{\hypertarget{ref-mucina2016}{}}%
Mucina, L., Bültmann, H., Dierßen, K., Theurillat, J.-P., Raus, T., Čarni, A., Šumberová, K., Willner, W., Dengler, J., García, R.G., Chytrý, M., Hájek, M., Di Pietro, R., Iakushenko, D., Pallas, J., Daniëls, F.J.A., Bergmeier, E., Santos Guerra, A., Ermakov, N., Valachovič, M., Schaminée, J.H.J., Lysenko, T., Didukh, Y.P., Pignatti, S., Rodwell, J.S., Capelo, J., Weber, H.E., Solomeshch, A., Dimopoulos, P., Aguiar, C., Hennekens, S.M., \& Tichý, L. 2016. \href{https://doi.org/10.1111/avsc.12257}{Vegetation of Europe: hierarchical floristic classification system of vascular plant, bryophyte, lichen, and algal communities} (R. Peet, Ed.). \emph{Applied Vegetation Science} 19: 3--264.

\leavevmode\vadjust pre{\hypertarget{ref-base}{}}%
R Core Team. 2022. \href{https://www.R-project.org/}{R: A language and environment for statistical computing}.

\end{CSLReferences}

\clearpage

\newpage

\hypertarget{tables}{%
\section*{Tables}\label{tables}}
\addcontentsline{toc}{section}{Tables}

\hypertarget{table-1}{%
\subsection*{Table 1}\label{table-1}}
\addcontentsline{toc}{subsection}{Table 1}

\clearpage

\newpage

\hypertarget{table-2}{%
\subsection*{Table 2}\label{table-2}}
\addcontentsline{toc}{subsection}{Table 2}

\clearpage

\newpage

\hypertarget{figures}{%
\section*{Figures}\label{figures}}
\addcontentsline{toc}{section}{Figures}

See Figure \ref{fig:figure-1}

\includegraphics{outputs/figures/figure_1_map_tmap_300dpi_8x11cm.tiff}

\clearpage

\newpage

\hypertarget{figure-2}{%
\subsection*{Figure 2}\label{figure-2}}
\addcontentsline{toc}{subsection}{Figure 2}

\clearpage

\newpage

\hypertarget{figure-3}{%
\subsection*{Figure 3}\label{figure-3}}
\addcontentsline{toc}{subsection}{Figure 3}

\clearpage

\newpage

\hypertarget{figure-4}{%
\subsection*{Figure 4}\label{figure-4}}
\addcontentsline{toc}{subsection}{Figure 4}

\clearpage

\newpage

\hypertarget{figure-5}{%
\subsection*{Figure 5}\label{figure-5}}
\addcontentsline{toc}{subsection}{Figure 5}

Fig. 5:

\clearpage

\newpage

\hypertarget{figure-6}{%
\subsection*{Figure 6}\label{figure-6}}
\addcontentsline{toc}{subsection}{Figure 6}

Fig. 6:

\clearpage

\newpage

\hypertarget{supplementary-material}{%
\section*{Supplementary Material}\label{supplementary-material}}
\addcontentsline{toc}{section}{Supplementary Material}

\hypertarget{table-s1}{%
\subsection*{Table S1}\label{table-s1}}
\addcontentsline{toc}{subsection}{Table S1}

Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten (mean, 1981--2010; ID, 3271; WGS84 (lat/lon), 48.85476 and 12.918911; CDC, 2022a, 2022b) and stream gauge Pfelling (ID, 10078000; WGS84 (lat/lon), 48.87975 and 12.74716; LfU, 2021a). HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.

\clearpage

\newpage

\hypertarget{table-s2}{%
\subsection*{Table S2}\label{table-s2}}
\addcontentsline{toc}{subsection}{Table S2}

\clearpage

\newpage

\hypertarget{table-s3}{%
\subsection*{Table S3}\label{table-s3}}
\addcontentsline{toc}{subsection}{Table S3}

\clearpage

\newpage

\hypertarget{session-info}{%
\subsection*{Session Info}\label{session-info}}
\addcontentsline{toc}{subsection}{Session Info}

\begin{verbatim}
## R version 4.2.2 (2022-10-31 ucrt)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 10 x64 (build 22621)
## 
## Matrix products: default
## 
## locale:
## [1] LC_COLLATE=German_Germany.utf8  LC_CTYPE=German_Germany.utf8   
## [3] LC_MONETARY=German_Germany.utf8 LC_NUMERIC=C                   
## [5] LC_TIME=German_Germany.utf8    
## 
## attached base packages:
## [1] stats     graphics  grDevices datasets  utils     methods   base     
## 
## other attached packages:
## [1] knitr_1.41    bookdown_0.31
## 
## loaded via a namespace (and not attached):
##  [1] here_1.0.1      rprojroot_2.0.3 digest_0.6.30   lifecycle_1.0.3
##  [5] magrittr_2.0.3  evaluate_0.19   highr_0.9       rlang_1.0.6    
##  [9] stringi_1.7.8   cli_3.4.1       renv_0.16.0     rstudioapi_0.14
## [13] vctrs_0.5.1     rmarkdown_2.18  tools_4.2.2     stringr_1.5.0  
## [17] glue_1.6.2      xfun_0.35       yaml_2.3.6      fastmap_1.1.0  
## [21] compiler_4.2.2  htmltools_0.5.3
\end{verbatim}

\end{document}

### 2022-12-15 manuscript.Rmd
Update

@@
 output:
-  bookdown::word_document2:
+  officedown::rdocx_document:
     reference_docx: template_word.docx
-    global_numbering: TRUE
 csl: template-journal-of-vegetation-science.csl
@@
 ---
+
+# Start
 
@@
 
-Open Research: Data and code are permanently available on Zenodo under: <https://doi.org/10.XXXX>.
+Open Research: Data and code are permanently available on Zenodo under: <!--# https://doi.org/10.XXXX -->.
 
 **Max 8000 words**
-
-See Figure \@ref(fig:figure-map)
-
-\clearpage
 
@@
 ```{r set-up, include = FALSE}
+library(knitr)
 library(bookdown)
-library(knitr)
+library(officedown)
+library(officer)
+library(tidyverse)
+library(flextable)
 knitr::opts_chunk$set(
   echo = FALSE,
+  message = FALSE,
   dpi = 50
+  )
+set_flextable_defaults(
+  font.family = "Times New Roman",
+  font.size = 10
   )
@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(table-s1)).
-Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <mark>Is that right?</mark> and a with an excavator the substrates were mixed <mark>Is that right?</mark> and the plots prepared.
+During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-s1)).
+Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
+--> and a with an excavator the substrates were mixed <!--# Is that right?
+--> and the plots prepared.
 The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016 ).
-The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <mark>check numbers</mark>, respectively.
+The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <!--# check numbers  -->, respectively.
 The seeds were received from a commercial producer of autochtonous seeds.
 From the species pools, 20 species were randomly selected for each plot.
-The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(table-2))<mark>check</mark>.
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(table-3)) <mark>more details and check</mark>.
+The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(fig:table-2))<!--# check  -->.
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:table-3)) <!--# More details and check  -->.
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
@@
 We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates).
-The experiment used a split plot design combined with randomized complete block design (Figure \@ref(figure-1)).
+The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-1)).
 The split plot was cuased by testing all 24 treatments on both sides of the dike.
@@
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(table-1)).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(fig:table-1)).
 The two seed mixture types were tested with two seeding densities (4 vs.
 8 g m\^-2 ).
-The vegetation was surveyed in June or July 2018--2021 (**Braun-Blanquet, 1928/1964**).
+The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964].
 Establishment rates of species
@@
 
-We performed all analyses in R (Version 4.2.2; @base), with the functions 'blme' (based on 'lme4') for BLMM [@lme4] **Chung, Rabe-Hesketh, Dorie, Gelman, & Liu, 2013)**; and 'DHARMa' for model evaluation [@DHARMa].
+We performed all analyses in R [Version 4.2.2; @base], with the functions 'blme' (based on 'lme4') for BLMM [@lme4, @chung2013]; and 'DHARMa' for model evaluation [@DHARMa].
 
@@
 We would like to thank our project partners Dr.
-Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) for numerous discussions on restoration and management of dike grasslands.
+Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) and Klaus Rachl and Stefan Radlmair (Regierung von Niederbayern) for numerous discussions on restoration and management of dike grasslands.
 Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
-<mark>Mention Naturschutzbehörde and funding from WIGES.</mark> We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H.
+We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H.
 Teixeira, and Linda Weggler for assisting with the field surveys or soil analyses in 2018--2020.
@@
 
-Data and code is available on Zenodo: <mark><https://doi.org/10.XXXX></mark>
+Data and code is available on Zenodo: <!--# https://doi.org/10.XXXX -->
 
@@
 The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020.
-<mark>funding number WIGES</mark>
+<!--# funding number of WIGES -->
 
@@
 
+<!---BLOCK_LANDSCAPE_START--->
+
 # Tables {.unnumbered}
 
-## Table 1 {.unnumbered}
+\## Table 1
 
-```{r table-1, fig.cap = "table-1"}
-#include_graphics(here::here("outputs", "tables", "figureS1.png"))
+Mischprobe aus mehreren Plots. Measured in \< 2mm fraction <!--# Write full description -->
+
+```{r table-1, fig.cap = "table_1"}
+read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
+  slice(-1) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  add_header_row(
+    top = FALSE,
+    values = read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>% slice(1)
+    ) %>%
+  fit_to_width(16.5, inc = 1L, max_iter = 20, unit = "cm")
 ```
@@
 
-```{r table-2, fig.cap = ""}
-#include_graphics(here::here("outputs", "tables", "figureS1.png"))
+Each plot received a individual set of 20 species with some restrictions to the number of species per functional group. <!--# Full description -->
+
+```{r table-2, fig.cap = "table_2"}
+read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  add_header_row(top = FALSE, values = c("", "", "#", "#", "%", "%")) %>%
+  autofit()
 ```
@@
 \clearpage
+
+<!---BLOCK_LANDSCAPE_STOP--->
 
@@
 
-```{r figure-1, fig.cap = "\\label{fig:figure-1}This is a caption"}
+```{r figure-1, fig.cap = "figure-1"}
 knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
@@
 
-```{r figure-2, fig.cap = ""}
+```{r figure-2, fig.cap = "figure-2"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
@@
 
-```{r figure-3, fig.cap = ""}
+```{r figure-3, fig.cap = "figure-3"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-4, fig.cap = ""}
+```{r figure-4, fig.cap = "figure-4"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-5, fig.cap = ""}
+```{r figure-5, fig.cap = "figure-5"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-6, fig.cap = ""}
+```{r figure-6, fig.cap = "figure-6"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
@@
 Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten (mean, 1981--2010; ID, 3271; WGS84 (lat/lon), 48.85476 and 12.918911; CDC, 2022a, 2022b) and stream gauge Pfelling (ID, 10078000; WGS84 (lat/lon), 48.87975 and 12.74716; LfU, 2021a).
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
 HQ2 = Highest discharge with a probability of occurrence every second year.
@@
 
-```{r table-s1}
-#knitr::include_graphics(here::here("outputs", "tables", "figureS1.png"))
+```{r table-s1, fig.cap = "table-s1"}
+read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
+  autofit()
 ```
@@
 
-```{r table-s2}
-#knitr::include_graphics(here::here("outputs", "tables", "figureS2.png"))
+Establishment rate <!--# Full description an include it here -->
+
+```{r table-s2, fig.cap = "table-s2"}
+knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))
 ```
@@
 
-```{r table-s3}
-#knitr::include_graphics(here::here("outputs", "tables", "table_a3_seedmixes.csv"))
-```
+See repository outputs/tables/table_a3_seedmixes.csv <!--# Write full link and full description -->
 

### 2022-12-15 R/show_table_establishment_rate.R

@@ -1,232 +1,0 @@
-# Grassland experiment on dikes
-# Establishment rates ####
-# Markus Bauer
-# 2022-10-20
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# A Preparation ###############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-### Packages ###
-library(here)
-library(tidyverse)
-library(gt)
-
-### Start ###
-rm(list = ls())
-setwd(here("data", "processed"))
-
-### Load data ###
-data <- read_csv("data_processed_traits.csv",
-                 col_names = TRUE, na = c("na", "NA"), col_types =
-                   cols(
-                     .default = "?",
-                     name = "f"
-                   )) %>%
-  select(name, family, total_seeded_2018, starts_with("rate_")) %>%
-  drop_na(total_seeded_2018) %>%
-  arrange(match(family, c("Poaceae", "Fabaceae"))) %>%
-  mutate(across(starts_with("rate"), ~ .x * 100),
-         name = str_replace_all(name, "_", " "))
-
-
-
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-# B Plot with gt ##############################################################
-#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-
-
-range(data$rate_2018, data$rate_2019, data$rate_2020, data$rate_2021)
-mean(data$rate_2018); sd(data$rate_2018)
-mean(data$rate_2019); sd(data$rate_2019)
-mean(data$rate_2020); sd(data$rate_2020)
-mean(data$rate_2021); sd(data$rate_2021)
-
-
-(table <- data %>%
-    gt() %>%
-    
-    
-    opt_table_lines("none") %>% ### Set general options ###
-    tab_options(
-      table.font.style = "Arial",
-      table.font.size = px(11),
-      table.font.color = "black",
-      column_labels.font.weight = "bold",
-      data_row.padding = px(4),
-      table.align = "left",
-      column_labels.border.top.style = "solid",
-      table_body.border.top.style = "solid",
-      table_body.border.bottom.style = "solid",
-      column_labels.border.top.color = "black",
-      table_body.border.top.color = "black",
-      table_body.border.bottom.color = "black",
-      column_labels.border.top.width = px(2),
[…]

### 2022-12-16 manuscript.Rmd
Update manuscript

@@
 output:
-  officedown::rdocx_document:
+  bookdown::word_document2:
     reference_docx: template_word.docx
@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-s1)).
+During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-flood-weather)).
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
@@
 From the species pools, 20 species were randomly selected for each plot.
-The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(fig:table-2))<!--# check  -->.
+The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(fig:table-seedmix))<!--# check  -->.
 The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:table-3)) <!--# More details and check  -->.
@@
 We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates).
-The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-1)).
+The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)).
 The split plot was cuased by testing all 24 treatments on both sides of the dike.
@@
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(fig:table-1)).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(fig:table-substrate)).
 The two seed mixture types were tested with two seeding densities (4 vs.
@@
 
-\## Table 1
+## Table 1
 
@@
 
-```{r table-1, fig.cap = "table_1"}
+```{r table-substrate, fig.cap = "table_substrate"}
 read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
@@
     ) %>%
-  fit_to_width(16.5, inc = 1L, max_iter = 20, unit = "cm")
+  autofit()
 ```
@@
 
-```{r table-2, fig.cap = "table_2"}
+```{r table-seedmix, fig.cap = "table_seedmix"}
 read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
@@
 
+\newpage
+
+## Table 3
+
+functional traits <!--# full description + table -->
+
+```{r table-traits, fig.cap = "table_traits"}
+read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  autofit()
+```
+
 <!---BLOCK_LANDSCAPE_STOP--->
@@
 
-```{r figure-1, fig.cap = "figure-1"}
+```{r figure-map, fig.cap = "figure-map"}
 knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
@@
 
-```{r figure-2, fig.cap = "figure-2"}
+```{r figure-effects, fig.cap = "figure-effects"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
@@
 
-```{r figure-3, fig.cap = "figure-3"}
+```{r figure-persistence, fig.cap = "figure-3"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-4, fig.cap = "figure-4"}
+```{r figure-fcs, fig.cap = "figure-4"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-5, fig.cap = "figure-5"}
+```{r figure-recovery, fig.cap = "figure-5"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-6, fig.cap = "figure-6"}
+```{r figure-nmds, fig.cap = "figure-6"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
@@
 
-```{r table-s1, fig.cap = "table-s1"}
+```{r table-flood-weather, fig.cap = "table-s1"}
 read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%
@@
 
-```{r table-s2, fig.cap = "table-s2"}
+```{r table-establishment, fig.cap = "table-s2"}
 knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))

### 2022-12-16 R/model_persistence_check.Rmd
Update persistence markdown

@@
 ```
-<br/>
-<br/>
-<b>Markus Bauer</b>
+
+<br/> <br/> <b>Markus Bauer</b>
 
@@
 
-[markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
+[markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de)
 
-ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
-<br>
-[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
-<br>
-GitHub: [markus1bauer](https://github.com/markus1bauer)
+ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174) <br> [Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao) <br> GitHub: [markus1bauer](https://github.com/markus1bauer)
 
@@
 
-Analysis guided by
-<br>
-<b>BARG</b> (Bayesian Analysis Reporting Guidelines): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
-<br>
-Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
-<br>
-Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
-<br>
-Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
+Analysis guided by <br> <b>BARG</b> (Bayesian Analysis Reporting Guidelines): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7) <br> Model check: Gabry et al.
+(2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378) <br> Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985) <br> Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
 
@@
 ```{r effect-sizes}
-draws1 %>%
-  gt::gt()
+posterior1 %>%
+  posterior::summarize_draws() %>%
+  knitr::kable()
 emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |

### 2022-12-16 R/model_recovery_check.Rmd
Update model_recovery_check.Rmd

@@
 # R hat
-rhat1 <- rhat(m_1)
-rhat2 <- rhat(m_2)
+rhat1 <- brms::rhat(m_1)
+rhat2 <- brms::rhat(m_2)
 # NEFF ratio
-neff1 <- neff_ratio(m_1)
-neff2 <- neff_ratio(m_2)
+neff1 <- brms::neff_ratio(m_1)
+neff2 <- brms::neff_ratio(m_2)
 # Long format of draws
@@
 ```{r prior-predictive-check}
-ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
+bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
   coord_cartesian(xlim = c(-2, 2))
@@
 ```{r rhat, collapse = TRUE}
-mcmc_rhat(rhat1)
-mcmc_rhat(rhat2)
+bayesplot::mcmc_rhat(rhat1)
+bayesplot::mcmc_rhat(rhat2)
 ```
@@
 ```{r ess, collapse = TRUE}
-mcmc_neff(neff1)
-mcmc_neff(neff2)
+bayesplot::mcmc_neff(neff1)
+bayesplot::mcmc_neff(neff2)
 ```
@@
 ```{r mcmc-trace, fig.height = 14}
-mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
-mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+bayesplot::mcmc_trace(
+  posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2)
+  )
+bayesplot::mcmc_trace(
+  posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2)
+  )
 ```
@@
 ```{r mcmc-pairs, collapse = TRUE, fig.height = 6.5}
-mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
+bayesplot::mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
            pars = c(
@@
            ))
-mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
+bayesplot::mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
            pars = c(
@@
 ```{r mcmc-parcoord, collapse = TRUE}
-mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
+bayesplot::mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
   theme(axis.text.x = element_text(angle = 45))
-mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
+bayesplot::mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
   theme(axis.text.x = element_text(angle = 45))
@@
 ```{r kernel-density}
-p1 <- ppc_dens_overlay(y, yrep1[1:50, ])
-p2 <- ppc_dens_overlay(y, yrep2[1:50, ])
+p1 <- bayesplot::ppc_dens_overlay(y, yrep1[1:50, ])
+p2 <- bayesplot::ppc_dens_overlay(y, yrep2[1:50, ])
 p1 / p2
@@
 ```{r histograms}
-p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
-p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001)
+p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001)
 p1 / p2

### 2022-12-16 R/model_fcs_check.Rmd
Update FCS

@@
 library(loo)
-library(tidybayes)
 library(emmeans)
@@
 ```{r possible-priors}
-get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
+brms::get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
             seed_density + substrate_depth +
@@
 
-### DHARMa
-
-```{r dharma, collapse = TRUE}
-DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
-DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
-```
-
-### Sampling efficency and effectiveness (BARG 2.B/C)
-
-#### Rhat (BARG 2.B)
-
-```{r rhat, collapse = TRUE}
-mcmc_rhat(rhat1)
-mcmc_rhat(rhat2)
-```
-
-#### Effective sampling size (ESS) (BARG 2.C)
-
-```{r ess, collapse = TRUE}
-mcmc_neff(neff1)
-mcmc_neff(neff2)
-```
-
-### MCMC diagnostics
+### Check computation (MCMC diagnostics, BARG 2.B/C)
 
@@
 ```{r mcmc-trace, fig.height = 14}
-mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
-mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+bayesplot::mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
+bayesplot::mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+```
+
+#### Sampling efficency: Rhat (BARG 2.B)
+
+```{r rhat, collapse = TRUE}
+bayesplot::mcmc_rhat(rhat1)
+bayesplot::mcmc_rhat(rhat1)
+```
+
+#### Sampling effectiveness: Effective sampling size (ESS) (BARG 2.C)
+
+```{r ess, collapse = TRUE}
+bayesplot::mcmc_neff(neff1)
+bayesplot::mcmc_neff(neff2)
 ```
@@
 ```{r mcmc-parcoord, collapse = TRUE}
-mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
+bayesplot::mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
   theme(axis.text.x = element_text(angle = 45))
-mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
+bayesplot::mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
   theme(axis.text.x = element_text(angle = 45))
+```
+
+#### Autocorrelation check
+
+```{r autocorrelation}
+bayesplot::mcmc_acf(posterior1, lags = 10)
+bayesplot::mcmc_acf(posterior2, lags = 10)
 ```
@@
 ```{r histogram}
-p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
-p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
+p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001)
+p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001)
 p1 / p2
@@
 
-#### LOO (Leave one out)
+#### LOO cross-validation (Leave one out)
 
@@
 
-### Autocorrelation check
+### DHARMa
 
-```{r autocorrelation}
-mcmc_acf(posterior1, lags = 10)
-mcmc_acf(posterior2, lags = 10)
+```{r dharma, collapse = TRUE}
+DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
+DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
 ```
@@
 ```{r posteriors, fig.height = 7}
-combined <- bind_rows(
+combined_models <- bind_rows(
   bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95) %>%
@@
   y = if_else(
-    combined$model == "m_2", -.2, if_else(
-      combined$model == "m_flat", -.4, if_else(
-        combined$model == "m_prior", -.6, 0
+    combined_models$model == "m_2", -.2, if_else(
+      combined_models$model == "m_flat", -.4, if_else(
+        combined_models$model == "m_prior", -.6, 0
         )
@@
 
-ggplot(data = combined, aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)) + 
+ggplot(
+  data = combined_models,
+  aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)
+  ) + 
   geom_vline(xintercept = 0, color = "grey") +

### 2022-12-16 R/model_persistence_check.Rmd
Update persistence

@@
 ```{r prior-predictive-check}
-ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
+bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
   coord_cartesian(xlim = c(-1, 1))
@@
 
-### DHARMa
-
-```{r dharma, collapse = TRUE}
-DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
-DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
-```
-
-### Sampling efficency and effectiveness (BARG 2.B/C)
-
-#### Rhat (BARG 2.B)
-
-```{r rhat, collapse = TRUE}
-mcmc_rhat(rhat1)
-mcmc_rhat(rhat1)
-```
-
-#### Effective sampling size (ESS) (BARG 2.C)
-
-```{r ess, collapse = TRUE}
-mcmc_neff(neff1)
-mcmc_neff(neff2)
-```
-
-### MCMC diagnostics
+### Check computation (MCMC diagnostics, BARG 2.B/C)
 

### 2022-12-16 manuscript.Rmd
Update

@@
   bookdown::word_document2:
-    reference_docx: template_word.docx
+    reference_docx: StylesTemplate.docx
+    global_numbering: true
 csl: template-journal-of-vegetation-science.csl
@@
 
-# Start
+# Document head {.unnumbered}
 
@@
 
+\clearpage
+
+\newpage
+
 # Keywords {.unnumbered}
 
-dike grassland
+Bayesian models
+
+dike grasslands
 
@@
 
+endangered species
+
+environmental filter
+
 species composition
 
-environmental filter
+restoration
+
+sand
+
+soil properties
+
+surveys
+
+vegetation
 
@@
 
-1.  How close is the vegetation to the reference state?
+1.  How strong differs the persistence of the sown species among the seed mixture-substrate combinations?
 
@@
 
-3.  How strong differs the persistence of the sown species among the seed mixture-substrate combinations?
+3.  How close is the vegetation to the reference state?
 
@@
 During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-flood-weather)).
-Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
+<!--# table ref is not working --> Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
 --> and a with an excavator the substrates were mixed <!--# Is that right?
@@
 The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)).
-The split plot was cuased by testing all 24 treatments on both sides of the dike.
+The split plot was caused by testing all 24 treatments on both sides of the dike.
 We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs.
@@
 The two seed mixture types were tested with two seeding densities (4 vs.
-8 g m\^-2 ).
-The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964].
-Establishment rates of species
+8 g m\^-2 ) <!--# include superscript -->.
+The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
+Establishment rates of species <!--# Refer to Table Sx -->.
+
+<!--# We measured FCS, recovery, persistence -->
+
+<!--# Mention traits -->
 
@@
 
-We performed all analyses in R [Version 4.2.2; @base], with the functions 'blme' (based on 'lme4') for BLMM [@lme4, @chung2013]; and 'DHARMa' for model evaluation [@DHARMa].
+A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
+Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
 
-<mark>We calculated Bayesian linear mixed-effects models (BLMM) with the random effect 'plot' and used the restricted maximum-likelihood estimation (REML), the optimiser Nelder-Mead and, for the random effect, the Wishart prior.
-To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model (Appendix A4).
+To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
+Furthermore, we included as a fixed effect the botanists of each plot.
+For the simple effects of the treatments we chose plausible weakly informative priors.
+To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
+For the computation, we used 4 chains, a thinning rate of 2, 5,000 iterations for warm-up and 10,000 in total.
+For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values and MCMC chain resolution by the effective sampling size (ESS).
+Posterior predictive check was done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].
+Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
+
+The software and the whole model specification and evaluation is stored on Zenodo <!--# insert citation --> and in an easily accessible a scroll-down document on GitHub (see \@ref(open-research)).
+There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+
+All analyses were performed in R [Version 4.2.2; @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
+
+<mark>To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model (Appendix A4).
 Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95% confidence intervals of the response variables.</mark>
@@
 
+We could identify a statistically clear positive effect of sand addition on the persistence of sown species and on the recovery rate (Figure \@ref(fig:figure-effects)).
+Furthermore, sown hay meadows were clearly closer to their reference plots than sown dry grasslands were to their references (Figure \@ref(fig:figure-effects)).
+
+The posterior distributions shown in the interactions plots which separates exposition and survey year is less clear. <!--# Go on here -->
+
 \clearpage
@@
 
-Text
+Mention drought in 2018 and 2019
 
@@
 ```{r figure-effects, fig.cap = "figure-effects"}
-#knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
+knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
 ```

### 2023-01-17 R/model_check_recovery_check.Rmd
Update

--- 2022-12-16 R/model_recovery_check.Rmd
@@
 
-### DHARMa
+### Check computation (MCMC diagnostics, BARG 2.B/C)
 
-```{r dharma, collapse = TRUE}
-DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
-DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
+#### Trace plots
+
+```{r mcmc-trace, fig.height = 14}
+bayesplot::mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
+bayesplot::mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
 ```
 
-### Sampling efficency and effectiveness (BARG 2.B/C)
-
-#### Rhat (BARG 2.B)
+#### Sampling efficency: Rhat (BARG 2.B)
 
@@
 bayesplot::mcmc_rhat(rhat1)
-bayesplot::mcmc_rhat(rhat2)
+bayesplot::mcmc_rhat(rhat1)
 ```
 
-#### Effective sampling size (ESS) (BARG 2.C)
+#### Sampling effectiveness: Effective sampling size (ESS) (BARG 2.C)
 
@@
 bayesplot::mcmc_neff(neff2)
-```
-
-### MCMC diagnostics
-
-#### Trace plots
-
-```{r mcmc-trace, fig.height = 14}
-bayesplot::mcmc_trace(
-  posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2)
-  )
-bayesplot::mcmc_trace(
-  posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2)
-  )
 ```
@@
   theme(axis.text.x = element_text(angle = 45))
+```
+
+### Autocorrelation check
+
+```{r autocorrelation}
+bayesplot::mcmc_acf(posterior1, lags = 10)
+bayesplot::mcmc_acf(posterior2, lags = 10)
 ```

### 2023-01-24 manuscript.Rmd
Update manuscript.Rmd

@@
 
-\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de)
+\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de) <!--# check if it still treated as bullet point -->
 
-Open Research: Data and code are permanently available on Zenodo under: <!--# https://doi.org/10.XXXX -->.
-
-**Max 8000 words**
+Max 8000 words <!--# Remove -->
 
@@
   font.family = "Times New Roman",
-  font.size = 10
+  font.size = 11
   )
@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:map)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-flood-weather)).
-<!--# table ref is not working --> Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
+During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table \@ref(tab:flood-weather), @lfu2021waterlevel;@lfu2021discharge].
+Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
 --> and a with an excavator the substrates were mixed <!--# Is that right?
 --> and the plots prepared.
-The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016 ).
+The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland [Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016].
 The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <!--# check numbers  -->, respectively.
@@
 From the species pools, 20 species were randomly selected for each plot.
-The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(fig:table-seedmix))<!--# check  -->.
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:table-3)) <!--# More details and check  -->.
+The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)) .
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
@@
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(fig:table-substrate)).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:substrate)).
 The two seed mixture types were tested with two seeding densities (4 vs.
@@
 
-The software and the whole model specification and evaluation is stored on Zenodo <!--# insert citation --> and in an easily accessible a scroll-down document on GitHub (see \@ref(open-research)).
+The software and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub (see \@ref(open-research)).
 There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
@@
 
-<mark>To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model (Appendix A4).
-Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95% confidence intervals of the response variables.</mark>
+<mark>To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model.
+Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95% confidence intervals of the response variables.</mark> <!--# Explain model selection -->
 
@@
 
-# Open research {.unnumbered}
+# Open research {open-research, .unnumbered}
 
@@
 
-<!---BLOCK_LANDSCAPE_START--->
-
 # Tables {.unnumbered}
 
-## Table 1
+## Table 1 {.unnumbered}
+
+Each plot received a individual set of 20 species with some restrictions to the number of species per functional group. <!--# Full description -->
+
+```{r table-seedmix, tab.id = "seedmix", tab.cap = "Seedmix"}
+read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  add_header_row(top = FALSE, values = c("", "", "#", "#", "%", "%")) %>%
+  autofit()
+```
+
+\clearpage
+
+\newpage
+
+## Table 2 {.unnumbered}
+
+functional traits <!--# full description -->
+
+```{r table-traits, tab.id = "traits", tab.cap = "Traits"}
+read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  autofit()
+```
+
+\clearpage
+
+\newpage
+
+## Table 3 {.unnumbered}
 
@@
 
-```{r table-substrate, fig.cap = "table_substrate"}
+```{r table-substrate, tab.id = "substrate", tab.cap = "Substrate"}
 read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
@@
 
-\clearpage
-
-\newpage
-
-## Table 2 {.unnumbered}
-
-Each plot received a individual set of 20 species with some restrictions to the number of species per functional group. <!--# Full description -->
-
-```{r table-seedmix, fig.cap = "table_seedmix"}
-read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
-  flextable() %>%
-  bold(part = "header") %>%
-  add_header_row(top = FALSE, values = c("", "", "#", "#", "%", "%")) %>%
-  autofit()
-```
-
-\clearpage
-
-\newpage
-
-## Table 3
-
-functional traits <!--# full description + table -->
-
-```{r table-traits, fig.cap = "table_traits"}
-read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
-  flextable() %>%
-  bold(part = "header") %>%
-  autofit()
-```
-
-<!---BLOCK_LANDSCAPE_STOP--->
-
 \newpage
@@
 
-```{r figure-map, fig.cap = "figure-map"}
+```{r figure-map, fig.cap = "Map"}
 knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
@@
 
-```{r figure-effects, fig.cap = "figure-effects"}
+```{r figure-effects, fig.cap = "Effects"}
 knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
@@
 
-```{r figure-persistence, fig.cap = "figure-3"}
+```{r figure-persistence, fig.cap = "Persistence"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-fcs, fig.cap = "figure-4"}
+```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-recovery, fig.cap = "figure-5"}
+```{r figure-recovery, fig.cap = "Recovery"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-nmds, fig.cap = "figure-6"}
+```{r figure-nmds, fig.cap = "NMDS"}
 #knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
@@
 
-```{r table-flood-weather, fig.cap = "table-s1"}
+```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Flood and weather data"}
 read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%

### 2023-01-25 manuscript.Rmd
Landscape orientation with officedown

@@
 output:
-  bookdown::word_document2:
+  officedown::rdocx_document:
     reference_docx: StylesTemplate.docx
-    global_numbering: true
+  #bookdown::word_document2:
+    #global_numbering: true
 csl: template-journal-of-vegetation-science.csl
@@
 
+-   <!--# We measured FCS, recovery, persistence -->
+
 We asked following question to evaluate the restoration success after four years:
@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:map)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412).
-The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table \@ref(tab:flood-weather), @lfu2021waterlevel;@lfu2021discharge].
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412).
+The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
+During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table \@ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
@@
 The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland [Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016].
-The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <!--# check numbers  -->, respectively.
+The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species , respectively.
 The seeds were received from a commercial producer of autochtonous seeds.
@@
 The two seed mixture types were tested with two seeding densities (4 vs.
-8 g m\^-2 ) <!--# include superscript -->.
+8 g^-2^).
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
-Establishment rates of species <!--# Refer to Table Sx -->.
+Establishment rates of species (Appendix Table \@ref(fig:table-establishment)).
 
-<!--# We measured FCS, recovery, persistence -->
+## External data
+
+Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our owen surveys in the surroundings on Danube dikes [@bauer2023]. We chose
 
@@
 Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
+<!--# Refer to Table Sx -->
 
@@
 
-# Open research {open-research, .unnumbered}
-
-Data and code is available on Zenodo: <!--# https://doi.org/10.XXXX -->
+# Open research {#sec-open-research-open-research-.unnumbered .unnumbered}
 
@@
 \newpage
+
+<!---BLOCK_LANDSCAPE_START--->
 
@@
 ```{r table-traits, tab.id = "traits", tab.cap = "Traits"}
-read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
-  flextable() %>%
-  bold(part = "header") %>%
-  autofit()
+#read_csv(here::here("data", "raw", "data_raw_table_3.csv")) %>%
+  #flextable() %>%
+  #bold(part = "header") %>%
+  #autofit()
 ```
@@
   slice(-1) %>%
-  flextable() %>%
+  qflextable() %>%
   bold(part = "header") %>%
@@
 \newpage
+
+<!---BLOCK_LANDSCAPE_STOP--->
 
@@
 ```{r figure-nmds, fig.cap = "NMDS"}
-#knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
+knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
 ```
@@
 
+<!---BLOCK_LANDSCAPE_STOP--->
+
 ## Table S2 {.unnumbered}
@@
 ```{r table-establishment, fig.cap = "table-s2"}
-knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))
+#knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))
 ```

### 2023-01-25 manuscript.Rmd
Update manuscript.Rmd

@@
   #bookdown::word_document2:
-    #global_numbering: true
 csl: template-journal-of-vegetation-science.csl
@@
 
-Max 8000 words <!--# Remove -->
+<mark>Max 8000 words</mark> <!--# Remove -->
 
@@
   )
-
-# read analysis
-#rmarkdown::render(here::here("results", "scripts", "Models.Rmd"), quiet = TRUE) # quiet to not get text from rendering
 ```
@@
 
-Mischprobe aus mehreren Plots. Measured in \< 2mm fraction <!--# Write full description -->
+Mischprobe aus mehreren Plots. Measured in \< 2mm fraction <!--# Write full description + superscript and subscript in header -->
 
@@
   slice(-1) %>%
-  qflextable() %>%
+  flextable() %>%
   bold(part = "header") %>%
@@
     ) %>%
-  autofit()
+  set_table_properties(layout = "autofit", width = 1)
 ```

### 2023-01-25 manuscript.Rmd
Update manuscript.Rmd

@@
 
-We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates).
+We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition, halfway up the slopes of the dike and arranged in six blocks (= replicates).
 The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)).
@@
 
-Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our owen surveys in the surroundings on Danube dikes [@bauer2023]. We chose
+Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys in the surroundings on Danube dikes [@bauer2023].
+We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
 
@@
 Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
-<!--# Refer to Table Sx -->
 
@@
 
-All analyses were performed in R [Version 4.2.2; @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
-
-<mark>To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model.
-Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95% confidence intervals of the response variables.</mark> <!--# Explain model selection -->
+All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
 

### 2023-01-25 manuscript.Rmd
Update manuscript.Rmd

@@
 A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
-Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
+Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
 
@@
 
-The posterior distributions shown in the interactions plots which separates exposition and survey year is less clear. <!--# Go on here -->
+The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:figure-persistence); \@ref(fig:figure-fcs); \@ref(fig:figure-recovery)) .
+Both expositions have similar trends but for all responses the values are clearly lower on the south exposition.
+Persistence values are more than 50% higher on the north exposition (Figure \@ref(fig:figure-persistence)).
+The effect of restoration treatments is in the interaction plots not clear.
+Hay meadow seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:figure-recovery)).
+Though, the sand admixture had no clear effect on the development.
+Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (Figure \@ref(fig:figure-persistence)).
+
+<!--# Go on here -->
 
@@
 ```{r figure-persistence, fig.cap = "Persistence"}
-#knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
+knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
 ```
@@
 ```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)"}
-#knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
+knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
 ```
@@
 ```{r figure-recovery, fig.cap = "Recovery"}
-#knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
+knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
 ```

### 2023-01-26 manuscript.Rmd
Update results section

@@
 ---
-title: "Dike experiment"
+title: "Development of restored dike grasslands to reference needs more than four years and can hardly modifyed by local site conditions"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 ---
-
-# Document head {.unnumbered}
-
-Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
-
-\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de) <!--# check if it still treated as bullet point -->
-
-<mark>Max 8000 words</mark> <!--# Remove -->
-
-\newpage
 
@@
 ```
+
+# Document head <!--# Remove --> {.unnumbered}
+
+Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
+
+\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de)
+
+Max 8000 words <!--# Remove -->
+
+\newpage
 
@@
 
-A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
-Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
-
 To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
 Furthermore, we included as a fixed effect the botanists of each plot.
-For the simple effects of the treatments we chose plausible weakly informative priors.
+For the simple effects of the treatments, we chose plausible weakly informative priors.
 To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
@@
 
-The software and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub (see \@ref(open-research)).
-There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
+Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
 
+Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub [cite Zenoto]<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
 All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
@@
 We could identify a statistically clear positive effect of sand addition on the persistence of sown species and on the recovery rate (Figure \@ref(fig:figure-effects)).
-Furthermore, sown hay meadows were clearly closer to their reference plots than sown dry grasslands were to their references (Figure \@ref(fig:figure-effects)).
-
+Furthermore, sown hay meadows were clearly closer to their reference plots than sown dry grasslands were to their references.
 The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:figure-persistence); \@ref(fig:figure-fcs); \@ref(fig:figure-recovery)) .
@@
 
-<!--# Go on here -->
+The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:figure-nmds)).
+The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands.
+In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:figure-recovery)) but the right direction of the development.
+One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed mixture compositions.
+The ordination presents the experimental plots not only in context with seed mixtures, but also with reference sites.
+The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap.
+The positions of reference sites is shifted to the left on the NMDS1 axis which means in the direction of early successional states.
+On the south exposition, we had negative reference sites which are located in the NMDS in between the positive reference sites and the recent state of restored plots.
+However, most of negative reference sites (ruderal, dry and anthropogenic vegetation) are situated in the upper half and explicitly recent restoration sites on the south exposition are close to them.
 
@@
 
-# Open research {#sec-open-research-open-research-.unnumbered .unnumbered}
+# Open research {#sec-open-research .unnumbered}
+
+Data and code is stored on Zenodo (Bauer et al. 2023) <!--# Update citation after upload -->
 

### 2023-01-26 manuscript.Rmd
Write table superscription

@@
 ---
-title: "Development of restored dike grasslands to reference needs more than four years and can hardly modifyed by local site conditions"
+title: "Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table \@ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
-Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?
+Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike<!--# Is that right?
 --> and a with an excavator the substrates were mixed <!--# Is that right?
@@
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
+We tested soil samples of the three substrates on both expositions by mixing several subsamples.
 The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:substrate)).
 The two seed mixture types were tested with two seeding densities (4 vs.
-8 g^-2^).
+8 g m^-2^).
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
@@
 
-Each plot received a individual set of 20 species with some restrictions to the number of species per functional group. <!--# Full description -->
+Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+The total species pool for hay meadows was 55 and for calcareous grassland 58.
+In total, seed mixtures had 16 or 32 g per plot.
 
 ```{r table-seedmix, tab.id = "seedmix", tab.cap = "Seedmix"}
-read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
+read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
+         show_col_types = FALSE) %>%
+  slice(-1) %>%
   flextable() %>%
-  bold(part = "header") %>%
-  add_header_row(top = FALSE, values = c("", "", "#", "#", "%", "%")) %>%
+  merge_at(part = "header", j = 2:3) %>%
+  align(align = "center", part = "all") %>%
+  align(align = "left", part = "all", j = 1) %>%
+  add_header_row(top = FALSE, values = c("", "Hay meadow", "Calcareous grassland", "", "", "")) %>%
+  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
+  bold(part = "header", i = 1) %>%
   autofit()
@@
 
-Mischprobe aus mehreren Plots. Measured in \< 2mm fraction <!--# Write full description + superscript and subscript in header -->
+Soil of the three substrates was analyzed for the fraction \< 2mm fraction.
+Soil texture was classified according to the *Bodenkundliche Kartieranleitung* [@BodenkundlKartieranl.2005].
+The pH was measured in CaCl~2~ solution.
+Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract.
+For calculating CaCO~3~, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
+To calculate total N and the C/N ratio, a subsample was ashed at 1000 °C.
 
 ```{r table-substrate, tab.id = "substrate", tab.cap = "Substrate"}
-read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
+read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
+         show_col_types = FALSE) %>%
   slice(-1) %>%
@@
     top = FALSE,
-    values = read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>% slice(1)
+    values = read_csv(
+      here::here("data", "raw", "data_raw_table_3_substrate.csv"),
+                 show_col_types = FALSE) %>%
+      slice(1)
     ) %>%
+  align(align = "center", part = "all") %>%
+  align(align = "left", part = "all", j = 1) %>%
+  compose(i = 1, j = 10, part = "header", value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))) %>%
+  compose(i = 1, j = 11, part = "header", value = as_paragraph("K", as_sub("2"), "O")) %>%
+  compose(i = 1, j = 12, part = "header", value = as_paragraph("Mg", as_sup("2+"))) %>%
+  compose(i = 1, j = 14, part = "header", value = as_paragraph("CaCO", as_sub("3"))) %>%
+  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
+  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
+  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
   set_table_properties(layout = "autofit", width = 1)

### 2023-01-26 manuscript.Rmd
Update manuscript.Rmd

@@
   message = FALSE,
-  dpi = 50
+  dpi = 300,
+  fig.cap = FALSE
   )
@@
 For calculating CaCO~3~, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
-To calculate total N and the C/N ratio, a subsample was ashed at 1000 °C.
+To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C.
 
@@
 
-```{r figure-map, fig.cap = "Map"}
+```{r figure-map, fig.cap = "Map", fig.asp = 0.7272}
 knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
 ```
+
+The experiment was located
 
@@
 
-```{r figure-effects, fig.cap = "Effects"}
+```{r figure-effects, fig.cap = "Effects", fig.asp = 3.3}
 knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
@@
 
-```{r figure-persistence, fig.cap = "Persistence"}
+```{r figure-persistence, fig.cap = "Persistence", fig.asp = 1.785}
 knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)"}
+```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 1.785}
 knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-recovery, fig.cap = "Recovery"}
+```{r figure-recovery, fig.cap = "Recovery", fig.asp = 1.785}
 knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
@@
 
-```{r figure-nmds, fig.cap = "NMDS"}
+```{r figure-nmds, fig.cap = "NMDS", fig.asp = 1.0312}
 knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))

### 2023-01-26 manuscript.Rmd
Update manuscript.Rmd

@@
 The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap.
-The positions of reference sites is shifted to the left on the NMDS1 axis which means in the direction of early successional states.
+The positions of reference sites are shifted to the left on the NMDS1 axis which means in the direction of early successional states.
 On the south exposition, we had negative reference sites which are located in the NMDS in between the positive reference sites and the recent state of restored plots.
@@
 
-```{r figure-map, fig.cap = "Map", fig.asp = 0.7272}
-knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
+```{r figure-map, fig.cap = "Map", fig.asp = 1.2854, fig.width = 5}
+knitr::include_graphics(here::here("outputs", "figures", "figure_1_map.png"))
 ```
@@
 
-```{r figure-effects, fig.cap = "Effects", fig.asp = 3.3}
+```{r fig.id = "figure-effects", fig.cap = "Effects", fig.asp = 0.3030, fig.width = 6.49}
 knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
@@
 
-```{r figure-persistence, fig.cap = "Persistence", fig.asp = 1.785}
-knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
+```{r fig.id = "figure-persistence", fig.cap = "Persistence", fig.asp = 0.4848, fig.width = 6.49}
+knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff"))
 ```
@@
 
-```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 1.785}
-knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
+```{r fig.id = "figure-fcs", fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 0.4848, fig.width = 6.49}
+knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff"))
 ```
@@
 
-```{r figure-recovery, fig.cap = "Recovery", fig.asp = 1.785}
-knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
+```{r fig.id = "figure-recovery", fig.cap = "Recovery", fig.asp = 0.4848, fig.width = 6.49}
+knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff"))
 ```
@@
 
-```{r figure-nmds, fig.cap = "NMDS", fig.asp = 1.0312}
+```{r fig.id = "figure-nmds", fig.cap = "NMDS", fig.asp = 0.9696, fig.width = 6.49}
 knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))

### 2023-01-27 manuscript.Rmd
Finish figure captions

@@
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table \@ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
+During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike<!--# Is that right?
---> and a with an excavator the substrates were mixed <!--# Is that right?
+--> and a with an excavator the substrates were mixed<!--# Is that right?
 --> and the plots prepared.
-The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland [Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016].
-The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species , respectively.
+The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B).
+The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
 The seeds were received from a commercial producer of autochtonous seeds.
@@
 
-To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
+To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed-effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
 Furthermore, we included as a fixed effect the botanists of each plot.
@@
 Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
-The total species pool for hay meadows was 55 and for calcareous grassland 58.
+The total species pool for hay meadows was 55 and for dry grassland 58.
 In total, seed mixtures had 16 or 32 g per plot.
@@
   align(align = "left", part = "all", j = 1) %>%
-  add_header_row(top = FALSE, values = c("", "Hay meadow", "Calcareous grassland", "", "", "")) %>%
+  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
   add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
@@
 
-```{r figure-map, fig.cap = "Map", fig.asp = 1.2854, fig.width = 5}
-knitr::include_graphics(here::here("outputs", "figures", "figure_1_map.png"))
+```{r figure-map, fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
+The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition (central photo).
+Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture type (H, D)) .
+The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates.
+The photo on the bottom shows one block from the side (Photo: Markus Bauer)."}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_1_map.png")
+  )
 ```
-
-The experiment was located
 
@@
 
-```{r fig.id = "figure-effects", fig.cap = "Effects", fig.asp = 0.3030, fig.width = 6.49}
-knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
+```{r fig.id = "figure-effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
+Furthermore, the median and the 66% and 95% credible intervals are shown.
+We evaluated the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
+Note that the zero lines indicate that both levels have equal values.
+This means that hay meadows are closer to their reference than dry grasslands  (C)."}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff")
+  )
 ```
@@
 
-```{r fig.id = "figure-persistence", fig.cap = "Persistence", fig.asp = 0.4848, fig.width = 6.49}
-knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff"))
+```{r fig.id = "figure-persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on a dike experiment over the years.
+The substrates had different sand admixtures and different seed mixture types were sown.
+Per plot were 20 species sown.
+Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff")
+  )
 ```
@@
 
-```{r fig.id = "figure-fcs", fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 0.4848, fig.width = 6.49}
-knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff"))
+```{r fig.id = "figure-fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favourable Conservation Status (FCS) of a dike experiment.
+The substrates had different sand admixtures and different seed mixture types were sown.
+The zero line indicate that target and non-target species are balanced.
+Positive values indicate that there are more target species.
+Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff")
+  )
 ```
@@
 
-```{r fig.id = "figure-recovery", fig.cap = "Recovery", fig.asp = 0.4848, fig.width = 6.49}
-knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff"))
+```{r fig.id = "figure-recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (d~jt,0~) of plots of a experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
+The substrates had different sand admixtures and different seed mixture types were sown.
+The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (@ref(fig:figure-nmds)).
+The grey area mark the standard deviation of the position of the reference sites.
+Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff")
+  )
 ```
-
-Fig. 5:
 
@@
 
-```{r fig.id = "figure-nmds", fig.cap = "NMDS", fig.asp = 0.9696, fig.width = 6.49}
-knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
+```{r fig.id = "figure-nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
+In addition, 98 positive and negative reference plots were included from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
+The circles show the standard error of the groups.
+2D stress: 0.21."}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff")
+  )
 ```
-
-Fig. 6:
 

### 2023-01-27 manuscript.Rmd
Update manuscript.Rmd

@@
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
-The seeds were received from a commercial producer of autochtonous seeds.
+The seeds were received from a commercial producer of autochthonous seeds.
 From the species pools, 20 species were randomly selected for each plot.
@@
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
-In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.
+In October 2018, *Bromus hordeaceus* was seeded as a nursery grass to provide safe sites under drought conditions.
 
@@
 A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
-Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).
+Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress 0.21).
 
@@
 
-Establishment rate <!--# Full description an include it here -->
+Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
+Indicated is the number of seeded plots and the percentage of these plots which were occupied by the respective species.
+This means that for each species only the seeded plots were included.
+The shades of grey indicate values of 0--33%, 33--50%, \>50%.
 
-```{r table-establishment, fig.cap = "table-s2"}
-#knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))
+```{r table-establishment, tab.id = "establishment", tab.cap = "Establishment rate"}
+read_csv(
+  "data_processed_traits.csv",
+                 col_names = TRUE, na = c("na", "NA"), col_types =
+                   cols(.default = "?", name = "f")
+  ) %>%
+  select(name, family, total_seeded_2018, starts_with("rate_")) %>%
+  drop_na(total_seeded_2018) %>%
+  arrange(match(family, c("Poaceae", "Fabaceae"))) %>%
+  mutate(across(starts_with("rate"), ~ .x * 100),
+         name = str_replace_all(name, "_", " ")) %>%
+  flextable() %>%
+  bold(part = "header") %>%
+  bg(bg = scales::col_numeric(palette = "viridis", domain = c(0, 1))) %>%
+  autofit()
 ```

### 2023-01-27 manuscript.Rmd
Update manuscript.Rmd

@@
 ```{r set-up, include = FALSE}
+library(here)
 library(knitr)
@@
   font.family = "Times New Roman",
-  font.size = 11
+  font.size = 11,
+  text.align = "center"
   )
@@
 
-Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+```{r table-seedmix, tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
 In total, seed mixtures had 16 or 32 g per plot.
-
-```{r table-seedmix, tab.id = "seedmix", tab.cap = "Seedmix"}
+All individual seed mixtures are stored in the repository in Zenodo ("outputs/tables/table_a3_seedmixes"")."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
   merge_at(part = "header", j = 2:3) %>%
-  align(align = "center", part = "all") %>%
-  align(align = "left", part = "all", j = 1) %>%
+  align(align = "center", part = "all", j = -1) %>%
   add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
@@
   bold(part = "header", i = 1) %>%
+  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
   autofit()
@@
 
-Soil of the three substrates was analyzed for the fraction \< 2mm fraction.
-Soil texture was classified according to the *Bodenkundliche Kartieranleitung* [@BodenkundlKartieranl.2005].
-The pH was measured in CaCl~2~ solution.
-Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract.
-For calculating CaCO~3~, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
-To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C.
-
-```{r table-substrate, tab.id = "substrate", tab.cap = "Substrate"}
+```{r table-substrate, ft.align = "left",tab.id = "substrate", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
+Soil texture was classified according to the Bodenkundliche Kartieranleitung [@BodenkundlKartieranl.2005].
+The pH was measured in CaCl2 solution.
+Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract.
+For calculating CaCO3, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
+To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C."}
 read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
@@
     ) %>%
-  align(align = "center", part = "all") %>%
-  align(align = "left", part = "all", j = 1) %>%
+  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
+  align(align = "center", part = "all", j = -1) %>%
   compose(i = 1, j = 10, part = "header", value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))) %>%
@@
 The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition (central photo).
-Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture type (H, D)) .
+Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture types H and D).
 The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates.
-The photo on the bottom shows one block from the side (Photo: Markus Bauer)."}
+The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer)."}
 knitr::include_graphics(
@@
 
-```{r fig.id = "figure-recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (d~jt,0~) of plots of a experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
+```{r fig.id = "figure-recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (*d~jt,0~*) of plots of an experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
 The substrates had different sand admixtures and different seed mixture types were sown.
-The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (@ref(fig:figure-nmds)).
-The grey area mark the standard deviation of the position of the reference sites.
+The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (Figure 5).
+The grey area marks the standard deviation of the position of the reference sites.
 Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
@@
 ```{r fig.id = "figure-nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
-In addition, 98 positive and negative reference plots were included from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
+In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
 The circles show the standard error of the groups.
@@
 
-Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
+```{r table-establishment, tab.id = "establishment", tab.cap = "Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
 Indicated is the number of seeded plots and the percentage of these plots which were occupied by the respective species.
 This means that for each species only the seeded plots were included.
-The shades of grey indicate values of 0--33%, 33--50%, \>50%.
-
-```{r table-establishment, tab.id = "establishment", tab.cap = "Establishment rate"}
+The shades of grey indicate the success of establishment."}
 read_csv(
-  "data_processed_traits.csv",
+  here("data", "processed", "data_processed_traits.csv"),
                  col_names = TRUE, na = c("na", "NA"), col_types =
@@
          name = str_replace_all(name, "_", " ")) %>%
+  rename(Species = name, Family = family, "Seeded plots [#]" = total_seeded_2018, "Establishment rate [%]" = rate_2018, "2019" = rate_2019, "2020" = rate_2020, "2021" = rate_2021) %>%
   flextable() %>%
+  align(part = "all", align = "center", j = -1) %>%
+  merge_at(part = "header", j = 4:7) %>%
+  add_header_row(top = FALSE, values = c("", "", "", "2018", "2019", "2020", "2021")) %>%
+  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
   bold(part = "header") %>%
-  bg(bg = scales::col_numeric(palette = "viridis", domain = c(0, 1))) %>%
+  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
+  bg(j = 4:7, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 100))) %>%
   autofit()
 ```
-
-\clearpage
-
-\newpage
-
-## Table S3 {.unnumbered}
-
-See repository outputs/tables/table_a3_seedmixes.csv <!--# Write full link and full description -->
 

### 2023-01-31 manuscript.Rmd
Update manuscript.Rmd

@@
     reference_docx: StylesTemplate.docx
-  #bookdown::word_document2:
 csl: template-journal-of-vegetation-science.csl
@@
 
-```{r set-up, include = FALSE}
+```{r set-up, include = FALSE, message = FALSE}
 library(here)
@@
 During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
-Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike<!--# Is that right?
---> and a with an excavator the substrates were mixed<!--# Is that right?
---> and the plots prepared.
+Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen.
+The substrates were mixed with a big roller and an excavator preparted the plots.
 The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B).
@@
 For calculating CaCO3, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
-To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C."}
+To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C.
+Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand."}
 read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
@@
   compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
+  align(align = "left", part = "footer") %>%
   set_table_properties(layout = "autofit", width = 1)
@@
 
-Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
+```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Three dry years (2018–2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017–2021), based on weather station Metten [mean, 1981–2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
 HQ2 = Highest discharge with a probability of occurrence every second year.
-HSW = Highest water level for shipping.
-
-```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Flood and weather data"}
+HSW = Highest water level for shipping."}
 read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%

### 2023-01-31 R/show_figure_6_nmds.R
Update show_figure_6_nmds.R

@@ -53,6 +53,11 @@ sites_nmds <- read_csv("data_processed_sites_nmds.csv",
                              col_names = TRUE, na = c("na", "NA", ""),
                              col_types = cols(.default = "?"))
 
+sites_nmds %>%
+  group_by(source, esy) %>%
+  filter(esy == "R1A" | esy == "R22" | esy == "V38") %>%
+  count()
+
 base::load(file = here("outputs", "models", "model_nmds.Rdata"))
 ordi
 
@@ -86,7 +91,7 @@ data <- data %>%
 sites_nmds <- sites_nmds %>%
   filter(!(target_type == "other")) %>%
   bind_rows(data) %>%
-  filter(!(reference == "-Reference" & exposition == "north"))
+  filter(!(reference == "negative_reference" & exposition == "north"))
 
 sites_nmds <- sites_nmds %>%
   ### Select variables to plot ###

### 2023-01-31 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
 
-To compare different models, you only have to change the models in section 'Load models'
+To compare different models, you only have to change the models in section `Load models`
 
@@
     botanist_year = factor(botanist_year),
-    n = recovery_time
+    n = recovery_completeness
     )

### 2023-01-31 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

--- 2022-12-16 R/model_fcs_check.Rmd
@@
 To compare different models, you only have to change the models in
-section 'Load models'
+section `Load models`
 
@@
 
-Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers
+Favourable Conservation Status (FCS) sensu Helm et al. (2015) Divers
 Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)
@@
 sites <- read_csv(
-  here("data", "processed", "data_processed_sites.csv"),
+  here("data", "processed", "data_processed_sites_spatial.csv"),
   col_names = TRUE, na = c("na", "NA", ""), col_types =
@@
 
-### Forest plot(BARG 3.B/5.B)
+### Forest plot (BARG 3.B/5.B)
 

### 2023-01-31 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
   knitr::kable()
-emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
+emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
           survey_year_fct, type = "response")
+emm$emmeans
 ```

### 2023-02-01 manuscript.Rmd
Update manuscript.Rmd

@@
 Both expositions have similar trends but for all responses the values are clearly lower on the south exposition.
-Persistence values are more than 50% higher on the north exposition (Figure \@ref(fig:figure-persistence)).
+Persistence values are more than 50% higher on the north exposition <!--# insert further percentages--> (Figure \@ref(fig:figure-persistence)).
 The effect of restoration treatments is in the interaction plots not clear.
@@
 Though, the sand admixture had no clear effect on the development.
-Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (Figure \@ref(fig:figure-persistence)).
+Persistence of both seed mixture types seems to be slightly positive affected <!--# insert percentage-->by sand admixture on the north exposition (Figure \@ref(fig:figure-persistence)).
 
@@
 ## Figure 1 {.unnumbered}
+
+<!--# Cite BayernAtlas-->
 

### 2023-02-01 manuscript.Rmd
Update manuscript.Rmd

@@
 
-"Ecological theory can point restoration toward important processes that need manipulation [...].
-However, for this information to be relevant, restoration ecology needs to employ evidence-based assessments [...]" (Suding 2011) --\> No evidence for theory with our project
+Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010; @Torok.2011]<!--# Cite Hedberg -->, is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g.
+@Freitag.2021].
+Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] and even by restoration through unsuited afforestation [@dudley2020].
+In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
 
--   Endangered grasslands
+Sowing high-diversity seed mixtures of local provenance produced by commercial but specialised seed companies is a promising way to scale up restoration efforts.
+Though, there are still open questions about specifying the seed mixtures to specific site conditions or even more to future climate conditions to improve efficiency and effectiveness of restoration efforts [@Torok.2021].
+For this reason, restoration ecology has to increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015].
+Rigorous, repeatable and transparent experiments are needed to guide evidence-based restoration [@Cooke.2018].
+Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
+Seeding in general is a way to overcome the dispersal filter, but we focus on environmental and the biotic filtering which are the main processes to be manipulated by the choice of the right substrate-seed mixture combination [@Torok.2017].
+This means that we can mutually adapt the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
+The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion.
 
--   Predictability of restorations --\> experiments, evidence-based restoration (cooke 2018)
-
--   Brudvig 2017 among restoration outcomes and in comparison to reference
-
--   Substrate modification to influence habitat filtering
+-   Evaluation: Brudvig 2017 among restoration outcomes and in comparison to reference
 
@@
 Mention drought in 2018 and 2019
+
+Compare with Mitchley 2012, Engst 2016, Freitag 2021, Kaulfuß 2022
 

### 2023-02-01 manuscript.Rmd
Update manuscript.Rmd

@@
 For this reason, restoration ecology has to increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015].
-Rigorous, repeatable and transparent experiments are needed to guide evidence-based restoration [@Cooke.2018].
+Rigorous, repeatable and transparent experiments linked to a hypothesis derived from theory are needed to guide evidence-based restoration [@Cooke.2018; @Wainwright.2018].
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Seeding in general is a way to overcome the dispersal filter, but we focus on environmental and the biotic filtering which are the main processes to be manipulated by the choice of the right substrate-seed mixture combination [@Torok.2017].
-This means that we can mutually adapt the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
+Seeding in general is a way to overcome the dispersal filter<!--# e.g.
+Cite Martin & Wilsey 2014 -->, but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right substrate-seed mixture combination [@Torok.2017].
+This means that a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
 The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion.
+
+-   Dike grasslands as case study, potential of dike grasslands
 
@@
 
--   Sowing a typical approach + priority effects + species pool
+-   Sowing: priority effects + species pool
 
@@
 
--   Dike grasslands as case study
-
 -   The aim of the study is
-
--   <!--# We measured FCS, recovery, persistence -->
 
@@
 In total, seed mixtures had 16 or 32 g per plot.
-All individual seed mixtures are stored in the repository in Zenodo ("outputs/tables/table_a3_seedmixes"")."}
+All individual seed mixtures are stored in the repository in Zenodo (outputs/tables/table_a3_seedmixes)."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),

### 2023-02-01 manuscript.Rmd
Update manuscript.Rmd

@@
     reference_docx: StylesTemplate.docx
-csl: template-journal-of-vegetation-science.csl
+csl: template-journal-of-applied-ecology.csl
 bibliography: bibliography.bib
@@
 library(knitr)
-library(bookdown)
+#library(bookdown)
 library(officedown)
@@
 
-Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010; @Torok.2011]<!--# Cite Hedberg -->, is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g.
-@Freitag.2021].
+Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010; @Torok.2011]<!--# Cite Hedberg -->, is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g., @Freitag.2021].
 Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] and even by restoration through unsuited afforestation [@dudley2020].
@@
 For this reason, restoration ecology has to increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015].
-Rigorous, repeatable and transparent experiments linked to a hypothesis derived from theory are needed to guide evidence-based restoration [@Cooke.2018; @Wainwright.2018].
+Rigorous, repeatable, and transparent experiments linked to a hypothesis derived from theory are needed to guide evidence-based restoration [@Cooke.2018; @Wainwright.2018].
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
@@
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
-Establishment rates of species (Appendix Table \@ref(fig:table-establishment)).
+Establishment rates of species (Appendix Table \@ref(tab:establishment)).
 
@@
 Both expositions have similar trends but for all responses the values are clearly lower on the south exposition.
-Persistence values are more than 50% higher on the north exposition <!--# insert further percentages--> (Figure \@ref(fig:figure-persistence)).
+Persistence values are more than 50% higher on the north exposition<!--# insert further percentages--> (Figure \@ref(fig:figure-persistence)).
 The effect of restoration treatments is in the interaction plots not clear.
@@
 
-Data and code is stored on Zenodo (Bauer et al. 2023) <!--# Update citation after upload -->
+Data and code are stored on Zenodo (Bauer et al. 2023) <!--# Update citation after upload -->
 
@@
 
-```{r table-seedmix, tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+```{r tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
 In total, seed mixtures had 16 or 32 g per plot.
-All individual seed mixtures are stored in the repository in Zenodo (outputs/tables/table_a3_seedmixes)."}
+All individual seed mixtures are stored in the repository in Zenodo ('outputs/tables/table_a3_seedmixes')."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
 
-```{r table-traits, tab.id = "traits", tab.cap = "Traits"}
+```{r tab.id = "traits", tab.cap = "Traits"}
 #read_csv(here::here("data", "raw", "data_raw_table_3.csv")) %>%
@@
 
-```{r table-substrate, ft.align = "left",tab.id = "substrate", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
+```{r tab.id = "substrate", ft.align = "left",tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
 Soil texture was classified according to the Bodenkundliche Kartieranleitung [@BodenkundlKartieranl.2005].
@@
 
-```{r table-establishment, tab.id = "establishment", tab.cap = "Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
+```{r tab.id = "establishment", tab.cap = "Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
 Indicated is the number of seeded plots and the percentage of these plots which were occupied by the respective species.

### 2023-02-02 manuscript.Rmd
Update manuscript.Rmd

@@
 library(knitr)
-#library(bookdown)
 library(officedown)
@@
 
-Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010; @Torok.2011]<!--# Cite Hedberg -->, is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g., @Freitag.2021].
-Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] and even by restoration through unsuited afforestation [@dudley2020].
+Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010], is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g., @Freitag.2021].
+Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b].
+It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] and even by restoration through unsuited afforestation [@dudley2020].
 In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
@@
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Seeding in general is a way to overcome the dispersal filter<!--# e.g.
-Cite Martin & Wilsey 2014 -->, but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right substrate-seed mixture combination [@Torok.2017].
+Seeding in general is a way to overcome the dispersal filter [@kiehl2006], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right substrate-seed mixture combination [@Torok.2017].
 This means that a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
 The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion.
+Modifying seed mixtures for certain site conditions came up with functional plant traits [@Funk.2008; @Laughlin.2014] but it is not easy to put it into practice for novel ecosystems like urban grasslands [@Bauer.2022].
+Substrates cannot only be modified for conservation purposes in urban areas, but also in quarries [@chenot-lescure2022] or dikes [@Liebrand.1996].
 
--   Dike grasslands as case study, potential of dike grasslands
+Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
+Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve the functionality of the construction [@KleberLerchbaumer.2017].
+Dikes can reconcile several requirements [@teixeira2022], but the substrate-seed mixture combination must be adapted.
 
--   Evaluation: Brudvig 2017 among restoration outcomes and in comparison to reference
+The aim of this study is to identify the ideal combination of substrates and seed mixtures for north and south exposed slopes in Central Europe to develop a vital and species-rich vegetation cover.
+We set up an experiment and tested agricultural soil with different amounts of sand admixture and different installation depths, as well as different seed mixture types and different seed densities.
+We expected a better development of dry grassland on the south exposition with sandy substrate and hay meadows on north exposition with less sandy substrate.
+Since seeds are expensive, practitioners like to know if the slopes need a higher seed density [cf.
+@KleberLerchbaumer.2017].
 
--   Sowing: priority effects + species pool
+To measure the success of restoration, we chose four indices.
+First, we observed the persistence of the seeded species, which is a key interest of seeding as a restoration approach [@Wilsey.2021].
+For this, it was surveyed if the seeded species are present in the respective plot in following years.
+Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
+Characteristic diversity is created by established species which belong to the habitat-specific species pool.
+In other words, these species are target species for a habitat type of interest.
+Third, the successional distance to the reference was determined.
+This measure quantifies the distance of a plot to the average reference site from an ordination [@Rydgren.2019].
+Fourth, we visualized the species composition of our experimental plots in comparison with reference sites to evaluate as well absolute success of the restoration outcomes.
 
--   Introduce FCS, Recovery time, Persistence
-
--   The aim of the study is
+<!--# Evaluation: Brudvig 2017 among restoration outcomes and in comparison to reference -->
 
@@
 
-2.  How strong differs the Favourable Conservation Status (FCS) among the seed mixture-substrate combinations?
+2.  How strong differs the Favorable Conservation Status (FCS) among the seed mixture-substrate combinations?
 
@@
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen.
-The substrates were mixed with a big roller and an excavator preparted the plots.
+The substrates were mixed with a big roller and an excavator prepared the plots.
 The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B).
@@
 The split plot was caused by testing all 24 treatments on both sides of the dike.
-We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs.
-30 cm).
+We tested three sand admixtures (0%, 25% and 50%) and tow soil depths (15 vs.
+30 cm) of practical interest [@KleberLerchbaumer.2017] and two .
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
 We tested soil samples of the three substrates on both expositions by mixing several subsamples.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:substrate)).
-The two seed mixture types were tested with two seeding densities (4 vs.
-8 g m^-2^).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table @ref(tab:substrate)).
+The two seed mixture types were tested with the normal seeding density and the increased density recommended for slopes [4 vs.
+8 g m^-2^ @Kiehl.2010; @KleberLerchbaumer.2017].
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
@@
 
+Batori 2016 neither found great differences between expositions
+
+persistence influenced by neighbourig plots
+
+Outlook: landscape, management are important
+
 \clearpage
@@
 <!--# funding number of WIGES -->
+
+\clearpage
+
+\newpage
 

### 2023-02-02 manuscript.Rmd
Update manuscript.Rmd

@@
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)) .
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits))<!--# describe difference --> .
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
@@
 Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-We tested soil samples of the three substrates on both expositions by mixing several subsamples.
+We tested soil samples of the three substrates on both expositions by mixing several sub-samples.
 The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table @ref(tab:substrate)).
@@
 To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
-For the computation, we used 4 chains, a thinning rate of 2, 5,000 iterations for warm-up and 10,000 in total.
+For the computation, we used 4 chains, a thinning rate of 2, 5000 iterations for warm-up and 10,000 in total.
 For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values and MCMC chain resolution by the effective sampling size (ESS).
@@
 
-Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub [cite Zenoto]<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub [!cite Zenodo!]<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
 All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
@@
 The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:figure-persistence); \@ref(fig:figure-fcs); \@ref(fig:figure-recovery)) .
-Both expositions have similar trends but for all responses the values are clearly lower on the south exposition.
-Persistence values are more than 50% higher on the north exposition<!--# insert further percentages--> (Figure \@ref(fig:figure-persistence)).
+Both expositions have similar trends but for all responses the values are clearly lower on the south exposition, e.g., persistence values are on average more than 46% higher on the north exposition (Figure \@ref(fig:figure-persistence)).
 The effect of restoration treatments is in the interaction plots not clear.
@@
 Though, the sand admixture had no clear effect on the development.
-Persistence of both seed mixture types seems to be slightly positive affected <!--# insert percentage-->by sand admixture on the north exposition (Figure \@ref(fig:figure-persistence)).
+Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:figure-persistence)).
 
@@
 20021/698).
-The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020.
-<!--# funding number of WIGES -->
+The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020 (No.
+80 002 312).
 
@@
 ```{r tab.id = "substrate", ft.align = "left",tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
-Soil texture was classified according to the Bodenkundliche Kartieranleitung [@BodenkundlKartieranl.2005].
+Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
 The pH was measured in CaCl2 solution.
@@
 
-<!--# Cite BayernAtlas-->
-
 ```{r figure-map, fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
-The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition (central photo).
+The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023].
 Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture types H and D).
@@
 Furthermore, the median and the 66% and 95% credible intervals are shown.
-We evaluated the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
+We evaluated the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
 Note that the zero lines indicate that both levels have equal values.
@@
 
-```{r fig.id = "figure-fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favourable Conservation Status (FCS) of a dike experiment.
+```{r fig.id = "figure-fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of a dike experiment.
 The substrates had different sand admixtures and different seed mixture types were sown.

### 2023-02-07 manuscript.Rmd
Update manuscript.Rmd

@@
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits))<!--# describe difference --> .
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)).
+As expected have the hay meadows mixtures a higher specific leaf area (SLA) than the dry meadows mixtures<!--# describe difference --> .
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
@@
 We tested soil samples of the three substrates on both expositions by mixing several sub-samples.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table @ref(tab:substrate)).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced Calciumcarbonat, and hardly changed the rather high pH values (Table\@ref(tab:substrate)).
+Phosphate and potassium were rather scarce for agricultural soils and Magnesium rather high [@lfl2022].
 The two seed mixture types were tested with the normal seeding density and the increased density recommended for slopes [4 vs.
@@
          show_col_types = FALSE) %>%
+  select(-starts_with("lfl")) %>%
   slice(-1) %>%
@@
                  show_col_types = FALSE) %>%
+      select(-starts_with("lfl")) %>%
       slice(1)

### 2023-02-08 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
+
+# Document head (remove later) <!--# Remove --> {.unnumbered}
 
@@
 
-# Document head <!--# Remove --> {.unnumbered}
-
 Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
@@
 # Abstract (max 300 words) {.unnumbered}
+
+<!--# Write -->
 
@@
 This measure quantifies the distance of a plot to the average reference site from an ordination [@Rydgren.2019].
-Fourth, we visualized the species composition of our experimental plots in comparison with reference sites to evaluate as well absolute success of the restoration outcomes.
-
-<!--# Evaluation: Brudvig 2017 among restoration outcomes and in comparison to reference -->
-
-We asked following question to evaluate the restoration success after four years:
+To complement the indices, the success of restoration or the difference from desired conditions needs to be evaluated [@Brudvig.2017b].
+Therefore, the species composition of the experimental plots were compared with reference sites.
+We asked following question to evaluate the restoration approaches and success after four years:
 
@@
 We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
+
+Write about traits.
 

### 2023-02-08 R/_prepare_data_vegetation.R
Update _prepare_data_vegetation.R

@@ -1213,6 +1213,148 @@ rm(list = setdiff(ls(), c(
 
 
 
+#______________________________________________________________________________
+## 7 Functional plant traits ###################################################
+
+### b TRY data 1 --------------------------------------------------------------
+
+data <- data.table::fread(
+  "data_raw_traitbase_try_20210306_13996.txt",
+  header = TRUE,
+  sep = "\t",
+  dec = ".",
+  quote = ""
+  ) %>%
+  as_tibble() #%>%
+  bind_rows(
+    data.table::fread(
+      "data_raw_traitbase_try_20210318_14157.txt",
+      header = TRUE,
+      sep = "\t",
+      dec = ".",
+      quote = ""
+    ) %>%
+      as_tibble() %>%
+      slice(-1)
+  )
+  rename(
+    name = "AccSpeciesName",
+    value = "StdValue",
+    trait = "TraitID"
+  ) %>%
+  select(name, value, trait) %>%
+  mutate(name = str_replace_all(name, " ", "_")) %>%
+  drop_na %>%
+  mutate(
+    trait = str_replace(trait, "26", "seedmass"),
+    trait = str_replace(trait, "3106", "height"),
+    trait = str_replace(trait, "3107", "height"),
+    trait = str_replace(trait, "3115", "sla"),
+    trait = str_replace(trait, "3116", "sla"),
+    trait = str_replace(trait, "3117", "sla")
+  )
+
+##### * Find synonyms ####
+data <- data %>%
+  mutate(
+    name = as_factor(name),
+    name = fct_recode(
+      name,
+      Carex_praecox_ssp_praecox = "Carex_praecox",
+      Plantago_major_ssp_intermedia = "Plantago_major_subsp._intermedia",
+      Ranunculus_serpens_ssp_nemorosus =
+        "Ranunculus_serpens_subsp._nemorosus"
+    ),
+    trait = as_factor(trait)
+  ) %>%
+  group_by(name, trait) %>%
+  summarise(across(where(is.double), ~median(.x, na.rm = TRUE))) %>%
+  pivot_wider(names_from = "trait", values_from = "value")
+test$name[which(!(test$name %in% data$name))]
+#data %>%
+#group_by(name) %>%
+#summarise(across(where(is.double), ~median(.x, na.rm = T))) %>%
+#filter(str_detect(name, "Equisetum"))
+traits <- traits %>%
+  left_join(data, by = "name") %>%
[…]

### 2023-02-08 manuscript.Rmd
Update manuscript.Rmd

@@
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)).
-As expected have the hay meadows mixtures a higher specific leaf area (SLA) than the dry meadows mixtures<!--# describe difference --> .
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:figure-traits)).
+As expected, the hay meadows mixtures have a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry meadows mixtures.
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
@@
 
-Write about traits.
+The functional traits specific leaf area (SLA), seed mass and canopy height were retrieved from the database LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 In total, seed mixtures had 16 or 32 g per plot.
-All individual seed mixtures are stored in the repository in Zenodo ('outputs/tables/table_a3_seedmixes')."}
+All individual seed mixtures are stored in Table A3."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
 
-functional traits <!--# full description -->
-
-```{r tab.id = "traits", tab.cap = "Traits"}
-#read_csv(here::here("data", "raw", "data_raw_table_3.csv")) %>%
-  #flextable() %>%
-  #bold(part = "header") %>%
-  #autofit()
-```
-
-\clearpage
-
-\newpage
-
-## Table 3 {.unnumbered}
-
-```{r tab.id = "substrate", ft.align = "left",tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
+```{r tab.id = "substrate", ft.align = "left", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
 Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
@@
 
-```{r figure-map, fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
+```{r fig.id = "figure-map", fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
 The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023].
@@
 
+functional traits <!--# full description -->
+
+```{r fig.id = "figure-traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm_traits.tiff")
+  )
+```
+
+\clearpage
+
+\newpage
+
+## Figure 3
+
 ```{r fig.id = "figure-effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
@@
 
-## Figure 3 {.unnumbered}
+## Figure 4 {.unnumbered}
 
@@
 
-## Figure 4 {.unnumbered}
+## Figure 5 {.unnumbered}
 
@@
 
-## Figure 5 {.unnumbered}
+## Figure 6 {.unnumbered}
 
@@
 
-## Figure 6 {.unnumbered}
+## Figure 7 {.unnumbered}
 
@@
 
-## Table S1 {.unnumbered}
+## Table A1 <!--# Is it cited in the text? --> {.unnumbered}
 
@@
 HSW = Highest water level for shipping."}
-read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%
+read_csv(here::here("data", "raw", "data_raw_table_a1.csv")) %>%
   flextable() %>%
@@
 
-## Table S2 {.unnumbered}
+## Table A2 <!--# Is it cited in the text? --> {.unnumbered}
 
@@
 
+## Table A3 {.unnumbered}
+
+Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->
+
 ## Session Info {.unnumbered}

### 2023-02-09 manuscript.Rmd
Update manuscript.Rmd

@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412).
+The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412).
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
@@
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:figure-traits)).
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Figure \@ref(fig:traits)).
 As expected, the hay meadows mixtures have a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry meadows mixtures.
@@
 We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition, halfway up the slopes of the dike and arranged in six blocks (= replicates).
-The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)).
+The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:map)).
 The split plot was caused by testing all 24 treatments on both sides of the dike.
@@
 We tested soil samples of the three substrates on both expositions by mixing several sub-samples.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced Calciumcarbonat, and hardly changed the rather high pH values (Table\@ref(tab:substrate)).
+The sand admixture changed the soil texture, increased the C/N ratio, but reduced Calciumcarbonat, and hardly changed the rather high pH values (Table \@ref(tab:substrate)).
 Phosphate and potassium were rather scarce for agricultural soils and Magnesium rather high [@lfl2022].
@@
 We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
-
-The functional traits specific leaf area (SLA), seed mass and canopy height were retrieved from the database LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
+The functional traits of specific leaf area (SLA), seed mass and canopy height were retrieved from the database LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 
-We could identify a statistically clear positive effect of sand addition on the persistence of sown species and on the recovery rate (Figure \@ref(fig:figure-effects)).
+We could identify a statistically clear positive effect of sand addition on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
 Furthermore, sown hay meadows were clearly closer to their reference plots than sown dry grasslands were to their references.
-The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:figure-persistence); \@ref(fig:figure-fcs); \@ref(fig:figure-recovery)) .
-Both expositions have similar trends but for all responses the values are clearly lower on the south exposition, e.g., persistence values are on average more than 46% higher on the north exposition (Figure \@ref(fig:figure-persistence)).
+The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:persistence); \@ref(fig:fcs); \@ref(fig:recovery)) .
+Both expositions have similar trends but for all responses the values are clearly lower on the south exposition, e.g., persistence values are on average more than 46% higher on the north exposition (Figure \@ref(fig:persistence)).
 The effect of restoration treatments is in the interaction plots not clear.
-Hay meadow seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:figure-recovery)).
+Hay meadow seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:recovery)).
 Though, the sand admixture had no clear effect on the development.
-Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:figure-persistence)).
+Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
 
-The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:figure-nmds)).
+The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
 The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands.
-In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:figure-recovery)) but the right direction of the development.
+In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:recovery)) but the right direction of the development.
 One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed mixture compositions.
@@
 
-```{r fig.id = "figure-map", fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
+```{r fig.id = "map", fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
 The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023].
@@
 
-```{r fig.id = "figure-traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
+```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
 knitr::include_graphics(
@@
 
-```{r fig.id = "figure-effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
+```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
 Furthermore, the median and the 66% and 95% credible intervals are shown.
@@
 
-```{r fig.id = "figure-persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on a dike experiment over the years.
+```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on a dike experiment over the years.
 The substrates had different sand admixtures and different seed mixture types were sown.
@@
 
-```{r fig.id = "figure-fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of a dike experiment.
+```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of a dike experiment.
 The substrates had different sand admixtures and different seed mixture types were sown.
@@
 
-```{r fig.id = "figure-recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (*d~jt,0~*) of plots of an experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
+```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (*d~jt,0~*) of plots of an experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
 The substrates had different sand admixtures and different seed mixture types were sown.
@@
 
-```{r fig.id = "figure-nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
+```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
 In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].

### 2023-02-09 manuscript.Rmd
Update manuscript.Rmd

@@
 We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
-The functional traits of specific leaf area (SLA), seed mass and canopy height were retrieved from the database LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
-
-<!--# Mention traits -->
+The functional traits of specific leaf area (SLA; available traits: 99.2% of all species), seed mass (98.8%) and canopy height (99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub [!cite Zenodo!]<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
-All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
+All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, 'metaMDS' from 'vegan' for the ordination [@vegan] and 'dbFD' from 'FD' for the calculation of community-weighted means of functional traits [@FD].
 
@@
 The German Federal Environmental Foundation (DBU) supported MB with a doctoral scholarship.
+The study has been supported by the TRY initiative on plant traits ([http://www.try-db.org).](http://www.try-db.org).) The TRY initiative and database is hosted, developed and maintained by J.
+Kattge and G.
+Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany).
+TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
 
@@
 
-functional traits <!--# full description -->
-
-```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
+```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The community-weighted means (CWM) of the seed mixtures used for the field experiment of the functional traits specific leaf area (SLA), seed mass and canopy height.
+The CWMs were weighted by seed weight in the seed mixture and  indicate differences between the target types hay meadows and dry grasslands .
+"}
 knitr::include_graphics(

### 2023-02-10 manuscript.Rmd
Update manuscript.Rmd

@@
   officedown::rdocx_document:
-    reference_docx: StylesTemplate.docx
-csl: template-journal-of-applied-ecology.csl
+    reference_docx: template_word.docx
+csl: template_references_j_appl_ecol.csl
 bibliography: bibliography.bib
@@
 Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b].
-It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] and even by restoration through unsuited afforestation [@dudley2020].
+It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] even by restoration through unsuited afforestation [@dudley2020].
 In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
 
-Sowing high-diversity seed mixtures of local provenance produced by commercial but specialised seed companies is a promising way to scale up restoration efforts.
+Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts.
 Though, there are still open questions about specifying the seed mixtures to specific site conditions or even more to future climate conditions to improve efficiency and effectiveness of restoration efforts [@Torok.2021].
@@
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Seeding in general is a way to overcome the dispersal filter [@kiehl2006], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right substrate-seed mixture combination [@Torok.2017].
-This means that a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
-The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion.
+Seeding in general is a way to overcome the dispersal filter [@kiehl2006; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
+This means a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
+The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion of unsuited species.
 Modifying seed mixtures for certain site conditions came up with functional plant traits [@Funk.2008; @Laughlin.2014] but it is not easy to put it into practice for novel ecosystems like urban grasslands [@Bauer.2022].
@@
 Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
-Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve the functionality of the construction [@KleberLerchbaumer.2017].
-Dikes can reconcile several requirements [@teixeira2022], but the substrate-seed mixture combination must be adapted.
+Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@KleberLerchbaumer.2017].
+Dikes can reconcile several requirements [@teixeira2022], but the seed mixture-substrate combination must be adapted.
 
@@
 # Discussion
+
+The vegetation of the dike experiment developed in the right direction, but with reduced velocity and significantly and lasting worse development of the south exposition.
+Sand admixture of 25% was sufficient to reach a positive effect.
+All in all, it was hardly possible to identify an ideal seed mixture-substrate combination.
+Though, hay meadows developed closer to its reference on the north exposition than dry grasslands.
+
+## The effect of seed mixture-substrate combinations
+
+Persistence, FCS
+
+sand admixture positive but 25% enough (ref. to chenot?)
+
+substrate depth does not matter (what can be discussed?)
+
+Higher seeding density not necessary for biodiversity (ref to practioners, evtl. to Batori?)
+
+no significant effect of combination (variability important, further research)
+
+hay meadows closer to reference
+
+Lasting effect of south exposition (drought, seeding late)
+
+## The success of the restoration approaches
 

### 2023-02-10 manuscript.Rmd
Update manuscript.Rmd

@@
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Seeding in general is a way to overcome the dispersal filter [@kiehl2006; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
+Seeding in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
 This means a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
 The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion of unsuited species.
-Modifying seed mixtures for certain site conditions came up with functional plant traits [@Funk.2008; @Laughlin.2014] but it is not easy to put it into practice for novel ecosystems like urban grasslands [@Bauer.2022].
+Modifying seed mixtures for certain site conditions came up with functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020] but it is not easy to put it into practice for novel ecosystems like urban grasslands [@Bauer.2022].
 Substrates cannot only be modified for conservation purposes in urban areas, but also in quarries [@chenot-lescure2022] or dikes [@Liebrand.1996].
@@
 To measure the success of restoration, we chose four indices.
-First, we observed the persistence of the seeded species, which is a key interest of seeding as a restoration approach [@Wilsey.2021].
-For this, it was surveyed if the seeded species are present in the respective plot in following years.
+First, we observed the persistence of the sown species, which is a key interest of seeding as a restoration approach [@Wilsey.2021].
+For this, it was surveyed if the sown species are present in the respective plot in following years.
 Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
@@
 As expected, the hay meadows mixtures have a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry meadows mixtures.
+The south exposed plots were sown in mid-April 2018 and the north exposition two weeks later.
+Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks.
+
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
-In October 2018, *Bromus hordeaceus* was seeded as a nursery grass to provide safe sites under drought conditions.
+In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
 
@@
 
-## The effect of seed mixture-substrate combinations
+## General effects of treatments and exposition
+
+As expected, sand admixture led to higher persistence of sown species.
+In addition, 50% admixture did not further improve the result and the substrate depth had no effect.
+Restoration on agricultural soils has often limited success due to high nutrient loads [@walker2004].
+Our results suggest a slightly better adaption of hay meadows to the north exposition than dry grasslands (Figure @ref(fig:recovery)).
+This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
+
+The vegetation on the south exposition performed consistently and significantly worse than the north exposition.
+One reason might be the removal of the geotextile on the south exposition which led to the drying of many seedlings why the distinction of the seed mixture types was leveled.
+The removal was necessary because of the death of several protected lizards.
+Moreover, the intense drought of 2018 and 2019 [@hari2020] might have decreased germination and establishment of sown species because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
+The interesting outcome of this unfavorable situation during establishment on the south exposition is the lasting negative effect.
+This suggests a legacy effect by unfavorable weather conditions after sowing [@Stuble.2017; @Groves.2020] which might have led to an alternative trajectory and could probably only be met by resowing.
+
+## No interaction effect of seed mixture-substrate combinations
 
 Persistence, FCS
-
-sand admixture positive but 25% enough (ref. to chenot?)
 
@@
 
-no significant effect of combination (variability important, further research)
+no significant effect of combination (variability important, further research, chenot with topsoil)
 
@@
 Outlook: landscape, management are important
+
+Plant traits (Plas 2020, Orrock 2023)
 
@@
 ```{r tab.id = "establishment", tab.cap = "Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
-Indicated is the number of seeded plots and the percentage of these plots which were occupied by the respective species.
-This means that for each species only the seeded plots were included.
+Indicated is the number of sown plots and the percentage of these plots which were occupied by the respective species.
+This means that for each species only the sown plots were included.
 The shades of grey indicate the success of establishment."}
@@
          name = str_replace_all(name, "_", " ")) %>%
-  rename(Species = name, Family = family, "Seeded plots [#]" = total_seeded_2018, "Establishment rate [%]" = rate_2018, "2019" = rate_2019, "2020" = rate_2020, "2021" = rate_2021) %>%
+  rename(Species = name, Family = family, "Seeded plots [#]" = total_sown_2018, "Establishment rate [%]" = rate_2018, "2019" = rate_2019, "2020" = rate_2020, "2021" = rate_2021) %>%
   flextable() %>%

### 2023-02-14 manuscript.Rmd
Update manuscript.Rmd

@@
 
-As expected, sand admixture led to higher persistence of sown species.
-In addition, 50% admixture did not further improve the result and the substrate depth had no effect.
-Restoration on agricultural soils has often limited success due to high nutrient loads [@walker2004].
-Our results suggest a slightly better adaption of hay meadows to the north exposition than dry grasslands (Figure @ref(fig:recovery)).
-This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
+As expected, sand admixture led to higher persistence of sown species but only on the north exposition and the effect size of about 6% in the fourth year after restoration is rather small.
+In addition, 50% admixture did not further improve the result.
+Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but can lead to positive results, if mixed with mineral material as sand and gravel [@chenot-lescure2022].
+Substrate depth did not significantly affect persistence or Favorable Conservation Status (FCS) similarly to earlier studies [@baer2004].
+Larger differences of soil depth might be necessary to create negative effects by greater soil depths as was shown for prairies [@dornbush2010].
+Neither, seeding density had an effect on persistence and FCS which fits to result of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary but higher densities do not further improve establishment of target species but have rather a slight negative effect.
 
-The vegetation on the south exposition performed consistently and significantly worse than the north exposition.
-One reason might be the removal of the geotextile on the south exposition which led to the drying of many seedlings why the distinction of the seed mixture types was leveled.
-The removal was necessary because of the death of several protected lizards.
+The vegetation on the south exposition performed consistently and significantly worse than the north exposition and had a different species composition which was not found in that clarity by @Batori.2016 in Hungary.
+One reason might be the removal of the geotextile, which had been implemented on the south exposition, because of the death of several protected lizards.
+This led to the drying of many seedlings why the distinction of the seed mixture types might be leveled.
 Moreover, the intense drought of 2018 and 2019 [@hari2020] might have decreased germination and establishment of sown species because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
-The interesting outcome of this unfavorable situation during establishment on the south exposition is the lasting negative effect.
-This suggests a legacy effect by unfavorable weather conditions after sowing [@Stuble.2017; @Groves.2020] which might have led to an alternative trajectory and could probably only be met by resowing.
+The interesting point here is the lasting negative effect which suggests a legacy effect by unfavorable weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
+The problems during the establishment phase might have led to an alternative trajectory and could probably only be met by resowing.
 
@@
 
-Persistence, FCS
-
-substrate depth does not matter (what can be discussed?)
-
-Higher seeding density not necessary for biodiversity (ref to practioners, evtl. to Batori?)
-
-no significant effect of combination (variability important, further research, chenot with topsoil)
-
-hay meadows closer to reference
-
-Lasting effect of south exposition (drought, seeding late)
+Our aim was to identify a ideal seed mixture-substrate combination in respect of restoration effectiveness and biodiversity.
+For evaluating effectiveness, we measured the establishment and persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
+Though, we could not identify an interaction effect for neither of the indices.
+We would have expected a better performance of hay meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
+Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
+Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions [Figure @ref(fig:traits); @Oberdorfer.1993; @Oberdorfer.1993b].
+Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
+Though, these two studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after five and about 15 years, respectively.
+Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the sown species could establish earlier than others and preempted the available niches [@Fukami.2015].
 
@@
 
-Mention drought in 2018 and 2019
-
-Compare with Mitchley 2012, Engst 2016, Freitag 2021, Kaulfuß 2022
-
-Batori 2016 neither found great differences between expositions
-
-persistence influenced by neighbourig plots
-
-Outlook: landscape, management are important
+The seed mixtures and positive references were similar but hardly overlapped (Figure \@ref(fig:nmds)).
+The position on the NMDS suggests that the seed mixture represent a latter successional stage than the positive references.
+The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure @ref(fig:recovery)).
+This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
+Though, after four years the vegetation was still distinct from positive references and seed mixtures as shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
+This result is not surprising since the recovery debt is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
+Our results support that dikes can promote biodiversity in agricultural landscapes [@Batori.2020] but the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
 
@@
 
-Text
+Variability important (different seed mixture types, different soils)
+
+Higher seeding density not necessary for biodiversity
+
+Outlook: landscape, management are important
 
@@
   compose(i = 1, j = 14, part = "header", value = as_paragraph("CaCO", as_sub("3"))) %>%
-  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
-  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
-  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
+  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
+  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
+  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
   align(align = "left", part = "footer") %>%
@@
 We evaluated the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
+The FCS is the ratio of target species and non-target species.
 Note that the zero lines indicate that both levels have equal values.
@@
   here("data", "processed", "data_processed_traits.csv"),
-                 col_names = TRUE, na = c("na", "NA"), col_types =
-                   cols(.default = "?", name = "f")
+  col_names = TRUE,
+  na = c("na", "NA"),
+  col_types = cols(.default = "?", name = "f")
   ) %>%
@@
   arrange(match(family, c("Poaceae", "Fabaceae"))) %>%
-  mutate(across(starts_with("rate"), ~ .x * 100),
+  mutate(
+    across(starts_with("rate"), ~ .x * 100),
     name = str_replace_all(name, "_", " ")) %>%
-  rename(Species = name, Family = family, "Seeded plots [#]" = total_sown_2018, "Establishment rate [%]" = rate_2018, "2019" = rate_2019, "2020" = rate_2020, "2021" = rate_2021) %>%
+  rename(
+    Species = name,
+    Family = family,
+    "Seeded plots [#]" = total_seeded_2018,
+    "Establishment rate [%]" = rate_2018,
+    "2019" = rate_2019,
+    "2020" = rate_2020,
+    "2021" = rate_2021
+    ) %>%
   flextable() %>%

### 2023-02-14 manuscript.Rmd
Update manuscript.Rmd

@@
 
-The vegetation on the south exposition performed consistently and significantly worse than the north exposition and had a different species composition which was not found in that clarity by @Batori.2016 in Hungary.
-One reason might be the removal of the geotextile, which had been implemented on the south exposition, because of the death of several protected lizards.
-This led to the drying of many seedlings why the distinction of the seed mixture types might be leveled.
+The vegetation on the south exposition performed consistently and significantly worse than the north exposition and had a different species composition which was also shown by @Batori.2016 in Hungary.
+Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the south exposition, was removed after two weeks because of the death of several protected lizards.
+This led to the drying of many seedlings why the distinction of the seed mixture types might be leveled on the south exposition.
 Moreover, the intense drought of 2018 and 2019 [@hari2020] might have decreased germination and establishment of sown species because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
@@
 This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
-Though, after four years the vegetation was still distinct from positive references and seed mixtures as shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
+On the south exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.
+
+The vegetation developed in general in the right direction but was still distinct from positive references and seed mixtures after four years as it was shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
 This result is not surprising since the recovery debt is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
 Our results support that dikes can promote biodiversity in agricultural landscapes [@Batori.2020] but the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
-
-Plant traits (Plas 2020, Orrock 2023)
 
@@
 The substrates had different sand admixtures and different seed mixture types were sown.
-The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (Figure 5).
+The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (Figure 7).
 The grey area marks the standard deviation of the position of the reference sites.

### 2023-02-14 manuscript.Rmd
Update manuscript.Rmd

@@
 
-The vegetation developed in general in the right direction but was still distinct from positive references and seed mixtures after four years as it was shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
-This result is not surprising since the recovery debt is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
-Our results support that dikes can promote biodiversity in agricultural landscapes [@Batori.2020] but the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
+The vegetation developed in general in the right direction but was still distinct from positive references and seed mixtures after four years.
+It was rather similar to the negative reference of perennial ruderal vegetation.
+The gap between goal and restoration outcome was also shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
+This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
 
@@
 
-Variability important (different seed mixture types, different soils)
-
-Higher seeding density not necessary for biodiversity
-
-Outlook: landscape, management are important
+Our results suggest that adapted seed mixtures can increase restoration efficiency by seeding hay meadows on the north exposition and not on the south exposition of dikes.
+Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, although the effect is small.
+The question remains if money is best invested in sand admixture or in other restoration measures.
+It seems not to be necessary to increase seeding density on dike slopes, which would reduce restoration costs.
+As well as the use of more deeper soil depth which would otherwise create costs for removal of topsoil.
+There was no perfect seed mixture-substrate combination, why we conclude that a variation of seed mixtures types and different soils along restoration sections would promote biodiversity better than a single solution [@bauer2023; @Holl.2022].
+The strong and lasting negative effect of drought on the south exposition might require a resowing.
+To close the recovery debt, the adaption of the management might be promising since it is a relevant factor aside of restoration approach and site characteristics [@Grman.2013; @tölgyesi2021].
+For example, starting sheep grazing on the restored sites will modify the disturbance regime and improve dispersal.
+All in all, our results support the finding that dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
+Though, the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
 

### 2023-02-15 manuscript_appendix.Rmd
Create manuscript_appendix.Rmd

--- 2023-02-14 manuscript.Rmd
@@
 ---
-title: "Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions"
+title: "Appendix of Bauer et al. (2023)"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 ---
-
-# Document head (remove later) <!--# Remove --> {.unnumbered}
 
@@
 
-Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
-
-\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de)
-
-Max 8000 words <!--# Remove -->
-
-\newpage
-
-# Abstract (max 300 words) {.unnumbered}
-
-<!--# Write -->
-
-\clearpage
-
-\newpage
-
-# Keywords {.unnumbered}
-
-Bayesian models
-
-dike grasslands
-
-embankment
-
-endangered species
-
-environmental filter
-
-species composition
-
-restoration
-
-sand
-
-soil properties
-
-surveys
-
-vegetation
-
-\clearpage
-
-\newpage
-
-# Introduction
-
-Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010], is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g., @Freitag.2021].
-Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b].
-It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] even by restoration through unsuited afforestation [@dudley2020].
-In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
-
-Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts.
-Though, there are still open questions about specifying the seed mixtures to specific site conditions or even more to future climate conditions to improve efficiency and effectiveness of restoration efforts [@Torok.2021].
-For this reason, restoration ecology has to increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015].
-Rigorous, repeatable, and transparent experiments linked to a hypothesis derived from theory are needed to guide evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Seeding in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
-This means a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
-The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion of unsuited species.
-Modifying seed mixtures for certain site conditions came up with functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020] but it is not easy to put it into practice for novel ecosystems like urban grasslands [@Bauer.2022].
-Substrates cannot only be modified for conservation purposes in urban areas, but also in quarries [@chenot-lescure2022] or dikes [@Liebrand.1996].
-
-Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
-Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@KleberLerchbaumer.2017].
-Dikes can reconcile several requirements [@teixeira2022], but the seed mixture-substrate combination must be adapted.
-
-The aim of this study is to identify the ideal combination of substrates and seed mixtures for north and south exposed slopes in Central Europe to develop a vital and species-rich vegetation cover.
-We set up an experiment and tested agricultural soil with different amounts of sand admixture and different installation depths, as well as different seed mixture types and different seed densities.
-We expected a better development of dry grassland on the south exposition with sandy substrate and hay meadows on north exposition with less sandy substrate.
-Since seeds are expensive, practitioners like to know if the slopes need a higher seed density [cf.
-@KleberLerchbaumer.2017].
-
-To measure the success of restoration, we chose four indices.
-First, we observed the persistence of the sown species, which is a key interest of seeding as a restoration approach [@Wilsey.2021].
-For this, it was surveyed if the sown species are present in the respective plot in following years.
-Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
-Characteristic diversity is created by established species which belong to the habitat-specific species pool.
-In other words, these species are target species for a habitat type of interest.
-Third, the successional distance to the reference was determined.
-This measure quantifies the distance of a plot to the average reference site from an ordination [@Rydgren.2019].
-To complement the indices, the success of restoration or the difference from desired conditions needs to be evaluated [@Brudvig.2017b].
-Therefore, the species composition of the experimental plots were compared with reference sites.
-We asked following question to evaluate the restoration approaches and success after four years:
-
-1.  How strong differs the persistence of the sown species among the seed mixture-substrate combinations?
-
-2.  How strong differs the Favorable Conservation Status (FCS) among the seed mixture-substrate combinations?
-
-3.  How close is the vegetation to the reference state?
-
-\clearpage
-
-\newpage
-
-# Material & Methods
-
-## Experimental design {.unnumbered}
-
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412).
-The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
-Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen.
-The substrates were mixed with a big roller and an excavator prepared the plots.
-The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B).
-The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
-The seeds were received from a commercial producer of autochthonous seeds.
-From the species pools, 20 species were randomly selected for each plot.
-The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Figure \@ref(fig:traits)).
-As expected, the hay meadows mixtures have a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry meadows mixtures.
-The south exposed plots were sown in mid-April 2018 and the north exposition two weeks later.
-Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks.
-
-The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
-In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
-
-We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition, halfway up the slopes of the dike and arranged in six blocks (= replicates).
-The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:map)).
-The split plot was caused by testing all 24 treatments on both sides of the dike.
-We tested three sand admixtures (0%, 25% and 50%) and tow soil depths (15 vs.
-30 cm) of practical interest [@KleberLerchbaumer.2017] and two .
-Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-We tested soil samples of the three substrates on both expositions by mixing several sub-samples.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced Calciumcarbonat, and hardly changed the rather high pH values (Table \@ref(tab:substrate)).
-Phosphate and potassium were rather scarce for agricultural soils and Magnesium rather high [@lfl2022].
-The two seed mixture types were tested with the normal seeding density and the increased density recommended for slopes [4 vs.
-8 g m^-2^ @Kiehl.2010; @KleberLerchbaumer.2017].
-The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
-Establishment rates of species (Appendix Table \@ref(tab:establishment)).
-
-## External data
-
-Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys in the surroundings on Danube dikes [@bauer2023].
-We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
-The functional traits of specific leaf area (SLA; available traits: 99.2% of all species), seed mass (98.8%) and canopy height (99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
-
-## Statistical analyses {.unnumbered}
-
-To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed-effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
-Furthermore, we included as a fixed effect the botanists of each plot.
-For the simple effects of the treatments, we chose plausible weakly informative priors.
-To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
-For the computation, we used 4 chains, a thinning rate of 2, 5000 iterations for warm-up and 10,000 in total.
-For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values and MCMC chain resolution by the effective sampling size (ESS).
-Posterior predictive check was done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].
-Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
-
-A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
-Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress 0.21).
-
-Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub [!cite Zenodo!]<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
-All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, 'metaMDS' from 'vegan' for the ordination [@vegan] and 'dbFD' from 'FD' for the calculation of community-weighted means of functional traits [@FD].
-
-\clearpage
-
-\newpage
-
-# Results
-
-We could identify a statistically clear positive effect of sand addition on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
-Furthermore, sown hay meadows were clearly closer to their reference plots than sown dry grasslands were to their references.
-The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:persistence); \@ref(fig:fcs); \@ref(fig:recovery)) .
-Both expositions have similar trends but for all responses the values are clearly lower on the south exposition, e.g., persistence values are on average more than 46% higher on the north exposition (Figure \@ref(fig:persistence)).
-The effect of restoration treatments is in the interaction plots not clear.
-Hay meadow seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:recovery)).
-Though, the sand admixture had no clear effect on the development.
-Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
-
-The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
-The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands.
-In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:recovery)) but the right direction of the development.
-One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed mixture compositions.
-The ordination presents the experimental plots not only in context with seed mixtures, but also with reference sites.
-The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap.
-The positions of reference sites are shifted to the left on the NMDS1 axis which means in the direction of early successional states.
-On the south exposition, we had negative reference sites which are located in the NMDS in between the positive reference sites and the recent state of restored plots.
-However, most of negative reference sites (ruderal, dry and anthropogenic vegetation) are situated in the upper half and explicitly recent restoration sites on the south exposition are close to them.
-
-\clearpage
-
-\newpage
-
-# Discussion
-
-The vegetation of the dike experiment developed in the right direction, but with reduced velocity and significantly and lasting worse development of the south exposition.
-Sand admixture of 25% was sufficient to reach a positive effect.
-All in all, it was hardly possible to identify an ideal seed mixture-substrate combination.
-Though, hay meadows developed closer to its reference on the north exposition than dry grasslands.
-
-## General effects of treatments and exposition
-
-As expected, sand admixture led to higher persistence of sown species but only on the north exposition and the effect size of about 6% in the fourth year after restoration is rather small.
-In addition, 50% admixture did not further improve the result.
-Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but can lead to positive results, if mixed with mineral material as sand and gravel [@chenot-lescure2022].
-Substrate depth did not significantly affect persistence or Favorable Conservation Status (FCS) similarly to earlier studies [@baer2004].
-Larger differences of soil depth might be necessary to create negative effects by greater soil depths as was shown for prairies [@dornbush2010].
-Neither, seeding density had an effect on persistence and FCS which fits to result of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary but higher densities do not further improve establishment of target species but have rather a slight negative effect.
-
-The vegetation on the south exposition performed consistently and significantly worse than the north exposition and had a different species composition which was not found in that clarity by @Batori.2016 in Hungary.
-One reason might be the removal of the geotextile, which had been implemented on the south exposition, because of the death of several protected lizards.
-This led to the drying of many seedlings why the distinction of the seed mixture types might be leveled.
-Moreover, the intense drought of 2018 and 2019 [@hari2020] might have decreased germination and establishment of sown species because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
-The interesting point here is the lasting negative effect which suggests a legacy effect by unfavorable weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
-The problems during the establishment phase might have led to an alternative trajectory and could probably only be met by resowing.
-
-## No interaction effect of seed mixture-substrate combinations
-
-Our aim was to identify a ideal seed mixture-substrate combination in respect of restoration effectiveness and biodiversity.
-For evaluating effectiveness, we measured the establishment and persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
-Though, we could not identify an interaction effect for neither of the indices.
-We would have expected a better performance of hay meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
-Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions [Figure @ref(fig:traits); @Oberdorfer.1993; @Oberdorfer.1993b].
-Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-Though, these two studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after five and about 15 years, respectively.
-Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the sown species could establish earlier than others and preempted the available niches [@Fukami.2015].
-
-## The success of the restoration approaches
-
-The seed mixtures and positive references were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the NMDS suggests that the seed mixture represent a latter successional stage than the positive references.
-The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure @ref(fig:recovery)).
-This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
-Though, after four years the vegetation was still distinct from positive references and seed mixtures as shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
-This result is not surprising since the recovery debt is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
-Our results support that dikes can promote biodiversity in agricultural landscapes [@Batori.2020] but the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
-
-Plant traits (Plas 2020, Orrock 2023)
-
-\clearpage
-
-\newpage
-
-# Conclusions
-
-Variability important (different seed mixture types, different soils)
-
-Higher seeding density not necessary for biodiversity
-
-Outlook: landscape, management are important
-
-\clearpage
-
-\newpage
-
-# Acknowledgements {.unnumbered}
-
-We would like to thank our project partners Dr.
-Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) and Klaus Rachl and Stefan Radlmair (Regierung von Niederbayern) for numerous discussions on restoration and management of dike grasslands.
-Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
-We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H.
-Teixeira, and Linda Weggler for assisting with the field surveys or soil analyses in 2018--2020.
-The German Federal Environmental Foundation (DBU) supported MB with a doctoral scholarship.
-The study has been supported by the TRY initiative on plant traits ([http://www.try-db.org).](http://www.try-db.org).) The TRY initiative and database is hosted, developed and maintained by J.
-Kattge and G.
-Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany).
-TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
-
-# Author contribution {.unnumbered}
-
-JH and JK designed the experiment. JH did the surveys in the years 2018--2020 and MB in 2019 and 2021. MB did the analyses and wrote the manuscript. JK and JH critically revised the manuscript.
-
-# Open research {#sec-open-research .unnumbered}
-
-Data and code are stored on Zenodo (Bauer et al. 2023) <!--# Update citation after upload -->
-
-Model evaluation is stored on GitHub: [github.com/markus1bauer/2023_danube_dike_experiment](https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown)
-
-# Funding {.unnumbered}
-
-MB is funded by a doctoral scholarship of the German Federal Environmental Foundation (DBU) (No.
-20021/698).
-The establishment of the experiment and the vegetation surveys were financed by the WIGES GmbH in the years 2018--2020 (No.
-80 002 312).
-
-\clearpage
-
-\newpage
-
-# References {.unnumbered}
-
-::: {#refs}
-:::
-
-\clearpage
-
-\newpage
-
-<!---BLOCK_LANDSCAPE_START--->
-
-# Tables {.unnumbered}
-
-## Table 1 {.unnumbered}
-
-```{r tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
-The total species pool for hay meadows was 55 and for dry grassland 58.
-In total, seed mixtures had 16 or 32 g per plot.
-All individual seed mixtures are stored in Table A3."}
-read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
-         show_col_types = FALSE) %>%
-  slice(-1) %>%
-  flextable() %>%
-  merge_at(part = "header", j = 2:3) %>%
-  align(align = "center", part = "all", j = -1) %>%
-  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
-  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
-  bold(part = "header", i = 1) %>%
-  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
-  autofit()
-```
-
-\clearpage
-
-\newpage
-
-## Table 2 {.unnumbered}
-
-```{r tab.id = "substrate", ft.align = "left", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
-Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
-The pH was measured in CaCl2 solution.
-Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract.
-For calculating CaCO3, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
-To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C.
-Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand."}
-read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
-         show_col_types = FALSE) %>%
-  select(-starts_with("lfl")) %>%
-  slice(-1) %>%
-  flextable() %>%
-  bold(part = "header") %>%
-  add_header_row(
-    top = FALSE,
-    values = read_csv(
-      here::here("data", "raw", "data_raw_table_3_substrate.csv"),
-                 show_col_types = FALSE) %>%
-      select(-starts_with("lfl")) %>%
-      slice(1)
-    ) %>%
-  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
-  align(align = "center", part = "all", j = -1) %>%
-  compose(i = 1, j = 10, part = "header", value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))) %>%
-  compose(i = 1, j = 11, part = "header", value = as_paragraph("K", as_sub("2"), "O")) %>%
-  compose(i = 1, j = 12, part = "header", value = as_paragraph("Mg", as_sup("2+"))) %>%
-  compose(i = 1, j = 14, part = "header", value = as_paragraph("CaCO", as_sub("3"))) %>%
-  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
-  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
-  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
-  align(align = "left", part = "footer") %>%
-  set_table_properties(layout = "autofit", width = 1)
-```
-
-\newpage
-
-<!---BLOCK_LANDSCAPE_STOP--->
-
-# Figures {.unnumbered}
-
-## Figure 1 {.unnumbered}
-
-```{r fig.id = "map", fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
-The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023].
-Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture types H and D).
-The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates.
-The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_1_map.png")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 2 {.unnumbered}
-
-```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The community-weighted means (CWM) of the seed mixtures used for the field experiment of the functional traits specific leaf area (SLA), seed mass and canopy height.
-The CWMs were weighted by seed weight in the seed mixture and  indicate differences between the target types hay meadows and dry grasslands .
-"}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm_traits.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 3
-
-```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
-Furthermore, the median and the 66% and 95% credible intervals are shown.
-We evaluated the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
-The FCS is the ratio of target species and non-target species.
-Note that the zero lines indicate that both levels have equal values.
-This means that hay meadows are closer to their reference than dry grasslands  (C)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 4 {.unnumbered}
-
-```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on a dike experiment over the years.
-The substrates had different sand admixtures and different seed mixture types were sown.
-Per plot were 20 species sown.
-Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 5 {.unnumbered}
-
-```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of a dike experiment.
-The substrates had different sand admixtures and different seed mixture types were sown.
-The zero line indicate that target and non-target species are balanced.
-Positive values indicate that there are more target species.
-Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 6 {.unnumbered}
-
-```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (*d~jt,0~*) of plots of an experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
-The substrates had different sand admixtures and different seed mixture types were sown.
-The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (Figure 5).
-The grey area marks the standard deviation of the position of the reference sites.
-Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 7 {.unnumbered}
-
-```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
-In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
-The circles show the standard error of the groups.
-2D stress: 0.21."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
 <!---BLOCK_LANDSCAPE_START--->
@@
 
-## Table A1 <!--# Is it cited in the text? --> {.unnumbered}
+## Table A1 {.unnumbered}
 
@@
 
+<!---BLOCK_LANDSCAPE_STOP--->
+
 \clearpage
@@
 
-<!---BLOCK_LANDSCAPE_STOP--->
+## Table A2 {.unnumbered}
 
-## Table A2 <!--# Is it cited in the text? --> {.unnumbered}
+Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->
+
+## Table A3 {.unnumbered}
 
@@
 ```
-
-\clearpage
-
-\newpage
-
-## Table A3 {.unnumbered}
-
-Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->
-
-## Session Info {.unnumbered}
-
-```{r sessioninfo}
-sessionInfo()
-```

### 2023-02-15 manuscript.Rmd
Update manuscript.Rmd

@@
 
-# Abstract (max 300 words) {.unnumbered}
-
-<!--# Write -->
+# Abstract {.unnumbered}
 
@@
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge].
+During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix A1, @lfu2021waterlevel; @lfu2021discharge].
 Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen.
@@
 The seeds were received from a commercial producer of autochthonous seeds.
-From the species pools, 20 species were randomly selected for each plot.
+From the species pools, 20 species were randomly selected for each plot (Appendix A2).
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
@@
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
-Establishment rates of species (Appendix Table \@ref(tab:establishment)).
+Establishment rates of species (Appendix A3).
 
@@
 
-<!---BLOCK_LANDSCAPE_START--->
-
-# Supplementary Material {.unnumbered}
-
-## Table A1 <!--# Is it cited in the text? --> {.unnumbered}
-
-```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Three dry years (2018–2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017–2021), based on weather station Metten [mean, 1981–2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
-HQ2 = Highest discharge with a probability of occurrence every second year.
-HSW = Highest water level for shipping."}
-read_csv(here::here("data", "raw", "data_raw_table_a1.csv")) %>%
-  flextable() %>%
-  bold(part = "header") %>%
-  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
-  autofit()
-```
-
-\clearpage
-
-\newpage
-
-<!---BLOCK_LANDSCAPE_STOP--->
-
-## Table A2 <!--# Is it cited in the text? --> {.unnumbered}
-
-```{r tab.id = "establishment", tab.cap = "Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
-Indicated is the number of sown plots and the percentage of these plots which were occupied by the respective species.
-This means that for each species only the sown plots were included.
-The shades of grey indicate the success of establishment."}
-read_csv(
-  here("data", "processed", "data_processed_traits.csv"),
-  col_names = TRUE,
-  na = c("na", "NA"),
-  col_types = cols(.default = "?", name = "f")
-  ) %>%
-  select(name, family, total_seeded_2018, starts_with("rate_")) %>%
-  drop_na(total_seeded_2018) %>%
-  arrange(match(family, c("Poaceae", "Fabaceae"))) %>%
-  mutate(
-    across(starts_with("rate"), ~ .x * 100),
-    name = str_replace_all(name, "_", " ")) %>%
-  rename(
-    Species = name,
-    Family = family,
-    "Seeded plots [#]" = total_seeded_2018,
-    "Establishment rate [%]" = rate_2018,
-    "2019" = rate_2019,
-    "2020" = rate_2020,
-    "2021" = rate_2021
-    ) %>%
-  flextable() %>%
-  align(part = "all", align = "center", j = -1) %>%
-  merge_at(part = "header", j = 4:7) %>%
-  add_header_row(top = FALSE, values = c("", "", "", "2018", "2019", "2020", "2021")) %>%
-  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
-  bold(part = "header") %>%
-  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
-  bg(j = 4:7, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 100))) %>%
-  autofit()
-```
-
-\clearpage
-
-\newpage
-
-## Table A3 {.unnumbered}
-
-Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->
-
 ## Session Info {.unnumbered}

### 2023-02-15 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions"
+title: "Can dike grassland restoration profit from ideal seed mixture-substrate combinations?"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 
-Max 8000 words <!--# Remove -->
+\clearpage
 
@@
 # Abstract {.unnumbered}
+
+Sowing is a well established restoration technique to overcome dispersal limitation.
+Though, adapted seed mixtures to certain site conditions promise a more effective restoration.
+This is especially important if the restored vegetation has to protect constructions like dikes.
+An ideal seed mixture-substrate combination would enhance erosion protection and species-rich grasslands.
 
@@
 
-Bayesian models
+artificial soil mixture
 
-dike grasslands
+community assembly
 
-embankment
+dry grasslands
 
-endangered species
+Favorable Conservation Status
 
-environmental filter
+hay meadow
+
+persistences
+
+river embankment
+
+soil restoration
+
+sowing
 
@@
 
-restoration
-
-sand
-
-soil properties
-
-surveys
-
-vegetation
+species-rich grassland
 
@@
 Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
-Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@KleberLerchbaumer.2017].
+Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@berendse2015].
 Dikes can reconcile several requirements [@teixeira2022], but the seed mixture-substrate combination must be adapted.

### 2023-02-15 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 ---
-title: "Appendix of Bauer et al. (2023)"
+title: "Appendix of Bauer et al. (2023) Dike experiment"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 ---
+
+Restoration Ecology, TUM School of Life Sciences, Technical University of Munich, Germany
+
+\* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de), ORCiD <https://orcid.org/0000-0001-5372-4174>
 
@@
 
-# Supplementary Material {.unnumbered}
+## Appendix A1 {.unnumbered}
 
-## Table A1 {.unnumbered}
+Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
+HQ2 = Highest discharge with a probability of occurrence every second year.
+HSW = Highest water level for shipping.
 
-```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Three dry years (2018–2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017–2021), based on weather station Metten [mean, 1981–2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
-HQ2 = Highest discharge with a probability of occurrence every second year.
-HSW = Highest water level for shipping."}
+```{r table-flood-weather, tab.id = "flood-weather", tab.cap = ""}
 read_csv(here::here("data", "raw", "data_raw_table_a1.csv")) %>%
@@
 
-\clearpage
-
-\newpage
-
-## Table A2 {.unnumbered}
+## Appendix A2 {.unnumbered}
 
@@
 
-## Table A3 {.unnumbered}
+## Appendix A3 {.unnumbered}
 
-```{r tab.id = "establishment", tab.cap = "Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
+Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
 Indicated is the number of sown plots and the percentage of these plots which were occupied by the respective species.
 This means that for each species only the sown plots were included.
-The shades of grey indicate the success of establishment."}
+The shades of grey indicate the success of establishment.
+
+```{r tab.id = "establishment", tab.cap = ""}
 read_csv(
@@
 ```
+
+# References {.unnumbered}
+
+::: {#refs}
+:::

### 2023-02-15 manuscript.Rmd
Update manuscript.Rmd

@@
 
+1.
 Sowing is a well established restoration technique to overcome dispersal limitation.
@@
 This is especially important if the restored vegetation has to protect constructions like dikes.
-An ideal seed mixture-substrate combination would enhance erosion protection and species-rich grasslands.
+An ideal seed mixture-substrate combination would concurrently enhance erosion protection and species-rich grasslands by a fast and successful establishment of target species.
+2.
+An experiment with 288 plots was conducted on both expositions of a dike and vegetation was surveyed 2018-2021.
+We tested different sand admixtures, substrate depths, seed densities and seed mixture types (hay meadows, dry calcareous grasslands), and measured the persistence of sown species, the Favorable Conservation Status (FCS) and the successional distance to reference sites as calculated from an ordination.
+3.  Sand admixture had a significant but slightly positive effect on all indices. However, substrate depth, seed density and seed mixture type had no significant effect on persistence or FCS.
+4.
+On the north exposition, hay meadow-seed mixtures developed closer to its reference than dry grasslands.
+Overall, the vegetation developed in the desired direction but a recovery debt remained after four years.
+Plots still exhibited similarities to negative references from ruderal vegetation.
+5.
+The south exposition was significantly worse than the north exposition which might be due to the severe drought during establishment and the addition and removal of a geotextile.
+This negative effect remained over the whole observation period.
+6.
+Synthesis and applications: Adapted seed mixtures can make restorations more efficient.
+Though, varying seed mixture-substrate combinations might foster biodiversity more than a desired 'ideal' combination.
+Furthermore, additional efforts in management or resowing due to severe legacy effects by drought might be necessary to reduce the recovery debt.
 
@@
 
-persistences
+persistence
 
@@
 
-Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts.
+Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts [@Freitag.2021].
 Though, there are still open questions about specifying the seed mixtures to specific site conditions or even more to future climate conditions to improve efficiency and effectiveness of restoration efforts [@Torok.2021].
@@
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Seeding in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
+Sowing in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
 This means a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
@@
 To measure the success of restoration, we chose four indices.
-First, we observed the persistence of the sown species, which is a key interest of seeding as a restoration approach [@Wilsey.2021].
+First, we observed the persistence of the sown species, which is a key interest of sowing as a restoration approach [@Wilsey.2021].
 For this, it was surveyed if the sown species are present in the respective plot in following years.
@@
 
-3.  How close is the vegetation to the reference state?
+3.  How close is the established vegetation to the reference state?
 
@@
 The effect of restoration treatments is in the interaction plots not clear.
-Hay meadow seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:recovery)).
+Hay meadow-seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:recovery)).
 Though, the sand admixture had no clear effect on the development.
@@
 Though, we could not identify an interaction effect for neither of the indices.
-We would have expected a better performance of hay meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
+We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
@@
 It was rather similar to the negative reference of perennial ruderal vegetation.
-The gap between goal and restoration outcome was also shown for other seeding experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
+The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
 This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
@@
 
-Our results suggest that adapted seed mixtures can increase restoration efficiency by seeding hay meadows on the north exposition and not on the south exposition of dikes.
+Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows on the north exposition and not on the south exposition of dikes.
 Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, although the effect is small.

### 2023-02-16 manuscript.Rmd
Update manuscript.Rmd

@@
 1.
-Sowing is a well established restoration technique to overcome dispersal limitation.
+Sowing is a well-established restoration technique to overcome dispersal limitation.
 Though, adapted seed mixtures to certain site conditions promise a more effective restoration.
 This is especially important if the restored vegetation has to protect constructions like dikes.
-An ideal seed mixture-substrate combination would concurrently enhance erosion protection and species-rich grasslands by a fast and successful establishment of target species.
+An ideal seed mixture-substrate combination would concurrently improve the ecosystem function erosion protection and enhance species-rich grasslands by a fast and successful establishment of target species.
 2.
-An experiment with 288 plots was conducted on both expositions of a dike and vegetation was surveyed 2018-2021.
+An experiment with 288 plots was conducted on both expositions of a dike and was surveyed 2018--2021.
 We tested different sand admixtures, substrate depths, seed densities and seed mixture types (hay meadows, dry calcareous grasslands), and measured the persistence of sown species, the Favorable Conservation Status (FCS) and the successional distance to reference sites as calculated from an ordination.
-3.  Sand admixture had a significant but slightly positive effect on all indices. However, substrate depth, seed density and seed mixture type had no significant effect on persistence or FCS.
+3.  Sand admixture had a significant but slightly positive effect on all indices. Substrate depth, seed density and seed mixture type had no significant effect on persistence or FCS.
 4.
@@
 The south exposition was significantly worse than the north exposition which might be due to the severe drought during establishment and the addition and removal of a geotextile.
-This negative effect remained over the whole observation period.
+This initial negative effect remained over the whole observation period.
 6.
-Synthesis and applications: Adapted seed mixtures can make restorations more efficient.
-Though, varying seed mixture-substrate combinations might foster biodiversity more than a desired 'ideal' combination.
-Furthermore, additional efforts in management or resowing due to severe legacy effects by drought might be necessary to reduce the recovery debt.
+Synthesis and applications: Adapted seed mixtures can make restorations more efficient like applying hay meadows on the north exposition.
+However, varying seed mixture-substrate combinations might foster biodiversity like beta diversity more than a desired 'ideal' combination.
+Furthermore, additional efforts in management might be necessary to reduce the recovery debt and resowing after a severe drought might be sensible due to strong legacy effects.
 
@@
 
-Sowing as an approach to restore semi-natural grasslands has long been established [@Kiehl.2010], is also able to restore functional diversity [@Engst.2016] and is continuously developed [e.g., @Freitag.2021].
-Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b].
-It is necessary to successfully restore grasslands since this habitat type provide several ecosystem services and a high biodiversity while it is worldwide endangered [@Dengler.2014; @Bardgett.2021] even by restoration through unsuited afforestation [@dudley2020].
+Grasslands provide several ecosystem services and a high biodiversity [@Dengler.2014; @Bardgett.2021].
+However, they are globally endangered [@Bardgett.2021]even by restoration through unsuited afforestation [@dudley2020].
 In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
-
+Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] and sowing is a long established restoration approach for species-rich grasslands [@Kiehl.2010].
 Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts [@Freitag.2021].
 Though, there are still open questions about specifying the seed mixtures to specific site conditions or even more to future climate conditions to improve efficiency and effectiveness of restoration efforts [@Torok.2021].
-For this reason, restoration ecology has to increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015].
-Rigorous, repeatable, and transparent experiments linked to a hypothesis derived from theory are needed to guide evidence-based restoration [@Cooke.2018; @Wainwright.2018].
+
+Restoration ecology can increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments linked to a hypothesis derived from theory, which will finally lead to evidence-based restoration [@Cooke.2018; @Wainwright.2018].
 Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Sowing in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on environmental and the biotic filtering which are the main assembly processes to be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
+Sowing in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on habitat and biotic filtering which are the main assembly processes which can be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
 This means a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
 The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion of unsuited species.
-Modifying seed mixtures for certain site conditions came up with functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020] but it is not easy to put it into practice for novel ecosystems like urban grasslands [@Bauer.2022].
-Substrates cannot only be modified for conservation purposes in urban areas, but also in quarries [@chenot-lescure2022] or dikes [@Liebrand.1996].
+Modifying seed mixtures for certain site conditions emerged with the rise of functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020] but it is not easy to put it into practice [@merchant2022].
+Substrates are artificial soil mixtures and are used in urban areas [@Bauer.2022], quarries [@chenot-lescure2022], or dikes [@Liebrand.1996].
 
-Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
-Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@berendse2015].
-Dikes can reconcile several requirements [@teixeira2022], but the seed mixture-substrate combination must be adapted.
+Dikes are promising sites for the restoration of species-rich grasslands, because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
+Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a vegetation cover to ensure dike stability [@berendse2015].
+Dikes can reconcile several requirements [@teixeira2022], which can be fostered by an adapted seed mixture-substrate combination.
 
-The aim of this study is to identify the ideal combination of substrates and seed mixtures for north and south exposed slopes in Central Europe to develop a vital and species-rich vegetation cover.
-We set up an experiment and tested agricultural soil with different amounts of sand admixture and different installation depths, as well as different seed mixture types and different seed densities.
-We expected a better development of dry grassland on the south exposition with sandy substrate and hay meadows on north exposition with less sandy substrate.
-Since seeds are expensive, practitioners like to know if the slopes need a higher seed density [cf.
-@KleberLerchbaumer.2017].
+The aim of this study is to identify the ideal combination of seed mixtures and substrates for north and south exposed slopes in Central Europe, which develops a vital and species-rich vegetation cover.
+We set up an experiment and tested agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
+We expected a better development of dry grassland on the south exposition with shallow sandy substrates and hay meadows on the north exposition and less sandy, deep substrates.
+Furthermore, higher seed densities are recommended for slopes [@KleberLerchbaumer.2017], but the benefit has not been proven, yet.
 
@@
 First, we observed the persistence of the sown species, which is a key interest of sowing as a restoration approach [@Wilsey.2021].
-For this, it was surveyed if the sown species are present in the respective plot in following years.
+For this purpose, the sown species of a specific plot were surveyed, if they are present in that plot in the following years.
 Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
@@
 Third, the successional distance to the reference was determined.
-This measure quantifies the distance of a plot to the average reference site from an ordination [@Rydgren.2019].
-To complement the indices, the success of restoration or the difference from desired conditions needs to be evaluated [@Brudvig.2017b].
-Therefore, the species composition of the experimental plots were compared with reference sites.
-We asked following question to evaluate the restoration approaches and success after four years:
+This measure quantifies the distance of a plot to the average reference site derived from an ordination [@Rydgren.2019].
+To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf.
+@Brudvig.2017b].
+This was reached by comparing the species composition of the experimental plots with reference sites.
+We asked following question to evaluate the restoration approaches and the success after four years:
 

### 2023-02-17 manuscript.Rmd
Update manuscript.Rmd

@@
   )
+ft <- officer::fp_text(shading.color = "yellow")
+
+word_spec <- function(x, prop = ft) ftext(text = toString(x) ,prop =  ft)
 ```
@@
 On the north exposition, hay meadow-seed mixtures developed closer to its reference than dry grasslands.
-Overall, the vegetation developed in the desired direction but a recovery debt remained after four years.
+Overall, the vegetation developed in the desired direction, but a recovery debt remained after four years.
 Plots still exhibited similarities to negative references from ruderal vegetation.
@@
 
+levee
+
 persistence
@@
 Grasslands provide several ecosystem services and a high biodiversity [@Dengler.2014; @Bardgett.2021].
-However, they are globally endangered [@Bardgett.2021]even by restoration through unsuited afforestation [@dudley2020].
+However, they are globally endangered [@Bardgett.2021] even by restoration through unsuited afforestation [@dudley2020].
 In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
-Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] and sowing is a long established restoration approach for species-rich grasslands [@Kiehl.2010].
+Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] and sowing is a long-established restoration approach for species-rich grasslands [@Kiehl.2010].
 Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts [@Freitag.2021].
@@
 
-Dikes are promising sites for the restoration of species-rich grasslands, because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
+Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
 Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a vegetation cover to ensure dike stability [@berendse2015].
@@
 
-The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412).
+The seed mixture-substrate combinations were tested with an experiment on a dike of the River Danube in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
 The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
 During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix A1, @lfu2021waterlevel; @lfu2021discharge].
-Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen.
-The substrates were mixed with a big roller and an excavator prepared the plots.
-The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B).
+For the substrates, sand (0--4 mm) and agricultural soil were used and the soil was from a dike construction site nearby (Steinkirchen).
+A big roller mixed both components and an excavator put the substrates in the prepared plots.
+
+The target vegetation were lowland hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020; Arrhenatherion elatioris, Cirsio-Brachypodion pinnati; EuroVegChecklist: CM01A, DA01B, @mucina2016].
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
 The seeds were received from a commercial producer of autochthonous seeds.
-From the species pools, 20 species were randomly selected for each plot (Appendix A2).
+From these species pools, 20 species were randomly selected for each plot (Appendix A2).
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
 The community-weighted means (CWM) of functional traits differed between the seed mixture types (Figure \@ref(fig:traits)).
-As expected, the hay meadows mixtures have a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry meadows mixtures.
-The south exposed plots were sown in mid-April 2018 and the north exposition two weeks later.
+As expected, the hay-meadow mixtures had a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry-meadow mixtures.
+The south exposed plots were sown in mid-April 2018 and the north exposition 14 days later.
 Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks.
-
-The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020.
+The management started with a cut without hay removal and a mowing height of 20 cm in August of the same year (2018), followed by standard deep cuts with hay removal in July 2019 and 2020.
 In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
 
-We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition, halfway up the slopes of the dike and arranged in six blocks (= replicates).
-The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:map)).
-The split plot was caused by testing all 24 treatments on both sides of the dike.
-We tested three sand admixtures (0%, 25% and 50%) and tow soil depths (15 vs.
-30 cm) of practical interest [@KleberLerchbaumer.2017] and two .
-Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed.
-We tested soil samples of the three substrates on both expositions by mixing several sub-samples.
-The sand admixture changed the soil texture, increased the C/N ratio, but reduced Calciumcarbonat, and hardly changed the rather high pH values (Table \@ref(tab:substrate)).
+We used 288 plots of the size 2.0 m × 2.0 m which were halfway up the slopes of the dike, distributed over the north and south exposition, and arranged in six blocks (= replicates).
+The experiment used a split-plot design combined with a randomized complete block design (Figure \@ref(fig:map)).
+The split plot was created by the two expositions of the dike, where all 24 treatment combinations were tested: sand admixtures (0%, 25% and 50%), soil depths (15 vs.
+30 cm) of practical interest [@KleberLerchbaumer.2017], and the two seed mixture types with the normal seed density and an increased density recommended for slopes [4 vs.
+8 g m^-2^ @Kiehl.2010; @KleberLerchbaumer.2017].
+
+Under the substrate, a 5 cm thick drainage layer of gravel (0-16 mm) was installed.
+Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots.
+The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly changed the quite high pH values (Table \@ref(tab:substrate)).
 Phosphate and potassium were rather scarce for agricultural soils and Magnesium rather high [@lfl2022].
-The two seed mixture types were tested with the normal seeding density and the increased density recommended for slopes [4 vs.
-8 g m^-2^ @Kiehl.2010; @KleberLerchbaumer.2017].
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
-Establishment rates of species (Appendix A3).
+The establishment rates of species are recorded in Appendix A3.
+`r word_spec("(Add mean values, range, how many of species pool established, etc.)")` <!--# add more infos -->
 
@@
 
-Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys in the surroundings on Danube dikes [@bauer2023].
-We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
-The functional traits of specific leaf area (SLA; available traits: 99.2% of all species), seed mass (98.8%) and canopy height (99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
+Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on Danube dikes in the surroundings [@bauer2023].
+We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included also lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
+The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 For the computation, we used 4 chains, a thinning rate of 2, 5000 iterations for warm-up and 10,000 in total.
-For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values and MCMC chain resolution by the effective sampling size (ESS).
-Posterior predictive check was done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].
+For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
+Posterior predictive checks were done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].
 Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
+A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
+Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
 
-A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time.
-Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress 0.21).
-
-Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible a scroll-down document on GitHub [!cite Zenodo!]<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
-All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, 'metaMDS' from 'vegan' for the ordination [@vegan] and 'dbFD' from 'FD' for the calculation of community-weighted means of functional traits [@FD].
+Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible scroll-down document on GitHub `r word_spec("(include Zenodo reference)")`.<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
 
@@
 
-We could identify a statistically clear positive effect of sand addition on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
-Furthermore, sown hay meadows were clearly closer to their reference plots than sown dry grasslands were to their references.
-The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:persistence); \@ref(fig:fcs); \@ref(fig:recovery)) .
+## Weak effects of restoration treatments
+
+We could identify a statistically clear positive effect of sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
+The posterior distributions are also shown in the interaction plots which separate exposition and survey year indicate.
+For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
 Both expositions have similar trends but for all responses the values are clearly lower on the south exposition, e.g., persistence values are on average more than 46% higher on the north exposition (Figure \@ref(fig:persistence)).
-The effect of restoration treatments is in the interaction plots not clear.
-Hay meadow-seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:recovery)).
-Though, the sand admixture had no clear effect on the development.
+In the interaction plots, the effects of restoration treatments are neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
 Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
 
+## Hay meadows on north exposition closer to reference
+
 The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
-The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands.
-In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:recovery)) but the right direction of the development.
-One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed mixture compositions.
-The ordination presents the experimental plots not only in context with seed mixtures, but also with reference sites.
+The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands and ascertain the right direction of the vegetation development.
+One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed-mixture compositions.
+
+The ordination presents the experimental plots also in context with reference sites.
 The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap.
-The positions of reference sites are shifted to the left on the NMDS1 axis which means in the direction of early successional states.
-On the south exposition, we had negative reference sites which are located in the NMDS in between the positive reference sites and the recent state of restored plots.
-However, most of negative reference sites (ruderal, dry and anthropogenic vegetation) are situated in the upper half and explicitly recent restoration sites on the south exposition are close to them.
+The positions of reference sites are shifted to the left in comparison to the seed mixtures which means in the direction of early successional states.
+Though, they are still different from the negative references of ruderal, dry, anthropogenic vegetation.
+Negative references were only available on the south exposition and they are located in the NMDS between the positive reference sites and the state of restored plots in 2021.
+Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this is especially the case on the north exposition (Figure \@ref(fig:nmds)).
 
@@
 Larger differences of soil depth might be necessary to create negative effects by greater soil depths as was shown for prairies [@dornbush2010].
-Neither, seeding density had an effect on persistence and FCS which fits to result of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary but higher densities do not further improve establishment of target species but have rather a slight negative effect.
+Neither, seed density had an effect on persistence and FCS which fits to result of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary but higher densities do not further improve establishment of target species but have rather a slight negative effect.
 
@@
 Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-Though, these two studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after five and about 15 years, respectively.
+However, these two studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after five and about 15 years, respectively.
 Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the sown species could establish earlier than others and preempted the available niches [@Fukami.2015].
@@
 The question remains if money is best invested in sand admixture or in other restoration measures.
-It seems not to be necessary to increase seeding density on dike slopes, which would reduce restoration costs.
+It seems not to be necessary to increase seed density on dike slopes, which would reduce restoration costs.
 As well as the use of more deeper soil depth which would otherwise create costs for removal of topsoil.
@@
 
-```{r tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
-In total, seed mixtures had 16 or 32 g per plot.
-All individual seed mixtures are stored in Table A3."}
+In total, plots received 16 or 32 g of seeds.
+All individual seed mixtures are stored in Appendix A3."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
   add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
-  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
+  add_header_row(top = FALSE, values = c("", "#", "#", "#", "wt%", "wt%")) %>%
   bold(part = "header", i = 1) %>%
@@
 
-## Table 2 {.unnumbered}
+## Table 2<!--# Check quotation --> {.unnumbered}
 
-```{r tab.id = "substrate", ft.align = "left", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction.
+```{r tab.id = "substrate", ft.align = "left", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2 mm.
 Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
@@
 The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023].
-Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture types H and D).
+Four treatments were conducted (Sand admixture, substrate depth, seed density, seed mixture types H and D).
 The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates.

### 2023-02-17 manuscript.Rmd
Update manuscript.Rmd

@@
 
-```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
 In total, plots received 16 or 32 g of seeds.
-All individual seed mixtures are stored in Appendix A3."}
+All individual seed mixtures are stored in Appendix A3.
+
+```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Seedmix"}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
 
-## Table 2<!--# Check quotation --> {.unnumbered}
+## Table 2 {.unnumbered}
 
-```{r tab.id = "substrate", ft.align = "left", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2 mm.
+Soil samples of the three substrates were analyzed for the fraction \< 2 mm.
 Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
-The pH was measured in CaCl2 solution.
-Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract.
-For calculating CaCO3, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33.
-To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C.
-Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand."}
+The pH was measured in CaCl~2~ solution.
+Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract.
+For calculating CaCO~3~, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33.
+To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C.
+Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.
+
+```{r tab.id = "substrate", ft.align = "left", tab.cap = "Substrate"}
 read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
@@
 
-```{r fig.id = "map", fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.
-The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023].
-Four treatments were conducted (Sand admixture, substrate depth, seed density, seed mixture types H and D).
-The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates.
-The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer)."}
+```{r fig.id = "map", fig.asp = 1.2854, fig.width = 5, fig.cap = "Map"}
 knitr::include_graphics(
@@
 ```
+
+The experiment was located on a dike at river Danube in SE Germany.
+The 288 plots were allocated in six blocks (white squares on upper photo) and on the north and south exposition (central photo) [both aerial photos: @bayerischevermessungsverwaltung2023].
+Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D.
+The western half of a block was with a shallow substrate depth and within this half the substrates had different sand admixtures.
+The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer).
 
@@
 
-```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The community-weighted means (CWM) of the seed mixtures used for the field experiment of the functional traits specific leaf area (SLA), seed mass and canopy height.
-The CWMs were weighted by seed weight in the seed mixture and  indicate differences between the target types hay meadows and dry grasslands .
-"}
+```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The community-weighted means (CWM) of the seed mixtures used for the field experiment: specific leaf area (SLA), seed mass and canopy height.
+The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target types hay meadows and dry calcareous grasslands."}
 knitr::include_graphics(
@@
 ```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
-Furthermore, the median and the 66% and 95% credible intervals are shown.
-We evaluated the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
+Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
 The FCS is the ratio of target species and non-target species.
 Note that the zero lines indicate that both levels have equal values.
-This means that hay meadows are closer to their reference than dry grasslands  (C)."}
+This means for instance that hay meadows are closer to their reference than dry grasslands  (C)."}
 knitr::include_graphics(
@@
 
-```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on a dike experiment over the years.
-The substrates had different sand admixtures and different seed mixture types were sown.
-Per plot were 20 species sown.
-Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
+```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on the dike experiment.
+The plots had substrates with different sand admixtures and were sown with different seed mixture types.
+Per plot 20 species were sown.
+Shown are the medians and 95 % credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 ```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of a dike experiment.
-The substrates had different sand admixtures and different seed mixture types were sown.
+The plots had substrates with different sand admixtures and were sown with different seed mixture types.
 The zero line indicate that target and non-target species are balanced.
 Positive values indicate that there are more target species.
-Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95 % credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 
-```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (*d~jt,0~*) of plots of an experiment on a dike to its respective reference sites (hay meadows or dry grasslands).
-The substrates had different sand admixtures and different seed mixture types were sown.
-The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (Figure 7).
+```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of experimental plots to its respective reference sites (hay meadows or dry calcareous grasslands).
+The plots had substrates with different sand admixtures and were sown with different seed mixture types.
+The zero lines indicate the mean position of the reference sites for each habitat type on the NMDS axis 1 (Figure 7).
 The grey area marks the standard deviation of the position of the reference sites.
-Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95 % credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(

### 2023-02-18 manuscript.Rmd
Update manuscript.Rmd

@@
 The establishment rates of species are recorded in Appendix A3.
-`r word_spec("(Add mean values, range, how many of species pool established, etc.)")` <!--# add more infos -->
+In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands) established by 2021.
+The species established 31 ± 22% of their sown plot.
 
@@
 Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this is especially the case on the north exposition (Figure \@ref(fig:nmds)).
-
-\clearpage
-
-\newpage
+\clearpage \newpage
 
@@
 
-The vegetation of the dike experiment developed in the right direction, but with reduced velocity and significantly and lasting worse development of the south exposition.
-Sand admixture of 25% was sufficient to reach a positive effect.
+The vegetation of the dike experiment developed in the desired direction, but with a descelerating recovery rate.
+On the south exposition, a significant worse effect during establishment phase remained over the complete observation period.
 All in all, it was hardly possible to identify an ideal seed mixture-substrate combination.
@@
 
-As expected, sand admixture led to higher persistence of sown species but only on the north exposition and the effect size of about 6% in the fourth year after restoration is rather small.
-In addition, 50% admixture did not further improve the result.
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but can lead to positive results, if mixed with mineral material as sand and gravel [@chenot-lescure2022].
+As expected, sand admixture reduced nutrient loads and led to higher persistence of sown species but 50% admixture did not further increase the effect.
+In addition, the effect only appeared on the north exposition and the effect size of about 6% in the fourth year after restoration is rather small.
 Substrate depth did not significantly affect persistence or Favorable Conservation Status (FCS) similarly to earlier studies [@baer2004].
-Larger differences of soil depth might be necessary to create negative effects by greater soil depths as was shown for prairies [@dornbush2010].
-Neither, seed density had an effect on persistence and FCS which fits to result of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary but higher densities do not further improve establishment of target species but have rather a slight negative effect.
+Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as it was shown for prairies [@dornbush2010].
+Neither, seed density had an effect on persistence and FCS which fits to results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.
 
-The vegetation on the south exposition performed consistently and significantly worse than the north exposition and had a different species composition which was also shown by @Batori.2016 in Hungary.
+The vegetation on the south exposition had a different species composition than the north exposition which was also shown by @Batori.2016 in Hungary.
 Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the south exposition, was removed after two weeks because of the death of several protected lizards.
-This led to the drying of many seedlings why the distinction of the seed mixture types might be leveled on the south exposition.
-Moreover, the intense drought of 2018 and 2019 [@hari2020] might have decreased germination and establishment of sown species because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
-The interesting point here is the lasting negative effect which suggests a legacy effect by unfavorable weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
-The problems during the establishment phase might have led to an alternative trajectory and could probably only be met by resowing.
+This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020].
+This drought could have decreased germination and establishment of sown species also in general because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
+The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
+The problems during the establishment phase might have led to an alternative trajectory `r word_spec("(reference?)")`<!--# Add ref--> and could probably only be met by resowing.
+The drying of seedlings might also have leveled the distinction of the seed mixture types on the south exposition.
 
@@
 
-Our aim was to identify a ideal seed mixture-substrate combination in respect of restoration effectiveness and biodiversity.
-For evaluating effectiveness, we measured the establishment and persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
+Our aim was to identify an ideal seed mixture-substrate combination in respect of restoration effectiveness and biodiversity.
+For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
 Though, we could not identify an interaction effect for neither of the indices.
@@
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions [Figure @ref(fig:traits); @Oberdorfer.1993; @Oberdorfer.1993b].
-Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-However, these two studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after five and about 15 years, respectively.
-Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the sown species could establish earlier than others and preempted the available niches [@Fukami.2015].
+Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions (Figure \@ref(fig:traits)) [@Oberdorfer.1993; @Oberdorfer.1993b].<!--# Check fig ref--> Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
+However, these studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
+Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and preempted the available niches for the species of related habitat types [@Fukami.2015].
 
@@
 
-The seed mixtures and positive references were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the NMDS suggests that the seed mixture represent a latter successional stage than the positive references.
-The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure @ref(fig:recovery)).
+The seed mixtures and positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
+The position on the NMDS suggests that the seed mixture represent a latter successional stage than the references.
+The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)).
 This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
@@
 
-The vegetation developed in general in the right direction but was still distinct from positive references and seed mixtures after four years.
-It was rather similar to the negative reference of perennial ruderal vegetation.
+The vegetation developed in general in the desired direction but was still distinct from positive references and seed mixtures after four years.
+On the south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
 The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
@@
 Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows on the north exposition and not on the south exposition of dikes.
-Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, although the effect is small.
-The question remains if money is best invested in sand admixture or in other restoration measures.
-It seems not to be necessary to increase seed density on dike slopes, which would reduce restoration costs.
-As well as the use of more deeper soil depth which would otherwise create costs for removal of topsoil.
-There was no perfect seed mixture-substrate combination, why we conclude that a variation of seed mixtures types and different soils along restoration sections would promote biodiversity better than a single solution [@bauer2023; @Holl.2022].
+Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, even if the effect is small.
+The question which remains is, if sand admixture is the most economical restoration measure to promote diversity on dikes.
+Seed density seems not to be necessary to be increased on dike slopes and soil depths of 30cm are not adverse compared to 15 cm thick substrates.
+There was no perfect seed mixture-substrate combination, why we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single solution [@bauer2023; @Holl.2022].
 The strong and lasting negative effect of drought on the south exposition might require a resowing.
-To close the recovery debt, the adaption of the management might be promising since it is a relevant factor aside of restoration approach and site characteristics [@Grman.2013; @tölgyesi2021].
-For example, starting sheep grazing on the restored sites will modify the disturbance regime and improve dispersal.
+To close the recovery debt, the adaption of the management might be promising since it is a crucial factor aside of the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
+For example, starting the already existing sheep grazing on the experimental sites will modify the disturbance regime and improve dispersal.
 All in all, our results support the finding that dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
-Though, the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
+Though, the stubborn recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
 
@@
 We would like to thank our project partners Dr.
-Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) and Klaus Rachl and Stefan Radlmair (Regierung von Niederbayern) for numerous discussions on restoration and management of dike grasslands.
+Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Klaus Rachl and Stefan Radlmair (Lower Bavaria Government) for numerous discussions on restoration and management of dike grasslands.
 Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
@@
 80 002 312).
-
-\clearpage
-
-\newpage
+\clearpage \newpage
 
@@
 
-Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
 In total, plots received 16 or 32 g of seeds.
-All individual seed mixtures are stored in Appendix A3.
-
-```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Seedmix"}
+All individual seed mixtures are stored in Appendix A3."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
 Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
-The pH was measured in CaCl~2~ solution.
-Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract.
-For calculating CaCO~3~, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33.
+The pH was measured in CaCl2 solution.
+Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract.
+For calculating CaCO3, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33.
 To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C.
@@
 
-```{r tab.id = "substrate", ft.align = "left", tab.cap = "Substrate"}
+```{r tab.id = "substrate", ft.align = "left", tab.cap = "Substrates"}
 read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
@@
 
-```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
-In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
-The circles show the standard error of the groups.
-2D stress: 0.21."}
+```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS"}
 knitr::include_graphics(
@@
 ```
+
+NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).<!--# How many observed species --> In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
+The circles show the standard error of the groups.
+2D stress: 0.21.
 

### 2023-02-21 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 
-## Appendix A1 {.unnumbered}
+# Appendix A1
 
 Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge].
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911) @cdc2022temp, @cdc2022prec] <!--# Check brackets -->and stream gauge Pfelling [ID: 10078000, WGS84, lat/lon, 48.87975, 12.74716, @lfu2021discharge].
 HQ2 = Highest discharge with a probability of occurrence every second year.
@@
 
-## Appendix A2 {.unnumbered}
+# Appendix A2
 
-Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->
+All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.
 
-## Appendix A3 {.unnumbered}
+# Appendix A3
 
@@
 
+# Appendix A4
+
+All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 = 4 years times 288 experimental plots).
+In total, 274 different species were found.
+The shades of grey indicate the amount of established plots.
+
+```{r tab.id = "specieslist", tab.cap = ""}
+read_csv(
+  here("outputs", "tables", "table_a4_specieslist.csv"),
+  col_names = TRUE,
+  na = c("na", "NA"),
+  col_types = cols(.default = "?", name = "f")
+  ) %>%
+  mutate(name = str_replace_all(name, "_", " ")) %>%
+  rename(Name = name, "Presence [# plots]" = sum) %>%
+  flextable() %>%
+  align(part = "all", align = "center", j = -1) %>%
+  bold(part = "header") %>%
+  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
+  bg(j = 2, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
+  autofit()
+```
+
 # References {.unnumbered}

### 2023-02-22 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 \* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de), ORCiD <https://orcid.org/0000-0001-5372-4174>
+
+<!--# Replace "Dike experiment" in the title -->
 
@@
 Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911) @cdc2022temp, @cdc2022prec] <!--# Check brackets -->and stream gauge Pfelling [ID: 10078000, WGS84, lat/lon, 48.87975, 12.74716, @lfu2021discharge].
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010, ID: 3271, WGS84: lat/lon, 48.85476, 12.918911, @cdc2022temp; @cdc2022prec] and stream gauge Pfelling [ID: 10078000, WGS84: lat/lon, 48.87975, 12.74716, @lfu2021discharge].
 HQ2 = Highest discharge with a probability of occurrence every second year.
@@
 # Appendix A3
+
+The community-weighted means (CWM) of the seed mixtures used for the field experiment: specific leaf area (SLA), seed mass and canopy height.
+The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target types hay meadows and dry calcareous grasslands.
+The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
+
+```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_a3_800dpi_16.5x5cm_traits.tiff")
+  )
+```
+
+### Acknowledgment
+
+This figure has been supported by the TRY initiative on plant traits (<http://www.try-db.org>).
+The TRY initiative and database is hosted, developed and maintained by J.
+Kattge and G.
+Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany).
+TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
+
+\clearpage
+
+\newpage
+
+# Appendix A4
 
@@
 
-# Appendix A4
+\clearpage
+
+\newpage
+
+# Appendix A5
 

### 2023-02-22 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Can dike grassland restoration profit from ideal seed mixture-substrate combinations?"
+title: "Fit by design: Developing substrate-specific seed mixtures for functional dike restoration"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 1.
-Sowing is a well-established restoration technique to overcome dispersal limitation.
-Though, adapted seed mixtures to certain site conditions promise a more effective restoration.
-This is especially important if the restored vegetation has to protect constructions like dikes.
-An ideal seed mixture-substrate combination would concurrently improve the ecosystem function erosion protection and enhance species-rich grasslands by a fast and successful establishment of target species.
+Sowing is a well-established restoration technique to overcome dispersal limitation and site-specific seed mixtures are most effective to achieve functional communities.
+This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes.
+Here, an improved seed--substrate combination would secure slope stability, reduce mowing efforts, and generate biodiverse grasslands.
 2.
-An experiment with 288 plots was conducted on both expositions of a dike and was surveyed 2018--2021.
-We tested different sand admixtures, substrate depths, seed densities and seed mixture types (hay meadows, dry calcareous grasslands), and measured the persistence of sown species, the Favorable Conservation Status (FCS) and the successional distance to reference sites as calculated from an ordination.
-3.  Sand admixture had a significant but slightly positive effect on all indices. Substrate depth, seed density and seed mixture type had no significant effect on persistence or FCS.
+A factorial field experiment addressed this topic on a dike at river Danube in S Germany in the period 2018--2021.
+On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favorable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
+3.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
 4.
-On the north exposition, hay meadow-seed mixtures developed closer to its reference than dry grasslands.
-Overall, the vegetation developed in the desired direction, but a recovery debt remained after four years.
-Plots still exhibited similarities to negative references from ruderal vegetation.
+Overall, the sown vegetation developed in the desired direction, but a recovery debt remained after four years, and some plots still showed similarities to negative references from ruderal sites.
+In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry grasslands.
 5.
-The south exposition was significantly worse than the north exposition which might be due to the severe drought during establishment and the addition and removal of a geotextile.
-This initial negative effect remained over the whole observation period.
+In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment and the addition and removal of a geotextile.
+This initial negative effect remained over the entire observation period.
 6.
-Synthesis and applications: Adapted seed mixtures can make restorations more efficient like applying hay meadows on the north exposition.
-However, varying seed mixture-substrate combinations might foster biodiversity like beta diversity more than a desired 'ideal' combination.
-Furthermore, additional efforts in management might be necessary to reduce the recovery debt and resowing after a severe drought might be sensible due to strong legacy effects.
+Synthesis and applications: Site-adapted seed mixtures make restoration more efficient.
+However, applying several seed--substrate combinations might foster beta diversity.
+Furthermore, additional efforts in management might be necessary to reduce the recovery debt and re-sowing after unfavorable conditions is recommended.
 
@@
 dry grasslands
+
+ecological restoration
 
@@
 
-Grasslands provide several ecosystem services and a high biodiversity [@Dengler.2014; @Bardgett.2021].
-However, they are globally endangered [@Bardgett.2021] even by restoration through unsuited afforestation [@dudley2020].
-In Europe, calcareous grasslands and hay meadows are on the red list [Category 3, vulnerable, @Janssen.2016].
-Restoration is seen as a key factor to sustain ecosystem services and biodiversity [@COP.2014; @UnitedNations.2019b] and sowing is a long-established restoration approach for species-rich grasslands [@Kiehl.2010].
-Sowing high-diversity seed mixtures of local provenance produced by commercial but specialized seed companies is a promising way to scale up restoration efforts [@Freitag.2021].
-Though, there are still open questions about specifying the seed mixtures to specific site conditions or even more to future climate conditions to improve efficiency and effectiveness of restoration efforts [@Torok.2021].
+Grasslands can support a very high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021].
+However, they are globally endangered [@Bardgett.2021] for example by misguided afforestation [@dudley2020], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016].
+Restoration is seen as a key factor to sustain biodiversity and ecosystem services [@COP.2014; @UnitedNations.2019b], and sowing is a well-established approach to establish species-rich grasslands [@Kiehl.2010].
+Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome the dispersal filters [@myers2009; @orrock2023].
+However, there are still open questions about adjusting the seed mixtures to specific site conditions and future climate conditions [@Torok.2021].
 
-Restoration ecology can increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments linked to a hypothesis derived from theory, which will finally lead to evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration approach are key predictors of the development of vegetation after sowing [@Brudvig.2017b].
-Sowing in general is a way to overcome the dispersal filter [@myers2009; @orrock2023], but we focus on habitat and biotic filtering which are the main assembly processes which can be manipulated by the choice of the right seed mixture-substrate combination [@Torok.2017].
-This means a mutually adaption of the substrate to the preferences of the target vegetation, and the seed mixtures to the characteristics of the chosen substrate.
-The right substrates should reduce habitat filtering and the right seed mixture should minimize competitive exclusion of unsuited species.
-Modifying seed mixtures for certain site conditions emerged with the rise of functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020] but it is not easy to put it into practice [@merchant2022].
-Substrates are artificial soil mixtures and are used in urban areas [@Bauer.2022], quarries [@chenot-lescure2022], or dikes [@Liebrand.1996].
+Restoration ecology can increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally lead to evidence-based restoration [@Cooke.2018; @Wainwright.2018].
+Local site conditions and the restoration method are key predictors of the development of vegetation after sowing [@Brudvig.2017b] and habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of the seed--substrate combination [@Torok.2017].
+This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
+Suitable substrates should reduce habitat filtering, while the seed mixture should minimize competitive exclusion of unsuitable species.
+Modifying seed mixtures to match specific site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
+This challenge is particularly interesting on artificial substrates that are used in urban areas [@Bauer.2022], quarries [@chenot-lescure2022], or on dikes [@Liebrand.1996].
 
-Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020].
-Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a vegetation cover to ensure dike stability [@berendse2015].
-Dikes can reconcile several requirements [@teixeira2022], which can be fostered by an adapted seed mixture-substrate combination.
+Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
+Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterize dikes [@Batori.2016; @berendse2015].
+Dikes can reconcile several requirements [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
 
-The aim of this study is to identify the ideal combination of seed mixtures and substrates for north and south exposed slopes in Central Europe, which develops a vital and species-rich vegetation cover.
-We set up an experiment and tested agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
-We expected a better development of dry grassland on the south exposition with shallow sandy substrates and hay meadows on the north exposition and less sandy, deep substrates.
-Furthermore, higher seed densities are recommended for slopes [@KleberLerchbaumer.2017], but the benefit has not been proven, yet.
+The aim of this study is to identify the best combination of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
+An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
+We expected a better development of calcareous grassland in south exposition with shallow sandy substrates, and mesic hay meadows in north exposition on less sandy deep substrate.
+Furthermore, higher seed densities were recommended for slopes [@KleberLerchbaumer.2017], albeit without experimental evidence.
 
 To measure the success of restoration, we chose four indices.
-First, we observed the persistence of the sown species, which is a key interest of sowing as a restoration approach [@Wilsey.2021].
-For this purpose, the sown species of a specific plot were surveyed, if they are present in that plot in the following years.
+First, we observed the persistence of the sown species, which is a key objective of this restoration measure [@Wilsey.2021].
+For this purpose, presence of the sown species was monitored for three consecutive years.
 Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
 Characteristic diversity is created by established species which belong to the habitat-specific species pool.
-In other words, these species are target species for a habitat type of interest.
-Third, the successional distance to the reference was determined.
-This measure quantifies the distance of a plot to the average reference site derived from an ordination [@Rydgren.2019].
+In other words, these species are associated with the habitat type of interest.
+Third, the successional distance to the reference grasslands was determined.
+This measure quantifies the ordination distance of a plot to the average reference site [@Rydgren.2019].
 To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf.
@@
 This was reached by comparing the species composition of the experimental plots with reference sites.
-We asked following question to evaluate the restoration approaches and the success after four years:
+We asked the following question to evaluate the restoration approaches and the success after four years:
 
-1.  How strong differs the persistence of the sown species among the seed mixture-substrate combinations?
+1.  How strong differs the persistence of the sown species among the seed--substrate combinations?
 
-2.  How strong differs the Favorable Conservation Status (FCS) among the seed mixture-substrate combinations?
+2.  How strong differs the Favorable Conservation Status (FCS) among the seed--substrate combinations?
 
@@
 
-The seed mixture-substrate combinations were tested with an experiment on a dike of the River Danube in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
-The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
+The combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at river Danube in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
+The climate was temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
 During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix A1, @lfu2021waterlevel; @lfu2021discharge].
-For the substrates, sand (0--4 mm) and agricultural soil were used and the soil was from a dike construction site nearby (Steinkirchen).
+The substrates consisted of sand (0--4 mm) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
 A big roller mixed both components and an excavator put the substrates in the prepared plots.
 
-The target vegetation were lowland hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020; Arrhenatherion elatioris, Cirsio-Brachypodion pinnati; EuroVegChecklist: CM01A, DA01B, @mucina2016].
+The target vegetation were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
-The seeds were received from a commercial producer of autochthonous seeds.
+The seeds were received from a commercial producer of autochthonous seeds (Co.
+Krimmer, Pulling).
 From these species pools, 20 species were randomly selected for each plot (Appendix A2).
 The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Figure \@ref(fig:traits)).
-As expected, the hay-meadow mixtures had a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry-meadow mixtures.
-The south exposed plots were sown in mid-April 2018 and the north exposition 14 days later.
-Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks.
-The management started with a cut without hay removal and a mowing height of 20 cm in August of the same year (2018), followed by standard deep cuts with hay removal in July 2019 and 2020.
+The community-weighted means (CWM) of functional traits differed between the seed mixture types (Appendix A3).
+As expected, the hay-meadow mixtures had a higher specific leaf area (SLA), lower seed mass, and higher canopy height than the dry-grassland mixtures.
+The south-exposed plots were sown in mid-April 2018 and the north exposition 14 days later.
+Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects like the death of several protected lizards.
+The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
 In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
@@
 The experiment used a split-plot design combined with a randomized complete block design (Figure \@ref(fig:map)).
-The split plot was created by the two expositions of the dike, where all 24 treatment combinations were tested: sand admixtures (0%, 25% and 50%), soil depths (15 vs.
-30 cm) of practical interest [@KleberLerchbaumer.2017], and the two seed mixture types with the normal seed density and an increased density recommended for slopes [4 vs.
-8 g m^-2^ @Kiehl.2010; @KleberLerchbaumer.2017].
+The split plot was created by the two expositions of the dike, where all 24 treatment combinations were tested, i.e., sand admixtures (0, 25, and 50%), soil depths (15 vs.
+30 cm), and the two seed mixture types with the normal seed density and an increased density recommended for slopes [4 vs.
+8 g m^-2^, @Kiehl.2010; @KleberLerchbaumer.2017].
 
@@
 The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly changed the quite high pH values (Table \@ref(tab:substrate)).
-Phosphate and potassium were rather scarce for agricultural soils and Magnesium rather high [@lfl2022].
+Phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022].
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
-The establishment rates of species are recorded in Appendix A3.
+The establishment rates of species are recorded in Appendix A4.
 In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands) established by 2021.
 The species established 31 ± 22% of their sown plot.
-
-## External data
+In total, 274 species were detected (Appendix A5).
 
@@
 We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included also lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
-The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed-effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
-Furthermore, we included as a fixed effect the botanists of each plot.
+Furthermore, we included as a fixed effect the botanists recording a certain plot.
 For the simple effects of the treatments, we chose plausible weakly informative priors.
 To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
-For the computation, we used 4 chains, a thinning rate of 2, 5000 iterations for warm-up and 10,000 in total.
+For the computation, we used four chains, a thinning rate of two, 5,000 iterations for warm-up, and 10,000 in total.
 For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
@@
 Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
+In total, 343 species were included in the ordination.
 
-Data, code and the whole model specification and evaluation is stored on Zenodo and in an easily accessible scroll-down document on GitHub `r word_spec("(include Zenodo reference)")`.<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+Data, code and the entire model specifications and evaluations are stored on GitHub and presented in an easily accessible document for scrolling through `r word_spec("(include Zenodo reference)")`.<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
 All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
@@
 We could identify a statistically clear positive effect of sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
-The posterior distributions are also shown in the interaction plots which separate exposition and survey year indicate.
-For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
-Both expositions have similar trends but for all responses the values are clearly lower on the south exposition, e.g., persistence values are on average more than 46% higher on the north exposition (Figure \@ref(fig:persistence)).
-In the interaction plots, the effects of restoration treatments are neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
-Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
+The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
+For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years.
+Both expositions had similar trends but for all responses the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:persistence)).
+For the interactions, the effects of restoration treatments were neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
+Persistence of both seed mixture types was slightly positively affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
 
@@
 The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
-The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands and ascertain the right direction of the vegetation development.
-One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed-mixture compositions.
+The NMDS confirmed that the seed mixtures were variable, but distinctive for hay meadows and dry grasslands and ascertained the intended direction of the vegetation development.
+One exception was that the development of hay meadows in south exposition did not develop towards its seed-mixture compositions.
 
-The ordination presents the experimental plots also in context with reference sites.
-The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap.
-The positions of reference sites are shifted to the left in comparison to the seed mixtures which means in the direction of early successional states.
-Though, they are still different from the negative references of ruderal, dry, anthropogenic vegetation.
-Negative references were only available on the south exposition and they are located in the NMDS between the positive reference sites and the state of restored plots in 2021.
-Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this is especially the case on the north exposition (Figure \@ref(fig:nmds)).
-\clearpage \newpage
+The ordination presents the experimental plots also in context with reference sites (Figure \@ref(fig:nmds)).
+The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped.
+The positions of reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states.
+Though, they were still different from the negative references of ruderal vegetation.
+Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
+Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this was especially the case on the north exposition (Figure \@ref(fig:nmds)).
+
+\clearpage
+
+\newpage
 
@@
 
-The vegetation of the dike experiment developed in the desired direction, but with a descelerating recovery rate.
+The vegetation of the dike experiment developed in the desired direction, but with a decelerating recovery rate.
 On the south exposition, a significant worse effect during establishment phase remained over the complete observation period.
-All in all, it was hardly possible to identify an ideal seed mixture-substrate combination.
+All in all, it was hardly possible to identify an best seed--substrate combination.
 Though, hay meadows developed closer to its reference on the north exposition than dry grasslands.
@@
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but can lead to positive results, if mixed with mineral material as sand and gravel [@chenot-lescure2022].
-As expected, sand admixture reduced nutrient loads and led to higher persistence of sown species but 50% admixture did not further increase the effect.
-In addition, the effect only appeared on the north exposition and the effect size of about 6% in the fourth year after restoration is rather small.
+As expected, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect.
+In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small.
 Substrate depth did not significantly affect persistence or Favorable Conservation Status (FCS) similarly to earlier studies [@baer2004].
-Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as it was shown for prairies [@dornbush2010].
+Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010].
 Neither, seed density had an effect on persistence and FCS which fits to results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.
 
-The vegetation on the south exposition had a different species composition than the north exposition which was also shown by @Batori.2016 in Hungary.
-Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the south exposition, was removed after two weeks because of the death of several protected lizards.
+The vegetation in south exposition had a different species composition which confirms the findings of @Batori.2016 in Hungary.
+Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks.
 This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020].
@@
 The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
-The problems during the establishment phase might have led to an alternative trajectory `r word_spec("(reference?)")`<!--# Add ref--> and could probably only be met by resowing.
+The problems during the establishment phase might have led to an alternative trajectory `r word_spec("(reference?)")`<!--# Add ref--> and could probably only be met by re-sowing.
 The drying of seedlings might also have leveled the distinction of the seed mixture types on the south exposition.
 
-## No interaction effect of seed mixture-substrate combinations
+## No interaction effect of seed--substrate combinations
 
-Our aim was to identify an ideal seed mixture-substrate combination in respect of restoration effectiveness and biodiversity.
+Our aim was to identify the best seed--substrate combination in respect of restoration effectiveness and biodiversity.
 For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
@@
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions (Figure \@ref(fig:traits)) [@Oberdorfer.1993; @Oberdorfer.1993b].<!--# Check fig ref--> Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-However, these studies did not work with an experimental set up of different seed mixture-substrate combinations, but analyzed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
+Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions [Appendix A3, @Oberdorfer.1993; @Oberdorfer.1993b].
+Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
+However, these studies did not work with an experimental set up of different seed--substrate combinations, but analyzed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
 Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and preempted the available niches for the species of related habitat types [@Fukami.2015].
@@
 The seed mixtures and positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the NMDS suggests that the seed mixture represent a latter successional stage than the references.
+The position on the NMDS suggests that the seed mixture represent a later successional stage than the references.
 The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)).
 This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
-On the south exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.
+On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.
 
 The vegetation developed in general in the desired direction but was still distinct from positive references and seed mixtures after four years.
-On the south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
+In south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
 The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
@@
 Seed density seems not to be necessary to be increased on dike slopes and soil depths of 30cm are not adverse compared to 15 cm thick substrates.
-There was no perfect seed mixture-substrate combination, why we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single solution [@bauer2023; @Holl.2022].
-The strong and lasting negative effect of drought on the south exposition might require a resowing.
+There was no perfect seed--substrate combination, why we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single solution [@bauer2023; @Holl.2022].
+The strong and lasting negative effect of drought on the south exposition might require a re-sowing.
 To close the recovery debt, the adaption of the management might be promising since it is a crucial factor aside of the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
@@
 The German Federal Environmental Foundation (DBU) supported MB with a doctoral scholarship.
-The study has been supported by the TRY initiative on plant traits ([http://www.try-db.org).](http://www.try-db.org).) The TRY initiative and database is hosted, developed and maintained by J.
-Kattge and G.
-Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany).
-TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
 
@@
 In total, plots received 16 or 32 g of seeds.
-All individual seed mixtures are stored in Appendix A3."}
+All individual seed mixtures are stored in Appendix A2."}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
 
-## Figure 2 {.unnumbered}
-
-```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The community-weighted means (CWM) of the seed mixtures used for the field experiment: specific leaf area (SLA), seed mass and canopy height.
-The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target types hay meadows and dry calcareous grasslands."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm_traits.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 3
+## Figure 2
 
@@
 
-## Figure 4 {.unnumbered}
+## Figure 3 {.unnumbered}
 
@@
 
-## Figure 5 {.unnumbered}
+## Figure 4 {.unnumbered}
 
@@
 
-## Figure 6 {.unnumbered}
+## Figure 5 {.unnumbered}
 
@@
 
-## Figure 7 {.unnumbered}
+## Figure 6 {.unnumbered}
 
@@
 
-## Session Info {.unnumbered}
+# Session Info
 

### 2023-02-22 manuscript.Rmd
Update manuscript.Rmd

@@
 
-Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows on the north exposition and not on the south exposition of dikes.
+Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows in north but not in south exposition of dikes.
 Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, even if the effect is small.
 The question which remains is, if sand admixture is the most economical restoration measure to promote diversity on dikes.
-Seed density seems not to be necessary to be increased on dike slopes and soil depths of 30cm are not adverse compared to 15 cm thick substrates.
-There was no perfect seed--substrate combination, why we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single solution [@bauer2023; @Holl.2022].
-The strong and lasting negative effect of drought on the south exposition might require a re-sowing.
+Seed density seems not to be necessary to be increased on dike slopes and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
+There was no perfect seed--substrate combination and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single uniform solution [@bauer2023; @Holl.2022].
+Strong and lasting negative effects of drought might require a re-sowing.
 To close the recovery debt, the adaption of the management might be promising since it is a crucial factor aside of the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
 For example, starting the already existing sheep grazing on the experimental sites will modify the disturbance regime and improve dispersal.
-All in all, our results support the finding that dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
-Though, the stubborn recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
+All in all, our results support the finding that restored dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
+Though, the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
 
@@
 
-Data and code are stored on Zenodo (Bauer et al. 2023) <!--# Update citation after upload -->
-
-Model evaluation is stored on GitHub: [github.com/markus1bauer/2023_danube_dike_experiment](https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown)
+Data and code are stored on Zenodo (Bauer et al.
+2023) <!--# Update citation after upload -->Model evaluation is stored on GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
 
@@
 80 002 312).
-\clearpage \newpage
+
+\clearpage
+
+\newpage
 
@@
 
+Characteristics of the substrates used for the sowing experiment on river dikes.
 Soil samples of the three substrates were analyzed for the fraction \< 2 mm.
 Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
-The pH was measured in CaCl2 solution.
-Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract.
-For calculating CaCO3, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33.
+The pH was measured in CaCl~2~ solution.
+Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract.
+For calculating CaCO~3~, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33.
 To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C.
@@
 
-```{r fig.id = "map", fig.asp = 1.2854, fig.width = 5, fig.cap = "Map"}
+```{r fig.id = "map", fig.asp = 1.2854, fig.width = 5, fig.cap = ""}
 knitr::include_graphics(
@@
 
+Local setting and design of the multifactorial experiment on grassland sowing at dikes.
 The experiment was located on a dike at river Danube in SE Germany.
-The 288 plots were allocated in six blocks (white squares on upper photo) and on the north and south exposition (central photo) [both aerial photos: @bayerischevermessungsverwaltung2023].
+The 288 plots were allocated in six blocks (white squares on upper photo) and on the north and south slope (central photo) [Both aerial photos: @bayerischevermessungsverwaltung2023].
 Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D.
 The western half of a block was with a shallow substrate depth and within this half the substrates had different sand admixtures.
-The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer).
+The photo on the bottom shows the northern slope of one block in 2021, four years after sowing (Photo: Markus Bauer).
 
@@
 
-```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years.
+```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years of sown grassland communities at a river dike.
 Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
@@
 
-```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on the dike experiment.
+```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species of sown grassland communities at a river dike.
 The plots had substrates with different sand admixtures and were sown with different seed mixture types.
 Per plot 20 species were sown.
-Shown are the medians and 95 % credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 
-```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of a dike experiment.
-The plots had substrates with different sand admixtures and were sown with different seed mixture types.
+```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of sown grassland communities at a river dike.
+The plots had substrates with different sand admixtures and were sown with different seed mixtures.
 The zero line indicate that target and non-target species are balanced.
 Positive values indicate that there are more target species.
-Shown are the medians and 95 % credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 
-```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of experimental plots to its respective reference sites (hay meadows or dry calcareous grasslands).
-The plots had substrates with different sand admixtures and were sown with different seed mixture types.
+```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of sown grassland communities at a river dike in comparison to the respective reference sites (hay meadows or dry calcareous grasslands).
+The plots had substrates with different sand admixtures and were sown with different seed mixtures.
 The zero lines indicate the mean position of the reference sites for each habitat type on the NMDS axis 1 (Figure 7).
 The grey area marks the standard deviation of the position of the reference sites.
-Shown are the medians and 95 % credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 
-```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS"}
+```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = ""}
 knitr::include_graphics(
@@
 
-NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).<!--# How many observed species --> In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
+NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
+In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
 The circles show the standard error of the groups.

### 2023-02-22 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 
-All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.
+All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/ table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.
 
 # Appendix A3
-
-The community-weighted means (CWM) of the seed mixtures used for the field experiment: specific leaf area (SLA), seed mass and canopy height.
-The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target types hay meadows and dry calcareous grasslands.
-The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 
-### Acknowledgment
+The community-weighted means (CWM) of the seed mixtures used for the dike experiment: specific leaf area (SLA), seed mass and canopy height.
+The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target habitat types hay meadows and calcareous grasslands.
+The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
-This figure has been supported by the TRY initiative on plant traits (<http://www.try-db.org>).
+#### Acknowledgment
+
+This figure was supported by the TRY initiative on plant traits (<http://www.try-db.org>).
 The TRY initiative and database is hosted, developed and maintained by J.
@@
 TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
-
-\clearpage
-
-\newpage
+\clearpage \newpage
 
@@
 read_csv(
-  here("outputs", "tables", "table_a4_specieslist.csv"),
+  here("outputs", "tables", "table_a5_specieslist.csv"),
   col_names = TRUE,
@@
   mutate(name = str_replace_all(name, "_", " ")) %>%
-  rename(Name = name, "Presence [# plots]" = sum) %>%
+  rename(
+    Name = name,
+    Seeded = seeded,
+    "Target species" = target,
+    "Presence [# plots]" = sum
+    ) %>%
   flextable() %>%
@@
   style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
-  bg(j = 2, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
+  bg(j = 4, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
   autofit()

### 2023-02-23 manuscript.Rmd
Update manuscript.Rmd

@@
 Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
-Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterize dikes [@Batori.2016; @berendse2015].
+Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterize dikes [@Batori.2016; @berendse2015; @husicka2003].
 Dikes can reconcile several requirements [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
@@
 Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots.
-The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly changed the quite high pH values (Table \@ref(tab:substrate)).
-Phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022].
+The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly change the pH values which were in the weak alkaline range (Table \@ref(tab:substrate)).
+The pH values correspond to a well established dike vegetation on river Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022].
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
 The establishment rates of species are recorded in Appendix A4.
-In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands) established by 2021.
+In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [@hedberg2010].
 The species established 31 ± 22% of their sown plot.
@@
 Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
-A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
+A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
 Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
-In total, 343 species were included in the ordination.
+Finally, 343 species were included in the ordination.
 
@@
 
-Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but can lead to positive results, if mixed with mineral material as sand and gravel [@chenot-lescure2022].
-As expected, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect.
+Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral compnent need not necessarily improve the outcome [@chenot-lescure2022].
+Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small.
-Substrate depth did not significantly affect persistence or Favorable Conservation Status (FCS) similarly to earlier studies [@baer2004].
+The Favorable Conservation Status (FCS) was hardly affected by sand admixture which corresponds to the experiment in a quarry [@chenot-lescure2022].
+Substrate depth did not significantly affect persistence or FCS similarly to earlier studies [@baer2004].
 Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010].
@@
 The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
-The problems during the establishment phase might have led to an alternative trajectory `r word_spec("(reference?)")`<!--# Add ref--> and could probably only be met by re-sowing.
+The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing.
 The drying of seedlings might also have leveled the distinction of the seed mixture types on the south exposition.
@@
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions [Appendix A3, @Oberdorfer.1993; @Oberdorfer.1993b].
+Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions with modified sub-associations[Appendix A3, @Oberdorfer.1993; @Oberdorfer.1993b; @husicka2003].
 Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
@@
 The 288 plots were allocated in six blocks (white squares on upper photo) and on the north and south slope (central photo) [Both aerial photos: @bayerischevermessungsverwaltung2023].
-Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D.
+Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D (hay meadows, dry grasslands).
 The western half of a block was with a shallow substrate depth and within this half the substrates had different sand admixtures.
@@
 ```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species of sown grassland communities at a river dike.
-The plots had substrates with different sand admixtures and were sown with different seed mixture types.
+The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
 Per plot 20 species were sown.
@@
 ```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of sown grassland communities at a river dike.
-The plots had substrates with different sand admixtures and were sown with different seed mixtures.
+The plots had substrates with different sand admixtures and were sown with two different seed mixtures.
 The zero line indicate that target and non-target species are balanced.
@@
 ```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of sown grassland communities at a river dike in comparison to the respective reference sites (hay meadows or dry calcareous grasslands).
-The plots had substrates with different sand admixtures and were sown with different seed mixtures.
+The plots had substrates with different sand admixtures and were sown with two different seed mixtures.
 The zero lines indicate the mean position of the reference sites for each habitat type on the NMDS axis 1 (Figure 7).
@@
 
-NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).
-In addition, 98 positive and negative reference plots were included (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
+The species composition of sown experimental plots on a river dike over time and in comparison with reference sites and the seed mixtures.
+Both expositions and both seed mixture types are shown in separated panels.
+The NMDS was based on Sørensen dissimilarity and data of 288 plots which were observed over four years after sowing in 2018 (circles).
+These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
 The circles show the standard error of the groups.
-2D stress: 0.21.
+2D-stress: 0.21.
 

### 2023-02-23 manuscript.Rmd
Update manuscript.Rmd

@@
 A factorial field experiment addressed this topic on a dike at river Danube in S Germany in the period 2018--2021.
-On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favorable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
+On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favourable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
 3.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
@@
 However, applying several seed--substrate combinations might foster beta diversity.
-Furthermore, additional efforts in management might be necessary to reduce the recovery debt and re-sowing after unfavorable conditions is recommended.
+Furthermore, additional efforts in management might be necessary to reduce the recovery debt and re-sowing after unfavourable conditions is recommended.
 
@@
 
-Favorable Conservation Status
+Favourable Conservation Status
 
@@
 
-Grasslands can support a very high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021].
+Grasslands can support a exceedingly high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021].
 However, they are globally endangered [@Bardgett.2021] for example by misguided afforestation [@dudley2020], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016].
@@
 For this purpose, presence of the sown species was monitored for three consecutive years.
-Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
+Second, we calculated the Favourable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
 Characteristic diversity is created by established species which belong to the habitat-specific species pool.
@@
 
-2.  How strong differs the Favorable Conservation Status (FCS) among the seed--substrate combinations?
+2.  How strong differs the Favourable Conservation Status (FCS) among the seed--substrate combinations?
 
@@
 
-The target vegetation were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
+The target vegetation was lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
@@
 The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly change the pH values which were in the weak alkaline range (Table \@ref(tab:substrate)).
-The pH values correspond to a well established dike vegetation on river Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022].
+The pH values correspond to a well-established dike vegetation on river Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022].
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
@@
 Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this was especially the case on the north exposition (Figure \@ref(fig:nmds)).
-
-\clearpage
-
-\newpage
+\clearpage \newpage
 
@@
 
-Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral compnent need not necessarily improve the outcome [@chenot-lescure2022].
+Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
 Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small.
-The Favorable Conservation Status (FCS) was hardly affected by sand admixture which corresponds to the experiment in a quarry [@chenot-lescure2022].
+The Favourable Conservation Status (FCS) was hardly affected by sand admixture which corresponds to the experiment in a quarry [@chenot-lescure2022].
 Substrate depth did not significantly affect persistence or FCS similarly to earlier studies [@baer2004].
@@
 The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing.
-The drying of seedlings might also have leveled the distinction of the seed mixture types on the south exposition.
+The drying of seedlings might also have levelled the distinction of the seed mixture types on the south exposition.
 
@@
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions with modified sub-associations[Appendix A3, @Oberdorfer.1993; @Oberdorfer.1993b; @husicka2003].
+Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
 Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-However, these studies did not work with an experimental set up of different seed--substrate combinations, but analyzed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
-Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and preempted the available niches for the species of related habitat types [@Fukami.2015].
+However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
+Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
 
@@
 The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)).
-This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b].
+This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
 On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.
@@
 
-```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
+```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of twenty species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
@@
 ```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years of sown grassland communities at a river dike.
-Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
+Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
 The FCS is the ratio of target species and non-target species.
@@
 The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
-Per plot 20 species were sown.
+Per plot twenty species were sown.
 Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
@@
 
-```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of sown grassland communities at a river dike.
+```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favourable Conservation Status (FCS) of sown grassland communities at a river dike.
 The plots had substrates with different sand admixtures and were sown with two different seed mixtures.

### 2023-02-24 manuscript.Rmd
Update manuscript.Rmd

@@
 For the computation, we used four chains, a thinning rate of two, 5,000 iterations for warm-up, and 10,000 in total.
-For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
+For evaluating the computation, the convergence of the Markov chain Monte Carlo (MCMC) chains was checked using trace plots and by the R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
 Posterior predictive checks were done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].

### 2023-02-24 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 
-<br/>
-<br/>
-<b>Markus Bauer</b>
+<br/> <br/> <b>Markus Bauer</b>
 
@@
 ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
-<br>
-[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
-<br>
-GitHub: [markus1bauer](https://github.com/markus1bauer)
+<br> [Google
+Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
+<br> GitHub: [markus1bauer](https://github.com/markus1bauer)
 
@@
 
-Bayesian analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
+Bayesian analysis motivated by Applestein et al. (2021) Restor Ecol
+[DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)
 
-Analysis guided by
-<br>
-<b>BARG</b> (Bayesian Analysis Reporting
-Guidelines): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
-<br>
-Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
-<br>
-Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
-<br>
-Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)
+Analysis guided by <br> <b>BARG</b> (Bayesian Analysis Reporting
+Guidelines): Kruschke (2021) Nat Hum Behav [DOI:
+10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
+<br> Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI:
+10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378) <br> Priors:
+Lemoine (2019) Oikos [DOI:
+10.1111/oik.05985](https://doi.org/10.1111/oik.05985) <br> Model check:
+Deapoli & Schoot (2017) Psychol Methods [DOI:
+10.1037/met0000065](https://doi.org/10.1037/met0000065)
 
@@
 
-#### Prior predictive check (BARG 1.E)
+#### Prior predictive check - Kernel density (BARG 1.E)
 
 ```{r prior-predictive-check}
-bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
+bayesplot::ppc_dens_overlay(yrep_prior[1:500, ])
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$site) +
   coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
-                 binwidth = 0.2) +
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$exposition) +
   coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
-                 binwidth = 0.2) +
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$survey_year_fct) +
   coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
-                 binwidth = 0.2) +
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$target_type) +
   coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
-                 binwidth = 0.2) +
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$seed_density) +
   coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
-                 binwidth = 0.1) +
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$sand_ratio) +
   coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
-                 binwidth = 0.2) +
+ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$substrate_depth) +
   coord_cartesian(xlim = c(-2, 2))

### 2023-02-28 manuscript.Rmd
Update manuscript (MCMC)

--- 2023-02-23 manuscript.Rmd
@@
 For the computation, we used four chains, a thinning rate of two, 5,000 iterations for warm-up, and 10,000 in total.
-For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
+We used the Markov Chain Monte Carlo method (MCMC) with the no-U-turn Sampler (NUTS), which is based on the Hamiltonian Monte Carlo approach (HMC).
+For evaluating the computation, the convergence of the four chains was checked using trace plots and evaluating R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
 Posterior predictive checks were done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].

### 2023-02-28 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Fit by design: Developing substrate-specific seed mixtures for functional dike restoration"
+title: "Fit by design: Developing substrate-specific seed mixtures for functional dike grasslands"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
 
-word_spec <- function(x, prop = ft) ftext(text = toString(x) ,prop =  ft)
+word_spec <- function(x, prop = ft) ftext(text = toString(x), prop =  ft)
 ```
@@
   align(align = "center", part = "all", j = -1) %>%
-  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
+  add_header_row(
+    top = FALSE,
+    values = c("", "Hay meadow", "Dry grassland", "", "", "")
+    ) %>%
   add_header_row(top = FALSE, values = c("", "#", "#", "#", "wt%", "wt%")) %>%
@@
   align(align = "center", part = "all", j = -1) %>%
-  compose(i = 1, j = 10, part = "header", value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))) %>%
-  compose(i = 1, j = 11, part = "header", value = as_paragraph("K", as_sub("2"), "O")) %>%
-  compose(i = 1, j = 12, part = "header", value = as_paragraph("Mg", as_sup("2+"))) %>%
-  compose(i = 1, j = 14, part = "header", value = as_paragraph("CaCO", as_sub("3"))) %>%
-  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
-  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
-  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100 g", as_sup("−1"))) %>%
+  compose(
+    i = 1, j = 10, part = "header",
+    value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))
+    ) %>%
+  compose(
+    i = 1, j = 11, part = "header",
+    value = as_paragraph("K", as_sub("2"), "O")
+    ) %>%
+  compose(
+    i = 1, j = 12, part = "header",
+    value = as_paragraph("Mg", as_sup("2+"))
+    ) %>%
+  compose(
+    i = 1, j = 14, part = "header",
+    value = as_paragraph("CaCO", as_sub("3"))
+    ) %>%
+  compose(
+    i = 2, j = 10, part = "header",
+    value = as_paragraph("mg 100 g", as_sup("−1"))
+    ) %>%
+  compose(
+    i = 2, j = 11, part = "header",
+    value = as_paragraph("mg 100 g", as_sup("−1"))
+    ) %>%
+  compose(
+    i = 2, j = 12, part = "header",
+    value = as_paragraph("mg 100 g", as_sup("−1"))
+    ) %>%
   align(align = "left", part = "footer") %>%
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff")
+  here::here(
+    "outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff"
+    )
   )
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff")
+  here::here(
+    "outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff"
+    )
   )

### 2023-02-28 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
   bold(part = "header") %>%
-  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
+  compose(
+    part = "body",
+    i = ~ Unit == "m3 s−1",
+    j = "Unit",
+    value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))
+    ) %>%
   autofit()
@@
   merge_at(part = "header", j = 4:7) %>%
-  add_header_row(top = FALSE, values = c("", "", "", "2018", "2019", "2020", "2021")) %>%
+  add_header_row(
+    top = FALSE,
+    values = c("", "", "", "2018", "2019", "2020", "2021")
+    ) %>%
   border_inner_h(part = "header", border = fp_border(width = 1)) %>%
@@
   style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
-  bg(j = 4:7, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 100))) %>%
+  bg(
+    j = 4:7,
+    bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 100))
+    ) %>%
   autofit()
@@
   style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
-  bg(j = 4, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
+  bg(
+    j = 4,
+    bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))
+    ) %>%
   autofit()

### 2023-02-28 R/_metadata.R
Update _metadata.R

@@ -70,7 +70,7 @@ address <- list(
 
 creator <- eml$creator(
   individualName = eml$individualName(
-    givenName = "Markus", 
+    givenName = "Markus",
     surName = "Bauer"
   ),
   positionName = "PhD student",
@@ -84,7 +84,7 @@ creator <- eml$creator(
 associatedParty <- list(
   eml$associatedParty(
     individualName = eml$individualName(
-      givenName = "Jakob", 
+      givenName = "Jakob",
       surName = "Huber"
     ),
     role = "Researcher",
@@ -93,7 +93,7 @@ associatedParty <- list(
   ),
   eml$associatedParty(
     individualName = eml$individualName(
-      givenName = "Johannes", 
+      givenName = "Johannes",
       surName = "Kollmann"
     ),
     role = "Professor",
@@ -105,14 +105,13 @@ associatedParty <- list(
   )
 )
 
-contact <- 
-  list(
-    individualName = creator$individualName,
-    electronicMailAddress = creator$electronicMailAddress,
-    address = address,
-    organizationName = "Technical University of Munich",
-    onlineUrl = "DOI address to the database"
-  )
+contact <- list(
+  individualName = creator$individualName,
+  electronicMailAddress = creator$electronicMailAddress,
+  address = address,
+  organizationName = "Technical University of Munich",
+  onlineUrl = "DOI address to the database"
+)
 
 
 
@@ -138,9 +137,9 @@ coverage <- set_coverage(
 ### 7 Description #############################################################
 
 
-pubDate = "2023"
+pubDate <- "2023"
 
-title = "Danube old dikes"
+title <- "Danube old dikes"
 
 abstract <- "Not written yet"
 

### 2023-02-28 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
             seed_density + substrate_depth +
-            (1 | site/plot) + (1 | botanist_year),
+            (1 | site / plot) + (1 | botanist_year),
           data = sites)
@@
   expand_limits(y = 0) +
-  ggtitle(expression(Student~italic(t)*"-distribution"))
+  ggtitle(expression(Student ~ italic(t) * "-distribution"))
 ```
@@
 ```{r mcmc-trace, fig.height = 14}
-bayesplot::mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
-bayesplot::mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
+bayesplot::mcmc_trace(
+  posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2)
+  )
+bayesplot::mcmc_trace(
+  posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2)
+  )
 ```
@@
 brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot)) 
+         re_formula =  ~ (1 | site / plot))
 brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site/plot))
+         re_formula =  ~ (1 | site / plot))
 ```
@@
 combined_models <- bind_rows(
-  bayesplot::mcmc_intervals_data(posterior1, prob = 0.66, prob_outer = 0.95) %>%
+  bayesplot::mcmc_intervals_data(
+    posterior1, prob = 0.66, prob_outer = 0.95
+    ) %>%
     mutate(model = "m_1"),
-  bayesplot::mcmc_intervals_data(posterior2, prob = 0.66, prob_outer = 0.95) %>%
+  bayesplot::mcmc_intervals_data(
+    posterior2, prob = 0.66, prob_outer = 0.95
+    ) %>%
     mutate(model = "m_2"),
-  bayesplot::mcmc_intervals_data(posterior_flat, prob = 0.66, prob_outer = 0.95) %>%
+  bayesplot::mcmc_intervals_data(
+    posterior_flat, prob = 0.66, prob_outer = 0.95
+    ) %>%
     mutate(model = "m_flat"),
-  bayesplot::mcmc_intervals_data(posterior_prior, prob = 0.66, prob_outer = 0.95) %>%
+  bayesplot::mcmc_intervals_data(
+    posterior_prior, prob = 0.66, prob_outer = 0.95
+    ) %>%
     mutate(model = "m_prior")

### 2023-02-28 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

@@
             seed_density + substrate_depth +
-            (1 | site/plot) + (1|botanist_year),
+            (1 | site / plot) + (1 | botanist_year),
           data = sites)
@@
   expand_limits(y = 0) +
-  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
+  ggtitle(expression(Student ~ italic(t) * "-distribution")) # Software standard
 ```

### 2023-02-28 manuscript.Rmd
Update manuscript.Rmd

@@
 2.
-A factorial field experiment addressed this topic on a dike at river Danube in S Germany in the period 2018--2021.
+A factorial field experiment addressed this topic on a dike at the Danube River in SE Germany in the 2018--2021 time period.
 On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favourable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
@@
 However, applying several seed--substrate combinations might foster beta diversity.
-Furthermore, additional efforts in management might be necessary to reduce the recovery debt and re-sowing after unfavourable conditions is recommended.
+Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt and re-sowing after unfavourable conditions.
 
@@
 
-artificial soil mixture
+Artificial soil mixture
 
-community assembly
+Community assembly
 
-dry grasslands
+Dry grasslands
 
-ecological restoration
+Ecological restoration
 
@@
 
-hay meadow
+Hay meadow
 
-levee
+Levee
 
-persistence
+Persistence
 
-river embankment
+River embankment
 
-soil restoration
+Soil restoration
 
-sowing
+Sowing
 
-species composition
+Species composition
 
-species-rich grassland
+Species-rich grassland
 
@@
 
-Grasslands can support a exceedingly high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021].
+Grasslands can support an exceedingly high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021].
 However, they are globally endangered [@Bardgett.2021] for example by misguided afforestation [@dudley2020], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016].
@@
 
-Restoration ecology can increase predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally lead to evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration method are key predictors of the development of vegetation after sowing [@Brudvig.2017b] and habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of the seed--substrate combination [@Torok.2017].
+Restoration ecology can increase the predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally lead to evidence-based restoration [@Cooke.2018; @Wainwright.2018].
+Local site conditions and the restoration method are key predictors of the development of vegetation after sowing [@Brudvig.2017b], and habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of the seed--substrate combination [@Torok.2017].
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
-Suitable substrates should reduce habitat filtering, while the seed mixture should minimize competitive exclusion of unsuitable species.
+Suitable substrates should reduce habitat filtering, while the seed mixture should minimize the competitive exclusion of unsuitable species.
 Modifying seed mixtures to match specific site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
@@
 An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
-We expected a better development of calcareous grassland in south exposition with shallow sandy substrates, and mesic hay meadows in north exposition on less sandy deep substrate.
+We expected a better development of calcareous grassland in the south exposition with shallow sandy substrates, and mesic hay meadows in north exposition on less sandy deep substrate.
 Furthermore, higher seed densities were recommended for slopes [@KleberLerchbaumer.2017], albeit without experimental evidence.
 
-To measure the success of restoration, we chose four indices.
+To measure the success of restoration, we chose three indices.
 First, we observed the persistence of the sown species, which is a key objective of this restoration measure [@Wilsey.2021].
@@
 Characteristic diversity is created by established species which belong to the habitat-specific species pool.
-In other words, these species are associated with the habitat type of interest.
-Third, the successional distance to the reference grasslands was determined.
-This measure quantifies the ordination distance of a plot to the average reference site [@Rydgren.2019].
+In other words, these species are associated with the habitat type of interest, whereas derived species not.
+Third, the recovery was determined by measuring the successional distance to the reference grasslands [@Rydgren.2019].
 To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf.
@@
 
-1.  How strong differs the persistence of the sown species among the seed--substrate combinations?
+1.  Mesic vs dry grassland mixtures are favoured by site conditions on northern and southern dike slopes, respectively, compared to their reference sites.
 
-2.  How strong differs the Favourable Conservation Status (FCS) among the seed--substrate combinations?
+2.  Higher seed density increases persistence of sown species and suppresses non-target species.
 
-3.  How close is the established vegetation to the reference state?
+3.  Nutrient reduction (by sand addition) and lower soil depth has similar effects on community dynamics.
+
+4.  Increased soil depth has positive effects on these community changes. à Fig. 2
 
@@
 
-# Material & Methods
+# Materials & Methods
 
@@
 
-The combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at river Danube in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
+The combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at the Danube River in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
 The climate was temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
@@
 
-The target vegetation was lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
+The target vegetation was lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist, codes CM01A, DA01B, @mucina2016].
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
@@
 Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots.
-The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly change the pH values which were in the weak alkaline range (Table \@ref(tab:substrate)).
-The pH values correspond to a well-established dike vegetation on river Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022].
-The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976].
+The sand admixture changed the soil texture, increased the C/N ratio, reduced calcium carbonate, but did hardly change the pH which were within the weak alkaline range (Table \@ref(tab:substrate)).
+The pH corresponded to a well-established dike vegetation on the Rhine River [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium was high [@lfl2022].
+The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and the Londo scale was used [@londo1976].
 The establishment rates of species are recorded in Appendix A4.
@@
 In total, 274 species were detected (Appendix A5).
+Persistence was derived from the 'species losses' component of the temporal beta-diversity index (TBI; 1 − *B*~sor~) which was calculated by comparing the seed mixtures with the respective species composition of each year using Sørensen dissimilarity [@legendre2019].
+The successional distance quantifies the ordination distance of a plot to the average reference site [*d~jt,0~*, @Rydgren.2019].
 
-Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on Danube dikes in the surroundings [@bauer2023].
+Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
 We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included also lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
@@
 Posterior predictive checks were done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].
-Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
+Finally, the models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
 A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
@@
 
-We could identify a statistically clear positive effect of sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
+We could identify a statistically clear positive effect of the sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
 The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
 For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years.
-Both expositions had similar trends but for all responses the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:persistence)).
+Both expositions had similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:persistence)).
 For the interactions, the effects of restoration treatments were neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
@@
 The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped.
-The positions of reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states.
-Though, they were still different from the negative references of ruderal vegetation.
+The positions of the reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states.
+Nonetheless, they still differed from the negative references of ruderal vegetation.
 Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
@@
 On the south exposition, a significant worse effect during establishment phase remained over the complete observation period.
-All in all, it was hardly possible to identify an best seed--substrate combination.
-Though, hay meadows developed closer to its reference on the north exposition than dry grasslands.
+All in all, it was hardly possible to identify a best seed--substrate combination, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
 
@@
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
-Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect.
+Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while a 50% admixture did not further increase the effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small.
-The Favourable Conservation Status (FCS) was hardly affected by sand admixture which corresponds to the experiment in a quarry [@chenot-lescure2022].
-Substrate depth did not significantly affect persistence or FCS similarly to earlier studies [@baer2004].
+The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to the experiment in a quarry [@chenot-lescure2022].
+Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@baer2004].
 Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010].
-Neither, seed density had an effect on persistence and FCS which fits to results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.
+Neither, seed density had an effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.
 
-The vegetation in south exposition had a different species composition which confirms the findings of @Batori.2016 in Hungary.
+The vegetation in south exposition had a different species composition, which confirms the findings of @Batori.2016 in Hungary.
 Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks.
 This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020].
-This drought could have decreased germination and establishment of sown species also in general because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
+This drought could have decreased germination and the establishment of sown species, also generally speaking, because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
 The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
@@
 
-Our aim was to identify the best seed--substrate combination in respect of restoration effectiveness and biodiversity.
+Our aim was to identify the best seed--substrate combination regarding restoration effectiveness and biodiversity.
 For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
-Though, we could not identify an interaction effect for neither of the indices.
+However, we could not identify an interaction effect for neither one of the indices.
 We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
+Although, both types are clearly plant-sociologically and functionally distinct, they are still relatively closely related because they contain shared species and could develop on similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
 Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
@@
 The seed mixtures and positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the NMDS suggests that the seed mixture represent a later successional stage than the references.
-The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)).
-This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
+The position on the NMDS suggests that the seed mixture represents a later successional stage than the references.
+The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)).
+This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north-exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
 On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.
 
-The vegetation developed in general in the desired direction but was still distinct from positive references and seed mixtures after four years.
-In south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
+The vegetation developed generally in the desired direction but was still distinct from positive references and seed mixtures after four years.
+In the south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
 The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
@@
 
-Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows in north but not in south exposition of dikes.
+Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows in the north but not in the south exposition of dikes.
 Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, even if the effect is small.
-The question which remains is, if sand admixture is the most economical restoration measure to promote diversity on dikes.
-Seed density seems not to be necessary to be increased on dike slopes and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
+The question which remains is if sand admixture is the most economical restoration measure to promote diversity on dikes.
+It does not seem necessary to increase seed density on the dike slopes, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
 There was no perfect seed--substrate combination and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single uniform solution [@bauer2023; @Holl.2022].
-Strong and lasting negative effects of drought might require a re-sowing.
-To close the recovery debt, the adaption of the management might be promising since it is a crucial factor aside of the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
+The strong and lasting negative effects of the drought might require a re-sowing.
+To close the recovery debt, the management adaptation might be promising since it is a crucial factor aside from the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
 For example, starting the already existing sheep grazing on the experimental sites will modify the disturbance regime and improve dispersal.
 All in all, our results support the finding that restored dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
-Though, the recovery debt highlights that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
+However, the recovery debt highlights the fact that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
 
@@
 
-```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species of sown grassland communities at a river dike.
+```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence (1-*B*~sor~) of sown species of sown grassland communities at a river dike.
 The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
-Per plot twenty species were sown.
+Per plot, twenty species were sown.
 Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}

### 2023-02-28 manuscript.Rmd
Update manuscript.Rmd

@@
 
-MB is funded by a doctoral scholarship of the German Federal Environmental Foundation (DBU) (No.
+MB was funded by a doctoral scholarship of the German Federal Environmental Foundation (DBU) (No.
 20021/698).
@@
 Soil samples of the three substrates were analyzed for the fraction \< 2 mm.
-Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
+The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
 The pH was measured in CaCl~2~ solution.
-Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract.
+Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in a CaCl~2~ extract.
 For calculating CaCO~3~, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33.
@@
 Local setting and design of the multifactorial experiment on grassland sowing at dikes.
-The experiment was located on a dike at river Danube in SE Germany.
-The 288 plots were allocated in six blocks (white squares on upper photo) and on the north and south slope (central photo) [Both aerial photos: @bayerischevermessungsverwaltung2023].
+The experiment was located on a dike at the Danube River in SE Germany.
+The 288 plots were allocated in six blocks (white squares on the upper photo) and on the north and south slope (central photo) [Both aerial photos: @bayerischevermessungsverwaltung2023].
 Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D (hay meadows, dry grasslands).
-The western half of a block was with a shallow substrate depth and within this half the substrates had different sand admixtures.
+The western half of a block was with a shallow substrate depth and within this, half of the substrates had different sand admixtures.
 The photo on the bottom shows the northern slope of one block in 2021, four years after sowing (Photo: Markus Bauer).
@@
 Note that the zero lines indicate that both levels have equal values.
-This means for instance that hay meadows are closer to their reference than dry grasslands  (C)."}
+This means, e.g., that hay meadows are closer to their reference than dry grasslands  (C)."}
 knitr::include_graphics(
@@
 The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
-Per plot, twenty species were sown.
-Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
+Twenty species were sown per plot.
+Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 The plots had substrates with different sand admixtures and were sown with two different seed mixtures.
-The zero line indicate that target and non-target species are balanced.
+The zero line indicates that target and non-target species are balanced.
 Positive values indicate that there are more target species.
-Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 The grey area marks the standard deviation of the position of the reference sites.
-Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
+Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM)."}
 knitr::include_graphics(
@@
 Both expositions and both seed mixture types are shown in separated panels.
-The NMDS was based on Sørensen dissimilarity and data of 288 plots which were observed over four years after sowing in 2018 (circles).
+The NMDS was based on the Sørensen dissimilarity and data of 288 plots observed over four years after sowing in 2018 (circles).
 These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].

### 2023-03-01 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 
-NUTS sampler is used.
+Markov Chain Monte Carlo (MCMC) method used with No-U-Turn Sampler
+(NUTS) sampler which is an extension of Hamiltonian Monte Carlo (HMC).
 
@@
   posterior::subset_draws(variable = variables)
-# R hat
-rhat1 <- brms::rhat(m_1)
-rhat2 <- brms::rhat(m_2)
-# NEFF ratio
-neff1 <- brms::neff_ratio(m_1)
-neff2 <- brms::neff_ratio(m_2)
 # Long format of draws
-hmc_diagnostics1 <- brms::nuts_params(m_1)
-hmc_diagnostics2 <- brms::nuts_params(m_2)
+hmc_diagnostics1 <- m_1 %>% brms::nuts_params()
+hmc_diagnostics2 <- m_2 %>% brms::nuts_params()
 y <- sites$n
 # Posterior predictive distribution
-yrep1 <- brms::posterior_predict(m_1, draws = 500)
-yrep2 <- brms::posterior_predict(m_2, draws = 500)
-yrep_prior <- brms::posterior_predict(m_prior, draws = 500)
-# Leave-one-out cross validation based on posterior likelihood
-loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
-loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
+yrep1 <- m_1 %>% brms::posterior_predict(draws = 500)
+yrep2 <- m_2 %>% brms::posterior_predict(draws = 500)
+yrep_prior <- m_prior %>% brms::posterior_predict(draws = 500)
 # Summary statistics
@@
 ```{r prior-predictive-check}
-bayesplot::ppc_dens_overlay(yrep_prior[1:500, ])
+bayesplot::ppc_dens_overlay(y, yrep_prior[1:500, ])
 ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$site) +
@@
 
-#### Sampling efficency: Rhat (BARG 2.B)
+#### Sampling efficency: R-hat (BARG 2.B)
 
 ```{r rhat, collapse = TRUE}
-bayesplot::mcmc_rhat(rhat1)
-bayesplot::mcmc_rhat(rhat1)
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
 ```
@@
 ```{r ess, collapse = TRUE}
-bayesplot::mcmc_neff(neff1)
-bayesplot::mcmc_neff(neff2)
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
 ```
@@
 ```{r loo}
+loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
+loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
 loo1

### 2023-03-01 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

@@
 
-NUTS sampler is used.
+Markov Chain Monte Carlo (MCMC) method used with No-U-Turn Sampler (NUTS) sampler which is an extension of Hamiltonian Monte Carlo (HMC).
 

### 2023-03-01 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
 ```{r loo}
+# Leave-one-out cross validation based on posterior likelihood
+loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
+loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
 loo1

### 2023-03-01 manuscript.Rmd
Update manuscript.Rmd

@@
 This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes.
-Here, an improved seed--substrate combination would secure slope stability, reduce mowing efforts, and generate biodiverse grasslands.
+Here, an improved seed--substrate combination will secure slope stability, reduce mowing efforts, and generate biodiverse grasslands.
 2.
 A factorial field experiment addressed this topic on a dike at the Danube River in SE Germany in the 2018--2021 time period.
-On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favourable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
+On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixture types (mesic hay meadow, semi-dry calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favourable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
 3.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
@@
 
-2.  Higher seed density increases persistence of sown species and suppresses non-target species.
+2.
+Nutrient reduction (by sand addition) and lower soil depth increase persistence of sown species and fosters target species in comparison to non-target species especially for dry grassland mixtures.
+Hay meadow mixtures can cope with no sand admixture and larger soil depths.
 
-3.  Nutrient reduction (by sand addition) and lower soil depth has similar effects on community dynamics.
-
-4.  Increased soil depth has positive effects on these community changes. à Fig. 2
+3.  Higher seed density increases generally persistence of sown species and suppresses non-target species.
 

### 2023-03-01 manuscript.Rmd
Update manuscript.Rmd

@@
 Grasslands can support an exceedingly high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021].
-However, they are globally endangered [@Bardgett.2021] for example by misguided afforestation [@dudley2020], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016].
+However, they are globally endangered [@Bardgett.2021], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016].
 Restoration is seen as a key factor to sustain biodiversity and ecosystem services [@COP.2014; @UnitedNations.2019b], and sowing is a well-established approach to establish species-rich grasslands [@Kiehl.2010].
 Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome the dispersal filters [@myers2009; @orrock2023].
-However, there are still open questions about adjusting the seed mixtures to specific site conditions and future climate conditions [@Torok.2021].
+However, there are still open questions about adjusting seed mixtures to specific site conditions and future climate conditions [@Torok.2021].
 
-Restoration ecology can increase the predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally lead to evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration method are key predictors of the development of vegetation after sowing [@Brudvig.2017b], and habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of the seed--substrate combination [@Torok.2017].
+Restoration ecology can increase the predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally strengthen evidence-based restoration [@Cooke.2018; @Wainwright.2018].
+Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b], and habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
@@
 
-The aim of this study is to identify the best combination of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
+The aim of this study is to identify suitable combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
 An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
-We expected a better development of calcareous grassland in the south exposition with shallow sandy substrates, and mesic hay meadows in north exposition on less sandy deep substrate.
-Furthermore, higher seed densities were recommended for slopes [@KleberLerchbaumer.2017], albeit without experimental evidence.
+We expected a better development of calcareous grassland in the south exposition with shallow and sandy substrates, and of mesic hay meadows in north exposition on less sandy and deep substrates.
+Furthermore for slopes, higher seed densities are recommended [@KleberLerchbaumer.2017], albeit without experimental evidence.
 
@@
 First, we observed the persistence of the sown species, which is a key objective of this restoration measure [@Wilsey.2021].
-For this purpose, presence of the sown species was monitored for three consecutive years.
-Second, we calculated the Favourable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015].
+For this purpose, the presence of the sown species was monitored for three consecutive years.
+Second, we calculated the Favourable Conservation Status (FCS) which distinguishes characteristic and derived diversity [@Helm.2015].
 Characteristic diversity is created by established species which belong to the habitat-specific species pool.
@@
 This was reached by comparing the species composition of the experimental plots with reference sites.
-We asked the following question to evaluate the restoration approaches and the success after four years:
+We tested following hypotheses after four years of observation:
 
-1.  Mesic vs dry grassland mixtures are favoured by site conditions on northern and southern dike slopes, respectively, compared to their reference sites.
+1.  Establishment of mesic vs dry grassland mixtures is facilitated by site conditions on northern and southern dike slopes, respectively.
 
-2.
-Nutrient reduction (by sand addition) and lower soil depth increase persistence of sown species and fosters target species in comparison to non-target species especially for dry grassland mixtures.
-Hay meadow mixtures can cope with no sand admixture and larger soil depths.
+2.  Nutrient reduction (by sand addition) and shallow soil increase establishment of dry grassland compared to mesic mixtures.
 
-3.  Higher seed density increases generally persistence of sown species and suppresses non-target species.
+3.  Reduced soil resources benefit especially target species in comparison to non-target species(, thus increasing conservation value).
+
+4.  Higher seed density increases generally establishment of sown plants and suppresses non-target species.
 

### 2023-03-01 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 ---
-title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
+title: "Analysis of Bauer et al. (2023) bioRxiv: <br> Favourable Conservation Status (FCS)"
 author: "<b>Markus Bauer</b> <br>"
@@
 
-#### Prior predictive check - Kernel density (BARG 1.E)
+#### Prior predictive check (BARG 1.E)
 
 ```{r prior-predictive-check}
-bayesplot::ppc_dens_overlay(y, yrep_prior[1:500, ])
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$site) +
-  coord_cartesian(xlim = c(-2, 2))
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$exposition) +
-  coord_cartesian(xlim = c(-2, 2))
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$survey_year_fct) +
-  coord_cartesian(xlim = c(-2, 2))
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$target_type) +
-  coord_cartesian(xlim = c(-2, 2))
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$seed_density) +
-  coord_cartesian(xlim = c(-2, 2))
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$sand_ratio) +
-  coord_cartesian(xlim = c(-2, 2))
-ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$substrate_depth) +
-  coord_cartesian(xlim = c(-2, 2))
+bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.5) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$site, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$exposition, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$survey_year_fct, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$target_type, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$seed_density, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$sand_ratio, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$substrate_depth, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
 ```
@@
 
-```{r effect-sizes}
+```{r effect-sizes, message = FALSE}
 posterior1 %>%
@@
   knitr::kable()
-emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
-          survey_year_fct, type = "response")
+emm <- emmeans(
+  m_1, revpairwise ~ target_type + sand_ratio | exposition | survey_year_fct,
+  type = "response"
+  )
 emm$emmeans
@@
 ```{r write-csv, echo = FALSE}
-write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
+draws1 %>% write_csv(here("outputs", "statistics", "table_fcs.csv"))
 ```

### 2023-03-01 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

@@
 ---
-title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence"
+title: "Analysis of Bauer et al. (2023) bioRxiv: <br> Persistence"
 author: "<b>Markus Bauer</b> <br>"
@@
 ```{r prior-predictive-check}
-bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
+bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.2) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
-                 binwidth = 0.2) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$site, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
-                 binwidth = 0.2) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$exposition, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
-                 binwidth = 0.2) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$survey_year_fct, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
-                 binwidth = 0.2) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$target_type, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
-                 binwidth = 0.1) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$seed_density, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
-                 binwidth = 0.2) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$sand_ratio, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
-                 binwidth = 0.2) +
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$substrate_depth, binwidth = 0.2
+  ) +
   coord_cartesian(xlim = c(-1, 1))
@@
 ```{r write-csv, echo = FALSE}
-write.csv(draws1, here("outputs", "statistics", "table_persistence.csv"))
+draws1 %>% write_csv(here("outputs", "statistics", "table_persistence.csv"))
 ```

### 2023-03-01 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
 ---
-title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Recovery completeness"
+title: "Analysis of Bauer et al. (2023) bioRxiv: <br> Recovery completeness"
 author: "<b>Markus Bauer</b> <br>"
@@
 ```{r prior-predictive-check}
-bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
-                 binwidth = 0.1) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
-ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
-                 binwidth = 0.2) +
-  coord_cartesian(xlim = c(-2, 2))
+bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.5) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$site, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$exposition, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$survey_year_fct, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$target_type, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$seed_density, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$sand_ratio, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
+ppc_stat_grouped(
+  y, yrep_prior[1:500, ], group = sites$substrate_depth, binwidth = 0.5
+  ) +
+  coord_cartesian(xlim = c(-4, 4))
 ```
@@
 ```{r write-csv, echo = FALSE}
-write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))
+draws1 %>% write_csv(here("outputs", "statistics", "table_recovery.csv"))
 ```

### 2023-03-01 manuscript.Rmd
Update manuscript.Rmd

@@
 Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterize dikes [@Batori.2016; @berendse2015; @husicka2003].
-Dikes can reconcile several requirements [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
+Dikes can reconcile several ecosystem functions like dike security with biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
 
@@
 We expected a better development of calcareous grassland in the south exposition with shallow and sandy substrates, and of mesic hay meadows in north exposition on less sandy and deep substrates.
-Furthermore for slopes, higher seed densities are recommended [@KleberLerchbaumer.2017], albeit without experimental evidence.
+Furthermore for slopes, higher seed densities are recommended for a succesfull establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
 
 To measure the success of restoration, we chose three indices.
-First, we observed the persistence of the sown species, which is a key objective of this restoration measure [@Wilsey.2021].
+First, we observed the persistence of the sown species, which is a key objective of the restoration measure sowing [@Wilsey.2021].
 For this purpose, the presence of the sown species was monitored for three consecutive years.
@@
 The combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at the Danube River in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
-The climate was temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix A1, @lfu2021waterlevel; @lfu2021discharge].
-The substrates consisted of sand (0--4 mm) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
+The climate of the region is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
+During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], as well as three minor floods which did not reach the plots [Appendix A1, @lfu2021waterlevel; @lfu2021discharge].
+The substrates consisted of calcareous sand (0--4 mm) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
 A big roller mixed both components and an excavator put the substrates in the prepared plots.
 
-The target vegetation was lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist, codes CM01A, DA01B, @mucina2016].
+The target vegetation types were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist, codes CM01A, DA01B, @mucina2016].
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
@@
 Krimmer, Pulling).
-From these species pools, 20 species were randomly selected for each plot (Appendix A2).
-The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
+From these species pools, 20 species were selected for each plot in a stratified, randomised manner (Appendix A2).
+Each mixture contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
 The community-weighted means (CWM) of functional traits differed between the seed mixture types (Appendix A3).
@@
 The south-exposed plots were sown in mid-April 2018 and the north exposition 14 days later.
-Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects like the death of several protected lizards.
+Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects for the seedlings.
 The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
@@
 
-We used 288 plots of the size 2.0 m × 2.0 m which were halfway up the slopes of the dike, distributed over the north and south exposition, and arranged in six blocks (= replicates).
+We used 288 plots of the size 2.0 m × 3.0 m, vertically oriented, halfway up the dike slopes, distributed over the north and south exposition, and arranged in six blocks (= replicates).
 The experiment used a split-plot design combined with a randomized complete block design (Figure \@ref(fig:map)).
@@
 The sand admixture changed the soil texture, increased the C/N ratio, reduced calcium carbonate, but did hardly change the pH which were within the weak alkaline range (Table \@ref(tab:substrate)).
-The pH corresponded to a well-established dike vegetation on the Rhine River [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium was high [@lfl2022].
+The pH corresponded to a well-established dike vegetation on the Rhine River [@husicka2003], phosphate and potassium were rather scarce for agricultural soils, but magnesium showed high concentrations [@lfl2022].
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and the Londo scale was used [@londo1976].
@@
 In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [@hedberg2010].
-The species established 31 ± 22% of their sown plot.
-In total, 274 species were detected (Appendix A5).
+The species established in 31 ± 22% (mean ± SD) of their sown plots.
+In total, 274 vascular plant species were detected (Appendix A5).
 Persistence was derived from the 'species losses' component of the temporal beta-diversity index (TBI; 1 − *B*~sor~) which was calculated by comparing the seed mixtures with the respective species composition of each year using Sørensen dissimilarity [@legendre2019].
@@
 Both expositions had similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:persistence)).
-For the interactions, the effects of restoration treatments were neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
+The interactions of restoration treatments were neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
 Persistence of both seed mixture types was slightly positively affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
@@
 The NMDS confirmed that the seed mixtures were variable, but distinctive for hay meadows and dry grasslands and ascertained the intended direction of the vegetation development.
-One exception was that the development of hay meadows in south exposition did not develop towards its seed-mixture compositions.
+As one exception, hay meadows in south exposition did not develop towards their seed-mixture compositions.
 
-The ordination presents the experimental plots also in context with reference sites (Figure \@ref(fig:nmds)).
-The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped.
+The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped (Figure \@ref(fig:nmds)).
 The positions of the reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states.
@@
 Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
-Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this was especially the case on the north exposition (Figure \@ref(fig:nmds)).
+Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)).
+This was especially the case in north exposition (Figure \@ref(fig:nmds)).
 \clearpage \newpage
@@
 The vegetation of the dike experiment developed in the desired direction, but with a decelerating recovery rate.
-On the south exposition, a significant worse effect during establishment phase remained over the complete observation period.
-All in all, it was hardly possible to identify a best seed--substrate combination, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
+A significantly worse effect during establishment phase remained over the complete observation period in south compared to north exposition.
+All in all, it was hardly possible to identify any best seed--substrate combination, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
 

### 2023-03-01 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 Markov Chain Monte Carlo (MCMC) method used with No-U-Turn Sampler
-(NUTS) sampler which is an extension of Hamiltonian Monte Carlo (HMC).
+(NUTS) which is an extension of Hamiltonian Monte Carlo (HMC).
 
@@
 ```{r possible-priors}
-brms::get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site / plot) + (1 | botanist_year),
-          data = sites)
+brms::get_prior(
+  n ~ target_type + sand_ratio + seed_density + substrate_depth +
+    exposition + survey_year_fct + botanist_year + (1 | site / plot),
+  data = sites
+  ) %>%
+  select(prior, class, coef, group, source)
 data <- data.frame(x = c(-5, 5))
@@
 ```{r prior-summary}
-brms::prior_summary(m_1, all = FALSE)
+m_1 %>%
+  brms::prior_summary(all = FALSE) %>%
+  select(prior, class, coef, group, source)
 ```
@@
 
-```{r prior-predictive-check}
+```{r prior-predictive-check, fig.height = 4}
 bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.5) +
@@
 ```{r mcmc-pairs, collapse = TRUE, fig.height = 6.5}
-bayesplot::mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
+m_1 %>% bayesplot::mcmc_pairs(
+  off_diag_args = list(size = 1.2),
   pars = c(
@@
     "b_expositionsouth", "sigma"
-           ))
-bayesplot::mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
+           )
+)
+m_2 %>% bayesplot::mcmc_pairs(
+  off_diag_args = list(size = 1.2),
   pars = c(
@@
     "b_expositionsouth", "sigma"
-           ))
+           )
+)
 ```
@@
 ```{r mcmc-parcoord, collapse = TRUE}
-bayesplot::mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
+posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) +
   theme(axis.text.x = element_text(angle = 45))
-bayesplot::mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
+posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) +
   theme(axis.text.x = element_text(angle = 45))
@@
 ```{r autocorrelation}
-bayesplot::mcmc_acf(posterior1, lags = 10)
-bayesplot::mcmc_acf(posterior2, lags = 10)
+posterior1 %>% bayesplot::mcmc_acf(lags = 10)
+posterior2 %>% bayesplot::mcmc_acf(lags = 10)
 ```
@@
 p1 / p2
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
+p1 / p2
 p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
@@
 p1 / p2
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
+p1 / p2
 p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
@@
 p1 / p2
-ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+p1 / p2
 p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
@@
 p1 / p2
-ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+p1 / p2
 p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
@@
 ```{r loo}
-loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
-loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
+loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
+loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
 loo1
@@
 p1 / p2
-
 ```
@@
 ```{r dharma, collapse = TRUE}
-DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
-DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
+m_1 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
+m_2 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
 ```
@@
 ```{r conditional-r2, collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site / plot))
-brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula =  ~ (1 | site / plot))
+m_1 %>% brms::bayes_R2(
+  probs = c(0.05, 0.5, 0.95), re_formula =  ~ (1 | site / plot)
+  )
+m_2 %>% brms::bayes_R2(
+  probs = c(0.05, 0.5, 0.95), re_formula =  ~ (1 | site / plot)
+  )
 ```
@@
 ```{r marginal-r2, collapse = TRUE}
-brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
-brms::bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
-         re_formula = 1 ~ 1)
+m_1 %>% brms::bayes_R2(
+  probs = c(0.05, 0.5, 0.95), re_formula = 1 ~ 1
+  )
+m_2 %>% brms::bayes_R2(
+  probs = c(0.05, 0.5, 0.95), re_formula = 1 ~ 1
+  )
 ```
@@
   posterior::summarize_draws() %>%
-  knitr::kable()
-emm <- emmeans(
-  m_1, revpairwise ~ target_type + sand_ratio | exposition | survey_year_fct,
+  knitr::kable() #%>%
+  #kableExtra::kable_styling(font_size = 10)
+emm <- m_1 %>% emmeans(
+  revpairwise ~ target_type + sand_ratio | exposition | survey_year_fct,
   type = "response"

### 2023-03-01 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

@@
 
-Markov Chain Monte Carlo (MCMC) method used with No-U-Turn Sampler (NUTS) sampler which is an extension of Hamiltonian Monte Carlo (HMC).
+Markov Chain Monte Carlo (MCMC) method used with No-U-Turn Sampler (NUTS) which is an extension of Hamiltonian Monte Carlo (HMC).
 
@@
 ```{r possible-priors}
-brms::get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site / plot) + (1 | botanist_year),
-          data = sites)
+brms::get_prior(
+  n ~ target_type + sand_ratio + seed_density + substrate_depth +
+    exposition + survey_year_fct + botanist_year + (1 | site / plot),
+  data = sites
+  ) %>%
+  select(prior, class, coef, group, source)
 ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
@@
   posterior::summarize_draws() %>%
-  knitr::kable()
-emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
-          survey_year_fct, type = "response")
+  knitr::kable() %>%
+  kableExtra::kable_styling(font_size = 10)
+emm <- m_1 %>% emmeans(
+  revpairwise ~ target_type + sand_ratio | exposition | survey_year_fct,
+  type = "response"
+  )
 emm$emmeans

### 2023-03-01 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
 ```{r possible-priors}
-brms::get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
-            seed_density + substrate_depth +
-            (1 | site / plot) + (1 | botanist_year),
-          data = sites)
+brms::get_prior(
+  n ~ target_type + sand_ratio + seed_density + substrate_depth +
+    exposition + survey_year_fct + botanist_year + (1 | site / plot),
+  data = sites
+  ) %>%
+  select(prior, class, coef, group, source)
 ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
@@
 # Leave-one-out cross validation based on posterior likelihood
-loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
-loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
+loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
+loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
 loo1

### 2023-03-01 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 sites %>% group_by(exposition) %>% count(site)
-boxplot(sites$n)
-ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
-ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
-ggplot(sites, aes(x = n)) + geom_density()
+plot1 <- ggplot(sites, aes(y = n)) + geom_boxplot()
+plot2 <- ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
+plot3 <- ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
+plot4 <- ggplot(sites, aes(x = n)) + geom_density()
+(plot1 + plot2) / (plot3 + plot4)
 ```
@@
 data <- data.frame(x = c(-5, 5))
-ggplot(data, aes(x = x)) +
+plot1 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 2)) +
@@
   ggtitle("Normal distribution for Intercept")
-ggplot(data, aes(x = x)) +
+plot2 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0.3, sd = 2)) +
@@
   ggtitle("Normal distribution for treatments")
-ggplot(data, aes(x = x)) +
+plot3 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
@@
   ggtitle("Cauchy distribution")
-ggplot(data, aes(x = x)) +
+plot4 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
@@
   ggtitle(expression(Student ~ italic(t) * "-distribution"))
+(plot1 + plot2) / (plot3 + plot4)
 ```
@@
 
-```{r prior-predictive-check, fig.height = 4}
+```{r prior-predictive-check, fig.height = 3}
 bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.5) +
-  coord_cartesian(xlim = c(-4, 4))
+  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ppc_stat_grouped(
@@
   ) +
-  coord_cartesian(xlim = c(-4, 4))
+  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ppc_stat_grouped(
@@
   ) +
-  coord_cartesian(xlim = c(-4, 4))
+  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ```
@@
   posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2)
-  )
+  ) + bayesplot::theme_default()
 bayesplot::mcmc_trace(
   posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2)
-  )
+  ) + bayesplot::theme_default()
 ```
@@
 
-```{r rhat, collapse = TRUE}
+```{r rhat, collapse = TRUE, fig.height = 3}
 m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
@@
 
-```{r ess, collapse = TRUE}
+```{r ess, collapse = TRUE, fig.height = 3}
 m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
@@
 loo2
-plot(loo1)
-plot(loo2)
+plot1 <- plot(loo1)
+plot2 <- plot(loo2)
+plot1 / plot2
 ```
@@
 
-```{r dharma, collapse = TRUE}
+```{r dharma, collapse = TRUE, fig.height = 5}
 m_1 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
@@
   posterior::summarize_draws() %>%
-  knitr::kable() #%>%
-  #kableExtra::kable_styling(font_size = 10)
+  knitr::kable()
 emm <- m_1 %>% emmeans(

### 2023-03-01 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

@@
 
-```{r dharma, collapse = TRUE}
+```{r dharma, collapse = TRUE, fig.height = 4}
 m_1 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)

### 2023-03-02 manuscript.Rmd
Update manuscript.Rmd

@@
 
-The aim of this study is to identify suitable combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
+The aim of this study is to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
 An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
-We expected a better development of calcareous grassland in the south exposition with shallow and sandy substrates, and of mesic hay meadows in north exposition on less sandy and deep substrates.
+We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deep substrates.
 Furthermore for slopes, higher seed densities are recommended for a succesfull establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
@@
 A significantly worse effect during establishment phase remained over the complete observation period in south compared to north exposition.
-All in all, it was hardly possible to identify any best seed--substrate combination, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
+All in all, it was hardly possible to identify any best seed--substrate combinations, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
 
@@
 Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010].
-Neither, seed density had an effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.
+Seed density had also no clear effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
 
 The vegetation in south exposition had a different species composition, which confirms the findings of @Batori.2016 in Hungary.
-Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks.
+Here, the differences might be due to some unintended methodical reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks.
 This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020].
-This drought could have decreased germination and the establishment of sown species, also generally speaking, because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023].
-The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
+This drought could have decreased germination and the establishment of sown species, also generally speaking, because a moist spring with a mesic temperature enhances establishment [@Larson.2021; @orrock2023].
+The interesting point here is the lasting negative effect on persistence and FCS on the southern slope which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
 The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing.
@@
 
-Our aim was to identify the best seed--substrate combination regarding restoration effectiveness and biodiversity.
+Our aim was to identify perfect seed--substrate combinations regarding restoration effectiveness and biodiversity.
 For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
@@
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly plant-sociologically and functionally distinct, they are still relatively closely related because they contain shared species and could develop on similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
+Although, both types are clearly phytosociologically and functionally distinct, they are still relatively closely related because they contain shared species and could develop under similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
 Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
 However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
-Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
+Furthermore, the non-existence of ideal combinations could be explained by priority effects which means that the species of the imperfect-adapted seed mixture type could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
 
@@
 
-The seed mixtures and positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
+The seed mixtures and their positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
 The position on the NMDS suggests that the seed mixture represents a later successional stage than the references.
@@
 This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north-exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
-On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.
+On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using a non-adapted seed mixture.
 
@@
 
-Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows in the north but not in the south exposition of dikes.
-Furthermore, to reduce nutrient load by sand admixture has a clear positive effect, even if the effect is small.
-The question which remains is if sand admixture is the most economical restoration measure to promote diversity on dikes.
-It does not seem necessary to increase seed density on the dike slopes, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
-There was no perfect seed--substrate combination and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single uniform solution [@bauer2023; @Holl.2022].
-The strong and lasting negative effects of the drought might require a re-sowing.
-To close the recovery debt, the management adaptation might be promising since it is a crucial factor aside from the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
-For example, starting the already existing sheep grazing on the experimental sites will modify the disturbance regime and improve dispersal.
+Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows in the north but not necessarily in the south exposition of dikes.
+Furthermore, the reduction of the nutrient load through sand admixture has a clearly positive effect, albeit the effect is small.
+The question remains if sand admixture is the most economical restoration measure to promote diversity on dikes.
+Increasing seed density on dike slopes does not appear to be necessary, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
+There were no perfect seed--substrate combinations and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single uniform solution [@bauer2023; @Holl.2022].
+The strong and lasting negative effects of the drought might require re-sowing.
+To close the recovery debt, the management adaptation might be promising since this is a crucial factor beside the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
+For example, the start of sheep grazing on the experimental plots, which already exists in the surroundings, will modify the disturbance regime and improve dispersal.
 All in all, our results support the finding that restored dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
@@
 We would like to thank our project partners Dr.
-Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Klaus Rachl and Stefan Radlmair (Lower Bavaria Government) for numerous discussions on restoration and management of dike grasslands.
+Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Klaus Rachl and Stefan Radlmair (Government of Lower Bavaria) for numerous discussions on restoration and management of dike grasslands.
 Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
@@
 Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D (hay meadows, dry grasslands).
-The western half of a block was with a shallow substrate depth and within this, half of the substrates had different sand admixtures.
+The western half of a block had a shallow substrate depth and within this, half of the substrates had different sand admixtures.
 The photo on the bottom shows the northern slope of one block in 2021, four years after sowing (Photo: Markus Bauer).
@@
 Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
-The FCS is the ratio of target species and non-target species.
+The FCS is the ratio of target species to non-target species.
 Note that the zero lines indicate that both levels have equal values.
@@
 
-```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of sown grassland communities at a river dike in comparison to the respective reference sites (hay meadows or dry calcareous grasslands).
+```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of sown grassland communities at a river dike in comparison to the respective reference sites (mesic hay meadows or semi-dry calcareous grasslands).
 The plots had substrates with different sand admixtures and were sown with two different seed mixtures.
@@
 These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
-The circles show the standard error of the groups.
+The ellipses show the standard error of the groups.
 2D-stress: 0.21.

### 2023-03-02 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 rm(list = ls())
+theme_mb <- function() {
+  theme(
+    panel.background = element_rect(fill = "white"),
+    text = element_text(size = 9, color = "black"),
+    strip.text = element_text(size = 10),
+    axis.text = element_text(angle = 0, hjust = 0.5, size = 9,
+                             color = "black"),
+    axis.title = element_text(angle = 0, hjust = 0.5, size = 9,
+                              color = "black"),
+    axis.line = element_line(),
+    legend.key = element_rect(fill = "white"),
+    legend.text = element_text(size = 9),
+    legend.position = "right",
+    legend.margin = margin(0, 0, 0, 0, "cm"),
+    plot.margin = margin(0, 0, 0, 0, "cm")
+  )
+}
 ```
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Sand ratio [vol%]")
+  labs(title = "Sand ratio [vol%]") + theme_mb()
 plot2 <- ggplot(sites %>% filter(survey_year == 2021),
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Substrate depth [cm]")
+  labs(title = "Substrate depth [cm]") + theme_mb()
 plot3 <- ggplot(sites %>% filter(survey_year == 2021),
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Target type")
+  labs(title = "Target type") + theme_mb()
 plot4 <- ggplot(sites %>% filter(survey_year == 2021),
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Seed density [g/m²]")
+  labs(title = "Seed density [g/m²]") + theme_mb()
 (plot1 + plot2) / (plot3 + plot4)
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Exposition")
+  labs(title = "Exposition") + theme_mb()
 plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
   geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
-  labs(title = "Survey year")
+  labs(title = "Survey year") + theme_mb()
 plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = site)) +
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Blocks")
+  labs(title = "Blocks") + theme_mb()
 plot4 <- ggplot(sites, aes(y = n, x = botanist_year)) +
@@
   labs(title = "Botanists and survey year") +
-  theme(axis.text.x = element_text(angle = 90))
+  theme_mb() + theme(axis.text.x = element_text(angle = 90))
 (plot1 + plot2) / (plot3 + plot4)
@@
   facet_grid(exposition ~ survey_year_fct) +
-  labs(title = "Target type vs. sand ratio [vol%]")
+  labs(title = "Target type vs. sand ratio [vol%]") + theme_mb()
 ggplot(data = sites,
@@
   facet_grid(exposition ~ survey_year_fct) +
-  labs(title = "Substrate depth [cm] vs. sand ratio [vol%]")
+  labs(title = "Substrate depth [cm] vs. sand ratio [vol%]") + theme_mb()
 ggplot(data = sites,
@@
   facet_grid(exposition ~ survey_year_fct) +
-  labs(title = "Target type vs. Seed density [g/m²]")
+  labs(title = "Target type vs. Seed density [g/m²]") + theme_mb()
 ```
@@
 sites %>% group_by(exposition) %>% count(site)
-plot1 <- ggplot(sites, aes(y = n)) + geom_boxplot()
-plot2 <- ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
-plot3 <- ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
-plot4 <- ggplot(sites, aes(x = n)) + geom_density()
+plot1 <- ggplot(sites, aes(y = n)) + geom_boxplot() + theme_mb()
+plot2 <- ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom() + theme_mb()
+plot3 <- ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03) + theme_mb()
+plot4 <- ggplot(sites, aes(x = n)) + geom_density() + theme_mb()
 (plot1 + plot2) / (plot3 + plot4)
@@
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for Intercept")
+  ggtitle("Normal distribution for Intercept") + theme_mb()
 plot2 <- ggplot(data, aes(x = x)) +
@@
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for treatments")
+  ggtitle("Normal distribution for treatments") + theme_mb()
+# See Lemoine 2019 https://doi.org/10.1111/oik.05985
 plot3 <- ggplot(data, aes(x = x)) +
@@
   expand_limits(y = 0) +
-  ggtitle("Cauchy distribution")
+  ggtitle("Cauchy distribution") + theme_mb()
+# Software standard
 plot4 <- ggplot(data, aes(x = x)) +
@@
   expand_limits(y = 0) +
-  ggtitle(expression(Student ~ italic(t) * "-distribution"))
+  ggtitle(expression(Student ~ italic(t) * "-distribution")) + theme_mb()
 (plot1 + plot2) / (plot3 + plot4)
@@
 
-```{r rhat, collapse = TRUE, fig.height = 3}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
+```{r rhat, collapse = TRUE}
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
 ```
@@
 
-```{r ess, collapse = TRUE, fig.height = 3}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
+```{r ess, collapse = TRUE}
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
 ```
@@
            )
-)
+) + bayesplot::theme_default()
 m_2 %>% bayesplot::mcmc_pairs(
@@
            )
-)
+) + bayesplot::theme_default()
 ```
@@
 posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) +
-  theme(axis.text.x = element_text(angle = 45))
+  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
 posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) +
-  theme(axis.text.x = element_text(angle = 45))
+  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
 ```
@@
 ```{r autocorrelation}
-posterior1 %>% bayesplot::mcmc_acf(lags = 10)
-posterior2 %>% bayesplot::mcmc_acf(lags = 10)
+posterior1 %>% bayesplot::mcmc_acf(lags = 10) + bayesplot::theme_default()
+posterior2 %>% bayesplot::mcmc_acf(lags = 10) + bayesplot::theme_default()
 ```
@@
 ```{r kernel-density}
-p1 <- bayesplot::ppc_dens_overlay(y, yrep1[1:50, ])
-p2 <- bayesplot::ppc_dens_overlay(y, yrep2[1:50, ])
+p1 <- bayesplot::ppc_dens_overlay(y, yrep1[1:50, ]) + bayesplot::theme_default()
+p2 <- bayesplot::ppc_dens_overlay(y, yrep2[1:50, ]) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth) + bayesplot::theme_default()
 p1 / p2
@@
 ```{r histogram}
-p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001)
-p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001)
+p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
@@
 #### LOO cross-validation (Leave one out)
+
+plot1 \<- plot(loo1)
+
+plot2 \<- plot(loo2)
+
+plot1 / plot2
 
@@
 loo2
-plot1 <- plot(loo1)
-plot2 <- plot(loo2)
-plot1 / plot2
+plot(loo1)
+plot(loo2)
 ```
@@
 ```{r loo-pit}
-p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
-p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
+p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
+p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object)) + bayesplot::theme_default()
 p1 / p2

### 2023-03-02 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

--- 2023-03-01 R/model_check_persistence.Rmd
@@
   facet_grid(~ survey_year_fct) +
-  labs(title = "Exposition")
+  labs(title = "Exposition") + theme_mb()
 plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
@@
 sites %>% group_by(exposition) %>% count(site)
-boxplot(sites$n)
-ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
-ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
-ggplot(sites, aes(x = n)) + geom_density()
+plot1 <- ggplot(sites, aes(y = n)) + geom_boxplot() + theme_mb()
+plot2 <- ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom() + theme_mb()
+plot3 <- ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03) + theme_mb()
+plot4 <- ggplot(sites, aes(x = n)) + geom_density() + theme_mb()
+(plot1 + plot2) / (plot3 + plot4)
 ```
@@
   select(prior, class, coef, group, source)
-ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
+plot1 <- ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
   stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
   expand_limits(y = 0) +
-  ggtitle("Beta distribution for Intercept")
+  ggtitle("Beta distribution for Intercept") + theme_mb()
 data <- data.frame(x = c(-1, 1))
-ggplot(data, aes(x = x)) +
+plot2 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .35)) +
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for treatments")
-ggplot(data, aes(x = x)) +
+  ggtitle("Normal distribution for treatments") + theme_mb()
+# See Lemoine 2019 https://doi.org/10.1111/oik.05985
+plot3 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
-  expand_limits(y = 0) + ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data, aes(x = x)) +
+  expand_limits(y = 0) + ggtitle("Cauchy distribution")  + theme_mb()
+# Software standard
+plot4 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) +
-  ggtitle(expression(Student ~ italic(t) * "-distribution")) # Software standard
+  ggtitle(expression(Student ~ italic(t) * "-distribution"))  + theme_mb()
+(plot1 + plot2) / (plot3 + plot4)
 ```
@@
 
-```{r prior-predictive-check}
+```{r prior-predictive-check, fig.height = 3}
 bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.2) +
-  coord_cartesian(xlim = c(-1, 1))
+  coord_cartesian(xlim = c(-1, 1)) + bayesplot::theme_default()
 ppc_stat_grouped(
-  y, yrep_prior[1:500, ], group = sites$site, binwidth = 0.2
+  y, yrep_prior[1:500, ], group = sites$site, binwidth = 0.5
   ) +
-  coord_cartesian(xlim = c(-1, 1))
+  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ppc_stat_grouped(
@@
   ) + 
-  coord_cartesian(xlim = c(-1, 1))
+  coord_cartesian(xlim = c(-1, 1)) + bayesplot::theme_default()
 ppc_stat_grouped(
@@
   ) +
-  coord_cartesian(xlim = c(-1, 1))
+  coord_cartesian(xlim = c(-1, 1)) + bayesplot::theme_default()
 ppc_stat_grouped(
@@
   ) +
-  coord_cartesian(xlim = c(-1, 1))
+  coord_cartesian(xlim = c(-1, 1)) + bayesplot::theme_default()
 ```
@@
 ```{r rhat, collapse = TRUE}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat()
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
 ```
@@
 ```{r ess, collapse = TRUE}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff()
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
 ```
@@
 ```{r kernel-density}
-p1 <- bayesplot::ppc_dens_overlay(y, yrep1[1:50, ])
-p2 <- bayesplot::ppc_dens_overlay(y, yrep2[1:50, ])
+p1 <- bayesplot::ppc_dens_overlay(y, yrep1[1:50, ]) + bayesplot::theme_default()
+p2 <- bayesplot::ppc_dens_overlay(y, yrep2[1:50, ]) + bayesplot::theme_default()
 p1 / p2
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site) + bayesplot::theme_default()
 p1 / p2
-ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
-ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
-p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density) + bayesplot::theme_default()
+p1 / p2
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio) + bayesplot::theme_default()
+p1 / p2
+p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth) + bayesplot::theme_default()
+p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth) + bayesplot::theme_default()
 p1 / p2
@@
 ```{r histograms}
-p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001)
-p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001)
+p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
-p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
-p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
+p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001) + bayesplot::theme_default()
+p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001) + bayesplot::theme_default()
 p1 / p2
@@
   posterior::summarize_draws() %>%
-  knitr::kable() %>%
-  kableExtra::kable_styling(font_size = 10)
+  knitr::kable()
 emm <- m_1 %>% emmeans(

### 2023-03-02 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

--- 2023-03-01 R/model_check_recovery_check.Rmd
@@
   select(prior, class, coef, group, source)
-ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
+plot1 <- ggplot(data = data.frame(x = c(-2, 0)), aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = -1, sd = 1)) +
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for Intecept")
+  ggtitle("Normal distribution for Intecept") + theme_mb()
 data <- data.frame(x = c(-2, 2))
-ggplot(data, aes(x = x)) +
+plot2 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .8)) +
   expand_limits(y = 0) +
-  ggtitle("Normal distribution for treatments")
-ggplot(data, aes(x = x)) +
+  ggtitle("Normal distribution for treatments") + theme_mb()
+# See Lemoine 2019 https://doi.org/10.1111/oik.05985
+plot3 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
   expand_limits(y = 0) +
-  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
-ggplot(data, aes(x = x)) +
+  ggtitle("Cauchy distribution") + theme_mb()
+# Software standard
+plot4 <- ggplot(data, aes(x = x)) +
   stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
   expand_limits(y = 0) +
-  ggtitle(expression(Student ~ italic(t) * "-distribution")) # Software standard
+  ggtitle(expression(Student ~ italic(t) * "-distribution")) + theme_mb()
+(plot1 + plot2) / (plot3 + plot4)
 ```
@@
 
-```{r prior-predictive-check}
+```{r prior-predictive-check, fig.height = 3}
 bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.5) +
-  coord_cartesian(xlim = c(-4, 4))
+  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ppc_stat_grouped(
@@
   ) +
-  coord_cartesian(xlim = c(-4, 4))
+  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ppc_stat_grouped(
   y, yrep_prior[1:500, ], group = sites$exposition, binwidth = 0.5
-  ) +
-  coord_cartesian(xlim = c(-4, 4))
+  ) +  coord_cartesian(xlim = c(-4, 4)) + bayesplot::theme_default()
 ppc_stat_grouped(

### 2023-03-02 manuscript.Rmd
Update manuscript.Rmd

@@
 For this purpose, the presence of the sown species was monitored for three consecutive years.
-Second, we calculated the Favourable Conservation Status (FCS) which distinguishes characteristic and derived diversity [@Helm.2015].
-Characteristic diversity is created by established species which belong to the habitat-specific species pool.
-In other words, these species are associated with the habitat type of interest, whereas derived species not.
-Third, the recovery was determined by measuring the successional distance to the reference grasslands [@Rydgren.2019].
+Second, we calculated the Favourable Conservation Status (FCS) which distinguishes habitat-characteristic and non-typical derived diversity [@Helm.2015].
+Third, the recovery completeness was determined by measuring the successional distance to the reference grasslands [@Rydgren.2019].
 To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf.
@@
 In total, 274 vascular plant species were detected (Appendix A5).
+The recovery completeness was described by the successional distance which quantifies the distance of a plot to the average reference site in the ordination [*d~jt,0~*, @Rydgren.2019].
 Persistence was derived from the 'species losses' component of the temporal beta-diversity index (TBI; 1 − *B*~sor~) which was calculated by comparing the seed mixtures with the respective species composition of each year using Sørensen dissimilarity [@legendre2019].
-The successional distance quantifies the ordination distance of a plot to the average reference site [*d~jt,0~*, @Rydgren.2019].
+The Favourable Conservation Status (FCS) is the ratio of characteristic and derived diversity, in our case species richness.
+Characteristic diversity consists of species which belong to a habitat-specific species pool and derived diversity consists of all other species.
+The habitat-specific species pool consisted of all sown species and other typical species of mesic and dry grasslands [Appendix A5, @Helm.2015].
 

### 2023-03-02 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
 ```{r rhat, collapse = TRUE}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
 ```
@@
 ```{r ess, collapse = TRUE}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
 ```

### 2023-03-02 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
 ```{r rhat, collapse = TRUE}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank(), axis.ticks.y = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank(), axis.ticks.y = element_blank())
 ```
@@
 ```{r ess, collapse = TRUE}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank(), axis.ticks.y = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank(), axis.ticks.y = element_blank())
 ```

### 2023-03-02 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 ---
-title: "Appendix of Bauer et al. (2023) Dike experiment"
+title: "Appendix of Bauer et al. (2023) bioRxiv"
 author: Markus Bauer*, Jakob Huber, Johannes Kollmann
@@
   font.size = 11,
-  text.align = "center"
+  text.align = "center",
+  padding = 2
   )
@@
 
-All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/ table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.
+All sown seed mixtures can be found on GitHub in the folder 'outputs/tables/ table_a2_seed_mixtures.csv'.
+There, we indicate which species were combined and their respective ratio in the specific seed mixture.
 
@@
 Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
-Indicated is the number of sown plots and the percentage of these plots which were occupied by the respective species.
+Indicated is the number of sown plots and the percentage of these plots which were occupied by the respective species (presence-absence data).
 This means that for each species only the sown plots were included.
@@
     Family = family,
-    "Seeded plots [#]" = total_seeded_2018,
+    "Sown plots [#]" = total_seeded_2018,
     "Establishment rate [%]" = rate_2018,

### 2023-03-02 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

--- 2023-03-02 R/model_check_recovery_check.Rmd
@@
 ```{r rhat, collapse = TRUE}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
 ```
@@
 ```{r ess, collapse = TRUE}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
 ```
@@
 posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) +
-  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
+  bayesplot::theme_default() + theme(axis.text.x = element_text(angle = 45))
 posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) + 
-  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
+  bayesplot::theme_default() + theme(axis.text.x = element_text(angle = 45))
 ```
@@
   geom_point(position = pos, color = "black") +
-  coord_cartesian(xlim = c(-1, .6)) +
+  coord_cartesian(xlim = c(-.9, .9)) +
   bayesplot::theme_default() +

### 2023-03-02 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

@@
 ```{r mcmc-parcoord, collapse = TRUE}
-posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) +
-  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
-posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) +
-  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
+posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) + bayesplot::theme_default() + theme(axis.text.x = element_text(angle = 45))
+posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) + bayesplot::theme_default() + theme(axis.text.x = element_text(angle = 45))
 ```

### 2023-03-02 manuscript.Rmd
Update manuscript.Rmd

@@
 Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt and re-sowing after unfavourable conditions.
-
-\clearpage
-
-\newpage
+\clearpage \newpage
 
@@
 
-## Weak effects of restoration treatments
-
-We could identify a statistically clear positive effect of the sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
-The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
-For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years.
-Both expositions had similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:persistence)).
-The interactions of restoration treatments were neither clear nor strong (Figures \@ref(fig:persistence), \@ref(fig:fcs), \@ref(fig:recovery)).
-Persistence of both seed mixture types was slightly positively affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:persistence)).
-
 ## Hay meadows on north exposition closer to reference
@@
 Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
-Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)).
+Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects)A, \@ref(fig:interactions)A).
 This was especially the case in north exposition (Figure \@ref(fig:nmds)).
+
+## Weak effects of restoration treatments
+
+We could identify a statistically clear positive effect of the sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
+The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:interactions)).
+For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years.
+Both expositions had similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:interactions)B).
+The interactions of restoration treatments were neither clear nor strong (Figures \@ref(fig:interactions)).
+Persistence of both seed mixture types was slightly positively affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:interactions)B).
 \clearpage \newpage
@@
 All in all, it was hardly possible to identify any best seed--substrate combinations, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
+
+## The success of the restoration approaches
+
+The seed mixtures and their positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
+The position on the NMDS suggests that the seed mixture represents a later successional stage than the references.
+The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:interactions)A).
+This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north-exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
+On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using a non-adapted seed mixture.
+
+The vegetation developed generally in the desired direction but was still distinct from positive references and seed mixtures after four years.
+In the south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
+The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
+This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
 
@@
 Furthermore, the non-existence of ideal combinations could be explained by priority effects which means that the species of the imperfect-adapted seed mixture type could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
-
-## The success of the restoration approaches
-
-The seed mixtures and their positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the NMDS suggests that the seed mixture represents a later successional stage than the references.
-The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)).
-This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north-exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
-On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using a non-adapted seed mixture.
-
-The vegetation developed generally in the desired direction but was still distinct from positive references and seed mixtures after four years.
-In the south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
-The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
-This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
 
@@
 
-```{r tab.id = "substrate", ft.align = "left", tab.cap = "Substrates"}
+```{r tab.id = "substrate", ft.align = "left", tab.cap = ""}
 read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
@@
 
-```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years of sown grassland communities at a river dike.
-Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C).
-The FCS is the ratio of target species to non-target species.
-Note that the zero lines indicate that both levels have equal values.
-This means, e.g., that hay meadows are closer to their reference than dry grasslands  (C)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 3 {.unnumbered}
-
-```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence (1-*B*~sor~) of sown species of sown grassland communities at a river dike.
-The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
-Twenty species were sown per plot.
-Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM)."}
-knitr::include_graphics(
-  here::here(
-    "outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff"
-    )
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 4 {.unnumbered}
-
-```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favourable Conservation Status (FCS) of sown grassland communities at a river dike.
-The plots had substrates with different sand admixtures and were sown with two different seed mixtures.
-The zero line indicates that target and non-target species are balanced.
-Positive values indicate that there are more target species.
-Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM)."}
-knitr::include_graphics(
-  here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff")
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 5 {.unnumbered}
-
-```{r fig.id = "recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The recovery or successional distance (*d~jt,0~*) of sown grassland communities at a river dike in comparison to the respective reference sites (mesic hay meadows or semi-dry calcareous grasslands).
-The plots had substrates with different sand admixtures and were sown with two different seed mixtures.
-The zero lines indicate the mean position of the reference sites for each habitat type on the NMDS axis 1 (Figure 7).
-The grey area marks the standard deviation of the position of the reference sites.
-Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM)."}
-knitr::include_graphics(
-  here::here(
-    "outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff"
-    )
-  )
-```
-
-\clearpage
-
-\newpage
-
-## Figure 6 {.unnumbered}
-
 ```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = ""}
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff")
+  here::here("outputs", "figures", "figure_2_nmds_800dpi_16.5x16cm.tiff")
   )
@@
 
+## Figure 3 {.unnumbered}
+
+```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_3_800dpi_16.5x5cm.tiff")
+  )
+```
+
+Effects of treatments on the development of sown grassland communities at a river dike.
+The posterior density distributions (grey) is calculated over all four surveyed years and both expositions.
+Shown are the medians, 66% and 95% credible intervals, which were derived from a Bayesian linear mixed-effects model (BLMM).
+(A) The persistence of sown species, (B) the Favourable Conservation Status (FCS) and (C) the recovery completeness compared to reference sites.
+The FCS is the ratio of target species to non-target species.
+Note that the zero lines indicate that both levels have equal values.
+This means, e.g., that hay meadows are closer to their reference than dry grasslands (C).
+
+\clearpage
+
+\newpage
+
+## Figure 4 {.unnumbered}
+
+```{r fig.id = "interactions", fig.asp = 1.2121, fig.width = 6.49, fig.cap = ""}
+knitr::include_graphics(
+  here::here("outputs", "figures", "figure_4_800dpi_16.5x20cm.tiff")
+  )
+```
+
+The development sown grassland communities at a river dike.
+The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
+Three indices are evaluated.
+(A) Recovery completeness (*d~jt~*~,0~): the zero lines indicate the mean position of the reference sites for each habitat type on the NMDS axis 1 (Figure \@ref(fig:nmds)).
+The grey area marks the standard deviation of the position of the reference sites.
+(B) Persistence of sown species: losses component of the temporal beta-diversity index (1 − *B*~sor~) (C) Favourable Conservation Status (FCS): the zero line indicates that target and non-target species are balanced.
+Positive values indicate that there are more target species.
+Shown are the medians and 95% credible intervals of the posterior distributions, which were derived from a Bayesian linear mixed-effects model (BLMM).
+
+\clearpage
+
+\newpage
+
 # Session Info

### 2023-03-02 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

@@
 ```{r rhat, collapse = TRUE}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank()) + axis.ticks.y = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank()) + axis.ticks.y = element_blank())
 ```
@@
 ```{r ess, collapse = TRUE}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank()) + axis.ticks.y = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank()) + axis.ticks.y = element_blank())
 ```

### 2023-03-03 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

@@
            )
-) + bayesplot::theme_default()
+)
 m_2 %>% bayesplot::mcmc_pairs(
@@
            )
-) + bayesplot::theme_default()
+)
 ```
@@
 #### LOO cross-validation (Leave one out)
-
-plot1 \<- plot(loo1)
-
-plot2 \<- plot(loo2)
-
-plot1 / plot2
 
@@
   geom_point(position = pos, color = "black") +
-  coord_cartesian(xlim = c(-1, 1)) +
+  coord_cartesian(xlim = c(-.65, 1)) +
   bayesplot::theme_default() +

### 2023-03-06 manuscript.Rmd
Update manuscript.Rmd

@@
 A factorial field experiment addressed this topic on a dike at the Danube River in SE Germany in the 2018--2021 time period.
-On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixture types (mesic hay meadow, semi-dry calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favourable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
-3.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
-4.
+On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixture types (mesic hay meadow, semi-dry calcareous grassland) in north or south exposition, and measured the recovery completeness by calculating the successional distance to reference sites, the persistence of sown species, and the Favourable Conservation Status (FCS) of target species in general.
+3.
 Overall, the sown vegetation developed in the desired direction, but a recovery debt remained after four years, and some plots still showed similarities to negative references from ruderal sites.
 In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry grasslands.
-5.
-In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment and the addition and removal of a geotextile.
-This initial negative effect remained over the entire observation period.
+4.  In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment. This initial negative effect remained over the entire observation period.
+5.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
 6.
-Synthesis and applications: Site-adapted seed mixtures make restoration more efficient.
+Synthesis and applications: Site-adapted seed mixtures can make restoration more efficient.
 However, applying several seed--substrate combinations might foster beta diversity.
-Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt and re-sowing after unfavourable conditions.
+Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt, as well as re-sowing after unfavourable conditions.
 \clearpage \newpage
@@
 
-Community assembly
-
 Dry grasslands
@@
 Ecological restoration
-
-Favourable Conservation Status
 
@@
 River embankment
-
-Soil restoration
 
@@
 
-To measure the success of restoration, we chose three indices.
-First, we observed the persistence of the sown species, which is a key objective of the restoration measure sowing [@Wilsey.2021].
+The success of restoration or the difference from desired conditions was evaluated [cf.
+@Brudvig.2017b] by comparing the species composition of the experimental plots with reference sites.
+The successional distance to the reference grasslands determined the recovery completeness [@Rydgren.2019].
+Furthermore, we observed the persistence of the sown species, which is a key objective of the restoration measure sowing [@Wilsey.2021].
 For this purpose, the presence of the sown species was monitored for three consecutive years.
-Second, we calculated the Favourable Conservation Status (FCS) which distinguishes habitat-characteristic and non-typical derived diversity [@Helm.2015].
-Third, the recovery completeness was determined by measuring the successional distance to the reference grasslands [@Rydgren.2019].
-To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf.
-@Brudvig.2017b].
-This was reached by comparing the species composition of the experimental plots with reference sites.
+Finally, the Favourable Conservation Status (FCS) was calculated which distinguishes habitat-characteristic and non-typical derived diversity [@Helm.2015].
 We tested following hypotheses after four years of observation:
@@
 
-2.  Nutrient reduction (by sand addition) and shallow soil increase establishment of dry grassland compared to mesic mixtures.
+2.  Nutrient reduction by sand addition and shallow substrates increase the establishment of dry-grassland compared to mesic seed mixtures.
 
-3.  Reduced soil resources benefit especially target species in comparison to non-target species(, thus increasing conservation value).
+3.  Reduced soil resources benefit especially target species in comparison to non-target species.
 
-4.  Higher seed density increases generally establishment of sown plants and suppresses non-target species.
+4.  Higher seed density increases the establishment of sown plants and suppresses non-target species.
 
@@
 
+A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
+Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
+Finally, 343 species were included in the ordination.
+
 To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed-effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
@@
 Finally, the models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].
-A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
-Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
-Finally, 343 species were included in the ordination.
 
@@
 The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to the experiment in a quarry [@chenot-lescure2022].
-Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@baer2004].
-Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010].
+Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
+Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a substrate depth of lower 15 cm since most of the roots are in this soil layer [@vannoppen2016].
 Seed density had also no clear effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.

### 2023-03-06 R/model_check_recovery.Rmd
Create model_check_recovery.Rmd

--- 2023-03-02 R/model_check_recovery_check.Rmd
@@
 ```{r rhat, collapse = TRUE}
-m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
-m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
+m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
 ```
@@
 ```{r ess, collapse = TRUE}
-m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
-m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
+m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
 ```
@@
 ```{r loo}
-# Leave-one-out cross validation based on posterior likelihood
 loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)

### 2023-03-06 manuscript.Rmd
Update manuscript.Rmd

@@
 We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deep substrates.
-Furthermore for slopes, higher seed densities are recommended for a succesfull establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
+Furthermore for slopes, higher seed densities are recommended for a successful establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
 

### 2023-03-07 manuscript.Rmd
Update manuscript.Rmd

@@
 1.
-Sowing is a well-established restoration technique to overcome dispersal limitation and site-specific seed mixtures are most effective to achieve functional communities.
+Sowing is a well-established restoration technique to overcome dispersal limitation.
+Site-specific seed mixtures are most effective to achieve functional communities.
 This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes.
-Here, an improved seed--substrate combination will secure slope stability, reduce mowing efforts, and generate biodiverse grasslands.
+Here, an improved seed--substrate combination will secure slope stability, reduce mowing efforts, and generate species-rich grasslands.
 2.
@@
 
-Hay meadow
-
 Levee
@@
 Species composition
-
-Species-rich grassland
 
@@
 Restoration ecology can increase the predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally strengthen evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b], and habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
+Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b].
+Hhabitat and biotic filtering are the main assembly factors which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
@@
 The aim of this study is to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
-An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types.
+An experiment was set up to test different substrate depths, sand admixtures, seed densities, and mixture types.
 We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deep substrates.
-Furthermore for slopes, higher seed densities are recommended for a successful establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
+For slopes, higher seed densities are recommended for a successful establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
 
@@
 The successional distance to the reference grasslands determined the recovery completeness [@Rydgren.2019].
-Furthermore, we observed the persistence of the sown species, which is a key objective of the restoration measure sowing [@Wilsey.2021].
-For this purpose, the presence of the sown species was monitored for three consecutive years.
-Finally, the Favourable Conservation Status (FCS) was calculated which distinguishes habitat-characteristic and non-typical derived diversity [@Helm.2015].
+Furthermore, we observed the persistence which is the presence of the sown species monitored over three consecutive years [@Wilsey.2021].
+Finally, the Favourable Conservation Status (FCS) was calculated which distinguishes habitat-characteristic diversity and non-typical derived diversity [@Helm.2015].
 We tested following hypotheses after four years of observation:
@@
 
-3.  Reduced soil resources benefit especially target species in comparison to non-target species.
+3.  Reduced soil resources benefit especially target species of species-rich grasslands.
 

### 2023-03-08 manuscript.Rmd
Update manuscript.Rmd

@@
 title: "Fit by design: Developing substrate-specific seed mixtures for functional dike grasslands"
-author: Markus Bauer*, Jakob Huber, Johannes Kollmann
+author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
 output:
@@
 6.
-Synthesis and applications: Site-adapted seed mixtures can make restoration more efficient.
+Synthesis and applications: Site-adapted seed mixtures can make restoration more effective.
 However, applying several seed--substrate combinations might foster beta diversity.
@@
 
-Restoration ecology can increase the predictability of restoration approaches [@Suding.2011; @Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally strengthen evidence-based restoration [@Cooke.2018; @Wainwright.2018].
+Restoration ecology can increase the predictability of restoration approaches [@Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally strengthen evidence-based restoration [@Cooke.2018; @Wainwright.2018].
 Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b].
@@
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
-Suitable substrates should reduce habitat filtering, while the seed mixture should minimize the competitive exclusion of unsuitable species.
+Suitable substrates should reduce habitat filtering, while the seed mixture should minimise the competitive exclusion of unsuitable species.
 Modifying seed mixtures to match specific site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
@@
 Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
-Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterize dikes [@Batori.2016; @berendse2015; @husicka2003].
+Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterise dikes [@Batori.2016; @berendse2015; @husicka2003].
 Dikes can reconcile several ecosystem functions like dike security with biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
@@
 The climate of the region is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], as well as three minor floods which did not reach the plots [Appendix A1, @lfu2021waterlevel; @lfu2021discharge].
+During the study, three exceptionally dry years (2018--2020) occurred [Appendix A1, @hari2020], as well as three minor floods which did not reach the plots (Appendix A1).
 The substrates consisted of calcareous sand (0--4 mm) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
@@
 
-The target vegetation types were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist, codes CM01A, DA01B, @mucina2016].
+The target vegetation types were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes: R22, R1A, @Chytry.2020; Arrhenatherion elatioris and Cirsio-Brachypodion pinnati according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
 The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
@@
 Each mixture contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
-The community-weighted means (CWM) of functional traits differed between the seed mixture types (Appendix A3).
-As expected, the hay-meadow mixtures had a higher specific leaf area (SLA), lower seed mass, and higher canopy height than the dry-grassland mixtures.
+The hay-meadow mixtures had higher community-weighted means (CWM) for specific leaf area (SLA), lower for seed mass, and higher for canopy height than the dry-grassland mixtures (Appendix A3).
 The south-exposed plots were sown in mid-April 2018 and the north exposition 14 days later.
 Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects for the seedlings.
-The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
+The management started with a cut at 20 cm height without hay removal in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
 In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
@@
 We used 288 plots of the size 2.0 m × 3.0 m, vertically oriented, halfway up the dike slopes, distributed over the north and south exposition, and arranged in six blocks (= replicates).
-The experiment used a split-plot design combined with a randomized complete block design (Figure \@ref(fig:map)).
+The experiment used a split-plot design combined with a randomised complete block design (Figure \@ref(fig:map)).
 The split plot was created by the two expositions of the dike, where all 24 treatment combinations were tested, i.e., sand admixtures (0, 25, and 50%), soil depths (15 vs.
-30 cm), and the two seed mixture types with the normal seed density and an increased density recommended for slopes [4 vs.
+30 cm), and the two seed mixture types with the normal seed density and an increased density [4 vs.
 8 g m^-2^, @Kiehl.2010; @KleberLerchbaumer.2017].
 
-Under the substrate, a 5 cm thick drainage layer of gravel (0-16 mm) was installed.
+Under the substrate, a 5 cm thick drainage layer of gravel (0--16 mm) was installed.
 Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots.
@@
 The establishment rates of species are recorded in Appendix A4.
-In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [@hedberg2010].
+In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [cf.
+@hedberg2010].
 The species established in 31 ± 22% (mean ± SD) of their sown plots.
 In total, 274 vascular plant species were detected (Appendix A5).
-The recovery completeness was described by the successional distance which quantifies the distance of a plot to the average reference site in the ordination [*d~jt,0~*, @Rydgren.2019].
+The recovery completeness was described by the successional distance which quantifies the distance of a plot to the average reference site in the ordination [*d~jt,0~*, @Rydgren.2019, Figure \@ref(fig:nmds)].
 Persistence was derived from the 'species losses' component of the temporal beta-diversity index (TBI; 1 − *B*~sor~) which was calculated by comparing the seed mixtures with the respective species composition of each year using Sørensen dissimilarity [@legendre2019].
-The Favourable Conservation Status (FCS) is the ratio of characteristic and derived diversity, in our case species richness.
+The Favourable Conservation Status (FCS) is the ratio of characteristic and derived diversity measured as species richness [@Helm.2015].
 Characteristic diversity consists of species which belong to a habitat-specific species pool and derived diversity consists of all other species.
-The habitat-specific species pool consisted of all sown species and other typical species of mesic and dry grasslands [Appendix A5, @Helm.2015].
+The habitat-specific species pool consisted of all sown species and other typical species of mesic and dry grasslands (Appendix A5).
 
-Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
-We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included also lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
+To compare the restoration outcomes with real references and not solely with seed mixtures, vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
+We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included also hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
 
@@
 
-A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualize variation in species composition in space and time (2D-stress 0.21).
+A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualise variation in species composition in space and time.
 Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
@@
 For the computation, we used four chains, a thinning rate of two, 5,000 iterations for warm-up, and 10,000 in total.
-We used the Markov Chain Monte Carlo method (MCMC) with the no-U-turn Sampler (NUTS), which is based on the Hamiltonian Monte Carlo approach (HMC).
-For evaluating the computation, the convergence of the four chains was checked using trace plots and evaluating R-hat values, and MCMC chain resolution by the effective sampling size (ESS).
+We used the Markov Chain Monte Carlo method (MCMC) with the no-U-turn Sampler (NUTS).
+For evaluating the computation, the convergence of the four chains was checked using trace plots and evaluating *R*-hat values, and MCMC chain resolution by the effective sampling size (ESS).
 Posterior predictive checks were done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019].
@@
 
-The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
+The ordination visualises the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
 The NMDS confirmed that the seed mixtures were variable, but distinctive for hay meadows and dry grasslands and ascertained the intended direction of the vegetation development.
@@
 Both expositions had similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:interactions)B).
-The interactions of restoration treatments were neither clear nor strong (Figures \@ref(fig:interactions)).
+The interactions of restoration treatments were neither clear nor strong.
 Persistence of both seed mixture types was slightly positively affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:interactions)B).
@@
 
-The vegetation of the dike experiment developed in the desired direction, but with a decelerating recovery rate.
-A significantly worse effect during establishment phase remained over the complete observation period in south compared to north exposition.
-All in all, it was hardly possible to identify any best seed--substrate combinations, although the hay meadows developed closer to their reference on the north exposition than the dry grasslands.
-
 ## The success of the restoration approaches
@@
 The seed mixtures and their positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the NMDS suggests that the seed mixture represents a later successional stage than the references.
+The position on the ordination suggests that the seed mixture represents a later successional stage than the references.
 The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:interactions)A).
 This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north-exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
-On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using a non-adapted seed mixture.
+On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an ineffective restoration by using a non-adapted seed mixture.
 
@@
 Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
-Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a substrate depth of lower 15 cm since most of the roots are in this soil layer [@vannoppen2016].
+Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a substrate depth of lower 15 cm since most of the roots are in this soil layer on dikes [@vannoppen2016].
 Seed density had also no clear effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
@@
 This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020].
-This drought could have decreased germination and the establishment of sown species, also generally speaking, because a moist spring with a mesic temperature enhances establishment [@Larson.2021; @orrock2023].
-The interesting point here is the lasting negative effect on persistence and FCS on the southern slope which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
+This drought could have also decreased germination and the establishment of sown species, because a moist spring with a mesic temperature enhances establishment [@Larson.2021; @orrock2023].
+The lasting negative effect on persistence and FCS on the southern slope suggests a legacy or year effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
 The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing.
@@
 
-Our results suggest that adapted seed mixtures can increase restoration efficiency by sowing hay meadows in the north but not necessarily in the south exposition of dikes.
+Our results suggest that adapted seed mixtures can increase restoration effectiveness by sowing hay meadows in the north but not necessarily in the south exposition of dikes.
 Furthermore, the reduction of the nutrient load through sand admixture has a clearly positive effect, albeit the effect is small.
@@
 All in all, our results support the finding that restored dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
-However, the recovery debt highlights the fact that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020; @Buisson.2022].
+However, the recovery debt highlights the fact that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020].
 
@@
 
-```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of twenty species with some restrictions to the number of species per functional group.
+Each plot received an individual set of twenty species with some restrictions to the number of species per functional group.
 The total species pool for hay meadows was 55 and for dry grassland 58.
-In total, plots received 16 or 32 g of seeds.
-All individual seed mixtures are stored in Appendix A2."}
+All individual seed mixtures are stored in Appendix A2.
+
+```{r tab.id = "seedmix", ft.align = "left", tab.cap = ""}
 read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
@@
 Characteristics of the substrates used for the sowing experiment on river dikes.
-Soil samples of the three substrates were analyzed for the fraction \< 2 mm.
+Soil samples of the three substrates were analysed for the fraction \< 2 mm.
 The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
@@
 
-Local setting and design of the multifactorial experiment on grassland sowing at dikes.
+Local setting and design of the multifactorial experiment on grassland sowing on dikes.
 The experiment was located on a dike at the Danube River in SE Germany.
@@
 Shown are the medians, 66% and 95% credible intervals, which were derived from a Bayesian linear mixed-effects model (BLMM).
-(A) The persistence of sown species, (B) the Favourable Conservation Status (FCS) and (C) the recovery completeness compared to reference sites.
+Shown are (A) the recovery completeness compared to reference sites, (B) the persistence of sown species, and (C) the Favourable Conservation Status (FCS).
 The FCS is the ratio of target species to non-target species.
 Note that the zero lines indicate that both levels have equal values.
-This means, e.g., that hay meadows are closer to their reference than dry grasslands (C).
+This means, e.g., that hay meadows are closer to their reference than dry grasslands (A).
 
@@
 
-The development sown grassland communities at a river dike.
+The development of grassland communities at a river dike over four years after sowing.
 The plots had substrates with different sand admixtures and were sown with two different seed mixture types.
@@
 (A) Recovery completeness (*d~jt~*~,0~): the zero lines indicate the mean position of the reference sites for each habitat type on the NMDS axis 1 (Figure \@ref(fig:nmds)).
-The grey area marks the standard deviation of the position of the reference sites.
-(B) Persistence of sown species: losses component of the temporal beta-diversity index (1 − *B*~sor~) (C) Favourable Conservation Status (FCS): the zero line indicates that target and non-target species are balanced.
+The grey area marks the standard deviation of the position of the reference sites (Figure \@ref(fig:nmds)).
+(B) Persistence of sown species: losses component of the temporal beta-diversity index (1 − *B*~sor~).
+(C) Favourable Conservation Status (FCS): the zero line indicates that target and non-target species are balanced.
 Positive values indicate that there are more target species.

### 2023-03-08 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 title: "Appendix of Bauer et al. (2023) bioRxiv"
-author: Markus Bauer*, Jakob Huber, Johannes Kollmann
+author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
 output:
@@
 \* Corresponding author: [markus1.bauer\@tum.de](mailto:markus1.bauer@tum.de), ORCiD <https://orcid.org/0000-0001-5372-4174>
-
-<!--# Replace "Dike experiment" in the title -->
 
@@
 Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010, ID: 3271, WGS84: lat/lon, 48.85476, 12.918911, @cdc2022temp; @cdc2022prec] and stream gauge Pfelling [ID: 10078000, WGS84: lat/lon, 48.87975, 12.74716, @lfu2021discharge].
-HQ2 = Highest discharge with a probability of occurrence every second year.
-HSW = Highest water level for shipping.
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010, ID: 3271, WGS84: lat/lon, 48.85476, 12.918911, @cdc2022temp; @cdc2022prec], stream gauge Pfelling [ID: 10078000, WGS84: lat/lon, 48.87975, 12.74716, @lfu2021discharge], and water level Deggendorf [ID: 10081004, UTM32: northing/easting,
+5415586, 790796<!--# Make WGS-->, @lfu2021waterlevel]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.
 
@@
 All sown seed mixtures can be found on GitHub in the folder 'outputs/tables/ table_a2_seed_mixtures.csv'.
-There, we indicate which species were combined and their respective ratio in the specific seed mixture.
+<!--# Cite Zenodo--> There, we indicate which species were combined and their respective ratio in the specific seed mixture.
+
+For both target vegetation types, a respective initial plant species collection was assembled. The two lists contained the following groups:
+
+-   Character species of the corresponding phytosociological units (Arrhenatherion and Mesobromion, as listed in standard literature) and of FFH-habitat types 6510 and 6210 as described for Bavaria
+
+-   Typical species of corresponding habitat types according to official directives for biotope mapping in Bavaria
+
+-   Species consistently occurring in our own vegetation records on existing river dikes of the region, conducted in 2017, and in species-rich grasslands, recorded within a wide-range habitat documentation project in the Danube valley near Straubing and Deggendorf from 2011.
+This project had been commissioned as planning grounds for state flood protection programs.
+
+The two species pools were derived from this collection by removing the following groups:
+
+-   Very rare and/or regionally absent species
+
+-   Woody shrubs, which were excluded from dike vegetation guidelines in Germany because of vortex erosion phenomena around their rooting system
+
+-   Nitrogen indicators
+
+-   Neophytic and/or invasive species or species with rapid clonal propagation with a high potential of forming mono-dominant stands
+
+-   Species of strong ruderal character
+
+-   Ephemeral/annual species
+
+-   Species, for which no seeds were available in the market or which are difficult to establish by propagule application, e.g., *Carex* spec. or cryptogams
+
+-   Taxonomically and functionally closely related and similar species
+
+For constructing concrete seed mixtures of 20 pant species, a pre-defined number of species within certain functional groups was selected randomly.
+This way, seed mixtures consisted of three tall grasses, four small grasses, three legumes, one hemiparasite (*Rhinanthus* spec.) and nine herbal perennials, three of which listed as character species in the literature.
+The actual choice was conducted in a manner, so that each individual species was assigned to each block and each treatment level combination with a near-constant frequency.
+Furthermore, all species of each functional group were chosen almost the same number of times.
+In total, plots received 24 or 48 g of seeds (4 vs.
+8 g m^-2^).
+
+\clearpage
+
+\newpage
 
@@
 
-The community-weighted means (CWM) of the seed mixtures used for the dike experiment: specific leaf area (SLA), seed mass and canopy height.
+The community-weighted means (CWM) of the seed mixtures used for the dike experiment are based on abundance data: specific leaf area (SLA), seed mass and canopy height.
 The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target habitat types hay meadows and calcareous grasslands.
@@
 TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
-\clearpage \newpage
+
+\clearpage
+
+\newpage
 

### 2023-03-09 manuscript.Rmd
Update manuscript.Rmd

@@
 2.
-A factorial field experiment addressed this topic on a dike at the Danube River in SE Germany in the 2018--2021 time period.
-On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixture types (mesic hay meadow, semi-dry calcareous grassland) in north or south exposition, and measured the recovery completeness by calculating the successional distance to reference sites, the persistence of sown species, and the Favourable Conservation Status (FCS) of target species in general.
+A factorial field experiment addressed this topic on a dike at River Danube in SE Germany in 2018--2021.
+Within 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixture types (mesic hay meadow, semi-dry calcareous grassland) in north and south exposition, and measured the recovery completeness by calculating the successional distance to reference sites, the persistence of sown species, and the Favourable Conservation Status (FCS) of target species.
 3.
 Overall, the sown vegetation developed in the desired direction, but a recovery debt remained after four years, and some plots still showed similarities to negative references from ruderal sites.
-In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry grasslands.
+In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry-grassland mixtures.
 4.  In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment. This initial negative effect remained over the entire observation period.
@@
 6.
-Synthesis and applications: Site-adapted seed mixtures can make restoration more effective.
+Synthesis and applications: Site-adapted seed mixtures make restoration more effective.
 However, applying several seed--substrate combinations might foster beta diversity.
@@
 Restoration is seen as a key factor to sustain biodiversity and ecosystem services [@COP.2014; @UnitedNations.2019b], and sowing is a well-established approach to establish species-rich grasslands [@Kiehl.2010].
-Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome the dispersal filters [@myers2009; @orrock2023].
+Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome dispersal filters [@myers2009; @orrock2023].
 However, there are still open questions about adjusting seed mixtures to specific site conditions and future climate conditions [@Torok.2021].
@@
 Restoration ecology can increase the predictability of restoration approaches [@Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally strengthen evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b].
-Hhabitat and biotic filtering are the main assembly factors which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
+Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b], while habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
-Suitable substrates should reduce habitat filtering, while the seed mixture should minimise the competitive exclusion of unsuitable species.
-Modifying seed mixtures to match specific site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
-This challenge is particularly interesting on artificial substrates that are used in urban areas [@Bauer.2022], quarries [@chenot-lescure2022], or on dikes [@Liebrand.1996].
+Suitable substrates reduce habitat filtering of the seeded species, while specific seed mixture minimises competitive exclusion of desired species and simultaneously prohibiting invasive species [@Funk.2008].
+Modifying seed mixtures to match the site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
+This challenge is particularly interesting for artificial substrates that are used in urban areas [@Bauer.2022], in quarries [@chenot-lescure2022], or on dikes [@Liebrand.1996].
 
 Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
-Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterise dikes [@Batori.2016; @berendse2015; @husicka2003].
-Dikes can reconcile several ecosystem functions like dike security with biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
+Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterise these habitats [@Batori.2016; @berendse2015; @husicka2003].
+Dikes can reconcile several ecosystem functions including both flood security and rich biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
 
@@
 An experiment was set up to test different substrate depths, sand admixtures, seed densities, and mixture types.
-We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deep substrates.
-For slopes, higher seed densities are recommended for a successful establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
+We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deeper substrates.
+For steep slopes, e.g., on dikes, high seed densities are recommended for successful vegetation establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
 
-The success of restoration or the difference from desired conditions was evaluated [cf.
-@Brudvig.2017b] by comparing the species composition of the experimental plots with reference sites.
-The successional distance to the reference grasslands determined the recovery completeness [@Rydgren.2019].
-Furthermore, we observed the persistence which is the presence of the sown species monitored over three consecutive years [@Wilsey.2021].
+The success of restoration, i.e., the difference from desired conditions, is evaluated by comparing the species composition with reference sites [cf.
+@Brudvig.2017b], since the successional distance to reference grasslands describes the recovery completeness [@Rydgren.2019].
+Furthermore, we observed the persistence, which is the presence of the sown species monitored over three consecutive years [@Wilsey.2021].
 Finally, the Favourable Conservation Status (FCS) was calculated which distinguishes habitat-characteristic diversity and non-typical derived diversity [@Helm.2015].
-We tested following hypotheses after four years of observation:
+Based on four years of monitoring, we tested the following hypotheses:
 
-1.  Establishment of mesic vs dry grassland mixtures is facilitated by site conditions on northern and southern dike slopes, respectively.
+1.  Site conditions on northern vs southern dike slopes facilitate establishment of mesic or dry grassland mixtures, respectively.
 
@@
 
-3.  Reduced soil resources benefit especially target species of species-rich grasslands.
+3.  Reduced soil resources benefit target species of species-rich grasslands.
 
-4.  Higher seed density increases the establishment of sown plants and suppresses non-target species.
+4.  High seed densities increase the establishment of sown plants and suppress non-target species.
 
@@
 
-# Materials & Methods
+# Materials and methods
 
-## Experimental design {.unnumbered}
+## Field experimental design {.unnumbered}
 
-The combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at the Danube River in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84 (lat/lon), 48.83895, 12.88412).
+Specific combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at the Danube River in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84: lat/lon, 48.83895/12.88412).
 The climate of the region is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
-During the study, three exceptionally dry years (2018--2020) occurred [Appendix A1, @hari2020], as well as three minor floods which did not reach the plots (Appendix A1).
+During the study, three exceptionally dry years (2018--2020) occurred [Appendix A1, @hari2020], as well as three minor floods, which, though, did not reach the plots (Appendix A1).
 The substrates consisted of calcareous sand (0--4 mm) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
@@
 From these species pools, 20 species were selected for each plot in a stratified, randomised manner (Appendix A2).
-Each mixture contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
+Each mixture contained seven grasses (60wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
 The hay-meadow mixtures had higher community-weighted means (CWM) for specific leaf area (SLA), lower for seed mass, and higher for canopy height than the dry-grassland mixtures (Appendix A3).
 The south-exposed plots were sown in mid-April 2018 and the north exposition 14 days later.
-Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects for the seedlings.
+In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
+In late-April 2018 due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects on seedling emergence.
 The management started with a cut at 20 cm height without hay removal in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
-In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.
 
-We used 288 plots of the size 2.0 m × 3.0 m, vertically oriented, halfway up the dike slopes, distributed over the north and south exposition, and arranged in six blocks (= replicates).
+We used 288 plots of the size 2.0 m × 3.0 m, vertically oriented, halfway up the dike slopes, distributed over the north and south exposition, and arranged in six blocks (=replicates).
 The experiment used a split-plot design combined with a randomised complete block design (Figure \@ref(fig:map)).
 The split plot was created by the two expositions of the dike, where all 24 treatment combinations were tested, i.e., sand admixtures (0, 25, and 50%), soil depths (15 vs.
-30 cm), and the two seed mixture types with the normal seed density and an increased density [4 vs.
-8 g m^-2^, @Kiehl.2010; @KleberLerchbaumer.2017].
+30 cm), the two seed mixture types, and two seed densities [4 vs.
+8 g m^-2^, cf.
+@Kiehl.2010; @KleberLerchbaumer.2017].
 
-Under the substrate, a 5 cm thick drainage layer of gravel (0--16 mm) was installed.
-Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots.
-The sand admixture changed the soil texture, increased the C/N ratio, reduced calcium carbonate, but did hardly change the pH which were within the weak alkaline range (Table \@ref(tab:substrate)).
-The pH corresponded to a well-established dike vegetation on the Rhine River [@husicka2003], phosphate and potassium were rather scarce for agricultural soils, but magnesium showed high concentrations [@lfl2022].
+Below the substrate, a 5-cm thick drainage layer of gravel (0--16 mm) was installed.
+Soil samples of the three substrates from both expositions were tested by mixing several sub-samples from different plots.
+The sand admixture changed the soil texture, increased the C/N ratio, reduced calcium carbonate, but did hardly change the pH which was within the weak alkaline range (Table \@ref(tab:substrate)).
+The pH corresponded to a well-established dike vegetation on River Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils, but magnesium showed high concentrations [@lfl2022].
+
+## Vegetation surveys
+
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and the Londo scale was used [@londo1976].
-The establishment rates of species are recorded in Appendix A4.
-In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [cf.
-@hedberg2010].
-The species established in 31 ± 22% (mean ± SD) of their sown plots.
-In total, 274 vascular plant species were detected (Appendix A5).
+The establishment rates of species were recorded in Appendix A4.
+Establishment success was high with 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands recorded by 2021, which are rather good ratios [cf.
+@hedberg2010]; the species established in 31 ± 22% (mean ± SD) of their sown plots.
+In total, 274 vascular plant species were found (Appendix A5).
+
 The recovery completeness was described by the successional distance which quantifies the distance of a plot to the average reference site in the ordination [*d~jt,0~*, @Rydgren.2019, Figure \@ref(fig:nmds)].
@@
 The Favourable Conservation Status (FCS) is the ratio of characteristic and derived diversity measured as species richness [@Helm.2015].
-Characteristic diversity consists of species which belong to a habitat-specific species pool and derived diversity consists of all other species.
+Characteristic diversity consists of species that belong to a habitat-specific species pool and derived diversity consists of all other species.
 The habitat-specific species pool consisted of all sown species and other typical species of mesic and dry grasslands (Appendix A5).
@@
 To compare the restoration outcomes with real references and not solely with seed mixtures, vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
-We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included also hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
+We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey, which included also hay meadows (R22), and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
 
-## Statistical analyses {.unnumbered}
+## Statistical analysis {.unnumbered}
 
 A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualise variation in species composition in space and time.
-Seven species were excluded because they had an accumulated cover over all plots of less than 0.5%.
+Seven species were excluded because they had an accumulated cover over all plots of\<0.5%.
 Finally, 343 species were included in the ordination.
@@
 To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed-effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019].
-Furthermore, we included as a fixed effect the botanists recording a certain plot.
+Furthermore, we included as a fixed effect the botanists, who recorded a certain plot.
 For the simple effects of the treatments, we chose plausible weakly informative priors.
 To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
+
 For the computation, we used four chains, a thinning rate of two, 5,000 iterations for warm-up, and 10,000 in total.
@@
 
-Data, code and the entire model specifications and evaluations are stored on GitHub and presented in an easily accessible document for scrolling through `r word_spec("(include Zenodo reference)")`.<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
-All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
+Data, code and the entire model specifications and evaluations are stored on GitHub and presented in an easily accessible document for scrolling through.<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+All analyses were performed in R [Version 4.2.2, @base], with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
 
@@
 
-The ordination visualises the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:nmds)).
-The NMDS confirmed that the seed mixtures were variable, but distinctive for hay meadows and dry grasslands and ascertained the intended direction of the vegetation development.
+The ordination showed the species composition of seed mixtures and the development of the plots during four years (Figure \@ref(fig:nmds)).
+The NMDS confirmed that the seed mixtures were variable, albeit distinctive for hay meadows and dry grasslands and confirming the intended direction of the vegetation development.
 As one exception, hay meadows in south exposition did not develop towards their seed-mixture compositions.
@@
 The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped (Figure \@ref(fig:nmds)).
-The positions of the reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states.
+The positions of the reference sites shifted to the left in comparison to the seed mixtures, which means in the direction of early-successional stages.
 Nonetheless, they still differed from the negative references of ruderal vegetation.
 Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
-Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects)A, \@ref(fig:interactions)A).
+Hay meadow-seed mixtures led to a closer development to hay-meadow references than dry grasslands to their references (Figure \@ref(fig:effects)A, \@ref(fig:interactions)A).
 This was especially the case in north exposition (Figure \@ref(fig:nmds)).
 
-## Weak effects of restoration treatments
+## Weak effects of substrates and seed density
 
-We could identify a statistically clear positive effect of the sand admixture on the persistence of sown species and on the recovery rate (Figure \@ref(fig:effects)).
+We could identify a statistically clear positive effect of the sand admixture on the persistence of sown species and on the recovery rate, but no effects of seed density or substrate depth (Figure \@ref(fig:effects)).
 The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:interactions)).
-For all three response variables, the vegetation developed strongly positive after one year, but the recovery rate slowed down in the following years.
-Both expositions had similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:interactions)B).
+For all three response variables, the vegetation developed positively after one year, while the recovery rate slowed down in the following years.
+Both expositions revealed similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:interactions)B).
 The interactions of restoration treatments were neither clear nor strong.
-Persistence of both seed mixture types was slightly positively affected by sand admixture on the north exposition (+ 6--7 ± 4%, Figure \@ref(fig:interactions)B).
+Persistence of both seed mixture types was slightly positively affected by sand admixture in north exposition (+ 6--7 ± 4%, Figure \@ref(fig:interactions)B).
 \clearpage \newpage
@@
 
-## The success of the restoration approaches
+## Success of the restoration approaches
 
 The seed mixtures and their positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)).
-The position on the ordination suggests that the seed mixture represents a later successional stage than the references.
+The position on the ordination suggests that the seed mixture represents a late-successional stage compared to the references.
 The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:interactions)A).
-This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north-exposed dike slopes [@Batori.2020; @Oberdorfer.1993].
-On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an ineffective restoration by using a non-adapted seed mixture.
+This can be expected from the requirements of hay meadows for mesic conditions, which can be provided on north-exposed dike slopes [@Oberdorfer.1993; @Batori.2020].
+In southern exposition, the plots of hay meadows developed rather towards dry grassland references which indicates an ineffective restoration due to a non-adapted seed mixture.
 
 The vegetation developed generally in the desired direction but was still distinct from positive references and seed mixtures after four years.
-In the south exposition, the plots were rather similar to the negative reference of dry, ruderal vegetation.
-The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural references [@Batori.2016].
+In the south exposition, the plots were rather similar to the negative reference of dry ruderal vegetation.
+The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural reference grassland [@Batori.2016].
 This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
@@
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
-Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while a 50% admixture did not further increase the effect.
-In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small.
-The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to the experiment in a quarry [@chenot-lescure2022].
+Similarly to a study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while a 50% admixture did not further increase this effect.
+In addition, the effect only appeared in north exposition and the effect size of about 6% in the 4^th^ year of restoration was rather small.
+The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to an experiment in a quarry [@chenot-lescure2022].
 Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
-Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a substrate depth of lower 15 cm since most of the roots are in this soil layer on dikes [@vannoppen2016].
+Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a substrate depth of\<15 cm, since most roots occur in the topsoil on dikes [@vannoppen2016].
 Seed density had also no clear effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
@@
 The vegetation in south exposition had a different species composition, which confirms the findings of @Batori.2016 in Hungary.
-Here, the differences might be due to some unintended methodical reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks.
-This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020].
-This drought could have also decreased germination and the establishment of sown species, because a moist spring with a mesic temperature enhances establishment [@Larson.2021; @orrock2023].
-The lasting negative effect on persistence and FCS on the southern slope suggests a legacy or year effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020].
-The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing.
-The drying of seedlings might also have levelled the distinction of the seed mixture types on the south exposition.
+However, the differences might also be due to methodical reasons, since the geotextile, which had been implemented on the southern slope, was removed after two weeks.
+This was unfortunate for at least some seedlings, and amplified by the intense drought in summer 2018 and 2019 [cf.
+@hari2020; @Larson.2021; @orrock2023].
+The lasting negative effect on persistence and FCS on the southern slope suggests a legacy effect of adverse weather conditions after sowing as observed by other studies [@Stuble.2017; @Groves.2020].
+These conditions during the establishment phase might have led to a special trajectory [@suding2004], and probably levelled the distinction of the seed mixture types in south exposition.
 
@@
 Our aim was to identify perfect seed--substrate combinations regarding restoration effectiveness and biodiversity.
-For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS.
-However, we could not identify an interaction effect for neither one of the indices.
+For evaluating effectiveness, we measured the persistence of the sown species, and FCS for investigating plant biodiversity.
+However, we could not identify an interaction effect for neither one of these indices.
 We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
-Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands).
-Although, both types are clearly phytosociologically and functionally distinct, they are still relatively closely related because they contain shared species and could develop under similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
-Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after one, five and about 15 years, respectively.
-Furthermore, the non-existence of ideal combinations could be explained by priority effects which means that the species of the imperfect-adapted seed mixture type could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
+Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows vs dry grasslands).
+Although, both types are clearly phytosociologically and functionally distinct, they are still relatively close, because they contain shared species and develop under similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993].
+Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
+However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after 1, 5 and 15yrs, respectively.
+Furthermore, the non-existence of ideal combinations could be explained by priority effects that means that the species of the imperfect-adapted seed mixture type could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
 
@@
 
-Our results suggest that adapted seed mixtures can increase restoration effectiveness by sowing hay meadows in the north but not necessarily in the south exposition of dikes.
-Furthermore, the reduction of the nutrient load through sand admixture has a clearly positive effect, albeit the effect is small.
-The question remains if sand admixture is the most economical restoration measure to promote diversity on dikes.
+Our results suggest that adapted seed mixtures can increase restoration effectiveness by sowing hay meadows in the north but not necessarily in south exposition of dikes.
+Furthermore, the reduction of the nutrient load through sand admixture was positive, albeit with small effect size.
+The question remains if sand admixture is the most efficient restoration measure to promote diversity on dikes.
 Increasing seed density on dike slopes does not appear to be necessary, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
-There were no perfect seed--substrate combinations and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity better than a single uniform solution [@bauer2023; @Holl.2022].
-The strong and lasting negative effects of the drought might require re-sowing.
+
+There were no perfect seed--substrate combinations and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity more than a single uniform solution [@bauer2023; @Holl.2022].
+Negative effects of drought in the sowing season might require re-sowing.
 To close the recovery debt, the management adaptation might be promising since this is a crucial factor beside the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
-For example, the start of sheep grazing on the experimental plots, which already exists in the surroundings, will modify the disturbance regime and improve dispersal.
-All in all, our results support the finding that restored dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
+For example, the introduction of sheep grazing on the experimental plots, which already exists in the surroundings, will modify the disturbance regime and improve dispersal.
+Overall, our results support the finding that restored dike grasslands can promote biodiversity in agricultural landscapes [@Batori.2020].
 However, the recovery debt highlights the fact that restored grasslands cannot substitute old-growth grasslands [@nerlekar2020].
@@
 Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Klaus Rachl and Stefan Radlmair (Government of Lower Bavaria) for numerous discussions on restoration and management of dike grasslands.
-Field work was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
+Fieldwork was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
 We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H.
@@
 
-JH and JK designed the experiment. JH did the surveys in the years 2018--2020 and MB in 2019 and 2021. MB did the analyses and wrote the manuscript. JK and JH critically revised the manuscript.
+JH and JK designed the experiment. JH did the surveys in the years 2018--2020, and MB in 2019 and 2021. MB did the analyses and wrote the manuscript. JK and JH critically revised the manuscript.
 
@@
 
-Data and code are stored on Zenodo (Bauer et al.
-2023) <!--# Update citation after upload -->Model evaluation is stored on GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
+Data and code are stored on Zenodo <!--# Include Zenodo ref -->Model evaluation is stored on GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
 
@@
 Characteristics of the substrates used for the sowing experiment on river dikes.
-Soil samples of the three substrates were analysed for the fraction \< 2 mm.
+Soil samples of the three substrates were analysed for the fraction \<2 mm.
 The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
@@
 To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C.
-Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.
+Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.<!--#Skelettanteil Humusanteil-->
 
@@
 Local setting and design of the multifactorial experiment on grassland sowing on dikes.
-The experiment was located on a dike at the Danube River in SE Germany.
-The 288 plots were allocated in six blocks (white squares on the upper photo) and on the north and south slope (central photo) [Both aerial photos: @bayerischevermessungsverwaltung2023].
+The experiment was located on a dike at River Danube in SE Germany.
+The 288 plots were allocated in six blocks (white squares on the upper photo) and on the north and south slope (central photo) [both aerial photos: @bayerischevermessungsverwaltung2023].
 Four treatments were conducted: sand admixture, substrate depth, seed density, and seed mixture types H and D (hay meadows, dry grasslands).
 The western half of a block had a shallow substrate depth and within this, half of the substrates had different sand admixtures.
-The photo on the bottom shows the northern slope of one block in 2021, four years after sowing (Photo: Markus Bauer).
+The photo on the bottom shows the northern slope of one block in 2021, four years after sowing (photo: Markus Bauer).
 
@@
 The species composition of sown experimental plots on a river dike over time and in comparison with reference sites and the seed mixtures.
-Both expositions and both seed mixture types are shown in separated panels.
+Both expositions and both seed mixture types are shown in separate panels.
 The NMDS was based on the Sørensen dissimilarity and data of 288 plots observed over four years after sowing in 2018 (circles).
-These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols) from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].
+These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols) from older dike grasslands in the surroundings [@bauer2023], and six plots from sPlotOpen [@Sabatini.2021].
 The ellipses show the standard error of the groups.
@@
 Effects of treatments on the development of sown grassland communities at a river dike.
-The posterior density distributions (grey) is calculated over all four surveyed years and both expositions.
+The posterior density distributions (grey) are calculated over all four surveyed years and both expositions.
 Shown are the medians, 66% and 95% credible intervals, which were derived from a Bayesian linear mixed-effects model (BLMM).

### 2023-03-09 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period.
-Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010, ID: 3271, WGS84: lat/lon, 48.85476, 12.918911, @cdc2022temp; @cdc2022prec], stream gauge Pfelling [ID: 10078000, WGS84: lat/lon, 48.87975, 12.74716, @lfu2021discharge], and water level Deggendorf [ID: 10081004, UTM32: northing/easting,
-5415586, 790796<!--# Make WGS-->, @lfu2021waterlevel]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.
+Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010, ID: 3271, WGS84: lat/lon, 48.85476/12.918911, @cdc2022temp; @cdc2022prec], stream gauge Pfelling [ID: 10078000, WGS84: lat/lon, 48.87975/12.74716, @lfu2021discharge], and water level Deggendorf [ID: 10081004, WGS84: lat/lon, 48.82508/12.96229, @lfu2021waterlevel].
+HQ2 = Highest discharge with a probability of occurrence every second year.
+HSW = Highest water level for shipping.
 
@@
 
-All sown seed mixtures can be found on GitHub in the folder 'outputs/tables/ table_a2_seed_mixtures.csv'.
-<!--# Cite Zenodo--> There, we indicate which species were combined and their respective ratio in the specific seed mixture.
+## Generating species pools
 
@@
 
+## Constructing seed mixtures
+
 For constructing concrete seed mixtures of 20 pant species, a pre-defined number of species within certain functional groups was selected randomly.
@@
 8 g m^-2^).
+
+All sown seed mixtures can be found on GitHub in the folder **'outputs/tables/ table_a2_seed_mixtures.csv'**.
+<!--# Cite Zenodo--> There, we indicate which species were combined and their respective ratio in the specific seed mixture.
 
@@
 The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target habitat types hay meadows and calcareous grasslands.
-The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
+The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2, 98.8, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
 Establishment rate of sown species [Nomenclature: @WorldFloraOnline.2021].
-Indicated is the number of sown plots and the percentage of these plots which were occupied by the respective species (presence-absence data).
+Indicated is the number of sown plots and the percentage of these plots that were occupied by the respective species (presence-absence data).
 This means that for each species only the sown plots were included.

### 2023-03-09 manuscript.Rmd
Update manuscript.Rmd

@@
 The sand admixture changed the soil texture, increased the C/N ratio, reduced calcium carbonate, but did hardly change the pH which was within the weak alkaline range (Table \@ref(tab:substrate)).
-The pH corresponded to a well-established dike vegetation on River Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils, but magnesium showed high concentrations [@lfl2022].
+The pH and C/N ratio were within the recommended range, as well as the clay ratio of the 25% sand admixture and the substrate depth of 30 cm [@husicka2003].
+Phosphate and potassium were rather scarce for agricultural soils, but magnesium showed high concentrations [@lfl2022].
 
@@
 Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
+Nevertheless, 33% of the 288 plots reached the state of the target habitat types by 2021 [EUNIS code R22, R1A, @Chytry.2020].
 Hay meadow-seed mixtures led to a closer development to hay-meadow references than dry grasslands to their references (Figure \@ref(fig:effects)A, \@ref(fig:interactions)A).
@@
 To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C.
-Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.<!--#Skelettanteil Humusanteil-->
+Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.<!--# Humusanteil-->
 

### 2023-03-09 manuscript.Rmd
Update manuscript.Rmd

@@
 
-Data, code and the entire model specifications and evaluations are stored on GitHub and presented in an easily accessible document for scrolling through.<!--# Cite Zenodo--> There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
+Data, code and the entire model specifications and evaluations are stored on GitHub and presented in an easily accessible document for scrolling through [@bauer2023experiment].
+There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
 All analyses were performed in R [Version 4.2.2, @base], with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
@@
 
-Data and code are stored on Zenodo <!--# Include Zenodo ref -->Model evaluation is stored on GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
+Data and code are stored on Zenodo [@bauer2023experiment]. Model evaluation is stored on GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
 

### 2023-03-09 manuscript.Rmd
Update manuscript.Rmd

@@
 To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C.
-Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.<!--# Humusanteil-->
+Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.
 
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_nmds_800dpi_16.5x16cm.tiff")
+  here::here("outputs", "figures", "figure_2_nmds_600dpi_16.5x16cm.tiff")
   )
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_3_800dpi_16.5x5cm.tiff")
+  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm.tiff")
   )
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_4_800dpi_16.5x20cm.tiff")
+  here::here("outputs", "figures", "figure_4_600dpi_16.5x20cm.tiff")
   )

### 2023-05-16 manuscript.Rmd
Update manuscript (first time after getting back)

@@
 This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes.
-Here, an improved seed--substrate combination will secure slope stability, reduce mowing efforts, and generate species-rich grasslands.
+Here, an improved seed--substrate combination will secure slope stability, make restorations more effective, and generate species-rich grasslands.
 2.
@@
 4.  In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment. This initial negative effect remained over the entire observation period.
-5.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
+5.  Sand admixture had a slightly positive effect on target variables, while the tested substrate depths, seed densities and mixture types had no effects on species persistence or FCS.
 6.
@@
 Restoration is seen as a key factor to sustain biodiversity and ecosystem services [@COP.2014; @UnitedNations.2019b], and sowing is a well-established approach to establish species-rich grasslands [@Kiehl.2010].
-Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome dispersal filters [@myers2009; @orrock2023].
+Sowing high-diversity mixtures of regional provenance [@bucharova2019] produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome dispersal filters [@myers2009; @orrock2023].
 However, there are still open questions about adjusting seed mixtures to specific site conditions and future climate conditions [@Torok.2021].
@@
 Restoration ecology can increase the predictability of restoration approaches [@Mouquet.2015] by using rigorous, repeatable, and transparent experiments based on advanced theory, which will finally strengthen evidence-based restoration [@Cooke.2018; @Wainwright.2018].
-Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b], while habitat and biotic filtering are the main assembly factors which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
+Local site conditions and the restoration method are key predictors for vegetation development after sowing [@Brudvig.2017b].
+The main assembly processes are habitat and biotic filtering which can be manipulated by the choice of seed--substrate combinations [@Torok.2017].
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
-Suitable substrates reduce habitat filtering of the seeded species, while specific seed mixture minimises competitive exclusion of desired species and simultaneously prohibiting invasive species [@Funk.2008].
+Suitable substrates reduce habitat filtering of the seeded species, while specific seed mixture minimises competitive exclusion of desired species while simultaneously prohibiting invasive species [@Funk.2008].
 Modifying seed mixtures to match the site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
-This challenge is particularly interesting for artificial substrates that are used in urban areas [@Bauer.2022], in quarries [@chenot-lescure2022], or on dikes [@Liebrand.1996].
+This challenge is particularly interesting for artificial substrates that can be easily modified and that are used in urban areas [@Bauer.2022], in quarries [@chenot-lescure2022], or on dikes [@Liebrand.1996].
 
 Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
-Steep slopes with different exposition, contrasting substrate layers and dense swards for erosion protection characterise these habitats [@Batori.2016; @berendse2015; @husicka2003].
+Steep slopes (\>1:3) with different exposition, contrasting substrate layers and dense swards for erosion protection characterise these habitats [@Batori.2016; @berendse2015; @husicka2003].
 Dikes can reconcile several ecosystem functions including both flood security and rich biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
@@
 
-2.  Nutrient reduction by sand addition and shallow substrates increase the establishment of dry-grassland compared to mesic seed mixtures.
+2.  Nutrient reduction by sand addition and shallow substrates increase the likeliness of the establishment of dry-grassland seed mixtures compared to mesic ones.
 
-3.  Reduced soil resources benefit target species of species-rich grasslands.
+3.  Reduced soil fertility benefit target species of species-rich grasslands.
 
-4.  High seed densities increase the establishment of sown plants and suppress non-target species.
+4.  High seed densities increase the likeliness of the establishment of sown plants and suppress non-target species compared to low density sowing.
 
@@
 
-Specific combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on a dike at the Danube River in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84: lat/lon, 48.83895/12.88412).
+Specific combinations of seed mixtures and substrates ('seed--substrate combinations') were tested on an existing dike covered by grassland at the Danube River in SE Germany (Figure \@ref(fig:map); 314 m a.s.l.; WGS84: lat/lon, 48.83895/12.88412).
 The climate of the region is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021].
 During the study, three exceptionally dry years (2018--2020) occurred [Appendix A1, @hari2020], as well as three minor floods, which, though, did not reach the plots (Appendix A1).
-The substrates consisted of calcareous sand (0--4 mm) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
-A big roller mixed both components and an excavator put the substrates in the prepared plots.
+The substrates consisted of calcareous sand (0--4 mm grain size) and agricultural soil obtained from a nearby dike construction site near the village of Steinkirchen.
+A big roller mixed both components and an excavator filled the substrates in the dug plots.
 
-The target vegetation types were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes: R22, R1A, @Chytry.2020; Arrhenatherion elatioris and Cirsio-Brachypodion pinnati according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
-The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
-The seeds were received from a commercial producer of autochthonous seeds (Co.
-Krimmer, Pulling).
+The target vegetation types were typical grassland types for Central Europe: lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS codes: R22, R1A, @Chytry.2020; Arrhenatherion elatioris and Cirsio-Brachypodion pinnati according to the EuroVegChecklist: CM01A, DA01B, @mucina2016].
+The species pool for seed mixtures of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
+The seeds were received from a commercial producer of autochthonous seeds [Co.
+Krimmer, Pulling, source area 16, @prasse2010].
 From these species pools, 20 species were selected for each plot in a stratified, randomised manner (Appendix A2).
-Each mixture contained seven grasses (60wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)).
+The aim of these random subsamples was to test types of seed mixtures and not a certain species composition.
+Each mixture contained seven grasses (60wt% of total seed mixture), three legumes (5%) and ten further non-legume forbs (35%) (Table \@ref(tab:seedmix)).
 The hay-meadow mixtures had higher community-weighted means (CWM) for specific leaf area (SLA), lower for seed mass, and higher for canopy height than the dry-grassland mixtures (Appendix A3).
@@
 The management started with a cut at 20 cm height without hay removal in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
+The surrounding area of the plots was mown thrice a year and the first time before flowering in May.
 
@@
 
-Below the substrate, a 5-cm thick drainage layer of gravel (0--16 mm) was installed.
+Below the substrate, a 5-cm thick drainage layer of gravel (0--16 mm grain size) was installed.
 Soil samples of the three substrates from both expositions were tested by mixing several sub-samples from different plots.
@@
 Furthermore, we included as a fixed effect the botanists, who recorded a certain plot.
-For the simple effects of the treatments, we chose plausible weakly informative priors.
+For the simple effects of the treatments (sand addition, substrate depth, seed density, seed mix, exposition), we chose plausible weakly informative priors.
 To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated.
@@
 The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural reference grassland [@Batori.2016].
-This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018].
+This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018] and five years might be too short for the assembly of secondary grasslands [cf.
+@nerlekar2020]
 
@@
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
-Similarly to a study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while a 50% admixture did not further increase this effect.
+Similarly to a study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while an increase from 25% to 50% admixture did not further increase this effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the 4^th^ year of restoration was rather small.
@@
 Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
-Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a substrate depth of\<15 cm, since most roots occur in the topsoil on dikes [@vannoppen2016].
+Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a thin substrate layer of \<15 cm, since most roots occur in the topsoil on dikes [@vannoppen2016].
 Seed density had also no clear effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
@@
 Each plot received an individual set of twenty species with some restrictions to the number of species per functional group.
-The total species pool for hay meadows was 55 and for dry grassland 58.
+The total species pool for the seed mixture for hay meadows was 55 and for dry grassland 58 (in total 93 different species).
 All individual seed mixtures are stored in Appendix A2.
@@
 Both expositions and both seed mixture types are shown in separate panels.
-The NMDS was based on the Sørensen dissimilarity and data of 288 plots observed over four years after sowing in 2018 (circles).
-These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols) from older dike grasslands in the surroundings [@bauer2023], and six plots from sPlotOpen [@Sabatini.2021].
+The NMDS was based on the Sørensen dissimilarity and data of 288 plots (72 per panel) observed over four years after sowing in 2018 (circles).
+These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols, 8--38 per panel) from older dike grasslands in the surroundings [@bauer2023], and six plots from sPlotOpen [@Sabatini.2021].
 The ellipses show the standard error of the groups.
@@
 Note that the zero lines indicate that both levels have equal values.
-This means, e.g., that hay meadows are closer to their reference than dry grasslands (A).
+This means, e.g., that hay meadows are closer to their reference than dry grasslands or 25% sand addition was closer to its reference than 0% addition (A).
 

### 2023-05-16 manuscript_appendix.Rmd
Update manuscript (first time after getting back)

@@
 
+The hay meadows pool had 55 species and the dry grasslands poll 58. In total, 93 different species were seeded.
+
 ## Constructing seed mixtures
@@
 
-The community-weighted means (CWM) of the seed mixtures used for the dike experiment are based on abundance data: specific leaf area (SLA), seed mass and canopy height.
+The community-weighted means (CWM) of plant traits of the seed mixtures used for the dike experiment are based on abundance data: specific leaf area (SLA), seed mass and canopy height.
 The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target habitat types hay meadows and calcareous grasslands.
@@
 All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 = 4 years times 288 experimental plots).
-In total, 274 different species were found.
+In total, 274 different species were found of which 93 were seeded.
 The shades of grey indicate the amount of established plots.

### 2023-05-19 manuscript.Rmd
Update manuscript

@@
 We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deeper substrates.
+In general, we expect a better development on sandy and shallow substrates because nutrient availability is reduced [@baer2004].
 For steep slopes, e.g., on dikes, high seed densities are recommended for successful vegetation establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
@@
 
-3.  Reduced soil fertility benefit target species of species-rich grasslands.
-
-4.  High seed densities increase the likeliness of the establishment of sown plants and suppress non-target species compared to low density sowing.
+3.  High seed densities and reduced soil fertility increase the likeliness of the establishment of sown plants and suppress non-target species compared to low density sowing.
 
@@
 From these species pools, 20 species were selected for each plot in a stratified, randomised manner (Appendix A2).
-The aim of these random subsamples was to test types of seed mixtures and not a certain species composition.
+The aim of these random and unique subsamples was to test types of seed mixtures and not a certain species composition.
 Each mixture contained seven grasses (60wt% of total seed mixture), three legumes (5%) and ten further non-legume forbs (35%) (Table \@ref(tab:seedmix)).
@@
 
+To compare the restoration outcomes with real references and not solely with seed mixtures, vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
+We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey, which included dry grasslands (*n* = 15), hay meadows (R22, *n* = 59), and as a negative reference ruderal, dry and anthropogenic vegetation (V38, *n* = 10).
+
 The recovery completeness was described by the successional distance which quantifies the distance of a plot to the average reference site in the ordination [*d~jt,0~*, @Rydgren.2019, Figure \@ref(fig:nmds)].
@@
 
-To compare the restoration outcomes with real references and not solely with seed mixtures, vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
-We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey, which included also hay meadows (R22), and as a negative reference ruderal, dry and anthropogenic vegetation (V38).
-
 ## Statistical analysis {.unnumbered}
 
-A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity was used to visualise variation in species composition in space and time.
-Seven species were excluded because they had an accumulated cover over all plots of\<0.5%.
+A non-metric multidimensional scaling ordination (NMDS) with Sørensen dissimilarity (presence--absence data) was used to visualise variation in species composition in space and time.
+Seven species were excluded because they had an accumulated cover over all plots of \<0.5%.
 Finally, 343 species were included in the ordination.
@@
 
-The ordination showed the species composition of seed mixtures and the development of the plots during four years (Figure \@ref(fig:nmds)).
+The ordination showed the species composition of seed mixtures and the development of the plots during four years (Figure \@ref(fig:nmds); 2D-stress: 0.21).
 The NMDS confirmed that the seed mixtures were variable, albeit distinctive for hay meadows and dry grasslands and confirming the intended direction of the vegetation development.
@@
 
-We could identify a statistically clear positive effect of the sand admixture on the persistence of sown species and on the recovery rate, but no effects of seed density or substrate depth (Figure \@ref(fig:effects)).
+A statistically clear positive effectof the sand admixture was identified on the persistence of sown species and on the recovery rate, but no effects of seed density or substrate depth (Figure \@ref(fig:effects); Persistence: *R*<sup>2</sup><sub>m</sub> = 0.86, *R*<sup>2</sup><sub>c</sub> = 0.89; Recovery: *R*<sup>2</sup><sub>m</sub> = 0.90, *R*<sup>2</sup><sub>c</sub> = 0.92; FCS: *R*<sup>2</sup><sub>m</sub> = 0.81, *R*<sup>2</sup><sub>c</sub> = 0.85).
 The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:interactions)).
@@
 
-The vegetation developed generally in the desired direction but was still distinct from positive references and seed mixtures after four years.
-In the south exposition, the plots were rather similar to the negative reference of dry ruderal vegetation.
+The vegetation developed generally in the desired direction.
+The development after one year was very fast and afterwards very slow.
+For practitioners, it would be more cost-efficient to start monitoring not in the year of seeding because ruderal species are too dominant for a sensible interpretation of the results.
+After four years, the vegetation was still distinct from positive references and seed mixtures.
+In the south exposition, the plots were rather similar to the negative reference of dry ruderal vegetation typical of grassland restoration when perennial species are still developing to become dominant [@eckhoff2023].
 The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural reference grassland [@Batori.2016].
 This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018] and five years might be too short for the assembly of secondary grasslands [cf.
-@nerlekar2020]
+@nerlekar2020].
+The annual *B.
+hordeaceus*, seeded in autumn 2018 as nursery plant, decreased but was still present in 179 of 288 plots in 2021.
 
@@
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
-Similarly to a study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while an increase from 25% to 50% admixture did not further increase this effect.
+Similarly to @chenot-lescure2022, sand admixture reduced nutrient loads and led to higher persistence of sown species while an increase from 25% to 50% admixture did not further increase this effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the 4^th^ year of restoration was rather small.
@@
 The question remains if sand admixture is the most efficient restoration measure to promote diversity on dikes.
-Increasing seed density on dike slopes does not appear to be necessary, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
+Increasing seed density on dike slopes does not appear to be necessary which contradicts common recommendations, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
 

### 2023-07-03 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Fit by design: Developing substrate-specific seed mixtures for functional dike grasslands"
+title: "Fit by design: Developing seed-substrate combinations to adapt dike grasslands to microclimate"
 author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
@@
 Sowing is a well-established restoration technique to overcome dispersal limitation.
-Site-specific seed mixtures are most effective to achieve functional communities.
+Seed mixtures adapted to certain environmental conditions like substrate or microclimate are most effective to achieve functional communities.
 This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes.
@@
 Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
-Steep slopes (\>1:3) with different exposition, contrasting substrate layers and dense swards for erosion protection characterise these habitats [@Batori.2016; @berendse2015; @husicka2003].
+In addition, dikes are interesting for experiments with seed-substrate combinations because the combinations can be tested on contrasting microclimates of the steep slopes (\>1:3) with different expositions.
+
+contrasting substrate layers and dense swards for erosion protection characterise these habitats [@Batori.2016; @berendse2015; @husicka2003].
 Dikes can reconcile several ecosystem functions including both flood security and rich biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
@@
 
-We used 288 plots of the size 2.0 m × 3.0 m, vertically oriented, halfway up the dike slopes, distributed over the north and south exposition, and arranged in six blocks (=replicates).
+We used 288 plots of the size 2.0 m × 3.0 m, vertically oriented, halfway up the dike slopes (1:2), distributed over the north and south exposition, and arranged in six blocks (=replicates).
 The experiment used a split-plot design combined with a randomised complete block design (Figure \@ref(fig:map)).
 The split plot was created by the two expositions of the dike, where all 24 treatment combinations were tested, i.e., sand admixtures (0, 25, and 50%), soil depths (15 vs.
-30 cm), the two seed mixture types, and two seed densities [4 vs.
-8 g m^-2^, cf.
-@Kiehl.2010; @KleberLerchbaumer.2017].
+30 cm), the two seed mixture types, and two seed densities (4 vs.
+8 g m^-2^).
+@Kiehl.2010 recommend 1--5 g m^-2^ for grassland restoration and @KleberLerchbaumer.2017 recommend an increased density of 5--8 g m^-2^ for slopes.
 
@@
 The NMDS confirmed that the seed mixtures were variable, albeit distinctive for hay meadows and dry grasslands and confirming the intended direction of the vegetation development.
-As one exception, hay meadows in south exposition did not develop towards their seed-mixture compositions.
+As one exception, hay meadows in south exposition did not develop towards their seed-mixture compositions as expected in hypothesis H1.
 
@@
 Nonetheless, they still differed from the negative references of ruderal vegetation.
-Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
+Negative references were only available on southern slopes and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021.
 Nevertheless, 33% of the 288 plots reached the state of the target habitat types by 2021 [EUNIS code R22, R1A, @Chytry.2020].
 Hay meadow-seed mixtures led to a closer development to hay-meadow references than dry grasslands to their references (Figure \@ref(fig:effects)A, \@ref(fig:interactions)A).
-This was especially the case in north exposition (Figure \@ref(fig:nmds)).
+This was especially the case in north exposition (H1; Figure \@ref(fig:nmds)).
 
@@
 
-A statistically clear positive effectof the sand admixture was identified on the persistence of sown species and on the recovery rate, but no effects of seed density or substrate depth (Figure \@ref(fig:effects); Persistence: *R*<sup>2</sup><sub>m</sub> = 0.86, *R*<sup>2</sup><sub>c</sub> = 0.89; Recovery: *R*<sup>2</sup><sub>m</sub> = 0.90, *R*<sup>2</sup><sub>c</sub> = 0.92; FCS: *R*<sup>2</sup><sub>m</sub> = 0.81, *R*<sup>2</sup><sub>c</sub> = 0.85).
+A statistically clear positive effect of the sand admixture (H2) was identified on the persistence of sown species and on the recovery rate, but no effects by substrate depth (H2) or seed density (H3) (Figure \@ref(fig:effects); Persistence: *R*<sup>2</sup><sub>m</sub> = 0.86, *R*<sup>2</sup><sub>c</sub> = 0.89; Recovery: *R*<sup>2</sup><sub>m</sub> = 0.90, *R*<sup>2</sup><sub>c</sub> = 0.92; FCS: *R*<sup>2</sup><sub>m</sub> = 0.81, *R*<sup>2</sup><sub>c</sub> = 0.85).
 The posterior distributions are also shown in the interaction plots that separate exposition and survey year (Figures \@ref(fig:interactions)).
@@
 Both expositions revealed similar trends but for all responses, the values were clearly lower in south exposition, e.g., persistence values were on average more than 46% higher in north exposition (Figure \@ref(fig:interactions)B).
-The interactions of restoration treatments were neither clear nor strong.
-Persistence of both seed mixture types was slightly positively affected by sand admixture in north exposition (+ 6--7 ± 4%, Figure \@ref(fig:interactions)B).
+The interactions of restoration treatments were neither clear nor strong (H2, H3).
+Persistence of both seed mixture types was slightly positively affected by sand admixture in north exposition (H2; + 6--7 ± 4%, Figure \@ref(fig:interactions)B).
 \clearpage \newpage
@@
 The position on the ordination suggests that the seed mixture represents a late-successional stage compared to the references.
-The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:interactions)A).
+The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands what we had more clearly expected in H1 (Figure \@ref(fig:interactions)A).
 This can be expected from the requirements of hay meadows for mesic conditions, which can be provided on north-exposed dike slopes [@Oberdorfer.1993; @Batori.2020].
-In southern exposition, the plots of hay meadows developed rather towards dry grassland references which indicates an ineffective restoration due to a non-adapted seed mixture.
+In south exposition, the hay meadow plots developed rather towards dry grassland references which indicates an ineffective restoration due to a not adapted seed mixture to the microclimatic conditions of southern slopes.
 
@@
 hordeaceus*, seeded in autumn 2018 as nursery plant, decreased but was still present in 179 of 288 plots in 2021.
+Reasons for the recovery debt might not only be abiotic conditions but can also be biotic factors like missing mycorrhiza in the substrates [@koziol2017] or the post-restoration management needs to be developed [@tölgyesi2022].
 
@@
 Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
-Similarly to @chenot-lescure2022, sand admixture reduced nutrient loads and led to higher persistence of sown species while an increase from 25% to 50% admixture did not further increase this effect.
+Similarly to @chenot-lescure2022, sand admixture reduced nutrient loads and led to higher persistence of sown species as expected by H2 while an increase from 25% to 50% admixture did not further increase this effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the 4^th^ year of restoration was rather small.
-The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to an experiment in a quarry [@chenot-lescure2022].
-Substrate depth did not significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
+The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to an experiment in a quarry [@chenot-lescure2022] but not to our expectations (H2).
+An increase of substrate depth from 15 to 30 cm did neither significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
 Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a thin substrate layer of \<15 cm, since most roots occur in the topsoil on dikes [@vannoppen2016].
-Seed density had also no clear effect on persistence and FCS which fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
+Seed density had also no clear effect on persistence and FCS which is contrary to H3 but fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
 
-The vegetation in south exposition had a different species composition, which confirms the findings of @Batori.2016 in Hungary.
-However, the differences might also be due to methodical reasons, since the geotextile, which had been implemented on the southern slope, was removed after two weeks.
+The vegetation in south exposition had a more ruderal and xerophytic species compositions than in north exposition, which contrasts @Batori.2016 who found different compositions in south exposition only for riverside slopes which caused a more mesotrophic vegetation.
+The differences in our experiment might be due to methodical reasons, since the geotextile, which had been implemented on the southern slope, was removed after two weeks.
 This was unfortunate for at least some seedlings, and amplified by the intense drought in summer 2018 and 2019 [cf.
 @hari2020; @Larson.2021; @orrock2023].
-The lasting negative effect on persistence and FCS on the southern slope suggests a legacy effect of adverse weather conditions after sowing as observed by other studies [@Stuble.2017; @Groves.2020].
-These conditions during the establishment phase might have led to a special trajectory [@suding2004], and probably levelled the distinction of the seed mixture types in south exposition.
+The lasting negative effect on persistence and FCS on the southern slope suggests a legacy effect of adverse weather conditions after sowing as observed by other studies [@Groves.2020; @atkinson2023].
+These conditions during the establishment phase might have led to a special trajectory [@suding2004], and probably leveled the distinction of the seed mixture types in south exposition.
 
@@
 
-Our aim was to identify perfect seed--substrate combinations regarding restoration effectiveness and biodiversity.
+Our aim was to identify perfect seed--substrate combinations regarding restoration effectiveness and biodiversity (H2, H3).
 For evaluating effectiveness, we measured the persistence of the sown species, and FCS for investigating plant biodiversity.
 However, we could not identify an interaction effect for neither one of these indices.
-We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture.
+We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture (H2).
 Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows vs dry grasslands).
@@
 Negative effects of drought in the sowing season might require re-sowing.
-To close the recovery debt, the management adaptation might be promising since this is a crucial factor beside the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2021].
+Restoration projects might account for the increasing frequency of droughts [@naumann2018] by include a re-sowing in planning or by combining seeding with hay transfer to improve the microclimate during establishment [@eckstein2005].
+We expect a minor effect of succession in the next ten years, which requires further interventions to close the recovery debt.
+The management adaptation might be promising since this is a crucial factor beside the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2022].
 For example, the introduction of sheep grazing on the experimental plots, which already exists in the surroundings, will modify the disturbance regime and improve dispersal.

### 2023-07-04 manuscript.Rmd
Update manuscript.Rmd

@@
 Persistence of both seed mixture types was slightly positively affected by sand admixture in north exposition (H2; + 6--7 ± 4%, Figure \@ref(fig:interactions)B).
-\clearpage \newpage
+
+\clearpage
+
+\newpage
 
@@
 The question remains if sand admixture is the most efficient restoration measure to promote diversity on dikes.
-Increasing seed density on dike slopes does not appear to be necessary which contradicts common recommendations, and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
+Increasing seed density on dike slopes does not appear to be necessary which contradicts common recommendations [@KleberLerchbaumer.2017], and soil depths of 30 cm are not adverse compared to 15 cm thick substrates.
 
@@
 Negative effects of drought in the sowing season might require re-sowing.
-Restoration projects might account for the increasing frequency of droughts [@naumann2018] by include a re-sowing in planning or by combining seeding with hay transfer to improve the microclimate during establishment [@eckstein2005].
+Restoration projects might account for the increasing frequency of droughts [@naumann2018] by include a re-sowing in planning or by combining seeding with hay transfer [@török2012] to improve the microclimate during establishment [@eckstein2005].
 We expect a minor effect of succession in the next ten years, which requires further interventions to close the recovery debt.
-The management adaptation might be promising since this is a crucial factor beside the restoration approach and the site characteristics [@Grman.2013; @tölgyesi2022].
+Management adaptation modifies the biotic filter and is a crucial factor in addition to the restoration approach and the site characteristics for restoration success [@Grman.2013; @tölgyesi2022].
 For example, the introduction of sheep grazing on the experimental plots, which already exists in the surroundings, will modify the disturbance regime and improve dispersal.
@@
 Characteristics of the substrates used for the sowing experiment on river dikes.
-Soil samples of the three substrates were analysed for the fraction \<2 mm.
-The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005].
-The pH was measured in CaCl~2~ solution.
+Soil samples of the three substrates were taken from 0--25 cm with a hand drill of 3.3 cm diameter and were analysed for the fraction \<2 mm.
+The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005] and the pH was measured in CaCl~2~ solution.
 Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in a CaCl~2~ extract.

### 2023-07-04 R/model_check_fcs.Rmd
Update model_check

@@
 
+The blue line (observed value) should be in the center of the
+distribution of 500 simulated data sets.
+
 ```{r prior-predictive-check, fig.height = 3}
@@
 
+The traces of the four chains should overlap each other.
+
 ```{r mcmc-trace, fig.height = 14}
@@
 
+R-hat values should be lower than 1.1.
+
 ```{r rhat, collapse = TRUE}
@@
 
+ESS should be greater than 0.1.
+
 ```{r ess, collapse = TRUE}
@@
 #### Pairs plot
+
+If the technical problem of divergent transitions occurs, points would
+be highlighted in green.
 
@@
 
+If the technical problem of divergent transitions occurs, points would
+be highlighted in green.
+
 ```{r mcmc-parcoord, collapse = TRUE}
@@
 #### Autocorrelation check
+
+Autocorrelation should go down to zero very fast.
 
@@
 #### Kernel density
+
+The kernel density estimate of the observed data (dark line) compared
+with estimates for 50 simulated data sets drawn from the posterior
+predictive distribution (thinner and lighter lines). The dark line
+should be near the simulated curves.
 
@@
 
+The dark line (computed from the observed data) should be in the center
+of the posterior predictive distribution.
+
 ```{r histogram}
@@
 
+All Pareto-k estimates should be \< 0.7.
+
 ```{r loo}
@@
 
-Leave one out probability integral transform
+Density of the computed leave one out probability integral transform
+(LOO PIT; dark curve) compared with the posterior predictive
+distribution (light curves). The LOO PIT curve should be within the
+range of light curves.
 
-```{r loo-pit}
+```{r loo-pit, message = FALSE}
 p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
@@
 
-### Forest plot (BARG 3.B/5.B)
+### Forest plot of effect sizes (BARG 3.B/5.B)
 

### 2023-07-04 R/model_check_persistence.Rmd
Update model_check

@@
 
+The blue line (observed value) should be in the center of the distribution of 500 simulated data sets.
+
 ```{r prior-predictive-check, fig.height = 3}
@@
 #### Pairs plot
+
+If the technical problem of divergent transitions occurs, points would be highlighted in green.
 
@@
 
+If the technical problem of divergent transitions occurs, points would be highlighted in green.
+
 ```{r mcmc-parcoord, collapse = TRUE}
@@
 #### Kernel density
+
+The kernel density estimate of the observed data (dark line) compared with estimates for 50 simulated data sets drawn from the posterior predictive distribution (thinner and lighter lines).
+The dark line should be near the simulated curves.
 
@@
 
+The dark line (computed from the observed data) should be in the center of the posterior predictive distribution.
+
 ```{r histograms}
@@
 
-Leave one out probability integral transform
+Computed leave one out probability integral transform (LOO PIT; dark curve) versus the posterior predictive distribution (light curves). The LOO PIT curve should be within the range of light curves.
 
-```{r loo-pit}
+```{r loo-pit, message = FALSE}
 p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
@@
 
-### Forest plot (BARG 2.B/5.B)
+### Forest plot of effect sizes (BARG 2.B/5.B)
 

### 2023-07-04 R/model_check_recovery.Rmd
Update model_check

@@
 
+Autocorrelation should go down to zero very fast.
+
 ```{r autocorrelation}

### 2023-07-04 manuscript.Rmd
Update manuscript.Rmd

@@
 Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt, as well as re-sowing after unfavourable conditions.
-\clearpage \newpage
+
+\clearpage
+
+\newpage
 
@@
 Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
-In addition, dikes are interesting for experiments with seed-substrate combinations because the combinations can be tested on contrasting microclimates of the steep slopes (\>1:3) with different expositions.
-
-contrasting substrate layers and dense swards for erosion protection characterise these habitats [@Batori.2016; @berendse2015; @husicka2003].
-Dikes can reconcile several ecosystem functions including both flood security and rich biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
+Several ecosystem functions can be reconciled by dike grasslands like erosion control [@husicka2003; @berendse2015] and biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
+Experiments with such seed-substrate combinations on dikes benefit from contrasting microclimates of the different expositions of the steep slopes (\>1:3) [@suggitt2010] .
 
@@
 
-2.  Nutrient reduction by sand addition and shallow substrates increase the likeliness of the establishment of dry-grassland seed mixtures compared to mesic ones.
+2.  Nutrient reduction by sand addition and shallow substrates improve the establishment of dry-grassland seed mixtures compared to mesic ones.
 
-3.  High seed densities and reduced soil fertility increase the likeliness of the establishment of sown plants and suppress non-target species compared to low density sowing.
+3.  High seed densities and reduced soil fertility improve the establishment of sown plants and suppress non-target species compared to low density sowing and high soil fertility.
 
@@
 The lasting negative effect on persistence and FCS on the southern slope suggests a legacy effect of adverse weather conditions after sowing as observed by other studies [@Groves.2020; @atkinson2023].
-These conditions during the establishment phase might have led to a special trajectory [@suding2004], and probably leveled the distinction of the seed mixture types in south exposition.
+These conditions during the establishment phase might have led to a special trajectory [@suding2004], and probably levelled the distinction of the seed mixture types in south exposition.
 
@@
 Furthermore, the non-existence of ideal combinations could be explained by priority effects that means that the species of the imperfect-adapted seed mixture type could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
-
-\clearpage
-
-\newpage
+\clearpage \newpage
 

### 2023-07-05 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "Fit by design: Developing seed-substrate combinations to adapt dike grasslands to microclimate"
+title: "Fit by design: Developing seed–substrate combinations to adapt dike grasslands to microclimatic variation"
 author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
@@
 Sowing is a well-established restoration technique to overcome dispersal limitation.
-Seed mixtures adapted to certain environmental conditions like substrate or microclimate are most effective to achieve functional communities.
+Seed mixtures adapted to certain environmental conditions, like substrate or microclimate, are most effective to achieve functional communities.
 This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes.
@@
 6.
-Synthesis and applications: Site-adapted seed mixtures make restoration more effective.
-However, applying several seed--substrate combinations might foster beta diversity.
+Synthesis and applications: Site-adapted seed mixtures make restoration more effective, while applying several seed--substrate combinations might foster beta diversity.
 Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt, as well as re-sowing after unfavourable conditions.
@@
 This means a close adaptation of the substrate to the niche of the target species or of the seed mixtures to the characteristics of the chosen substrate.
-Suitable substrates reduce habitat filtering of the seeded species, while specific seed mixture minimises competitive exclusion of desired species while simultaneously prohibiting invasive species [@Funk.2008].
+Suitable substrates reduce habitat filtering of the seeded species, while specific seed mixture minimises competitive exclusion of desired species and simultaneously prohibit invasive species [@Funk.2008].
 Modifying seed mixtures to match the site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
@@
 
-Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
+Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands ,fore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
 Several ecosystem functions can be reconciled by dike grasslands like erosion control [@husicka2003; @berendse2015] and biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
-Experiments with such seed-substrate combinations on dikes benefit from contrasting microclimates of the different expositions of the steep slopes (\>1:3) [@suggitt2010] .
+Experiments with such seed-substrate combinations on dikes benefit from contrasting microclimates of the different expositions of the steep slopes (\>1:3) [@suggitt2010].
 
-The aim of this study is to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
-An experiment was set up to test different substrate depths, sand admixtures, seed densities, and mixture types.
+The aim of this study was to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
+Thus, an experiment was set up to test different substrate depths, sand admixtures, seed densities, and mixture types.
 We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deeper substrates.
@@
 The species pool for seed mixtures of hay meadows and dry grasslands consisted of 55 and 58 species, respectively.
-The seeds were received from a commercial producer of autochthonous seeds [Co.
+The seeds were supplied by a commercial producer of autochthonous seeds [Co.
 Krimmer, Pulling, source area 16, @prasse2010].
-From these species pools, 20 species were selected for each plot in a stratified, randomised manner (Appendix A2).
+From these species pools, 20 species were selected for each plot in a stratified randomised manner (Appendix A2).
 The aim of these random and unique subsamples was to test types of seed mixtures and not a certain species composition.
@@
 There, the sections are referenced to the Bayesian analysis reporting guidelines [BARG, @kruschke2021].
-All analyses were performed in R [Version 4.2.2, @base], with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
+All analyses were performed in R [Version 4.2.3, @base], with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation, and 'metaMDS' from 'vegan' for the ordination [@vegan].
 
@@
 The ordination showed the species composition of seed mixtures and the development of the plots during four years (Figure \@ref(fig:nmds); 2D-stress: 0.21).
-The NMDS confirmed that the seed mixtures were variable, albeit distinctive for hay meadows and dry grasslands and confirming the intended direction of the vegetation development.
-As one exception, hay meadows in south exposition did not develop towards their seed-mixture compositions as expected in hypothesis H1.
+The NMDS confirmed that the seed mixtures were variable, albeit distinctive for hay meadows and dry grasslands, and confirming the intended direction of the vegetation development.
+As one exception, hay meadows in south exposition did not develop towards their seed-mixture compositions as expected in hypothesis 1 (H1).
 
@@
 This can be expected from the requirements of hay meadows for mesic conditions, which can be provided on north-exposed dike slopes [@Oberdorfer.1993; @Batori.2020].
-In south exposition, the hay meadow plots developed rather towards dry grassland references which indicates an ineffective restoration due to a not adapted seed mixture to the microclimatic conditions of southern slopes.
+In south exposition, the hay meadow plots developed rather towards dry grassland references, which indicates an ineffective restoration due to a not adapted seed mixture to the microclimatic conditions of southern slopes.
 
@@
 The gap between goal and restoration outcome was also shown for other sowing experiments or restorations [@mitchley2012; @Engst.2016; @Kaulfuss.2022] or for dike vegetation compared with semi-natural reference grassland [@Batori.2016].
-This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018] and five years might be too short for the assembly of secondary grasslands [cf.
+This result is not surprising since the 'recovery debt' is a general phenomenon of grassland restoration [@MorenoMateos.2017; @jones2018], and five years might be too short for the assembly of secondary grasslands [cf.
 @nerlekar2020].
@@
 hordeaceus*, seeded in autumn 2018 as nursery plant, decreased but was still present in 179 of 288 plots in 2021.
-Reasons for the recovery debt might not only be abiotic conditions but can also be biotic factors like missing mycorrhiza in the substrates [@koziol2017] or the post-restoration management needs to be developed [@tölgyesi2022].
+Reasons for the recovery debt might not only be abiotic conditions but can also be biotic factors like missing mycorrhiza in the substrates [@koziol2017], or the post-restoration management needs to be developed [@tölgyesi2022].
 
@@
 
-Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
-Similarly to @chenot-lescure2022, sand admixture reduced nutrient loads and led to higher persistence of sown species as expected by H2 while an increase from 25% to 50% admixture did not further increase this effect.
+Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004], but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022].
+Similarly to @chenot-lescure2022, sand admixture reduced nutrient loads and led to higher persistence of sown species as expected by H2, while an increase from 25% to 50% admixture did not further increase this effect.
 In addition, the effect only appeared in north exposition and the effect size of about 6% in the 4^th^ year of restoration was rather small.
 The Favourable Conservation Status (FCS) was hardly affected by the sand admixture, which corresponds to an experiment in a quarry [@chenot-lescure2022] but not to our expectations (H2).
-An increase of substrate depth from 15 to 30 cm did neither significantly affect persistence or FCS, similarly to earlier studies [@husicka2003; @baer2004].
+An increase of substrate depth from 15 to 30 cm did neither significantly affect persistence nor FCS, similarly to earlier studies [@husicka2003; @baer2004].
 Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010] or a thin substrate layer of \<15 cm, since most roots occur in the topsoil on dikes [@vannoppen2016].
-Seed density had also no clear effect on persistence and FCS which is contrary to H3 but fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
+Seed density had also no clear effect on persistence and FCS, which is contrary to H3 but fits the results of @Kaulfuss.2022, who found that a certain amount of seeds is necessary for a successful establishment of target species, but higher densities do not further improve the outcome, but rather have a slightly negative effect.
 
-The vegetation in south exposition had a more ruderal and xerophytic species compositions than in north exposition, which contrasts @Batori.2016 who found different compositions in south exposition only for riverside slopes which caused a more mesotrophic vegetation.
+The vegetation in south exposition had a more ruderal and xerophytic species compositions than in north exposition, which contrasts @Batori.2016 who found different compositions in south exposition only for riverside slopes that caused a more mesotrophic vegetation.
 The differences in our experiment might be due to methodical reasons, since the geotextile, which had been implemented on the southern slope, was removed after two weeks.
@@
 The lasting negative effect on persistence and FCS on the southern slope suggests a legacy effect of adverse weather conditions after sowing as observed by other studies [@Groves.2020; @atkinson2023].
-These conditions during the establishment phase might have led to a special trajectory [@suding2004], and probably levelled the distinction of the seed mixture types in south exposition.
+These conditions during the establishment phase might had led to a special trajectory [@suding2004], and probably levelled the distinction of the seed mixture types in south exposition.
 
@@
 For evaluating effectiveness, we measured the persistence of the sown species, and FCS for investigating plant biodiversity.
-However, we could not identify an interaction effect for neither one of these indices.
+However, we could not identify an interaction effect for any of these indices.
 We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture (H2).
@@
 Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022].
-However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after 1, 5 and 15yrs, respectively.
+However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after 1, 5 and 15 yrs, respectively.
 Furthermore, the non-existence of ideal combinations could be explained by priority effects that means that the species of the imperfect-adapted seed mixture type could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].
-\clearpage \newpage
+
+\clearpage
+
+\newpage
 
@@
 Negative effects of drought in the sowing season might require re-sowing.
-Restoration projects might account for the increasing frequency of droughts [@naumann2018] by include a re-sowing in planning or by combining seeding with hay transfer [@török2012] to improve the microclimate during establishment [@eckstein2005].
+Restoration projects should account for the increasing frequency of droughts [@naumann2018] by re-sowing or by combining seeding with hay transfer [@török2012] to improve the microclimate during establishment [@eckstein2005].
 We expect a minor effect of succession in the next ten years, which requires further interventions to close the recovery debt.
@@
 
-We would like to thank our project partners Dr.
-Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Klaus Rachl and Stefan Radlmair (Government of Lower Bavaria) for numerous discussions on restoration and management of dike grasslands.
+First, we likeWe would like to thank our project partners Dr.
+Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Stefan Radlmair and the late Klaus Rachl (Government of Lower Bavaria) for numerous discussions on restoration and management of dike grasslands.
 Fieldwork was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
@@
 The German Federal Environmental Foundation (DBU) supported MB with a doctoral scholarship.
+Thank you also to three anonymous referees for their valuable suggestions improving the manuscript.
 
@@
 
-Each plot received an individual set of twenty species with some restrictions to the number of species per functional group.
+Each plot received an individual set of 20 species with some restrictions to the number of species per functional group.
 The total species pool for the seed mixture for hay meadows was 55 and for dry grassland 58 (in total 93 different species).

### 2023-08-03 manuscript.Rmd
Update manuscript.Rmd

@@
 
-Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands ,fore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
+Dikes are promising sites for the restoration of species-rich grasslands because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in agricultural landscapes [@Batori.2020].
 Several ecosystem functions can be reconciled by dike grasslands like erosion control [@husicka2003; @berendse2015] and biodiversity [@teixeira2022], which can be fostered by an adapted seed--substrate combination.
@@
 The aim of this study was to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes.
-Thus, an experiment was set up to test different substrate depths, sand admixtures, seed densities, and mixture types.
+Thus, an experiment was set up to test different substrate depths, sand admixtures, seed densities, and seed mixture types.
 We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deeper substrates.
@@
 The sand admixture changed the soil texture, increased the C/N ratio, reduced calcium carbonate, but did hardly change the pH which was within the weak alkaline range (Table \@ref(tab:substrate)).
-The pH and C/N ratio were within the recommended range, as well as the clay ratio of the 25% sand admixture and the substrate depth of 30 cm [@husicka2003].
+@husicka2003 recommends soil properties for dike substrates: the pH values and C/N ratios of the tested substrates were within the recommended ranges.
+Furthermore, the clay ratio was within the proposed range for the treatment 25% sand admixture and the substrate depth for the treatment of 30 cm depth [@husicka2003].
 Phosphate and potassium were rather scarce for agricultural soils, but magnesium showed high concentrations [@lfl2022].
@@
 To compare the restoration outcomes with real references and not solely with seed mixtures, vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys on the Danube dikes in the surroundings [@bauer2023].
-We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey, which included dry grasslands (*n* = 15), hay meadows (R22, *n* = 59), and as a negative reference ruderal, dry and anthropogenic vegetation (V38, *n* = 10).
+We selected six dry grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 82 plots of our own survey, which included dry grasslands (*n* = 15), hay meadows (R22, *n* = 59), and as a negative reference ruderal, dry and anthropogenic vegetation (V38, *n* = 9 ✕ 2, plots used for both seed mixture types).
 
@@
 The position on the ordination suggests that the seed mixture represents a late-successional stage compared to the references.
-The NMDS shows a slightly better adaptation of hay meadows to the north exposition than of dry grasslands what we had more clearly expected in H1 (Figure \@ref(fig:interactions)A).
+The NMDS shows a slightly better adaptation of the hay meadows to the north exposition than the dry grasslands.
+This effect, albeit stronger, was expected in H1 (Figure \@ref(fig:interactions)A).
 This can be expected from the requirements of hay meadows for mesic conditions, which can be provided on north-exposed dike slopes [@Oberdorfer.1993; @Batori.2020].
@@
 
-First, we likeWe would like to thank our project partners Dr.
+We would like to thank our project partners Dr.
 Markus Fischer, Frank Schuster, and Christoph Schwahn (WIGES GmbH) as well as Stefan Radlmair and the late Klaus Rachl (Government of Lower Bavaria) for numerous discussions on restoration and management of dike grasslands.
@@
 The NMDS was based on the Sørensen dissimilarity and data of 288 plots (72 per panel) observed over four years after sowing in 2018 (circles).
-These experimental plots were compared with the seed mixtures (black squares) and 98 positive and negative reference plots (filled symbols, 8--38 per panel) from older dike grasslands in the surroundings [@bauer2023], and six plots from sPlotOpen [@Sabatini.2021].
+These experimental plots were compared with the seed mixtures (black squares) and 89 positive and negative reference plots (filled symbols, 8--38 per panel) from older dike grasslands in the surroundings [@bauer2023], and from sPlotOpen [@Sabatini.2021].
 The ellipses show the standard error of the groups.
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm.tiff")
+  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm_modified.tiff")
   )

### 2023-08-03 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 ---
-title: "Appendix of Bauer et al. (2023) bioRxiv"
+title: "Appendix of Bauer et al. (2023) Journal of Applied Ecology"
 author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
@@
 
-All sown seed mixtures can be found on GitHub in the folder **'outputs/tables/ table_a2_seed_mixtures.csv'**.
-<!--# Cite Zenodo--> There, we indicate which species were combined and their respective ratio in the specific seed mixture.
+All sown seed mixtures can be found on GitHub in the folder **'outputs/tables/ table_a2_seed_mixtures.csv'** [@bauer2023experiment].
+There, we indicate which species were combined and their respective ratio in the specific seed mixture.
 
@@
 
-All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 = 4 years times 288 experimental plots).
+All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 plots = 4 years times 288 experimental plots).
 In total, 274 different species were found of which 93 were seeded.

### 2023-08-03 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@
 
--   Species, for which no seeds were available in the market or which are difficult to establish by propagule application, e.g., *Carex* spec. or cryptogams
+-   Species, for which no seeds were available in the market or which are difficult to establish by propagule application, e.g. *Carex* sp. or cryptogams
 
@@
 The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target habitat types hay meadows and calcareous grasslands.
-The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2, 98.8, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
+The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2, 98.8, and 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].
 
@@
   ) %>%
-  mutate(name = str_replace_all(name, "_", " ")) %>%
+  mutate(
+    name = str_replace(name, "_ssp", "_ssp."),
+    name = str_replace(name, "_spec", "_sp."),
+    name = str_replace_all(name, "_", " ")
+    ) %>%
   rename(

### 2023-08-03 manuscript.Rmd
Update manuscript.Rmd

@@
 In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry-grassland mixtures.
-4.  In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment. This initial negative effect remained over the entire observation period.
+4.  In south exposition, the sown communities established poorly which might be due to a severe drought during establishment. This initial negative effect remained over the entire observation period.
 5.  Sand admixture had a slightly positive effect on target variables, while the tested substrate depths, seed densities and mixture types had no effects on species persistence or FCS.
@@
 Modifying seed mixtures to match the site conditions could be based on functional plant traits [@Funk.2008; @Laughlin.2014; @Balazs.2020], although this is not easy to implement [@merchant2022; @Bauer.2022].
-This challenge is particularly interesting for artificial substrates that can be easily modified and that are used in urban areas [@Bauer.2022], in quarries [@chenot-lescure2022], or on dikes [@Liebrand.1996].
+This challenge is particularly interesting for artificial substrates that can be modified and are often used in urban areas [@Bauer.2022], quarries [@chenot-lescure2022], or dikes [@Liebrand.1996].
 
@@
 The management started with a cut at 20 cm height without hay removal in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020.
-The surrounding area of the plots was mown thrice a year and the first time before flowering in May.
+The surrounding area of the plots was mown thrice a year, and the first time before flowering in May.
 
@@
 
-There were no perfect seed--substrate combinations and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity more than a single uniform solution [@bauer2023; @Holl.2022].
+There were no perfect seed--substrate combinations and thus we conclude that a variation of seed mixture types and different substrates along restoration sections would promote biodiversity more than a single solution [@bauer2023; @Holl.2022].
 Negative effects of drought in the sowing season might require re-sowing.
@@
 Fieldwork was supported by Clemens Berger and Uwe Kleber-Lerchbaumer (Wasserwirtschaftsamt Deggendorf).
-We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Leonardo H.
+We thank Holger Paetsch, Simon Reith, Anna Ritter, Jakob Strak, Dr.
+Leonardo H.
 Teixeira, and Linda Weggler for assisting with the field surveys or soil analyses in 2018--2020.

### 2023-08-03 manuscript.Rmd
Reduce dpi of figures

@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_nmds_600dpi_16.5x16cm.tiff")
+  here::here("outputs", "figures", "figure_2_nmds_500dpi_16.5x16cm.tiff")
   )
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_4_600dpi_16.5x20cm.tiff")
+  here::here("outputs", "figures", "figure_4_500dpi_16.5x20cm.tiff")
   )

### 2023-08-03 manuscript_appendix.Rmd
Reduce dpi of figures

@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_a3_800dpi_16.5x5cm_traits.tiff")
+  here::here("outputs", "figures", "figure_a3_300dpi_16.5x5cm_traits.tiff")
   )

### 2023-08-03 R/show_appendix_a3_figure_traits.R

@@ -100,6 +100,6 @@ graph_a + theme(legend.position = "none") +
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_a3_800dpi_16.5x5cm_traits.tiff"),
-  dpi = 800, width = 16.5, height = 5, units = "cm"
+  here("outputs", "figures", "figure_a3_300dpi_16.5x5cm_traits.tiff"),
+  dpi = 300, width = 16.5, height = 5, units = "cm"
 )

### 2023-08-03 R/show_figure_2_nmds.R

@@ -212,8 +212,8 @@ for (group in levels(sites$group_type)) {
 
 ### Save ###
 
-ggsave(here("outputs", "figures", "figure_2_nmds_600dpi_16.5x16cm.tiff"),
-       dpi = 800, width = 16.5, height = 16, units = "cm")
+ggsave(here("outputs", "figures", "figure_2_nmds_500dpi_16.5x16cm.tiff"),
+       dpi = 500, width = 16.5, height = 16, units = "cm")
 graph_a + theme(legend.position = "right")
-ggsave(here("outputs", "figures", "figure_2_nmds_600dpi_18x13cm.tiff"),
-       dpi = 600, width = 18, height = 13, units = "cm")
+ggsave(here("outputs", "figures", "figure_2_nmds_500dpi_18x13cm.tiff"),
+       dpi = 500, width = 18, height = 13, units = "cm")

### 2023-08-03 R/show_figure_3a_recovery.R

@@ -123,8 +123,8 @@ get_variables(m2)
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_3a_recovery_800dpi_24x8cm.tiff"),
-  dpi = 800, width = 24, height = 8, units = "cm"
+  here("outputs", "figures", "figure_3a_recovery_600dpi_24x8cm.tiff"),
+  dpi = 600, width = 24, height = 8, units = "cm"
 )
 
 (graph_a <- p1 +

### 2023-08-03 R/show_figure_3b_persistence.R

@@ -124,8 +124,8 @@ get_variables(m2)
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_3b_persistence_800dpi_24x8cm.tiff"),
-  dpi = 800, width = 24, height = 8, units = "cm"
+  here("outputs", "figures", "figure_3b_persistence_600dpi_24x8cm.tiff"),
+  dpi = 600, width = 24, height = 8, units = "cm"
 )
 
 (graph_b <- p1 +

### 2023-08-03 R/show_figure_3c_fcs.R

@@ -124,8 +124,8 @@ get_variables(m2)
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_3c_fcs_800dpi_24x8cm2.tiff"),
-  dpi = 800, width = 24, height = 8, units = "cm"
+  here("outputs", "figures", "figure_3c_fcs_600dpi_24x8cm2.tiff"),
+  dpi = 600, width = 24, height = 8, units = "cm"
 )
 
 (graph_c <- p1 +

### 2023-08-03 R/show_figure_4_interaction.R

@@ -42,6 +42,6 @@ sd <- 0.25475
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_4_600dpi_16.5x20cm.tiff"),
-  dpi = 600, width = 16.5, height = 20, units = "cm"
+  here("outputs", "figures", "figure_4_300dpi_16.5x20cm.tiff"),
+  dpi = 300, width = 16.5, height = 20, units = "cm"
 )

### 2023-08-03 R/show_figure_4a_recovery.R

@@ -139,14 +139,14 @@ sd <- sum(as.numeric(as.character(
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_4a_recovery_800dpi_24x8cm.tiff"),
-  dpi = 800, width = 24, height = 8, units = "cm"
+  here("outputs", "figures", "figure_4a_recovery_600dpi_24x8cm.tiff"),
+  dpi = 600, width = 24, height = 8, units = "cm"
   )
 
 p1 + theme(legend.position = "bottom")
 ggsave(
-  here("outputs", "figures", "figure_4a_recovery_800dpi_16.5x8cm.tiff"),
-  dpi = 800, width = 16.5, height = 8, units = "cm"
+  here("outputs", "figures", "figure_4a_recovery_600dpi_16.5x8cm.tiff"),
+  dpi = 600, width = 16.5, height = 8, units = "cm"
   )
 
 (graph_a <- p1 +

### 2023-08-03 R/show_figure_4b_persistence.R

@@ -140,15 +140,15 @@ theme_mb <- function() {
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_4b_persistence_800dpi_24x8cm.tiff"),
-  dpi = 800, width = 24, height = 8, units = "cm"
+  here("outputs", "figures", "figure_4b_persistence_600dpi_24x8cm.tiff"),
+  dpi = 600, width = 24, height = 8, units = "cm"
   )
 
 p1 + theme(legend.position = "bottom") +
   scale_y_continuous(limits = c(0, 1.02), breaks = seq(-100, 400, .25))
 ggsave(
-  here("outputs", "figures", "figure_4b_persistence_800dpi_16.5x8cm.tiff"),
-  dpi = 800, width = 16.5, height = 8, units = "cm"
+  here("outputs", "figures", "figure_4b_persistence_600dpi_16.5x8cm.tiff"),
+  dpi = 600, width = 16.5, height = 8, units = "cm"
   )
 
 (graph_b <- p1 +

### 2023-08-03 R/show_figure_4c_fcs.R

@@ -134,14 +134,14 @@ theme_mb <- function() {
 ### Save ###
 
 ggsave(
-  here("outputs", "figures", "figure_4c_fcs_800dpi_24x8cm.tiff"),
-  dpi = 800, width = 24, height = 8, units = "cm"
+  here("outputs", "figures", "figure_4c_fcs_600dpi_24x8cm.tiff"),
+  dpi = 600, width = 24, height = 8, units = "cm"
   )
 
 p1 + theme(legend.position = "bottom")
 ggsave(
-  here("outputs", "figures", "figure_4c_fcs_800dpi_16.5x8cm.tiff"),
-  dpi = 800, width = 16.5, height = 8, units = "cm"
+  here("outputs", "figures", "figure_4c_fcs_600dpi_16.5x8cm.tiff"),
+  dpi = 600, width = 16.5, height = 8, units = "cm"
   )
 
 (graph_c <- p1 +

### 2023-08-03 manuscript.Rmd
Reduce dpi of figure 2

@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_2_nmds_500dpi_16.5x16cm.tiff")
+  here::here("outputs", "figures", "figure_2_nmds_300dpi_16.5x16cm.tiff")
   )
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_4_500dpi_16.5x20cm.tiff")
+  here::here("outputs", "figures", "figure_4_300dpi_16.5x20cm.tiff")
   )

### 2023-08-03 R/show_figure_2_nmds.R

@@ -212,8 +212,8 @@ for (group in levels(sites$group_type)) {
 
 ### Save ###
 
-ggsave(here("outputs", "figures", "figure_2_nmds_500dpi_16.5x16cm.tiff"),
-       dpi = 500, width = 16.5, height = 16, units = "cm")
+ggsave(here("outputs", "figures", "figure_2_nmds_300dpi_16.5x16cm.tiff"),
+       dpi = 300, width = 16.5, height = 16, units = "cm")
 graph_a + theme(legend.position = "right")
-ggsave(here("outputs", "figures", "figure_2_nmds_500dpi_18x13cm.tiff"),
-       dpi = 500, width = 18, height = 13, units = "cm")
+ggsave(here("outputs", "figures", "figure_2_nmds_300dpi_18x13cm.tiff"),
+       dpi = 300, width = 18, height = 13, units = "cm")

### 2023-08-09 manuscript.Rmd
Add German abstract, conflict of interests

@@
 Overall, the sown vegetation developed in the desired direction, but a recovery debt remained after four years, and some plots still showed similarities to negative references from ruderal sites.
-In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry-grassland mixtures.
+In north exposition, hay meadow-seed mixtures developed closer to their reference communities than dry-grassland mixtures to their reference.
 4.  In south exposition, the sown communities established poorly which might be due to a severe drought during establishment. This initial negative effect remained over the entire observation period.
-5.  Sand admixture had a slightly positive effect on target variables, while the tested substrate depths, seed densities and mixture types had no effects on species persistence or FCS.
+5.  Sand admixture had a slightly positive effect on target variables, while the tested substrate depths, seed densities and seed mixture types had no effects on species persistence or FCS.
 6.
-Synthesis and applications: Site-adapted seed mixtures make restoration more effective, while applying several seed--substrate combinations might foster beta diversity.
+*Synthesis and applications:* Site-adapted seed mixtures make restoration more effective, while applying several seed--substrate combinations might foster beta diversity.
 Furthermore, additional management efforts are recommended, as they might be necessary to reduce the recovery debt, as well as re-sowing after unfavourable conditions.
+
+\clearpage
+
+\newpage
+
+# Zusammenfassung
+
+1.
+Die Aussaat ist eine bewährte Renaturierungstechnik da die Samenausbreitung in der Landschaft häufig eingeschränkt ist.
+Saatgutmischungen, die an ihr Substrat oder Mikroklima angepasst sind, sind am effektivsten, um Pflanzengesellschaften erfolgreich zu etablieren.
+Dies ist besonders wichtig, wenn die etablierte Vegetation Infrastrukturobjekte wie Straßenränder und Deiche schützen soll.
+In diesem Fall wird eine verbesserte Saatgut-Substrat-Kombination die Hangstabilität sichern, die Wiederherstellung effektiver machen und artenreiches Grünland hervorbringen.
+
+2.
+Ein faktorieller Feldversuch widmete sich diesem Thema auf einem Deich an der Donau in Süddeutschland in den Jahren 2018--2021.
+Auf 288 Parzellen untersucthen wir drei Sandbeimischungen, zwei Substrattiefen, zwei Saatgutdichten und zwei Saatmischungstypen (Glatthaferwiese, Halbtrockenrasen) in Nord- und Südexposition und ermittelten den Erfolg der Renaturierung, indem wir den Sukzessionsabstand zu Referenzflächen, die Persistenz der angesäten Arten und den günstigen Erhaltungszustand (*Favourable Conservation Status*, FCS) der Zielarten berechneten.
+
+3.
+Insgesamt entwickelte sich die eingesäte Vegetation in die gewünschte Richtung, doch blieb nach vier Jahren eine 'Renaturierungsschuld' bestehen, und einige Parzellen wiesen immer noch Ähnlichkeiten mit negativen Referenzen von Ruderalstandorten auf.
+In der Nordexposition entwickelten sich die Glatthaferwiesen-Saatmischungen näher an den ihre Referenz als die Trockenrasenmischungen.
+
+4.
+In der Südexposition etablierten sich die ausgesäten Gemeinschaften schlecht, was auf eine starke Trockenheit während der Etablierung zurückzuführen sein könnte.
+Dieser anfängliche negative Effekt blieb über den gesamten Beobachtungszeitraum bestehen.
+
+5.
+Die Sandbeimischung wirkte sich leicht positiv auf die Zielvariablen aus, während die untersuchten Substrattiefen, Saatdichten und Saatmischungsarten keine Auswirkungen auf die Persistenz der Arten oder den FCS hatten.
+
+6.
+*Synthese und Anwendungen:* Standortangepasste Saatmischungen machen die Renaturierung effektiver, während die Anwendung verschiedener Saat-Substrat-Kombinationen die Beta-Diversität fördern könnte.
+Darüber hinaus werden zusätzliche Bewirtschaftungsmaßnahmen empfohlen, da sie notwendig sein könnten, um die 'Renaturierungsschuld' zu verringern, sowie die Wiederaussaat nach ungünstigen Bedingungen.
 
@@
 The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and the Londo scale was used [@londo1976].
+No special permits were necessary.
 The establishment rates of species were recorded in Appendix A4.
@@
 
-# Author contribution {.unnumbered}
+# Conflict of interest statement
 
-JH and JK designed the experiment. JH did the surveys in the years 2018--2020, and MB in 2019 and 2021. MB did the analyses and wrote the manuscript. JK and JH critically revised the manuscript.
+The authors declare no conflict of interest.
 
-# Open research {#sec-open-research .unnumbered}
+# Authors' contribution {.unnumbered}
 
-Data and code are stored on Zenodo [@bauer2023experiment]. Model evaluation is stored on GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
+Jakob Huber and Johannes Kollmann conceived the ideas and designed the experiment.
+Jakob Huber did the surveys in the years 2018--2020, and Markus Bauer in 2019 and 2021.
+Markus Bauer did the analyses and wrote the manuscript.
+Johannes Kollmann and Jakob Huber critically revised the manuscript and gave final approval for publication.
+
+# Data availability statement {#sec-open-research .unnumbered}
+
+'Data available via the Dryad Digital Repository
+
+Data and code available via Zenodo repository https://doi.org/10.5281/zenodo.7713396 [@bauer2023experiment].
+Model evaluation can also be directly accessed via GitHub: <https://github.com/markus1bauer/2023_danube_dike_experiment/tree/main/markdown>
 
@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm_modified.tiff")
+  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm.tiff")
   )

### 2023-08-09 manuscript.Rmd
Update manuscript.Rmd

@@
 knitr::include_graphics(
-  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm.tiff")
+  here::here("outputs", "figures", "figure_3_300dpi_16.5x5cm.tiff")
   )
